### 2020-11-17 index.Rmd
Hello world

---
title: "Everest Bio"
description: |
  Projet de recherche CREIDD et ERPI
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

### 2020-11-17 index.Rmd
version un peu plus complete

@@
 ---
-title: "Everest Bio"
+title: "Everest Bio)"
 description: |
+  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
   Projet de recherche CREIDD et ERPI
+
+author:
+  - first_name: "Mauricio"
+    last_name: "Camargo"
+    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    orcid_id: 0000-0003-3867-2438 
+  - first_name: "Nadège"
+    last_name: "Troussier"
+    url: https://recherche.utt.fr/icd-directory/nadege-troussier
+    affiliation: CREIDD
+    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
+    orcid_id: 0000-0001-6707-0300
+  - first_name: "Fabio"
+    last_name: "Cruz"
+    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    orcid_id: 0000-0001-8529-5327
+  - first_name: "Fedoua"
+    last_name: "Kasmi"
+    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    orcid_id: 0000-0001-5159-0264
+  - first_name: "Pavlo"
+    last_name: "Santander"
+    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    #orcid_id: 0000-0001-6328-1338
+bibliography: library.bib
+link-citations: yes
+linkcolor: blue 
 site: distill::distill_website
@@
 ```
+
+# Positionnement stratégique du projet
+
+Dans un contexte de consommation mondiale croissante et de pression accrue sur les ressources, qui plus est, celles dédiées à la survie de l’espèce humaine, il est urgent de dissocier la croissance économique de l'utilisation de ces dernières.
+Ceci pourrait notamment permettre d'accroître la résistance de l'Europe aux incertitudes liées à l'approvisionnement en matières premières et à la sécurité des chaînes de valeur, comme c'est le cas actuellement avec la crise sanitaire [@Sanye-Mengual2019].
+
+Il est donc temps de rendre nos filières industrielles plus résilientes et adaptées aux nouvelles conditions imposées par la planète.
+Pour soutenir une transition industrielle, dont celle vers une bioéconomie répondant au concept d’économie circulaire, ce projet cherche à développer une méthodologie permettant d’évaluer les services écosystémiques, et donc les externalités des organisations industrielles émergentes.
+Par la mise en commun de compétences du ICD/CREIDD^[Institut Charles Delaunay/Centre de recherches et d’études interdisciplinaires sur le développement durable de l'UTT (Université technologique de Troyes)]   et de l’ERPI^[  Equipe de Recherche sur les Processus Innovatifs de l’UL (Université de Lorraine)], cette méthodologie, basée sur un couplage analyse du cycle de vie et modélisation par dynamique de systèmes, cherche à faciliter l’évaluation d’un projet industriel dès sa phase amont en considérant ses potentiels impacts positifs et/ou négatifs sur son territoire.
+L’approche proposée sera testée sur le cas du recyclage, l’un des piliers de l’économie circulaire, et en particulier sur la mise en place d’un démonstrateur de type « smart-grid du recyclage » du plastique en circuit court.
+Ce projet permet également de soutenir les acteurs publics et privés par le développement d’outils d’aide à la décision supportés par les technologies numériques tel que défini dans l’axe efficacité énergétique de l’annexe 1 du texte d’appel à projet.
+
+# Contenu scientifique
+
+Le concept d'économie circulaire (EC) est un élément central pour promouvoir un modèle durable, régénérateur et inclusif qui peut aider de manière significative nos économies à se réconcilier avec les limites et les frontières de notre planète en restaurant les systèmes naturels, en réduisant les émissions de GES (gaz à effet de serre), et en minimisant la perte de capital naturel et de biodiversité.
+Le fonctionnement en circuit court est l’un des piliers pour rendre les opérations d’une filière plus efficaces et rationnelles, tout en créant de la valeur locale [@Capasso2019].
+Cependant son opérationnalisation nécessite des prises de décision qui s’avèrent difficiles, car elles challengent le paradigme actuel des activités industrielles, centrées principalement sur l’évaluation technico-économiques et, encore trop peu et trop récemment sur des considérations environnementales.
+En effet, la vision traditionnelle reste prégnante bien que limitée car elle ne considère pas systématiquement l’ensemble des impacts d’une activité sur les écosystèmes.
+
+Comme démontré par les travaux réalisés depuis 2001 par le CREIDD sur les thématiques de l’écologie industrielle, l’éco-conception, l’analyse de cycle de vie et l’évaluation des risques environnementaux, la compréhension des mécanismes de transition industrielle en incluant des dimensions de durabilité, sont fondamentaux.
+De même, ils ont montré l’importance d’une vision intégrée pour la conception des systèmes industriels-territoires [@Vadoudi2014; @Vadoudi2015; @Vadoudi2017; @Bruel2014; @Bruel2016; @Bruel2018].
+Plus récemment, des travaux ont montré que le rapprochement de l'écologie industrielle et de l’économie écologique peut être un moyen d’aller au-delà de l’étude physique des flux de matière et d’énergie [@Bruel2019; @Bruel2016].
+En particulier dans ce projet on s’intéressera à la quantification et prise en compte des services rendus par une organisation industrielle à son territoire (espace naturel, humain et social).
+Ceci soulève la question des externalités environnementales et plus particulièrement des services écosystémiques rendus.
+
+Les services écosystémiques ont été définis par [@DeGroot2002] comme la capacité des processus et des constituants de la nature à fournir des biens et services qui répondent aux besoins humains, directement ou indirectement.
+Ces biens et services sont généralement associés à des fonctions de régulation, des fonctions d'habitat, des fonctions de production et des fonctions d'information.
+Plus précisément, dans le domaine de l’environnement, les externalités négatives constituent des situations de pollutions, d’altération des ressources naturelles, de destruction de paysages, de pertes de biodiversité et d’autres nuisances environnementales qui affectent le bien-être d’individus sans que cette perte ne soit compensée par un mécanisme marchand.
+La plupart du temps, les externalités environnementales sont des coûts additionnels pris en charge par les autorités publiques (ex : gouvernement, collectivités territoriales) et les citoyens.
+Elles se matérialisent notamment par la pollution atmosphérique, les nuisances sonores, les émissions de gaz à effet de serre, la pollution des eaux et des sols, mais également par les atteintes à la biodiversité.
+
+Des études soulignent que les décideurs, les développeurs de produits, les dirigeants d’entreprises, les administrateurs publics ou les consommateurs prendraient des décisions différentes s’ils avaient l’information leur permettant d’évaluer plus largement les conséquences environnementales de leurs décisions [@VandenBergh2012; @Hond2000; @Bithas2011; @ORourke1996] ou s’ils devaient également payer les prix reflétant la valeur monétaire des externalités de l’utilisation des matières et de l’énergie.
+Elles concluent aussi que, fondamentalement, les problèmes environnementaux sont causés par les défaillances de la réglementation et du marché qui peuvent être corrigées si les décideurs ont la bonne information et s’ils sont exposés aux bons prix.
+
+De plus, les changements environnementaux sont liés à des effets de deux natures: leviers indirects et pressions directes.
+Par leviers indirects, le Millenium Ecosystem Assessment (MEA) [@MEA2005] adresse les changements démographiques, économiques, sociopolitiques, scientifiques et technologiques.
+Quant aux pressions directes, elles incluent la conversion des sols, la surexploitation des ressources naturelles, l’apport excessif de nutriments, les maladies, les invasions d’espèces et le changement climatique.
+Ces pressions affectent les écosystèmes de différentes manières selon les contextes et agissent à travers différentes échelles organisationnelles, temporelles et spatiales.
+Les systèmes industriels sont fortement impliqués et responsables des pressions qu’ils exercent sur la biodiversité et les services écosystémiques.
+Le MEA a identifié six défis majeurs concernant directement les impacts des activités industrielles :la rareté de l’eau douce, le changement climatique, les changements d’habitat, les espèces invasives, la surexploitation des océans et la surcharge de nutriments.
+Ces derniers peuvent conduire à des dépendances qui varient en fonction des secteurs d’activités et au sein même d’un même secteur, selon la technologie employée et du contexte de l’activité de production ou de consommation <span style="color:blue">*</span>.
+
+<aside>
+
+<span style="color:blue">*</span>Les systèmes industriels impactent de façon directe l’écosystème, notamment en occupant les sols avec leurs équipements de production et par la pollution résultant des processus de production.
+Ils impactent aussi de manière indirecte par l’intermédiaire de leurs fournisseurs de matières premières ou de produits semi-finis, ainsi que par les usages et fin de vie engendrés.
+Même si certaines entreprises considèrent ces liens comme des contraintes, les prendre en compte peut permettre de mieux appréhender les risques et d’identifier des opportunités
+
+</aside>
+
+Par ailleurs, la prise en compte des services écosystémiques peut présenter de nouvelles opportunités pour les entreprises, comme favoriser l’émergence de nouvelles technologies et de nouveaux produits permettant de réduire la dégradation, de restaurer les écosystèmes ou d’augmenter l’efficacité dans l’utilisation des services écosystémiques.
+Cela peut aussi permettre l’obtention de nouvelles parts de marché grâce au lancement d’un nouveau produit ou service à faible impact sur les écosystèmes, donc disposant d’une éco-labellisation.
+Au niveau de la réglementation, on peut noter l’engagement du gouvernement, concrétisé notamment par la Stratégie Nationale pour la Biodiversité (SNB), pour développer des politiques favorables à la conservation des écosystèmes ou des incitations visant à protéger ou restaurer des écosystèmes qui fournissent des services.
+L’intégration de cette relation impacts/dépendances au niveau des systèmes d’information permettrait d’avoir une autre vision des entreprises au regard de leurs activités industrielles.
+Cependant, elle est complexe à mettre en œuvre et spécifique à chaque secteur.
+Aujourd’hui, la valeur des services écosystémiques est peu prise en compte voire pas reconnue par et dans notre système économique, que ce soit aux yeux des décideurs privés et publics ou des consommateurs.
+La perte de valeur causée par l’ensemble des pressions qui s’exercent sur les services écosystémiques est invisible, ce qui ne permet pas d’influencer les décideurs et de peser dans les arbitrages au niveau des processus de décisions.
+L’évaluation de la relation impacts/dépendances des entreprises vis-à-vis des services écosystémiques s’avère donc être un réel défi méthodologique.
+
+Depuis 2013, l’ERPI développe le concept de Green Fablab  pour contribuer à une meilleure prise en compte des aspects environnementaux en intégrant les communautés d’utilisateurs présentes dans ces espaces de conception.
+
+<aside> [<img src="http://lf2l.fr/assets/images/3-projects/gf/Logo-GF.png" alt="Gren Fablab" style="width:100px">](http://lf2l.fr/projects/green-fablab/) </aside>
+
+Un premier démonstrateur a été conçu pour traiter le problème du recyclage de matières plastiques issues des déchets domestiques, adoptant une approche de type recyclage distribué en circuit court et en petites quantités ou « smart-grid du recyclage » [@Santander2020].
+Plus précisément, l'enjeux était de développer une manière plus efficace de recyclage mécanique des thermoplastiques, qui sont généralement disponibles en grandes quantités au niveau local, tels que les PS, PP, ABS, PET, car le processus de recyclage traditionnel actuel s'est avéré inefficace sur le plan économique et environnemental.
+En effet, sous le paradigme d’économies d’échelle le recyclage est réalisé de manière centralisée en acheminant les déchets vers des unités de production capables de traiter grands volumes pour minimiser le coût.
+Or, la complexité de tri des multi-matériaux, la faible masse volumique qui rend le transport peu rentable et la quantité d’émissions générées par le processus de collecte expliquent cette inefficacité.
+Pour information en France le taux de recyclage de plastique est d’aprox.
+15%.
+
+Les travaux iniciaux, ont démontré dans un premier temps, la faisabilité technique de cette approche qui intègre plusieurs technologies (imprimantes 3D, extrudeuses et dispositifs de mesure notamment) pour fabriquer les fils supports à l’impression 3D [@CruzSanchez2017], conduisant plus récemment à un recyclage par extrusion directe [@Arthur2020].
+Pour assurer la faisabilité économique, le système de fabrication se doit d’être peu cher, facile d’utilisation et adapté à la production de petites quantités.
+Pour cette raison, dès le début de leur réflexion, les chercheurs ont fait le choix d’utiliser des technologies open source [@CruzSanchez2014].
+Une approche open source permet aussi de donner plus facilement accès, et ainsi diffuser plus largement des connaissances en proposant de la formation et du service autour des logiciels, valorisant le savoir-faire développé.
+Dans un second temps, un état de l’art approfondi a été réalisé afin de déterminer l’état de maturité de chacune des étapes constituant une approche de recyclage en circuit court [@CruzSanchez2020].
+
+A ce stade des recherches, il est clair que les services écosystémiques et les externalités (positives et négatives) de cette filière de recyclage innovante n’ont pas encore été évalués.
+Par exemple, nous pouvons citer les effets des quantités de plastiques évités sur l’écosystème et la biodiversité, ou encore ceux des additifs chimiques (tels que les plastifiants) sur la santé humaine et animal.
+Dans ce projet il s’agit donc à la fois de construire une grille d’analyse des impacts des systèmes industriels sur leur territoire à travers l’évaluation des services écosystémiques générique et appliquée au Green Fablab.
+Ainsi, le projet permettra une meilleure prise en compte des externalités environnementales (écologiques et sociales) dans les processus de décision en phase amont de conception de filières industrielles.
+Du fait des compétences complémentaires des deux équipes, nous chercherons à mieux comprendre sur le Green Fablab quelles sont les externalités environnementales et les services écosystémiques rendus à une échelle locale au moyen d’une démarche d’Analyse de cycle de vie couplée à une modélisation en dynamique des systèmes.
+Cet exemple permettra de développer une méthode de collecte et interprétation des données et un outil d’évaluation des services écosystémiques associés.
+
+# Objectif
+
+Développer une méthodologie générique permettant d’évaluer les services écosystémiques rendus par des activités industrielles fonctionnant en circuit court afin d’améliorer la prise de décisions des acteurs industriels et du secteur public.
+Validation sur le cas d’une filière de recyclage du plastique en circuit court.
+
+# Méthodologie
+
+L’approche méthodologique comporte les étapes suivantes :
+
+1.	Proposer et valider des indicateurs à utiliser pour l’évaluation des services écosystémiques d’une activité de production, et pour un fonctionnement en circuit court.
+2.	Proposer un protocole de récolte et de structuration des données et information nécessaires pour évaluer un cas particulier, instrumenté dans un outil numérique pour le traitement des données et l’évaluation des impacts.
+3.	Développer un modèle d'évaluation des conditions opérationnelles permettant de construire des scénarios d’évaluation d’une activité ou filière industrielle dans un contexte donné.
+4.	Appliquer le modèle développé au cas du recyclage en circuit court des matières plastiques. Validation et retour d’expérience pour la prise en compte des conditions spécifiques du contexte local.
+
+# Résultats attendus
+
+- 	Cadre d’indicateurs d’évaluation des services écosystémiques pour le recyclage en circuit court permettant d’évaluer l’impact local (écologique et social) des évolutions des systèmes de production.
+- 	Modèle d’évaluation des impacts sur l’écosystème d’une stratégie en circuit court par rapport à un mode de fonctionnement traditionnel.
+
+-->	Ces deux premiers éléments seront formalisés dans un outil numérique d’évaluation des impacts environnementaux, si possible open source.
+
+- 	Application pilote du modèle au cas du recyclage de matière plastique en mode distribué au cas du Green Fablab.
+- 	Recommandations pour l’évaluation d’externalités dans le contexte de mise en place de filières industrielles en mode circuit court.
+
+-->	Ces deux derniers éléments feront l’objet d’un rapport d’analyse des impacts du Green Fablab et des hypothèses de généralisation que l’on peut en tirer sur l’ntérêt de la mise en place de filières de production en circuits courts.
+
+#	Détails du programme de recherche
+
+## Rôles des partenaires:
+
+ERPI apportera sa compétence sur la formalisation des services écosystémiques rendus par les systèmes de production sur la base d’une modélisation en dynamique de systèmes et le démonstrateur.
+ICD/CREIDD apportera sa compétence sur l’évaluation des impacts écologiques et sociaux via la monétarisation des services écosystémiques.
+Les deux partenaires collaboreront autour du même cas d’étude qui permettra de déployer de façon conjointe les méthodologies déjà mises au point dans le cadre de travaux de thèse dans chacun des laboratoires pour proposer un modèle d’analyse des impacts locaux (écologiques et sociaux) des transformations des systèmes de production.
+
+##	Déroulement et phasage des travaux. Le projet se déroulera en deux phases :
+
+```{r layout="l-page",  fig.cap="Planning"}
+knitr::include_graphics("figures/Planning.jpg")
+```
+
+### Phase 1 (6 mois postdoc) à Troyes :
+
+appréhender les deux propositions méthodologiques des laboratoires; proposer protocole de collecte et analyse des données; proposer le modèle d’évaluation en dynamique des systèmes (modélisation agent permettant de modéliser un système complexe et de simuler son comportement en tenant compte des interactions et rétroactions au sein du système).
+
+### Phase 2 (6 mois postdoc) à Nancy :
+
+déployer la méthodologie sur le cas d’étude : collecte de données sur le Green Fablab et au sein de son territoire de développement, évaluations des services écosystémiques liés çà l’activité du Green Fablab, préconisations sur l’analyse des intérêts et limites de la mise en place des circuits industriels courts.
+
+## Livrables et attendus
+
+1.	Un article dans un journal international indexé
+2.	Participation à une conférence internationale
+3.	Un modèle opérationnel avec une maquette d’outil logiciel d’évaluation des impacts locaux
+4.	Rapport final sur l’évaluation du GreenFablab et les généralisations possibles pour les circuits industriels courts.
+
+#	Marchés visés et perspectives de transférabilité
+
+Les secteurs industriels et agro industriels cherchant la mise en place de stratégies centrées sur le circuit court sont particulièrement concernés notamment dans cette phase de transition post-crise qui a montré les limites des approches traditionnelles.
+
+De même, les acteurs publics sont aujourd’hui à l'affût d’outils permettant à la fois de mieux évaluer les impacts des systèmes de production sur leur territoire et pouvoir de fait ajuster l’allocation des ressources en connaissance globale des impacts et dépendances engendrés sur l’écosystème local.
+
+La mise en commun des compétences de l’ERPI et du CREIDD/ICD permettent donc de coupler une approche de modélisation des systèmes industriels en dynamique des systèmes avec une méthode d’évaluation des impacts environnementaux par la monétarisation des services rendus pour fournir une méthode d’évaluation des impacts locaux des circuits courts, tenant compte des fortes interactions liées aux bouclages de flux au sein du territoire.
+Cette méthode et cet outil seront adapté à l’évaluation des impacts locaux de toute activité industrielle et pourront être valorisés par de la mise à disposition de savoir-faire (de modélisation de l’activité industrielle avec l’ERPI, de développement d’indicateurs d’évaluation des services écosystémiques spécifiques avec le CREIDD).

### 2020-11-17 index.Rmd
adding ppt

@@
 ---
-title: "Everest Bio)"
+title: "Everest Bio"
 description: |
@@
 
+require(tidyverse)
+require(xaringan)
+require(xaringanExtra)
 # Learn more about creating websites with Distill at:
@@
 Ce projet permet également de soutenir les acteurs publics et privés par le développement d’outils d’aide à la décision supportés par les technologies numériques tel que défini dans l’axe efficacité énergétique de l’annexe 1 du texte d’appel à projet.
+
+# Presentation
+
+```{r embed-xaringan, echo=FALSE}
+
+xaringanExtra::embed_xaringan(url = "slides/index.html",
+                              ratio = "16:9",
+                              max_width = 600)
+
+#xaringanExtra::use_share_again(url = "slides/index.html")
+```
 

### 2020-11-17 slides/index.Rmd
adding ppt

---
title: "Everest Bio"
subtitle: |
  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
  Projet de recherche CREIDD et ERPI
author: "Fabio Xie"
institute: "CREIDD, ERPI"
date: "2020/11/18 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

## The problem: Plastic waste

.pull-left[ 
- US recycled less than 9% of its plastic waste.
- EU, recycled about 30%. However, this number is what is collected, not from what is in circulation*. 
- China’s ban on plastic trash
- Plastic trash could top 13 billion tons by 2050
- Economics of plastic recycling historically have been challenging
- Little financial incentive to encourage consumers to recycle their own plastic waste

## We barely recycle plastic!!.. 
]

.pull-right[ 
![Plastic waste](https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80)
]

.footnote[
*Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018. Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling. Waste Manag. Res. 36, 445–453
]

---

# Challengue

The development of sustainable industrial supply chains

.pull-left[
.small[

- Les seuls critères technico-économiques ne permettent pas (plus) d’avoir une prise de décision éclairée

- Besoin d’évaluer les filières de manière différente, notamment les impacts réels sur les écosystèmes

- Une vision plus holistique est nécessaire pour évaluer la faisabilité de ces nouvelles filières
]
 ]

---

### 2020-11-17 docs/slides/index.Rmd
version complete

---
title: "Everest Bio"
subtitle: |
  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
  Projet de recherche CREIDD et ERPI
author: "Fabio Cruz / Mauricio Camargo"
institute: "CREIDD, ERPI"
date: "2020/11/18 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "assets/Fabio.css", "assets/Fabio-fonts.css"]
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "assets/macros.js"
---

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

## The problem: Plastic waste

.pull-left[ 
- US recycled less than 9% of its plastic waste.
- EU, recycled about 30%. However, this number is what is collected, not from what is in circulation*. 
- China’s ban on plastic trash
- Plastic trash could top 13 billion tons by 2050
- Economics of plastic recycling historically have been challenging
- Little financial incentive to encourage consumers to recycle their own plastic waste

## We barely recycle plastic!!.. 
]

.pull-right[ 
![Plastic waste](https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80)
]

.footnote[
*Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018. Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling. Waste Manag. Res. 36, 445–453
]

---

# Challengue

The development of sustainable industrial supply chains

.left-column[
.small[

- Only technico-economic criteria alone do not (no longer) enables a informed decision making

- Need to assess value chains in a different way, including actual impacts on ecosystems

- A more holistic vision is needed to assess the feasibility of these new sectors.
]
 ]

.right-column[ 
.polaroid[ ![](figures/Recycling.png) ]
]

---

# Towards a local distributed recycling approach

.pull-left[
- Local closed loop
- AM adds value
- Small quantities 
- Reduction of landfilling
- Minimize the use of virgin materials

![](Figures/Green-fablab-1.jpg)

]

.pull-right[

![](http://lf2l.fr/assets/images/3-projects/gf/Logo-GF.png)
http://lf2l.fr/projects/green-fablab

.center[![:scale 80%](Figures/Green-fablab-circuit.png)]

]

---

## Distributed recycling via additive manufacturing (DRAM)
Technical system

.center[![:scale 75%](Figures/Green-fablab-0.png)]

.footnote[
Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020. Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy. J. Clean. Prod. 264, 121602. https://doi.org/10.1016/j.jclepro.2020.121602 
]

---

## Distributed recycling via additive manufacturing (DRAM)
Technical system --> Global system

.center[![:scale 75%](Figures/DRAM-05.png)]

---

## Distributed recycling via additive manufacturing (DRAM)

Taking into account the environment and their ecosystem services (ES).

.pull-left[
![:scale 90%](Figures/Eco-Services-00.jpg)
]

--

.pull-right[
![](Figures/Eco-Services-01.png)

- How the future recycling chain could be including the environment?
]

.footnote[
Bruel, A., Kronenberg, J., Troussier, N., & Guillaume, B. (2019). Linking industrial ecology and ecological economics: A theoretical and empirical foundation for the circular economy. Journal of Industrial Ecology, 23(1), 12-21.
]

---

# Main Goals

- To develop a generic methodology to assess the ecosystem services rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors.

- Validation on the case of a short-circuit plastic recycling chain.

---

# Methods

- In line with the thesis work previously carried out by the two teams, development of a coupled Systems Dynamics and LCA approach.

- Application on a case study, the GreenFablab, by evaluating its environmental impact when setting up a short plastic recycling circuit.

.center[ ![:scale 80%](Figures/Goals.png)]

---

# Distributed recycling via additive manufacturing (DRAM)

Global system

.pull-left[
![](Figures/DRAM-07.png)
]

.pull-right[
- Establish and evaluate scenarios in a systemic and dynamic way

- Evaluate the influences of the main operating variables on the system

- Taking into account the priorities of the multiple stakeholders

- Facilitate your decision making public-private actors
]
.footnote[
Santander, P., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., 2020. Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach. Resour. Conserv. Recycl. 154, 104531. https://doi.org/10.1016/j.resconrec.2019.104531 
]

---

# Delivrables

1. An article in an indexed international journal
2. Participation in an international conference 
3. An operational model with a model of a software tool for assessing local impacts
4. Final report on the evaluation of Green Fablab and possible generalisations for short industrial circuits.

---

# Valorisations

- Method and prototype of a tool for the evaluation of local impacts of circular production systems

---
class: middle, center

Thanks !

![:scale 70%](Figures/DRAM-bd.png)

### 2020-11-17 index.Rmd
version complete

@@
 bibliography: library.bib
+csl: journal-of-cleaner-production.csl
 link-citations: yes
@@
 
-xaringanExtra::embed_xaringan(url = "slides/index.html",
-                              ratio = "16:9",
-                              max_width = 600)
+embed_xaringan(url = "slides/index.html", ratio = "16:9")
 
-#xaringanExtra::use_share_again(url = "slides/index.html")
 ```
@@
 Comme démontré par les travaux réalisés depuis 2001 par le CREIDD sur les thématiques de l’écologie industrielle, l’éco-conception, l’analyse de cycle de vie et l’évaluation des risques environnementaux, la compréhension des mécanismes de transition industrielle en incluant des dimensions de durabilité, sont fondamentaux.
-De même, ils ont montré l’importance d’une vision intégrée pour la conception des systèmes industriels-territoires [@Vadoudi2014; @Vadoudi2015; @Vadoudi2017; @Bruel2014; @Bruel2016; @Bruel2018].
-Plus récemment, des travaux ont montré que le rapprochement de l'écologie industrielle et de l’économie écologique peut être un moyen d’aller au-delà de l’étude physique des flux de matière et d’énergie [@Bruel2019; @Bruel2016].
+De même, ils ont montré l’importance d’une vision intégrée pour la conception des systèmes industriels-territoires [@Vadoudi2014; @Vadoudi2015; @Troussier2017; @Bruel2014; @Bruel2016; @Bruel2018].
+Plus récemment, des travaux ont montré que le rapprochement de l'écologie industrielle et de l’économie écologique peut être un moyen d’aller au-delà de l’étude physique des flux de matière et d’énergie [@Bruel2016].
 En particulier dans ce projet on s’intéressera à la quantification et prise en compte des services rendus par une organisation industrielle à son territoire (espace naturel, humain et social).

### 2020-11-17 index.Rmd
adding hakim

@@
 author:
+  - first_name: "Nadège"
+    last_name: "Troussier"
+    url: https://recherche.utt.fr/icd-directory/nadege-troussier
+    affiliation: CREIDD
+    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
+    orcid_id: 0000-0001-6707-0300
   - first_name: "Mauricio"
@@
     orcid_id: 0000-0003-3867-2438 
-  - first_name: "Nadège"
-    last_name: "Troussier"
-    url: https://recherche.utt.fr/icd-directory/nadege-troussier
-    affiliation: CREIDD
-    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
-    orcid_id: 0000-0001-6707-0300
+  - first_name: "Hakim"
+    last_name: "Boudaoud"
+    url: https://erpi.univ-lorraine.fr/people/Hakim-Boudaoud/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    orcid_id: 0000-0003-4452-5952
+
   - first_name: "Fabio"

### 2020-11-18 00-References.Rmd
introducing refs

---
title: "References"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
---

# Service Ecosystémiques

## 2016

- Clement Morlat. Modélisation dynamique des systèmes de coûts pour une gestion durable des territoires. Economies et finances. Université Paris-Saclay, 2016. Français. ffNNT : 2016SACLV115ff.
fftel-01617502f. https://tel.archives-ouvertes.fr/tel-01617502/document

# Developpement durable

## 2020

---

Coming soon more ! `r emo::ji("smile")`

### 2020-11-20 00-References.Rmd
adding refs

@@
 repository_url: https://github.com/LF2L/everest-bio
+#bibliography: Biblio.bib
+#nocite: '@*'
 ---
+
+# Circular Economy
+
+## On the definition
+
+- Calisto Friant, M., Vermeulen, W.J.V., Salomone, R., 2020.
+A typology of circular economy discourses: Navigating the diverse visions of a contested paradigm.
+Resour.
+Conserv.
+Recycl.
+161, 104917.
+https://doi.org/10.1016/j.resconrec.2020.104917
+
+- Morseletto, P., 2020. Targets for a circular economy. Resour. Conserv. Recycl. 153, 104553. https://doi.org/10.1016/j.resconrec.2019.104553
+
+- Schöggl, J.-P., Stumpf, L., Baumgartner, R.J., 2020.
+The narrative of sustainability and circular economy - A longitudinal review of two decades of research.
+Resour.
+Conserv.
+Recycl.
+163, 105073.
+https://doi.org/10.1016/j.resconrec.2020.105073
 
@@
 
-## 2020
+##
 

### 2020-11-20 01-Sustainable-indicators.Rmd
adding refs

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: Biblio.bib
#nocite: '@*'
---

# Abstract

Recycling is key strategy in order to establish in the circular economy umbrella concept.  
What are the the 'pertinent' indicators to evaluate the local distributed recycling network in a perspective of revelance of and also in the quality and feasability to obtain data.

Quels indicateurs pour évaluer la soutenabilité : pertinence, disponibilité, facilité de mise en œuvre ; s’accorcher au territoire : analyse des enjeux du territoire (périmètre thèse pavlo) => interview des acteurs, collecte d’info sur le territoire => impact quels sont les enjeux ? quels sont les indicateurs que l’on peut associer et les méthodes d’évaluation associée avec Nadège, Mauricio et Hakim

### 2020-11-23 02-supply-chain.Rmd
adding the research axis

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: Biblio.bib
#nocite: '@*'

author:
  - first_name: "Sabrina?"
    last_name: "Master 2"
    url: 
    affiliation: CREIDD?, ERPI?
    affiliation_url:

  - first_name: "Fedoua"
    last_name: "Kasmi"
    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-5159-0264

  - first_name: "Pavlo"
    last_name: "Santander"
    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    #orcid_id: 0000-0001-6328-1338

  - first_name: "Fabio"
    last_name: "Cruz"
    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-8529-5327

  - first_name: "Nadège"
    last_name: "Troussier"
    url: https://recherche.utt.fr/icd-directory/nadege-troussier
    affiliation: CREIDD
    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
    orcid_id: 0000-0001-6707-0300

  - first_name: "Hakim"
    last_name: "Boudaoud"
    url: https://erpi.univ-lorraine.fr/people/Hakim-Boudaoud/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-4452-5952

---

# Abstract

Master 2: sur la chaine de valeur localisée sur le cas d’étude (périmètre de pavlo) sur la base d’une analyse par les acteurs effectifs et potentiels; quels ont les freins et leviers au développement du plastique recyclé dans le territoire envisagé; analyse des services écosystémiques actuels et impactés. Pas que PLA mais aussi polypro en particulier… (Sabrina, avec Fedoua Kasmi et Hakim)

### 2020-11-23 03-comportements.Rmd
adding the research axis

--- 2020-11-23 02-supply-chain.Rmd
@@
 ---
-title: "Sustainable Indicators"
+title: "Sustainable behaviour"
 description: |
-  Some additional details about the website
+  some
 output:
@@
 author:
-  - first_name: "Sabrina?"
-    last_name: "Master 2"
+  - first_name: " Master 3"
+    last_name: ""
     url: 
@@
     affiliation_url:
-
-  - first_name: "Fedoua"
-    last_name: "Kasmi"
-    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    orcid_id: 0000-0001-5159-0264
-
-  - first_name: "Pavlo"
-    last_name: "Santander"
-    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    #orcid_id: 0000-0001-6328-1338
 
@@
 
+  - first_name: "Mauricio"
+    last_name: "Camargo"
+    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
+    affiliation: ERPI
+    affiliation_url: https://erpi.univ-lorraine.fr/
+    orcid_id: 0000-0003-3867-2438
+
 ---
@@
 
-Master 2: sur la chaine de valeur localisée sur le cas d’étude (périmètre de pavlo) sur la base d’une analyse par les acteurs effectifs et potentiels; quels ont les freins et leviers au développement du plastique recyclé dans le territoire envisagé; analyse des services écosystémiques actuels et impactés.
-Pas que PLA mais aussi polypro en particulier… (Sabrina, avec Fedoua Kasmi et Hakim)
+Master 3: Mise en place de la collecte des bouchons : pourrait être analyse sur le comportement des acteurs => quel changement dans ces profils de gens ?
+=> autre master (identifier ce que ça change chez les gens qui participent ou pas) avec Tatiana et Laure !!!
+doctorant avec master côté Nancy (avec Hakim et Mauricio)

### 2020-11-27 03-comportements.Rmd
Rationale for article 3

@@
 repository_url: https://github.com/LF2L/everest-bio
-#bibliography: Biblio.bib
-#nocite: '@*'
+bibliography: 03-comportement.bib
+nocite: '@*'
 
@@
 doctorant avec master côté Nancy (avec Hakim et Mauricio)
+
+# Rationale
+
+Some ideas:
+
+- Circular economy decisions are very complex but often the perceptions, attitudes, and personal values of decision makers directly influence organizations’ strategic actions towards a circular economy.
+Both active participation of organizations and the role of decision makers are pivotal to implement a circular economy for plastics [@Khan2020].
+
+- Identifying and assessing specific barriers associated with the workplace context could be crucial for achieving better employee engagement and a lower ecological footprint for organizations [@Yuriev2020]

### 2020-11-27 03-comportements.Rmd
Putting elements fro mthe paper of 2020

@@
 
+## On Circular Economy (CE)
+
 - Circular economy decisions are very complex but often the perceptions, attitudes, and personal values of decision makers directly influence organizations’ strategic actions towards a circular economy.
@@
 - Identifying and assessing specific barriers associated with the workplace context could be crucial for achieving better employee engagement and a lower ecological footprint for organizations [@Yuriev2020]
+
+### Barriers of CE implementation
+
+- @Khan2020 identified  barriers to deploy CE Plastics in order of importance are as follows. The foremost barrier is that organizations (Entreprises) do not have easy access to recycling facilities. 
+Second, organizations cannot transport plastic waste to recycling facilities. 
+Third, organizations do not have enough space to store plastic waste. 
+Fourth, organizations do not have enough time to sort plastic waste. 
+Fifth, organizations do not have sufficient funds to pursue plastic recycling. 
+Sixth, organizations do not have skilled personnel to sort plastic waste. 
+Seventh, organizations do not have an environmental expert at the management level. 
+Lastly, organizations do not know about potential buyers of plastic waste. 
+These findings imply that prominent barriers are physical factors rather than knowledge. Overall, these findings contribute to the literature on the barriers of a circular economy
+
+## On Theory of planned Behaviour
+
+- @Ajzen1991 developed **Theory of Planned Behaviour (TPB)**  which is one of the most influencing model for designing behavioral interventions [@Yuriev2020].
+Therefore, researchers have been increasingly employing the TPB model across various disciplines including environmental science and sustainability management
+TPB postulates considers three main aspects (1) attitude towards behavioral intention, (2) subjective norms, and (3) perceived behavioral control (PCB),  together they shape behavioral intention as well as actual behavior.
+To date, TPB has received around 90,000 citations [@Yuriev2020]
+
+-	Theory of planned behavior (TPB) is based on the assumption that some conscious reasoning is involved in the formation of intentions to perform a behavior.
+  - Behavior partly on the control of the individual
+  -	Behavior is predicted by attitudinal and normative factors and perceived behavioral control (PBC). 
+-	PBC reflects the extent to which the individual feels able to perform the behavior. 
+-	Past behavior tends to predict intentions and future behavior
+-	The factors that influenced the past behavior continue to influence the intentions and future behavior, but past behavior does not cause future behavior.
+
+```{r}
+
+```
+
+## On Distributed Recycling via Additive Manufacturing
+
+- The centralized schemes is the current paradigm for recycling concerns large majority of research on recycling behaviour comes within the scope of municipal waste management schemes.
+
+- Centralized recycling schemes have been criticized for inducing much waste transportation, which limits the ecological and economic benefits of recycling, especially in low density areas. 
+Therefore, in order to mitigate CO2 emissions and financial costs of transporting, the concept of distributed recycling emerged.
+Distributed recycling schemes are characterized by decentralized plastic waste collection, sorting and transformation.
+It includes in-house recycling, or recycling in local small-scale recycling networks, be it in a community, a company, or a public organisation.
+If understandings of distributed recycling regarding the decentralisation level differs, scholars agree on its potential for reducing gas emissions from waste collection  and creating groundbreaking alternative value chains to the established raw-resources based manufacturing .
+
+For Kreiger (2014), distributed recycling schemes could bring benefits in any economic context, independently of development levels.
+In the present study, the technology enabling recycling in a distributed recycling scheme is 3D printing, which we call distributed recycling via additive manufacturing (DRAM).
+A large variety of goods can be produced recycling plastic with 3D technology.
+Therefore, we believe DRAM has the potential for enhancing the circular economy approach and “close the loop”.

### 2020-11-27 03-comportements.Rmd
adding info on behaivour

@@
 Therefore, we believe DRAM has the potential for enhancing the circular economy approach and “close the loop”.
+
+# On pro-environmental behaviours
+
+- @Yuriev2020 identified nine systematic literature reviews on pro-environmental behaviors  (Li et al., 2019; Lo et al., 2012; Koop et al., 2019; Staddon et al., 2016; Varotto and Spagnolli, 2017; Inoue and Alfaro-Barrantes, 2015; Francoeur et al., 2019; Norton et al., 2015; Yuriev et al., 2018).
+These are the only existing systematic literature reviews from the last 10 years that covered various individual environmental actions. Having

### 2020-11-29 01-Sustainable-indicators.Rmd
adding the research axis
adding LCA and 3D printing

@@
 repository_url: https://github.com/LF2L/everest-bio
-#bibliography: Biblio.bib
-#nocite: '@*'
+bibliography: 01-Sustainable-indicators.bib
+nocite: '@*'
 ---
@@
 quels sont les indicateurs que l’on peut associer et les méthodes d’évaluation associée avec Nadège, Mauricio et Hakim
+
+# Rationale
+
+## LCA and 3D Printing
+
+- AM’s environmental performance is seldom investigated [@Saade2020].

### 2020-11-29 03-comportements.Rmd
TPB

@@
 ---
+```{r}
+require(DiagrammeR)
+require(tidyverse)
+require(kableExtra)
+```
 
@@
 Therefore, researchers have been increasingly employing the TPB model across various disciplines including environmental science and sustainability management
-TPB postulates considers three main aspects (1) attitude towards behavioral intention, (2) subjective norms, and (3) perceived behavioral control (PCB),  together they shape behavioral intention as well as actual behavior.
-To date, TPB has received around 90,000 citations [@Yuriev2020]
+TPB postulates considers three main aspects
+
+1.  Attitude towards behavioral intention, 
+2. Subjective Norms (SN), and 
+3. Perceived Behavioral Control (PCB),
+
+together they shape behavioral intention as well as actual behavior.  To date, TPB has received around 90,000 citations [@Yuriev2020]
+
+```{r, include=TRUE, echo=FALSE}
+
+mermaid("
+graph LR
+  A[\"Attitude toward the act (Att)\"]-->D[Behavioural Intention]
+  B[\"Subjective Norm (SN)\"]-->D[Behavioural Intention]
+  C[\"Perceived Behavioural Control (PBC)\"]-->D[Behavioural Intention]
+  D[Behavioural Intention]-->E[Behaviour]
+  C[Perceived Behavioural Control]-.->E[Behaviour]
+
+  classDef className font-size:20px;
+  class A,B,C,D className;
+")
+```
 
@@
 ```{r}
+TPB <- 
+tribble(
+  ~Variable, ~Definition, ~Definition.recycling,
+  "Attitude", 
+    "Attitude toward the behavior and refers to the degree to which a person has a favorable or unfavorable evaluation or appraisal of the behavior in question",
+      "The extent to which plastic recycling is valued by people, whether positive or negative",
 
+  "Subjective Norms",
+   "The perceived social pressure to perform or not to perform the behavior",
+      "The extent to which people are influenced by perceived norms of plastic recycling in their  surroundings",
+
+  "Perceived Behavioral Control (PCB)",   
+    "The perceived ease or difficulty of performing the behavior and it is assumed to reflect past experience as well as anticipated impediments and obstacles", 
+        "the perceived power (and knowledge) of people to implement plastic recycling",
+
+  "Behavioral intention",   
+    "They are indications of how hard people are willing to try, of how much of an effort they are planning to exert, in order to perform the behavior",
+    "A perceived likelihood or subjective probability of decision makers that they will implement plastic recycling in their organizations",
+
+  "Behaviour", 
+    " ",
+      "The extent to which organizations have implemented best practices of plastic recycling"
+)
+```
+
+```{r, include=TRUE}
+
+kbl(TPB) %>%
+  kable_paper(full_width = F)
 ```

### 2020-12-15 02-supply-chain.Rmd
add ref

@@
 repository_url: https://github.com/LF2L/everest-bio
-#bibliography: Biblio.bib
+bibliography: 02-supply-chain.bib
 #nocite: '@*'
@@
 Pas que PLA mais aussi polypro en particulier… (Sabrina, avec Fedoua Kasmi et Hakim)
+
+## Rational
+
+- @Alkhuzaim2020 provide insights into more effective environmentally sustainable supply chain and circularity performance evaluation, accounting, and appraisal using emergy based performance measurements.

### 2021-01-12 01-Sustainable-indicators.Rmd
add ref
adding PPS&Q article Sustainable Indicators

@@
 nocite: '@*'
+editor_options: 
+  chunk_output_type: console
 ---
 
-# Abstract
+```{r, include=FALSE}
 
-Recycling is key strategy in order to establish in the circular economy umbrella concept.  
-What are the the 'pertinent' indicators to evaluate the local distributed recycling network in a perspective of revelance of and also in the quality and feasability to obtain data.
+#library(rticles)
+#library(rmarkdown)
+#render("01-Sustainable-indicators.Rmd", output_format = "word_document")
+#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document")
+#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article")
 
-Quels indicateurs pour évaluer la soutenabilité : pertinence, disponibilité, facilité de mise en œuvre ; s’accorcher au territoire : analyse des enjeux du territoire (périmètre thèse pavlo) => interview des acteurs, collecte d’info sur le territoire => impact quels sont les enjeux ?
+```
+
+# Intial Thougths
+Quels indicateurs pour évaluer la soutenabilité: pertinence, disponibilité, facilité de mise en œuvre; s’accorcher au territoire: analyse des enjeux du territoire (périmètre thèse pavlo) =>
+
+interview des acteurs, collecte d’info sur le territoire => impact quels sont les enjeux?
 quels sont les indicateurs que l’on peut associer et les méthodes d’évaluation associée avec Nadège, Mauricio et Hakim
+
+# Problem, Purpose statements & Research questions
+
+The development of short supply chain is becoming a topic of growing interest among consumers, researchers and public bodies in Europe.
+More than ever, the resilience of a territory relies in the capacity of becoming less dependant of outlier productors [@reference], whiwh is a elements highligtly identified by the pandemic conditions.
+However, the evaluation of pertinent sustainable indicators for this short supply networks is one the  major topic of discussion in the scientific and practitioners communities. 
+The problem relies in the selection of these 'pertinent' indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
+Moreover, depending of the material or product and their technological process associated to, this entakes difficulties in terms of dependance of stakeholders beyond the scope of the short circuit.
+
+The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@ref]. 
+The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to propose additoanl cascading loops  to certain types plastic waste.
+More precisely, the use of recycled assets in the printing process chaing of additive manufacturing technology can give add value to wastes to create possible products or scientific equipement a a lower cost than the commercial.
+In a sense, this apporache could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe.
+
+Therefore, the main research question is  *how to evaluate the global sustainability of short supply chains to foster the plastic recycling networks in a local territory?*.
+More precisely, *What are the the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*
+One element to highlight the impact that third-spaces as innovations labs, fablabs and/or makerspace can play an role in order to apporaprio agents of change  the development of
+
+The objectives of this research are:
+
+- Establish a grid of economical, political, environementa and social indicators.
+- Define model of stakeholders that can be impacted (positive / negative) for the case of plastic recycling
+- ...
+
+Therefore, the purpose of this research is to set a baseline of sustainable indicators to evaluate a local short supply chain network for distributed recycling.
+The main perspectives relies in the articulation of means of implementation and means evaluations based sustaianble decision tools for this type of networks.
 
@@
 - AM’s environmental performance is seldom investigated [@Saade2020].
+
+## LCA and Social practices
+
+- Llinks social practices to the life cycle inventory of LCA [@Suski2020].

### 2021-01-15 01-Sustainable-indicators.Rmd
sorting the site from teams de drive
improving 1%

@@
 repository_url: https://github.com/LF2L/everest-bio
-bibliography: 01-Sustainable-indicators.bib
+#bibliography: 01-Sustainable-indicators.bib
+bibliography: library.bib
 nocite: '@*'
@@
 #library(rmarkdown)
-#render("01-Sustainable-indicators.Rmd", output_format = "word_document")
-#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document")
-#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article")
+#render("01-Sustainable-indicators.Rmd", output_format = "word_document", output_dir = "01-Sustainable-Indicators")
+#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document", output_dir = "01-Sustainable-Indicators")
+#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article", output_dir = "01-Sustainable-Indicators")
 
@@
 
+## Mind mapping
+
+```{r, include=FALSE}
+library('mindr')
+### text -> widget
+input <- c("# Chapter 1", "## Section 1.1", "## Section 1.2", "# Chapter 2")
+mm(from = input, type = "text", root = "Ideas to develop")
+
+input <- system.file("examples/md/bookdownplus1.md", package = "mindr")
+mm(from = input, type = "file", root = "mindr")
+
+```
+
+:::l-page
+<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
+:::
+
 # Problem, Purpose statements & Research questions
@@
 
-The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@ref]. 
+The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@reference]. 
 The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to propose additoanl cascading loops  to certain types plastic waste.

### 2021-01-15 02-supply-chain.Rmd
improving 1%

@@
 ---
-title: "Sustainable Indicators"
+title: "Supply chain Axis"
 description: |

### 2021-01-15 03-comportements.Rmd
adding PPS&Q article Sustainable Indicators
improving 1%

@@
 ---
-title: "Sustainable behaviour"
+title: "Environmental behaviour & practices"
 description: |
@@
 These are the only existing systematic literature reviews from the last 10 years that covered various individual environmental actions. Having
+
+- Chan, L., Bishop, B., 2013. A moral basis for recycling: Extending the theory of planned behaviour. J. Environ. Psychol. 36, 96–102. https://doi.org/10.1016/j.jenvp.2013.07.010

### 2021-01-15 01-Sustainable-indicators.Rmd
correcting the biblio

@@
 bibliography: library.bib
-nocite: '@*'
+#nocite: '@*'
 editor_options: 

### 2021-01-15 03-comportements.Rmd
correcting the biblio

@@
 bibliography: 03-comportement.bib
-nocite: '@*'
+#nocite: '@*'
 
@@
 ---
-```{r}
+```{r, include=FALSE}
 require(DiagrammeR)
@@
 
-```{r}
+```{r, include=FALSE}
 TPB <- 
@@
 
-```{r, include=TRUE}
+```{r, include=TRUE, echo=FALSE}
 

### 2021-01-18 02-supply-chain.Rmd
adding elements to supply chain

@@
 
+# Problem, Purpose statements & Research questions
+
+A new paradigm of plastic recycling, called distributed plastic recycling, has emerged in the literature in order to face the socio-environmental challenges related to plastic waste management.
+Under this new model of small recycling centers, the main hipohesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
+To do so, the use of additive manufacturing enables the technical paths.
+
+ However, as with any recycling system, its feasibility must be evaluated before its implementation.
+Although research has been conducted regarding the technical feasibility of distributed plastic recycling, little is known about its feasibility from the supply chain point of view [@CruzSanchez2020].
+.content-box-yellow[From a supply chain perspective, the establishment of  recycling networks...
+]
+
+This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
+
+The purpose of this research is to explore and assess the local impact derived from the implementation of a distributed plastic recycling chain.
+The study intends to research which and how the ecosystem services are impacted due to the implementation of the plastic recycling chain proposed.
+While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of ths distributed approaches
+
+This study seeks to address the following questions:
+
+- What are the appropriate ecosystem service indicators for assessing distributed plastic recycling?
+
+- How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
+
+- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
+
 ## Rational

### 2021-01-19 01-Sustainable-indicators.Rmd
sustainable indicator PPS&Q V1.0.0

@@
 
-# Problem, Purpose statements & Research questions
+# Rationale
 
 The development of short supply chain is becoming a topic of growing interest among consumers, researchers and public bodies in Europe.
-More than ever, the resilience of a territory relies in the capacity of becoming less dependant of outlier productors [@reference], whiwh is a elements highligtly identified by the pandemic conditions.
+More than ever, the resilience of a territory relies in the capacity of becoming less dependant of outlier productors [@reference], which is an element identified by the pandemic conditions.
+
+<!-- Problem -->
 However, the evaluation of pertinent sustainable indicators for this short supply networks is one the  major topic of discussion in the scientific and practitioners communities. 
-The problem relies in the selection of these 'pertinent' indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
+The problem relies in the selection of these 'pertinent' sustainable indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
 Moreover, depending of the material or product and their technological process associated to, this entakes difficulties in terms of dependance of stakeholders beyond the scope of the short circuit.
 
-The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@reference]. 
-The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to propose additoanl cascading loops  to certain types plastic waste.
-More precisely, the use of recycled assets in the printing process chaing of additive manufacturing technology can give add value to wastes to create possible products or scientific equipement a a lower cost than the commercial.
-In a sense, this apporache could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe.
+<!-- Contex -->
+The context of this research is the development of a short plastic recycling network for distributing recycling purposes [@Santander2020]. 
+The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to foster the use of certains plastic waste materials in order to extend eventually (multiple) lifecycle for a printed product.
+More precisely, the use of recycled assets in the printing process chain of additive manufacturing technology can give add value to wastes to create possible final products or even scientific equipement [@Pearce2020a] a a lower cost than the commercial.
+In a sense, this approach could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe, even if this intervention remains largely case-dependent.
 
-Therefore, the main research question is  *how to evaluate the global sustainability of short supply chains to foster the plastic recycling networks in a local territory?*.
-More precisely, *What are the the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*
-One element to highlight the impact that third-spaces as innovations labs, fablabs and/or makerspace can play an role in order to apporaprio agents of change  the development of
+<!-- Conceptual Framework -->
+Nevertheless, there remain a gap in the scientific literature to define in what sense DRAM could be considered as sustainable transition in the global aspect of the term. 
+The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
+enhancing human well-being to more equitably meet the needs of both current and future generations.
+@Clark2020 developed an integrative framework for sustainability considering five major pilards: 
+(1) environment and development, 
+(2) governance, 
+(3) complexity, and 
+(4) context dependence.
+
+At the core of research on sustainability are the intertwined nature–society interactions.
+Sustainability science research has focused on the four key elements involved in those interactions:
+
+- *Goals* (what people want from sustainable development), 
+- *Resources* (the capital assets of the Anthropocene System, which may be natural or anthropogenic), - *Actors* (communities, firms, states and other entities with agency that strive to use resources to achieve their goals),
+- *Institutions* (rules, norms, culture, beliefs that shape the behavior of actors).
+
+These key elements are bound together through key relationships of consumption and production, mediated by the relative power of different actor groups to affect one another’s actions and beliefs.
+
+Therefore, contextualizing the concptual framework to the DRAM context, the main research question is for this project are:
+
+1. *How to evaluate the global sustainability of short supply chains to foster the plastic recycling networks in a local territory?*.
+
+2.*What are the the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*
+
+One element to highlight the impact that third-spaces as innovations labs, fablabs and/or makerspace can play an role as agents of change in the development of this recycling practicesl [@Roux-Marchand2020]
 
@@
 
-- Establish a grid of economical, political, environementa and social indicators.
+- Establish a grid of economical, political, environemental and social indicators.
 - Define model of stakeholders that can be impacted (positive / negative) for the case of plastic recycling
@@
 Therefore, the purpose of this research is to set a baseline of sustainable indicators to evaluate a local short supply chain network for distributed recycling.
-The main perspectives relies in the articulation of means of implementation and means evaluations based sustaianble decision tools for this type of networks.
 
-# Rationale
+Based on the results of these indicators, the main challguen will be the articulation and means of implementation / evaluations to build  decision tools for this type of networks.
+
+# Ideas
 

### 2021-01-19 01-Sustainable-indicators.Rmd
sustainable indicator PPS&Q V1.0.1

@@
 
-Therefore, contextualizing the concptual framework to the DRAM context, the main research question is for this project are:
+Therefore, contextualizing thi sustainable concptual framework to the DRAM context, the main research question is for this project are:
 
@@
 
-2.*What are the the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*
+2.*What are the 'pertinent' qualitative and quantitative indicators to evaluate the local distributed recycling network in terms of revelance of quality and feasibility to obtain appropriate data with local stakeholders?*
 
-One element to highlight the impact that third-spaces as innovations labs, fablabs and/or makerspace can play an role as agents of change in the development of this recycling practicesl [@Roux-Marchand2020]
+One element to highlight is the impact that third-spaces such as innovations labs, fablabs and/or makerspace can play, having a role of agents of change in the development of this recycling practices [@Roux-Marchand2020].
 

### 2021-01-19 01-Sustainable-indicators.Rmd
adding the minmapping for all

@@
 
-# Intial Thougths
+# Initial Thougths
 Quels indicateurs pour évaluer la soutenabilité: pertinence, disponibilité, facilité de mise en œuvre; s’accorcher au territoire: analyse des enjeux du territoire (périmètre thèse pavlo) =>
@@
 (4) context dependence.
-
 At the core of research on sustainability are the intertwined nature–society interactions.

### 2021-01-19 03-comportements.Rmd
adding the minmapping for all
figure mermaid corrections

@@
 require(kableExtra)
+require(widgetframe)
 ```
@@
 doctorant avec master côté Nancy (avec Hakim et Mauricio)
+
+:::l-page
+<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
+:::
 
@@
 graph LR
-  A[\"Attitude toward the act (Att)\"]-->D[Behavioural Intention]
-  B[\"Subjective Norm (SN)\"]-->D[Behavioural Intention]
-  C[\"Perceived Behavioural Control (PBC)\"]-->D[Behavioural Intention]
-  D[Behavioural Intention]-->E[Behaviour]
-  C[Perceived Behavioural Control]-.->E[Behaviour]
+  A[Attitude toward the act <br/> -ATT-]-->D[Behavioural Intention <br/>]
+  B[Subjective Norm -SN-<br/>]-->D[Behavioural Intention]
+  C[Perceived Behavioural Control -PBC-<br/>]-->D[Behavioural Intention]
+  D[Behavioural Intention <br/>]-->E[Behaviour]
+  C[Perceived Behavioural Control -PCB-]-.->E[Behaviour]
 
-  classDef className font-size:20px;
+  classDef className font-size:18px, height:60px ;
   class A,B,C,D className;
 ")
+
+#
+#  
 ```
@@
 
-```{r, include=TRUE, echo=FALSE}
+```{r, include=TRUE, layout="l-page", echo=FALSE}
 

### 2021-01-19 01-Sustainable-indicators.Rmd
references and adding elements de plavlo

@@
 However, the evaluation of pertinent sustainable indicators for this short supply networks is one the  major topic of discussion in the scientific and practitioners communities. 
-The problem relies in the selection of these 'pertinent' sustainable indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
+The problem relies in the selection of 'pertinent' sustainable indicators and trade-offs that need to be considered for a holistic evaluation and the scope of the short supply chain. 
 Moreover, depending of the material or product and their technological process associated to, this entakes difficulties in terms of dependance of stakeholders beyond the scope of the short circuit.
@@
 The development of the development of distributing recycling approach via additive manufacturing (DRAM) [@CruzSanchez2020] is emerging as an interesting topic to foster the use of certains plastic waste materials in order to extend eventually (multiple) lifecycle for a printed product.
-More precisely, the use of recycled assets in the printing process chain of additive manufacturing technology can give add value to wastes to create possible final products or even scientific equipement [@Pearce2020a] a a lower cost than the commercial.
+More precisely, the use of recycled assets in the printing process chain of additive manufacturing technology can give add value to wastes to create possible final products or even scientific equipement [@Pearce2020a] at a lower cost than the commercial.
 In a sense, this approach could be an operationalization strategy for the development of secondary raw materials, which is one of major pillars in the recycling strategy for the Circular economy in Europe, even if this intervention remains largely case-dependent.
@@
 <!-- Conceptual Framework -->
-Nevertheless, there remain a gap in the scientific literature to define in what sense DRAM could be considered as sustainable transition in the global aspect of the term. 
+Nevertheless, there remain a gap in the scientific literature related to in what extend the DRAM could be considered as sustainable in the global aspect of the term. 
 The challenges of sustainable development today are generally seen in terms that go beyond just meeting basic human needs to embrace a broader vision of sustainability as fairness: 
@@
 (4) context dependence.
-At the core of research on sustainability are the intertwined nature–society interactions.
-Sustainability science research has focused on the four key elements involved in those interactions:
+At the core of research on sustainability, there are a intertwined nature–society interactions.
+Sustainability science research has focused on the four key elements involved in the interactions of:
 
 - *Goals* (what people want from sustainable development), 
-- *Resources* (the capital assets of the Anthropocene System, which may be natural or anthropogenic), - *Actors* (communities, firms, states and other entities with agency that strive to use resources to achieve their goals),
+- *Resources* (the capital assets of the Anthropocene System, which may be natural or anthropogenic),
+- *Actors* (communities, firms, states and other entities with agency that strive to use resources to achieve their goals), 
 - *Institutions* (rules, norms, culture, beliefs that shape the behavior of actors).
@@
 
-Therefore, contextualizing thi sustainable concptual framework to the DRAM context, the main research question is for this project are:
+Therefore, contextualizing the sustainable conceptual framework to the DRAM context, the main research questions for this project are:
 
@@
 
+## LCA
+
+- Review on LCA [@Visentin2020]
+
 ## LCA and 3D Printing

### 2021-01-19 02-supply-chain.Rmd
sustainable indicator PPS&Q V1.0.0
adding the minmapping for all
references and adding elements de plavlo

--- 2021-01-15 02-supply-chain.Rmd
@@
 repository_url: https://github.com/LF2L/everest-bio
-bibliography: 02-supply-chain.bib
+#bibliography: 02-supply-chain.bib
+bibliography: library.bib
 #nocite: '@*'
@@
 
-## Rational
+:::l-page
+<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
+:::
+
+# Rationale
+
+A new paradigm of plastic recycling, called distributed plastic recycling, has emerged in the literature in order to face the socio-environmental challenges related to plastic waste management.
+Under this new model of small recycling centers, the main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
+To do so, the use of additive manufacturing enables the technical paths.
+
+  However, as with any recycling system, its feasibility must be evaluated before its implementation.
+Although research has been conducted regarding the technical feasibility of distributed plastic recycling, little is known about its feasibility from the supply chain perspective [@CruzSanchez2020] and its impact in ecosystem services.
+From a supply chain perspective, the feasibility evaluation for the establishment of recycling networks should be oriented towards sustainable development. 
+In addition, the notion of sustainability could be used as a framework to analyze and manage the impact of human activities (or supply chain) on ecosystem services [@Abson2014].
+A network is sustainable, if it integrates the economic, environmental and social dimensions, traditionally referred to as the three pillars of sustainability (’triple bottom-lines - TBL) (Hacking and Guthrie, 2008).
+In addition, @Bautista2016 proposes the integration of political and technological dimensions (TBL+) if they have a great importance in the system to evaluate..
+However, literature reviews about supply chains networks highlight :
+(1) the little consideration of social, technological and political aspects in sustainability assessments, and 
+(2) the great consideration of economic and environmental aspects 
+[@EspinozaPerez2017c, @Fonseca2018, @Moreno-Camacho2019].
+
+This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
+
+The purpose of this research is to explore and assess the local impact, considering sustainability dimensions and ecosystem services, derived from the implementation of a distributed plastic recycling chain.
+The study intends to research, based on the notion of sustainability, which and how the ecosystem services are impacted due to the implementation of the plastic recycling chain proposed. 
+While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches
+
+This study seeks to address the following questions:
+
+- What are the appropriate ecosystem service indicators for assessing distributed plastic recycling? 
+- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
+- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
+
+## Ideas
 

### 2021-01-19 03-comportements.Rmd
references and adding elements de plavlo

@@
 repository_url: https://github.com/LF2L/everest-bio
-bibliography: 03-comportement.bib
+#bibliography: 03-comportement.bib
+bibliography: library.bib
 #nocite: '@*'

### 2021-01-19 02-supply-chain.Rmd
lucidchart

@@
 :::l-page
-<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
+<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
 :::

### 2021-01-19 03-comportements.Rmd
lucidchart

@@
 :::l-page
-<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
+<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="rc17nDan15JX"></iframe></div>
 :::

### 2021-01-19 02-supply-chain.Rmd
adding link to the lucidchart

@@
 ---
-title: "Supply chain Axis"
+title: "DRAM and ES"
 description: |
@@
 
+[**Link to modify the Graph**](https://lucid.app/lucidchart/invitations/accept/f6847ab0-3fd4-4749-a581-669058760d2d)
+
 :::l-page

### 2021-01-19 02-supply-chain.Rmd
lucid chart update

@@
 :::l-page
-<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
+<div style="width: 100%; height: 480px; margin: 10px; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:95%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
 :::

### 2021-01-19 03-comportements.Rmd
adding link to the lucidchart
lucid chart update

@@
 
+[**Link to modify the Graph**](https://lucid.app/lucidchart/invitations/accept/f6847ab0-3fd4-4749-a581-669058760d2d)
+
 :::l-page
-<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="rc17nDan15JX"></iframe></div>
+<div style="width: 100%; height: 480px; margin: 10px; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:95%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="rc17nDan15JX"></iframe></div>
 :::

### 2021-04-11 slides/index.Rmd
big commit for the ppt

@@
   Projet de recherche CREIDD et ERPI
-author: "Fabio Xie"
+author: "Fabio Cruz / Mauricio Camargo / Nadège Troussier"
 institute: "CREIDD, ERPI"
@@
     lib_dir: libs
+    css: ["default"]
     nature:
@@
       countIncrementalSlides: false
+      beforeInit: "assets/macros.js"
+      navigation:
+        scroll: false # disable slide transitions by scrolling
 ---
 
-## The problem: Plastic waste
+```{r setup, include = FALSE, echo=FALSE, message=FALSE}
+options(htmltools.dir.version = FALSE)
+
+knitr::opts_chunk$set(include= TRUE, echo=FALSE, message=FALSE, fig.path="figures/")
+
+library(tidyverse)
+# Link for the Figures
+URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
+```
+
+```{r, include=TRUE, echo=FALSE}
+# CSS for the CSS
+htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
+htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
+```
+
+```{r share-again, echo=FALSE}
+xaringanExtra::use_share_again()
+```
+
+---
+
+class: middle, left
+
+# Agenda
+
+1. .content-box-yellow[Who am I?]
+2. ERPI Laboratory
+3. Green Fablab
+4. Everest Bio
+5. Proposition and Research axis
+
+---
+
+class: top, left
+background-image: url(`r paste0(URL, 'Fabio/vosviewer/Fabio.jpg')`)
+background-position: right
+background-size: 70%
+
+# Who am I?
+
+.pull-left-1[
+```{r, echo=FALSE, out.width = '60%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Fabio/Fabio.png'))
+```
+]
+
+---
+
+class: left
+background-position: 0px 75px
+background-size: contain
+
+--
+
+background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-01.jpg')`)
+
+## Are open source 3D printer good enough?
+
+---
+
+## Are open source 3D printer good enough?
+
+Geometrical accuracy perspective
+
+```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '80%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Metodologies/Master-recherche/Master-00.png'))
+```
+
+.footnote[
+Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
+Towards a standard experimental protocol for open source additive manufacturing.
+Virtual Phys.
+Prototyp.
+9, 151–167.
+https://doi.org/10.1080/17452759.2014.919553
+]
+
+---
+
+class: left
+background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-02.jpg')`)
+background-position: 0px 75px
+background-size: contain
+
+## Can we print recycled objects?
+
+Recycling feasibility (Lab conditions)
+
+---
+
+class: left
+background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-03.jpg')`)
+background-position: 0px 75px
+background-size: contain
+
+## What about the supply chain printed recycled objects?
+
+.pull-down[Research of Pavlo Santander. Thesis Defended Dec. 2020]
+
+---
+
+class: left
+background-image: url(`r paste0(URL, 'DRAM/DRAM-05.jpeg')`)
+background-position: 100px 125px
+background-size: 80%
+
+## How an innovation lab could be a driver for local plastic recycling process?
+
+.footnote[
+Roux-Marchand, T., Cruz, F., Dupont, L., Camargo, M., Osorio, F., 2020.
+Connecting the strategic intent of innovation labs and projects: the case of the Green Fablab, in: 2020 IEEE International Conference on Engineering, Technology and Innovation (ICE/ITMC).
+IEEE, pp.
+1–10.
+https://doi.org/10.1109/ICE/ITMC49519.2020.9198320
+
+Alexandre, A., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
+Mechanical Properties of Direct Waste Printing of Polylactic Acid with Universal Pellets Extruder: Comparison to Fused Filament Fabrication on Open-Source Desktop Three-Dimensional Printers.
+3D Print.
+Addit.
+Manuf.
+3dp.2019.0195.
+https://doi.org/10.1089/3dp.2019.0195
+]
+
+---
+
+## What if distributed recycling could be aligned with Circular Economy priorities?
+
+```{r, out.width = '80%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'DRAM/DRAM-10.png'))
+```
+
+Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
+Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy.
+J.
+Clean.
+Prod.
+264, 121602.
+https://doi.org/10.1016/j.jclepro.2020.121602
+
+---
+
+class: middle
+
+# However...
+
+.left-column[
+```{r, out.width = '80%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Various/Signos/attention-00.png'))
+```
+]
+
+.right-column[
+- Where is the environment in the techno-centrical approaches?
+-  The root of the plastic waste problem needs to be addressed: the extraction and production.
+-  Responsibility to act in the plastics economy
+
+- **Adaptive injustice**: *those who find ways to adapt to changing social realities, whether forced or voluntary, are not those who are responsible for the negative changes to which they are adapting.
+Specifically, it is an adaptive injustice to expect communities to figure out what to do with continual flow of plastics into the economy.*
+
+.content-box-red[**It’s time to retire this ‘privatizing profits, socializing costs’ model.**]
+
+]
+
+.footnote[
+Conlon, K., 2020. Adaptive injustice: Responsibility to act in the plastics economy. Resour. Conserv. Recycl. 153, 104563. https://doi.org/10.1016/j.resconrec.2019.104563
+]
+
+---
+
+class: middle
+
+# Agenda
 
 .pull-left[
+1. Who am I?
+2. .content-box-yellow[ERPI Laboratory]
+3. Green Fablab
+4. Everest Bio
+5. Proposition and Research axis
+]
+
+.pull-right[
+
+.brand-blue[Equipe de Recherche sur le Processus Innovatifs - ERPI]
+
+```{r, out.width = '80%', fig.align='center'}
+knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
+```
+]
+
+---
+
+## .small[Equipe de Recherche sur le Processus Innovatifs - ERPI]
+
+A .red[Multidisciplinary] team in **Industrial Engineering** specialized in the study of Innovation processes
+
+.pull-left[
+
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
+```
+
+45 Members average
+
+24 permanent researchers <br>
+(10 full Pr., 13 associated Pr, 1 Research engineer) <br>
+1 Studies engineer <br>
+5 Postdoc  <br>
+3 Temporary lecturers  <br>
+2 Admin. <br>
+
+]
+
+.pull-right[
+
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'LF2L/Methodology-complet-00.jpg'))
+```
+
+Research platform: **LF2L** - http://lf2l.fr
+]
+
+---
+
+# Research domains at ERPI:
+
+.pull-left[
+.pull-left[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/01-Innovation-metrology.jpg'))
+```
+
+.orange[
+**Innovation capability**
+
+Product <br>
+Process  <br>
+Business Model <br>
+
+]
+]
+.pull-right[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/02-Prospective.jpg'))
+```
+.blue[
+**Technological  Emergence/maturity**
+
+Product-Process <br>
+Industrial supply chain <br>
+]]]
+
+.pull-right[
+.pull-left[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/03-Design.jpg'))
+```
+.green[
+**Materialized**
+
+Creative Exploration <br>
+Feasibility Product-Process <br>
+Physic & digital (virtual) Prototyping <br>
+]
+]
+.pull-right[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/04-Acceptability.jpg'))
+```
+.purple[
+**Front-end validation**
+Multi-actors Acceptability <br>
+User eXperience & test by use <br>
+Living Lab <br>
+]]]
+
+.center.Large[Creator of **methods & tools** supporting innovation process]
+
+---
+
+## Scope: The Fuzzy Front End of innovation
+
+.pull-left[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Scope-00.jpg'))
+```
+]
+
+.pull-right[
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Purpose-00.jpg'))
+```
+.footnote[
+Martinez-Hernandez, E., 2017. Trends in sustainable process design—from molecular to global scales. Curr. Opin. Chem. Eng. 17, 35–41. <br/> https://doi.org/10.1016/j.coche.2017.05.005 
+]
+]
+
+Think earlier in the sustainable design and their impact
+
+---
+
+## Innovation: a response to current social challenges
+
+```{r, out.width = '95%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Fields-00.jpg'))
+```
+
+.tiny[Tran Thi Hoang, G., Dupont, L., & Camargo, M. (2019). Application of Decision-Making Methods in Smart City Projects: A Systematic Literature Review. Smart Cities, 2(3), 433-452.]
+
+---
+
+class: middle
+
+# Agenda
+
+.pull-left[
+1. Who am I?
+2. ERPI Laboratory
+3. .content-box-yellow[Green Fablab]
+4. Everest Bio
+5. Proposition and Research axis
+]
+
+.pull-right[
+
+```{r, out.width = '100%', fig.align='center'}
+knitr::include_graphics('http://lf2l.fr/assets/images/3-projects/gf/Logo-GF.png')
+```
+*Circular economy and 3D printing: Towards a distributed recycling paradigm*
+]
+
+---
+
+class: top, left
+background-image: url(`r paste0(URL, 'Plastics/Plastic-problem-03.svg')`)
+background-position: right
+background-size: 70%
+
+## Plastics waste since  olden times
+
+.left-column[
+.tiny[
 - US recycled less than 9% of its plastic waste.
@@
 
-## We barely recycle plastic!!.. 
-]
+```{r, out.width = '60%', fig.align='center'}
+knitr::include_graphics('https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80')
+```
 
-.pull-right[ 
-![Plastic waste](https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80)
-]
+]]
 
 .footnote[
+Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782
+
 *Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018.
@@
 36, 445–453
+
 ]
@@
 
-.pull-left[
-.small[
-
-- Les seuls critères technico-économiques ne permettent pas (plus) d’avoir une prise de décision éclairée
-
-- Besoin d’évaluer les filières de manière différente, notamment les impacts réels sur les écosystèmes
-
-- Une vision plus holistique est nécessaire pour évaluer la faisabilité de ces nouvelles filières
+.left-column[
+.footnotesize[
+- Only technico-economic criteria alone do not (no longer) enables a informed decision making 
+- Need to assess value chains in a different way, including actual impacts on ecosystems
+- A more holistic vision is needed to assess the feasibility of these new sectors.
 ]
@@
 
+.right-column[ 
+.polaroid[ ![](figures/Recycling.png) ]
+]
+
 ---
+
+## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
+
+.pull-left[
+
+-Local closed loop  <br>
+-AM adds value  <br>
+-Small quantities   <br>
+-Reduction of landfilling  <br>
+-Minimize the use of virgin materials  <br>
+
+```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
+knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-2.jpg'))
+```
+
+]
+.pull-right[
+
+```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-1.jpg'))
+```
+
+http://lf2l.fr/projects/green-fablab
+]
+
+.footnote[
+Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
+Towards a standard experimental protocol for open source additive manufacturing.
+Virtual Phys.
+Prototyp.
+9, 151–167.
+https://doi.org/10.1080/17452759.2014.919553
+]
+
+---
+
+.center[![:scale 70%](figures/Green-fablab-circuit.png)]
+
+---
+
+---
+
+class: middle
+
+# Agenda
+
+.pull-left[
+1. Who am I?
+2. ERPI Laboratory
+3. Green Fablab
+4. .content-box-yellow[Everest Bio]
+5. Proposition and Research axis
+]
+
+.pull-right[
+
+```{r, out.width = '100%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/logos/logo-2.jpg'))
+```
+]
+
+---
+
+## People in Everest Bio
+
+.pull-left[
+```{r, out.width = '200px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
+```
+]
+
+.pull-rigth[
+```{r, out.width = '200px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Nadege.jpg'))
+```
+
+```{r, out.width = '200px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
+```
+
+```{r, out.width = '200px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Cristian.jpg'))
+```
+
+]
+---
+
+## Research Question & Goal
+
+- To develop a generic methodology to assess the ecosystem services rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors.
+
+- Validation on the case of a short-circuit plastic recycling chain.
+
+---
+
+## Methodology
+
+- In line with the thesis work previously carried out by the two teams, development of a coupled Systems Dynamics and LCA approach.
+
+- Application on a case study, the GreenFablab, by evaluating its environmental impact when setting up a short plastic recycling circuit.
+
+.center[ ![:scale 80%](figures/Goals.png)]
+
+---
+
+## Purpose of Everest Bio
+
+Taking into account the environment and their ecosystem services (ES).
+
+.pull-left[
+
+```{r, out.width = '90%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Ecoservices/Eco-Services-00.jpg'))
+```
+]
+
+.pull-right[
+![](figures/Eco-Services-01.png)
+
+- How the future recycling chain could be including the environment?
+]
+
+.footnote[
+Bruel, A., Kronenberg, J., Troussier, N., & Guillaume, B.
+(2019).
+Linking industrial ecology and ecological economics: A theoretical and empirical foundation for the circular economy.
+Journal of Industrial Ecology, 23(1), 12-21.
+]
+
+---
+
+### Ecosystem Services as a boundary object for sustainability
+
+---
+
+### Systems Dynamics
+
+---
+
+## Distributed recycling via additive manufacturing (DRAM)
+Technical system
+
+.center[![:scale 75%](figures/Green-fablab-0.png)]
+
+.footnote[
+Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
+Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy.
+J.
+Clean.
+Prod.
+264, 121602.
+https://doi.org/10.1016/j.jclepro.2020.121602
+]
+
+---
+
+## Distributed recycling via additive manufacturing (DRAM)
+Technical system --> Global system
+
+.center[![:scale 75%](figures/DRAM-05.png)]
+
+---
+
+## Towards systemic solutions
+
+Global system
+
+.pull-left[
+![](figures/DRAM-07.png)
+]
+
+.pull-right[
+- Establish and evaluate scenarios in a systemic and dynamic way
+- Evaluate the influences of the main operating variables on the system
+- Taking into account the priorities of the multiple stakeholders
+- Facilitate your decision making public-private actors
+]
+
+.footnote[
+Santander, P., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., 2020.
+Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach.
+Resour.
+Conserv.
+Recycl.
+154, 104531.
+https://doi.org/10.1016/j.resconrec.2019.104531
+]
+
+---
+
+# Delivrables
+
+1. An article in an indexed international journal
+2. Participation in an international conference 
+3. An operational model with a model of a software tool for assessing local impacts
+4. Final report on the evaluation of Green Fablab and possible generalisations for short industrial circuits.
+
+---
+
+# Valorisations
+
+- Method and prototype of a tool for the evaluation of local impacts of circular production systems
+
+---
+
+class: middle, center
+
+Thanks !
+
+![:scale 70%](figures/DRAM-bd.png)

### 2021-04-11 slides/index.Rmd
primera version ppt ahora si completa

@@
 
+class: left middle
+
+## My research questions so far...
+
+---
+
 class: left
@@
 background-size: contain
-
---
 
@@
 
-## How an innovation lab could be a driver for local plastic recycling process?
+## How an innovation lab could could help as agent of change?
 
@@
 .right-column[
+
+- Technical and economic criteria alone do not (yet) allow for informed decisions.
+
 - Where is the environment in the techno-centrical approaches?
+
 -  The root of the plastic waste problem needs to be addressed: the extraction and production.
@@
 
+## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
+
+.left-column[ 
+Small scale: 2 km radius (neighbourhood scale) <br>
+Low processing capacity, <br>
+Technologies: cheap, easy to use <br>
+Active role of users <br>
+
+```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
+knitr::include_graphics('figures/GF-users.jpg')
+```
+]
+
+.right-column[ 
 .center[![:scale 70%](figures/Green-fablab-circuit.png)]
 
----
+]
 
@@
 .pull-left[
-```{r, out.width = '200px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Mauricio.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Hakim.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
 ```
@@
 
-.pull-rigth[
-```{r, out.width = '200px', fig.align='center'}
+.pull-right[
+```{r, out.width = '500px', fig.align='center'}
 knitr::include_graphics(paste0(URL, 'Everest-bio/Nadege.jpg'))
@@
 
-```{r, out.width = '200px', fig.align='center'}
+```{r, out.width = '500px', fig.align='center'}
 knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
@@
 
-```{r, out.width = '200px', fig.align='center'}
+```{r, out.width = '500px', fig.align='center'}
 knitr::include_graphics(paste0(URL, 'Everest-bio/Cristian.jpg'))
@@
 ]
+
 ---
@@
 
-- To develop a generic methodology to assess the ecosystem services rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors.
+- To develop a generic methodology to assess the **ecosystem services** rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors.
 
@@
 
-- In line with the thesis work previously carried out by the two teams, development of a coupled Systems Dynamics and LCA approach.
+- In line with the thesis work previously carried out by the two teams, development of a coupled **Systems Dynamics and LCA approach**.
 
-- Application on a case study, the GreenFablab, by evaluating its environmental impact when setting up a short plastic recycling circuit.
+- Application on a case study, the Green Fablab, by evaluating its environmental impact when setting up a short plastic recycling circuit.
 
@@
 
-### Ecosystem Services as a boundary object for sustainability
+class: middle
 
----
+### Ecosystem Services as a **boundary object** for sustainability
 
-### Systems Dynamics
+.pull-left[
 
----
+In that sense, Our focus is towards becoming an explicit management tool:
 
-## Distributed recycling via additive manufacturing (DRAM)
-Technical system
+- Creating Systems, Normative and Transformative knowledge using as case study distributed recycling
 
-.center[![:scale 75%](figures/Green-fablab-0.png)]
+- better interdisciplinary knowledge integration, greater focus on normative knowledge, and improved recognition of the ecosystem services concept as a potential transformative tool.
+
+]
+
+.pull-right[
+```{r, out.width = '90%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Ecoservices/Abson2014-00.jpg'))
+```
+]
 
 .footnote[
-Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
-Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy.
-J.
-Clean.
-Prod.
-264, 121602.
-https://doi.org/10.1016/j.jclepro.2020.121602
+Abson, D.J., von Wehrden, H., Baumgärtner, S., Fischer, J., Hanspach, J., Härdtle, W., Heinrichs, H., Klein, A.M., Lang, D.J., Martens, P., Walmsley, D., 2014.
+Ecosystem services as a boundary object for sustainability.
+Ecol.
+Econ.
+https://doi.org/10.1016/j.ecolecon.2014.04.012
 ]
@@
 
-## Distributed recycling via additive manufacturing (DRAM)
-Technical system --> Global system
+class: top, left
+background-image: url(`r paste0(URL, 'Ecoservices/Vanderwilde2021-01.jpg')`)
+background-position: 290px 0px
+background-size: 75%
 
-.center[![:scale 75%](figures/DRAM-05.png)]
+### We look to connect <br> Ecosystem services and LCA
+
+Hoping to contributing in <br> sustainability uncertainties.
+
+.footnote[
+Vanderwilde, C.P., Newell, J.P., 2021. Ecosystem services and life cycle assessment: A bibliometric review. https://doi.org/10.1016/j.resconrec.2021.105461 <br>
+Diwekar, U., Amekudzi-Kennedy, A., Bakshi, B., Baumgartner,et al, 2021.
+A perspective on the role of uncertainty in sustainability science and engineering.
+Resour.
+Conserv.
+Recycl.
+164, 105140.
+https://doi.org/10.1016/j.resconrec.2020.105140
+]
+
+---
+
+### Systems Dynamics of DRAM
+
+Technical system --> Global *system* embedded in a *territory*!
+
+```{r, out.width = '90%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'DRAM/DRAM-Territory-00.jpg'))
+```
 
@@
 .pull-left[
-![](figures/DRAM-07.png)
+```{r, out.width = '100%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'DRAM/DRAM-08.png'))
+```
+
 ]
@@
 - Establish and evaluate scenarios in a systemic and dynamic way
-- Evaluate the influences of the main operating variables on the system
+- Evaluate the influences of the main operating variables on the system taking ecosystem services boundaries
 - Taking into account the priorities of the multiple stakeholders
@@
 
-# Delivrables
+# Delivrables & Valorisations
 
@@
 
----
-
-# Valorisations
-
-- Method and prototype of a tool for the evaluation of local impacts of circular production systems
+- Method and [**prototype of a tool**](https://fabbiocrux.github.io/everest-bio-tool/) for the evaluation of local impacts of circular production systems
 

### 2021-04-12 slides/index.Rmd
final

@@
 institute: "CREIDD, ERPI"
-date: "2020/11/18 (updated: `r Sys.Date()`)"
+date: '2020/11/18 (updated: `r Sys.Date()`)'
 output:
@@
     css: ["default"]
+    seal: false 
     nature:
@@
 ```
+
+---
+
+class: title-slide, left, middle
+background-image: url(`r paste0(URL, 'Everest-bio/logos/Logos.png')`)
+background-position: 0px 0px
+background-size: contain
+
+# `r rmarkdown::metadata$title`
+
+## `r rmarkdown::metadata$subtitle`
+
+### `r rmarkdown::metadata$author`
+
+### `r rmarkdown::metadata$date`
 
@@
 
+---
+
+class: middle, left
+background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
+background-position: center
+background-size: contain
+
+---
+class: middle
+
+# EU projects
+
+.pull-left[
+```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
+```
+https://www.smagrinet.eu/
+
+```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
+```
+
+https://digiterri.eu/
+
+] 
+.pull-right[
+
+```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
+```
+
+https://www.inedit-project.eu/
+]
+
+---
+
 class: middle, center

### 2021-04-12 slides/index.Rmd
final

@@
 ```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Pavlo.jpg'))
+```
+
 ]

### 2021-04-12 01-Sustainable-Indicators/ES-Literature/ES-presentation.Rmd
presentation

---
title: "Everest Bio"
subtitle: "Ecosystem services for Distributed recycling via Additive Manufacturing"  
author: 
  - "Fabio CRUZ"
  - ""
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)
# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

#library(xaringanBuilder)
#build_pdf("ES-presentation.Rmd")

```

```{r, include=FALSE, echo=FALSE}
# CSS for the CSS
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
```

class: title-slide, right, middle
background-position: left
background-size: contain

.pull-right[

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author`

### `r rmarkdown::metadata$date`
]

---

# Agenda

1. Ecosystem Services 
2. ES and Distributed Recycling
3. Tool

---

# Definition

---

## Types of ES

--
## Barriers and complexities of ES
- Adoption of ES in decision-making processes, for example data availability and accuracy, and lack of resources (time, competences, and money) to produce the assessments [@Longato2021]
- “the multiple and overlapping scales of ES” in a plan at the urban scale, considering also that ES knowledge is not always easily translatable into specific spatial units

### 2021-04-12 03-Sustainable-behaviour.Rmd
presentation

--- 2021-01-19 03-comportements.Rmd
@@
     orcid_id: 0000-0003-3867-2438 
-
+always_allow_html: true        
 ---
@@
 require(widgetframe)
+```
+
+```{r, include=FALSE}
+
+#library(rticles)
+#library(rmarkdown)
+#render("03-Sustainable-behaviour.Rmd", output_format = "word_document", output_dir = "03-Sustainable-behaviour")
+
+#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document", output_dir = "01-Sustainable-Indicators")
+#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article", output_dir = "01-Sustainable-Indicators")
+
 ```

### 2021-04-12 docs/01-Sustainable-Indicators/ES-Literature/ES-Literature.Rmd
presentation

---
title: "Literature review on Ecosystem services for Distributed Recycling"
output:
  html_document:
    toc: no
    toc_float: yes
    keep_md: yes
permalink: /competences/
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
library(tidyverse)
library(revtools)

```

## Initial database for Screening

```{r Screening.ES-Rec-Plast }
Screening <- read_bibliography("Scopus/ES-Rec-Plast.csv")
# Screening
screen_abstracts(Screening)
```

## Screened
```{r data, include=FALSE}

# Filter the selected documents and changing the names. Made on 30/03 -----
# Reading data
Screened <- read_csv("Scopus/ES-Rec-Plast.csv")

# names(Screened)
# Screened <- Screened %>% filter(screened_abstracts == 'selected') %>% 
#   rename(
#     screened_abstracts_i = screened_abstracts,
#     notes_i = notes
#     )
# write_csv(Screened, file = 'Scopus/ES-Rec-Plast-Screened.csv')

# Re-Screening for selecting the best for Ecosystem Service ----
Screened <- read_bibliography('Scopus/ES-Rec-Plast-Screened.csv')
screen_abstracts(Screened)

Screened$notes
```

```{r}

Screened <- read_bibliography("Scopus/ES-Rec-Plast.csv")
Screened %>% group_by(document_type) %>% tally()
```

### 2021-09-03 00-ES/Article/Draft.Rmd
ordenando el zafarrancho

---
title: "Distributed recycling for additive manufacturing: an ecosystem services perspective "
documentclass: extarticle
fontsize: 14pt
geometry: "left=3cm, right=2cm,top=2.5cm,bottom=2cm"
output: 
  bookdown::pdf_document2:
    toc: false
  #   keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
# abstract
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
#options(tinytex.engine_args = '--shell-escape')

library(readxl)
library(here)
library(tidyverse)
library(flextable)
library(rsvg)
set_flextable_defaults(fonts_ignore=TRUE)

#URL for Figurs
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

```

\linenumbers
\onehalfspacing

# Introduction

<!-- DRAM -->
Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management. 
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
However, as with any recycling system, its feasibility must be evaluated before its implementation. Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain. Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory. 
The purpose of this research is to identify the the set of principles, criteria and indicators from ecosystem services framework, that can be associated to distributed recycling approach, evaluating their pertinence in the local impact in terms of availability of data. 
The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.

This study seeks to address the following questions: 
- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?

While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches. 
Main tasks in this research include a systematic literature review of ecosystem services in recycling field, and the creation of a database and online tool to map these element in the local territory.

# Background

<!--# Intro -->
Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2009]. 
Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@ref].
Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].

<!--# Definition of Ecosystem Services -->
Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017]. Ecosystem goods (e.g; Food) and services (e.g. waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997]. 
  <!--# Functions vs Services -->
It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself. The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits. 
By contrast, the latter are those processes and functions where people can (or could have the potential [@ref]) obtain benefits. The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach. Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@ref]. 
One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003]. This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders [@Honeck2021].

<!--# Classification of ES -->
Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
The Economics of Ecosystems and BiodiversityTBB [@ref],
THe Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES) . 
In the heart of the four main, they share four main categories of ES:
**Provisioning** (e.g. food and medicines); 
**Regulating** (e.g. pollination and climate regulation), 
**Supporting** (e.g soil formation and fixation of solar energy) and 
**Cultural / Information** services (e.g. artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].

<!--# Strong sustainability and ES -->
Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital [@Costanza1997] and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework [@Bruel2016].
  <!-- Strong sustainability -->
From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it [@Ekins2003].
More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of *critical* components that make a major contribution to welfare.
  <!--# Main environmental issue -->
The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience [@Ekins2003].

  <!-- CICES -->
The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref]. 
In CICES framework, @Potschin argued the conceptual framework of cascading aspect from ecosystesm service tos of the and are commonly divided into 
@Mustajoki2019

<!-- \begin{landscape} -->
```{r table-CICES, include=FALSE}
# From the CICES intial
CICES <- read_excel(here("tables/CICES.xlsx"), sheet = "CICES V5.1",  skip = 4 )
CICES <- CICES %>% filter(Filter == "CICES" ) %>% select(Section,Division, Group, Class,`Class type`)

CICES %>% flextable() %>%
  set_caption("CICES ") %>%
  #autofit() %>% 
  width(j=1:5, width = c(1, 1, 2, 2, 2)) %>% 
  fontsize(size=10, part = "all") %>% 
  #fit_to_width(max_width = 8) %>% 
  merge_v(j = c("Section", "Division",  "Class type")) %>% #"Group", "Class",
  theme_booktabs()

#names(CICES)
```
<!-- \end{landscape} -->

<!--  Research themes in ES -->
Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field. Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.

Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies. Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.

<!-- Importance of ES in the decision making process -->
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers. It is difficult to provide information about pressure from industrial systems in corporate information systems. EE uses valuation techniques to reveal the value of nature and develops ways to overcome the current technical and ethical challenges to valuation, for example, by broadening the dominant monetary perspective on the value of nature by nonmonetary and deliberative approaches influence decision makers.

- Hoy en dia es necesario tener en cuenta no solo un factor technic-econonomic en el momento de evaluar soluciones en amount. Tambien, es necesario estavlecer cuales serain las implicationes y los impactos para el territoirio desde el punto de vista de servicios ecosistemicos

## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.

<!-- Importance of ES in the Engineering -->
The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
  <!-- Engineering blindness -->
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal. This scenario is not true today.
  <!-- Engineering withing ecological constraints -->
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@ref].
  <!-- MEA and Planeatry results -->
According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
  <!-- Causas of exceeding Planeatry boundaries -->
Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions [@Liu2019g].
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
<!-- Purpose of strong sustainability -->
Ideally, it is needed to (re)designed industrial activites to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016]. 
  <!-- Expand boundaries of Engineering -->
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].

<!-- Sustainability frameworks -->
@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level. 
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
<!-- They hightligthed that differens Systemic design approaches are   -->
  <!-- TES -->
@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
This theoretical framework aims to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g. for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

relies on the idea of TES and develops ways of enhancing synergies between a local scale manufacturing process and the land around it.

The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing. 
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not

# Methodology

The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filière considering the technological and ecological spheres.

Four steps were proposed as illustrated in figure XX .

  <!-- Step 1 Assessments-->
The goal of *Asessments* step is to identify the bounddaries for the technoological and ecological systems to be evaluated.
  <!-- Step 2 Plannig-->
In the *Planning* step, the main aim is to jeopordize the key ecosystems services and the respective scales that are going to be included in the analysis. 
These elements will be a intersection of the technological and geographihcal issues based on a analysis of each systems.
  <!-- Step 3 Evaluate-->
In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
  <!-- Step 3 Management-->
Finally, ini the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.

An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
In the following sub-sections, each stage of the methodology is explained.

```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='80%'}

#library(magick)
#image_write(image_read_svg(img_url,  width = 350), path = "Figures/Methodology.jpeg", format = "jpeg")

# img_url <- paste0(URL, 'Everest-bio/Methodology.svg')
# rsvg_pdf(img_url, "Figures/Methodology.pdf")

knitr::include_graphics('Figures/Methodology.pdf')
```

## Assessment

### Definition of the Tech- and Eco- Spheres

It is needed to define two types of boundaries: technological and ecological.
<!-- Technological -->
Regarding the technological sphere, it involves choosing the human activites that can be a single process, life cycle, or economic network.
Concerning the ecological sphere, it relies on specifying the geographical regions that the activity is implemented.

# Case study: Distribuuting recycling via Additive Manufacturing
## Indicators in Ecosystem Services Distributed recycling The

\newpage

# References

### 2021-09-03 00-ES/ES-Literature/ES-Literature.Rmd
ordenando el zafarrancho

---
title: "Literature review on Ecosystem services for Distributed Recycling"
output:
  html_document:
    toc: no
    toc_float: yes
    keep_md: yes
permalink: /competences/
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
library(tidyverse)
library(revtools)
library(readxl)
```

## Initial database for Screening

```{r Screening.ES-Rec-Plast }
Screening <- read_bibliography("Scopus/ES-Rec-Plast.csv")
# Screening
screen_abstracts(Screening)

```

## Screened
```{r data, include=FALSE}

# Filter the selected documents and changing the names. Made on 30/03 -----
# Reading data
Screened <- read_csv("Scopus/ES-Rec-Plast.csv")

names(Screened)
Screened <- Screened %>% filter(screened_abstracts == 'selected') %>%
  rename(
    screened_abstracts_i = screened_abstracts,
    notes_i = notes
    )
#write_csv(Screened, file = 'Scopus/ES-Rec-Plast-Screened.csv')
# ---- Document exported on 19 July ---
# write_csv(Screened %>% select(label,title, abstract, doi, notes_i) , "Scopus/Screened-WD.csv")

names(Screened)

# Re-Screening for selecting the best for Ecosystem Service ----
Screened <- read_bibliography('Scopus/ES-Rec-Plast-Screened.csv')
screen_abstracts(Screened)

Screened$notes
```

## CICES V 5.1

```{r}
library(readxl)
library(here)
library(yaml)
library(xlsx)
library(tidyverse)

CICES <- read_excel(here("CICES/Finalised-V5.1_18032018.xlsx"), sheet = "CICES V5.1",  skip = 4 )
names(CICES)

Test <- CICES %>% select(Division, Group, Class, Code, `Class type`, `Simple descriptor`)
#write_yaml(V1, "GF/CICES-GF.yml")

# Ordering the Factors
Test <- Test %>%
  mutate(Division = factor(Division, Test %>% pull(Division) %>% unique())) %>% 
  mutate(Group = factor(Group, Test %>% pull(Group) %>% unique()))

Divisiones <- Test$Division %>% levels()
Grupos <- Test$Group %>% levels()

Total_preguntas <- Test %>% group_by(Division,Group) %>% tally()
#Encuesta <- list(Test$Division %>% levels())
```

```{r}
# Biomass
Preguntas <- 
  Test %>% 
  filter(Division == Divisiones[4]) %>% 
  filter(Group == Grupos[11]) 
Preguntas

paste(Preguntas$`Code`, Preguntas$`Simple descriptor`, sep = ", ")

```

### 2021-09-03 00-ES/ES-Literature/slides/Eco-Services.Rmd
ordenando el zafarrancho

---
title: "Everest Bio"
subtitle: "Ecosystem services for Distributed recycling via Additive Manufacturing"  
author:
- "Fabio CRUZ"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
#      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      navigation:
        scroll: false # disable slide transitions by scrolling      
---

```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanExtra)
library(xaringanthemer)

```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE,
  include = TRUE
)

# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

#library(xaringanBuilder)
#build_pdf("ES-presentation.Rmd")

# xaringanExtra
xaringanExtra::use_panelset()
```

```{r xaringan-themer, include=FALSE, warning=FALSE}

style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF", 
  base_font_size = "24px",
  colors = c(
    red = "#f34213",
    purple = "#3e2f5b",
    orange = "#ff8811",
    green = "#d9edc2",
    white = "#FFFFFF",
    grey = "#F5F5F5"
  ),
   extra_css = list(
    ".remark-slide-content h1" = list(
      "margin-bottom" = 0, 
      "margin-top" = 0),
     ".remark-slide-content > h1:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content > h2:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content > h3:first-of-type" = list(
       "margin-top" = "5px",
       "margin-bottom" = "10px"
     ),
    ".remark-slide-content" = list (
        "padding-top" =  "25px",
        "padding-left" =  "50px",
        "padding-right" =  "50px",
        "padding-bottom" =  "25px"
    ),

    ".small" = list("font-size" = "90%"),

    ".Large , .Large .remark-code, .Large .remark-inline-code" = list("font-size"= "144%"), 
    ".large , .large .remark-code, .large .remark-inline-code" = list("font-size"= "120%"), 
    ".small , .small .remark-code, .small .remark-inline-code" = list("font-size"= "90%"), 
    ".footnotesize, 
    .footnotesize .remark-code, .footnotesize .remark-inline-code" = list( "font-size"= "80%"),

    ".scriptsize , .scriptsize .remark-code, .scriptsize .remark-inline-code" = list("font-size"= "70%"),
    ".tiny , .tiny .remark-code, .tiny .remark-inline-code" = list("font-size"= "60%"),

    ".footnote" = list (
        "position" =  "absolute",
        "bottom" =  "0",
        "padding-right" = "8em", # to avoid the page numbering 
        "font-size" =  "60%"
    ),
    ".fn" = list(
      "vertical-align" = "super",
      "font-size" = "60%",
      "color" = "purple"
    )

  )
)

```

## Research Question at Everest Bio

- How to develop a generic methodology to assess the **ecosystem services** (ES) rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors?

### Goals:

- .large.bg-green[To propose and validate indicators to be used for the evaluation of ES of a production activity, and for a short circuit operation.]

.tiny[

- Propose a protocol for collecting and structuring the data and information necessary to evaluate a particular case, instrumented in a digital tool for data processing and impact assessment.

- Develop an evaluation model of the operational conditions allowing the construction of evaluation scenarios of an activity or industrial sector in a given context.

- To apply the developed model to the case of short circuit recycling of plastics. Validation and feedback to take into account the specific conditions of the local context.

]

---

# Agenda

1. Ecosystem Services + Tool (prototype)
2. Fedoua and territorial
3. Point Cristian

---

class: inverse center middle

# Ecosystem services

---

# Methodology

Explorative search (as using systematic literature approach)

- **Database**: Scopus
- **Filters**: Title, Abstract and Keywords
- **Search Equation**: "ecosystem services AND recycl*"
- **Quantity of Articles**:  542 referencias
- **Date of search**: February 10 /2021
- **Criteria**:
  - On ecosystem services theory
  - Examples (eventually in recycling)
  - Papers could be useful for Everest Bio

---

class: top left
background-image: url('figures/ES-Rec.png')
background-position: 100% 50%
background-size: 60%

## Definitions

- *Ecosystem process:*

- *Ecosystem Functions*

- *Ecosystem Services*

*- Goods and Services*:

---

## Ecosystem function <br> & Services

.small.pull-left[

>**Ecosystem functions** refer variously to the habitat, biological or system properties or processes of ecosystems. <br>
Ecosystem functions as **'the capacity of natural processes and components to provide goods and services that satisfy human needs, directly or indirectly'**.fn[1] 
]

.footnote[
1. Costanza, R., D’Arge, R., de Groot, R., Farber, S., Grasso, M., Hannon, B., Limburg, K., Naeem, S., O’Neill, R. V., Paruelo, J., Raskin, R.G., Sutton, P., van den Belt, M., 1997. The value of the world’s ecosystem services and natural capital. Nature 387, 253–260. https://doi.org/10.1038/387253a0
]

---

class: top, left, middle
background-image: url(`r paste0(URL, 'Ecoservices/MEA2005-00.jpg')`)
background-position: right
background-size: 55%

.pull-left[
Ecosystem Services  consist of <br> **flows of materials, energy, and <br> information from .bg-green[Natural capital stocks] which combine with manufactured and human capital services to produce human welfare**.fn[1]

]

.footnote[
1. Costanza, R., D’Arge, R., de Groot, R., Farber, S., Grasso, M., Hannon, B., Limburg, K., Naeem, S., O’Neill, R. V., Paruelo, J., Raskin, R.G., Sutton, P., van den Belt, M., 1997. The value of the world’s ecosystem services and natural capital. Nature 387, 253–260. https://doi.org/10.1038/387253a0
]

---

class: top, left
background-image: url(`r paste0(URL, 'Ecoservices/Natural-capital.png')`)
background-position: 100% 20%
background-size: 55%

## Natural capital

.pull-left[

Stock of renewable and non-renewable natural resources (materials/manufactured/information) available to society.

Each form of capital stock generates, either autonomously or in conjunction with services from other capital stocks, a flow of services that may be used to transform materials, or the spatial configuration of materials, to enhance the welfare of humans.

**The human use of this flow of services may or may not leave the original capital stock intact**

]

.footnote[
Components of natural capital, developed from the natural capital figure in the EU MAES report on Mapping and assessment of ecosystems and their services (European Commission, 2013).
]

---

class: top, left, middle
background-image: url(`r paste0(URL, 'Ecoservices/Torres2021-00.jpg')`)
background-position: right
background-size: 80%

.bg-grey.Large[8 Key themes and <br> 22 Approaches <br> (Tools, Frameworks, <br>Management, Perspectives)]

.small[Publications identified <br> (n = 27,628)]

.footnote[
1. Torres, A.V., Tiwari, C., Atkinson, S.F., 2021. Progress in ecosystem services research: A guide for scholars and practitioners. Ecosyst. Serv. 49, 101267. https://doi.org/10.1016/j.ecoser.2021.101267
]

---

class: left, bottom
background-image: url(`r paste0(URL, 'Ecoservices/Torres2021-01.jpg')`)
background-position: center top
background-size: 80%

- Computational modelling and non-monetary valuation are considered *emergent topics*.

---

## Typologies of ES:

1. **Regulation functions:** Functions relates to the capacity of natural and semi-natural ecosystems to regulate essential ecological processes and life support systems through bio-geochemical cycles and other biospheric processes. In addition to maintaining ecosystem (and biosphere) health, these regulation functions provide many services that have direct and indirect benefits to humans (such as clean air, water and soil, and biological control services).

2. **Habitat functions:** natural ecosystems provide refuge and reproduction habitat to wild plants and animals and thereby contribute to the (in situ) conservation of biological and genetic diversity and evolutionary processes.

3. **Production functions:** Photosynthesis and nutrient uptake by autotrophs converts energy, carbon dioxide, water and nutrients into a wide variety of carbohydrate structures which are then used by secondary producers to create an even larger variety of living biomass. This broad diversity in carbohydrate structures provides many ecosystem goods for human consumption, ranging from food and raw materials to energy resources and genetic material.

4. **Information functions:** Because most of human evolution took place within the context of undomesticated habitat, natural ecosystems provide an essential ‘reference function’ and contribute to the maintenance of human health by providing opportunities for reflection, spiritual enrichment, cognitive develop- ment, recreation and aesthetic experience.

---

layout: true

## Benchmarking of Tools

---

### InvEST & SolVES

The two major tools used to assess ecosystem services quantitatively are the Integrated
Valuation of Ecosystem Services and Trade-offs (**InVEST**) and the Social Values for Ecosystem a toolkit for mapping natural capital and ecosystem services in the UK Resources (**SOLVES**)[@Zhang2019g]

.pull-left[
```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/tools/InVEST.png'))
```

https://github.com/natcap/invest

]

.pull-right[
```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/tools/SolVES-00.png'))
```

[SolVES website](https://www.usgs.gov/centers/gecsc/science/social-values-ecosystem-services-solves#:~:text=Ecosystem%20services%20are%20the%20benefits,contribute%20to%20human%20well%2Dbeing.&text=SolVES%20is%20designed%20to%20assess,social%20values%20of%20ecosystem%20services.)

]

.footnote[Zhang, X., Estoque, R.C., Xie, H., Murayama, Y., Ranagalage, M., 2019. Bibliometric analysis of highly cited articles on ecosystem services. PLoS One 14, e0210707. https://doi.org/10.1371/journal.pone.0210707
]

---

### EcoservR, NEVO, ARIES

.pull-left[
```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/tools/EcoservR-01.png'))
```
https://ecoservr.github.io/EcoservR/basemap
https://github.com/ecoservR/ecoserv_tool
]

.pull-right[

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/tools/NEVO.png'))
```

https://ecosystemsknowledge.net/NEVO

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/tools/ARIES.png'))
```

https://ecosystemsknowledge.net/aries

]

These tools are focused on UK!

.footnote[
Ecosystems Knowledge Network: https://ecosystemsknowledge.net/tool/mapping

]

---

layout: true

## Benchmarking of EU Projects

---

### OpenNESS

Integrating methods for ecosystem service assessment: Experiences from real world situations

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/EU/OpenNESS.png'))
```

http://www.openness-project.eu/

Case studies nature-based solutions  **Bayesian networks + ES** --> http://openness.hugin.com/

Roy Haines-Young and Marion Potschin. They worked in the development of CICES

.footnote[
Dunford, R., Harrison, P., et al, 2018. Integrating methods for ecosystem service assessment: Experiences from real world situations. Ecosyst. Serv. 29, 499–514. https://doi.org/10.1016/j.ecoser.2017.10.014
]

---

layout: false

## CICES V5.1

Towards a Common International Classification of Ecosystem Services (CICES) for Integrated Environmental and Economic Accounting

```{r, out.width = '800px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Ecoservices/CICES/CICES.png'))
```

---

## Barriers and complexities

- Adoption of ES in decision-making processes, for example data availability and accuracy, and lack of resources (time, competences, and money) to produce the assessments .fn[@Longato2021]

- "the multiple and overlapping scales of ES" in a plan at the urban scale, considering also that ES knowledge is not always easily translatable into specific spatial units

- The **Waste-Resource Paradox**: Practical dilemmas and societal implications in the transition to a circular economy .fn[@Greer2021]
.small[

- Material: Closing a material loop, which incentivizes overproduction
- Energy: Reducing plastic waste, which requires a new high energy demand to be processed
- Economic: Creating new use for an old waste, which may result in a potential commodification ofwaste and a new market barrier for circular SMEs
- Social: Secondary material recovery, at a cost to human health
  ]

.footnote[
- Longato, D., Cortinovis, C., Albert, C., Geneletti, D., 2021. Practical applications of ecosystem services in spatial planning: Lessons learned from a systematic literature review. Environ. Sci. Policy 119, 72–84. https://doi.org/10.1016/j.envsci.2021.02.001

- Greer, R., von Wirth, T., Loorbach, D., 2021. The Waste-Resource Paradox: Practical dilemmas and societal implications in the transition to a circular economy. J. Clean. Prod. 303, 126831. https://doi.org/10.1016/j.jclepro.2021.126831
]

---

class: inverse center middle

# Prototyping the tool

---

## Definitions

According to CICES V5.1:  is built on the principle that a classification of services needs to describe the contribution that ecosystems make to human well-being, defined in terms of ‘what ecosystems do’.
Thus, in the classification the definition of a service needs to highlight the ecological outcomes that particular ecosystem characteristics or processes generate, that can ultimately benefit people. The aim has therefore been to build a classification that identifies the purposes or uses that people have for the different kinds of ecosystem service and associate them with the particular ecosystem attributes or behaviours that support them

---

# Valorization of SE

---

# Strong and Weak Sustainability

Strong: Coming from Ecological rationality

>The capital is not sustiable, nor reemplazable, interchangable by the financial capital of the physical capital.

Weak: Coming from Economical rationality

### 2021-09-08 00-ES/Article/Draft.Rmd
Proposition on the methodology

@@
 fontsize: 14pt
-geometry: "left=3cm, right=2cm,top=2.5cm,bottom=2cm"
+#geometry: "left=3cm, right=2cm,top=2.5cm,bottom=2cm"
 output: 
@@
   \usepackage{setspace}
+  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
 
@@
 \linenumbers
-\onehalfspacing
+<!-- \onehalfspacing -->
 
@@
 <!-- Purpose of strong sustainability -->
-Ideally, it is needed to (re)designed industrial activites to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
+Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
   <!-- Expand boundaries of Engineering -->
@@
 
-Four steps were proposed as illustrated in figure XX .
+Four major steps are proposed as illustrated in figure XX .
 
   <!-- Step 1 Assessments-->
-The goal of *Asessments* step is to identify the bounddaries for the technoological and ecological systems to be evaluated.
+The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
   <!-- Step 2 Plannig-->
-In the *Planning* step, the main aim is to jeopordize the key ecosystems services and the respective scales that are going to be included in the analysis. 
+In the *Assessment* step, the main aim is to jeopordize the key ecosystems services and the respective scales that are going to be included in the analysis. 
 These elements will be a intersection of the technological and geographihcal issues based on a analysis of each systems.
@@
   <!-- Step 3 Management-->
-Finally, ini the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
+Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
 This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
@@
 
-```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='80%'}
+```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht'}
 
@@
 
-## Assessment
+## Planning
 
-### Definition of the Tech- and Eco- Spheres
+It is needed to define two types of scopes: technological and ecological.
 
-It is needed to define two types of boundaries: technological and ecological.
+```{r Terminology}
+Terminology <- read_csv2("tables/Terminology.csv")
+# Terminology <-  table_1 %>%  set_names(" ", "PLA", "Recycled PLA")
+
+#std_border = officer::fp_border(color="orange", width = 1)
+
+Terminology %>% flextable() %>%
+  set_caption("Terminology used in the deifnition of the spheres") %>%
+  width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
+  theme_booktabs() %>% 
+  hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
+  padding(padding = 0)
+
+```
+
+### Definition of the Tech-Sphere
+
 <!-- Technological -->
-Regarding the technological sphere, it involves choosing the human activites that can be a single process, life cycle, or economic network.
-Concerning the ecological sphere, it relies on specifying the geographical regions that the activity is implemented.
+Regarding the technological sphere, three scales are analysed: *Equipment*, *Value chain* and *Economy* scales.
+  <!-- Equipment -->
+The technological system at the equipment scale is represented as $T_{i,j}$ which consists of the *i-th* facility for the *j-th* technological activity. 
+For example, in the case of a specific technological activity ($j = 1$) such as corn farming, $T_{1,1}$ and $T_{1,1}$ represent two different facilities or farms for this activity. 
+  <!-- Value chain -->
+Technological systems at the value chain scale are indicated as $\underline{T_{j}}$.
+These represent average value chain activities within a region, whose information is generally available from inventory databases.
+  <!-- Economy -->
+Technological systems at the economy scale are represented as $\doverline{T_{j}}$.
+These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.
 
-# Case study: Distribuuting recycling via Additive Manufacturing
+In a given problem, the scales at which technologies systems should be modeled are determined based on whether the data are available and whether the activities are site-specific.
+
+### Definition of the Eco-sphere
+
+<!-- Intro -->
+Concerning the ecological sphere, it relies on specifying the geographical regions where the activity is implemented. 
+  <!-- GOal -->
+The main aim is to include explicitly the ecosystem goods and services, and the ecosystem itself in the system boundary. 
+Thus, interactions within and between technological and ecological systems can be integred explicitly, enabling the assessment of regional variation and absolute environmental sustainability regarding each ES considered.
+
+<!-- Procedure for the three levels -->
+In this step requires information about ecosystems in which the selected technological systems are nested. 
+Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.   <!-- Specification at Equipment scale -->
+The ecosystem local to $T_{i,j}$ is represented by $E_{i,j}$.
+For example, this could be the campus around a manufacturing facility or an agricultural farm.
+
+<!-- Value chain scale -->
+At the *value chain* scale, the "local ecosystem" for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
+The averaged local ecosystem can be justified as the general landscape characteristics around the specific activity.
+For instance, electricity generation from coal-fired power plants needs a large amount of water for cooling: thus, it is likely that these facilities are located close to water sources.
+
+Likewise, the local ecosystem for an *economic scale* may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as $\overline{E}_{j}$.
+The aggregation relationships between activities and their surrounding ecosystems at various scales have been depicted by the dotted lines in figure XX.
+
+#### Scope of Ecosystems Serviceshed
+
+The largest ecological scale that needs to be considered varies according to the type of ES. 
+The "largest ecological scale" is analogous to the concept of a “serviceshed” in the ES literature [@Liu2019g].
+
+It is indicated by outer circles in figure X. 
+The notation used is $E^{*}_{i,j,k}$ to represent the serviceshed for the $k-th$ ES, in which the $i-th$ facility of the $j-th$ technological activity is nested.
+
+For example, due to the global flow of $CO_{2}$, the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else. 
+Thus, the largest ecological scale to evaluate the carbon sequestration ES is the global scale. 
+In contrast, criteria air pollutants, such as $SO_{2}$ and $NO{x}$ can only be transported and regulated by ecosystems within a narrower geographic boundary. 
+Thus, the largest ecological scale to evaluate air quality regulation service is the regional scale. 
+Larger ecological scales, such as a global scale, may not be relevant to this service.
+
+If facilities $T_{1,n}\dots,T_{m,n}$ are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity $\underline{T}_{n}$.
+Although such averaging implicitly assumes substitutability by implying that ES produced in one serviceshed can be used by beneficiaries in another serviceshed, this average may have to be used in the absence of spatial information at the serviceshed or smaller scales.
+The average serviceshed is denoted as $\underline{E}^{*}_{j,k}$ for value chain activities and $\overline{E}^{*}_{j,k}$ for economic activities.
+
+## Assesstment of Demand and Supply for key ES
+
+### Inventory of the Technological Systems
+
+<!-- Intro -->
+Consider a situation where a production flowsheet for an existing or new process is already available.
+A preliminary assessment of these environmental interventions must be carried out to obtain information about the different types of demands created by manufacturing facilities, and the kind of ecosystems that can supply these services to satisfy the demand.
+
+@Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
+It represents the total amount of ES needed to  mitigate the emission or atisfy the resource use?
+For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.
+
+Environmentally-extended input-output (EEIO) data for activities at equipment, value chain and economy scale, LCI databases, and  detailed engineering models can supply information to quantify the respective demand for each service.
+Also, inventory of technological systems comprises all relevant flows associated with the functional unit, regardless of the scale at which technological activities are modeled.
+
+### Inventory of the Ecological Systems
+
+<!-- Intro to problem of LCA -->
+Usually, Life cycle analysis  do not integrate explicitaly models and data about ecosystem goods and services [@ref]
+Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.
+
+The main object is to establish the ability of of ecosystems to provide the demanded services. 
+For example, green plants supply the carbon sequestration service by taking up atmospheric $CO_{2}$ and sequestering it as organic matter through photosynthesis. 
+This can be understood as the dependence of production systems on ES. 
+Alternatively, it can be interpreted as the ES that nature can supply in order to produce the functional unit.
+
+<!-- Establish ecological models -->
+There is a research efforts to establish the knowledge about the supply of ES using ecological models such as 
+  <!-- Ecological models -->
+i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas (USEPA
+
+- to complete the different odels for each ES?
+- More references on this
+
+### Allocation
+
+One key point is determining the allocation of each ES for multiple users in a selected servicehed.
+<!-- Strategies of allocation -->
+Two possible allocation strategies are proportional or avoid allocation [@ref].
+
+  <!-- Proportional -->
+Proportional allocation splits the ES supply according to selected quantities such as population, demand, or money.
+  <!-- Avoided -->
+Avoided allocation only considers total demand and supply of an ES within the serviceshed.
+
+  <!-- Explaining proportional -->
+Proportional allocation can face similar challenges as allocation between multiple co-products in conventional LCA. 
+Allocating an ES between multiple users is analogous to determining their right of use. Two ethics of interpreting this are as follows:
+
+- *Private ownership* implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed. 
+For calculating ES supply under a private ownership scenario, land ownership information within the serviceshed is needed
+
+- *Public ownership* implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership. 
+This approach allocates all ES supply from the serviceshed based on the selected properties of the users. 
+If allocation is done in proportion to the demand of ES, the resulting metric is identical to that of the avoided  allocation approach.
+
+However, there could be practical issues with this land ownership based allocation of ES are the public availability of land ownership data and the possible applicability of other ES ownership schemes.
+
+  <!-- Conclusion -->
+Proportional allocation can provide local sustainability metrics; while for avoided allocation, all activities in a selected serviceshed are assumed to have identical sustainability metrics.
+
+## Evaluation
+
+###Impact Assessment
+
+In this step, the echno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
+Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
+For the k-th ES, the sustainability metric $V_{k}$ is:
+
+$$
+V_{k} = \frac{S_{k} - D_{k}}{D_{k}}
+$$
+
+where, $S_{k}$ and $D_{k}$ are the supply and demand of the $k-th$ ES, respectively.
+
+The basic results from TES consist of  of pairs of numbers ${D}$
+
+This metric indicates the extent to which the technological activity is within the relevant ecosystem’s carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
+Absolute environmental sustainability for the $k-th$ ES is defined at the serviceshed scale (indicated by $^{*}) :
+
+$$
+V_{k}^{*} \geq 0, \forall k
+$$
+
+Strong sustainability requires satisfaction of this criterion in the corresponding servicesheds for each ES. 
+If metrics are calculated for the average serviceshed, then satisfaction of equation (2) suggests only weak sustainability, since it implicitly assumes that the absolute environmental sustainability in one serviceshed can be used to compensate for unsustainability in another.
+Thus, the unsustainability in some servicesheds would be overlooked due to the averaging. 
+This problem would be potentially solved by disaggregating the average serviceshed and calculating the metrics for each component serviceshed separately. 
+However, this will require more data.
+
+###
+## Management
+
+# Case study: Distributing recycling via Additive Manufacturing
 ## Indicators in Ecosystem Services Distributed recycling The

### 2021-09-14 00-ES/Article/Draft.Rmd
version beta sent to Nadege

@@
 fontsize: 14pt
-#geometry: "left=3cm, right=2cm,top=2.5cm,bottom=2cm"
+geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
 output: 
   bookdown::pdf_document2:
-    toc: false
-  #   keep_tex: TRUE
+    toc: true
+    keep_tex: TRUE
     #pandoc_args: "--latex-engine-opt=--shell-escape"
@@
   \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
+  \usepackage{tabu}
 
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%')
 options(knitr.kable.NA = '')
@@
 
-<!-- DRAM -->
-Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management. 
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
-However, as with any recycling system, its feasibility must be evaluated before its implementation.
-Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
+<!-- Intro -->
+The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
+No country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
+Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
+We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.
 
-This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory. 
-The purpose of this research is to identify the the set of principles, criteria and indicators from ecosystem services framework, that can be associated to distributed recycling approach, evaluating their pertinence in the local impact in terms of availability of data.
-The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.
+<!-- Gap in the literature -->
+However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
+The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
+This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements. 
+  <!-- Case study -->
+As a case application, the study of distributed recycling manufacturing will be describe.
+Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
+Therefore, new approaches need to be explored in order to reduce ar at least recycling this material. 
+Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
 
-This study seeks to address the following questions: 
+The expected results seek to address the following questions:
+
 - What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
@@
 - What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory? 
+From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators   for deployments distributed recycling approach,
 
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-Main tasks in this research include a systematic literature review of ecosystem services in recycling field, and the creation of a database and online tool to map these element in the local territory.
+In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
+This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.
+
+\textcolor{red}{The article is structure as follows.... ( to complete) } section \@ref(background) ...
+
+<!-- The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.
+-->
 
 # Background
+\label{background}
+
+## Ecosystem services
 
 <!--# Intro -->
-Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2009].
-Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@ref].
+Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002].
+Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
 Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
@@
 
+<!--  Research themes in ES -->
+Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field.
+Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
+Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
+It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
+
+Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
+Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
+
 <!--# Classification of ES -->
 Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
-The Economics of Ecosystems and BiodiversityTBB [@ref],
-THe Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES) . 
+The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
+The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
 In the heart of the four main, they share four main categories of ES:
@@
 artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].
+
+```{r Fig:ES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
+# img_url <- paste0(URL, 'Everest-bio/ES')
+#download.file(paste0(URL, 'Everest-bio/ES/', 'Comparison.png'), "Figures/Comparison.png")
+# rsvg_pdf(img_url, "Figures/Methodology.pdf")
+
+knitr::include_graphics('Figures/Comparison.png')
+
+```
 
@@
 The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref].
-In CICES framework, @Potschin argued the conceptual framework of cascading aspect from ecosystesm service tos of the and are commonly divided into 
-@Mustajoki2019
+In CICES framework, @Potschin-Young2018 argued the conceptual framework of cascading aspect from ecosystesm service are  commonly divided Groups, division.
+<!-- @Mustajoki2019 -->
 
@@
 
+CICES %>% pull(Section) 
+names(CICES)
 CICES %>% flextable() %>%
@@
 
-<!--  Research themes in ES -->
-Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field.
-Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
-Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
+```{r Fig-ES-cices, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
+# img_url <- paste0(URL, 'Everest-bio/ES')
+# rsvg_pdf(img_url, "Figures/Methodology.pdf")
 
-Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
-Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
+knitr::include_graphics('Figures/cices.png')
 
-<!-- Importance of ES in the decision making process -->
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers.
-It is difficult to provide information about pressure from industrial systems in corporate information systems.
-EE uses valuation techniques to reveal the value of nature and develops ways to overcome the current technical and ethical challenges to valuation, for example, by broadening the dominant monetary perspective on the value of nature by nonmonetary and deliberative approaches influence decision makers.
+```
 
-- Hoy en dia es necesario tener en cuenta no solo un factor technic-econonomic en el momento de evaluar soluciones en amount.
-Tambien, es necesario estavlecer cuales serain las implicationes y los impactos para el territoirio desde el punto de vista de servicios ecosistemicos
+\textcolor{red}{to complete ... }
+
+## Distributed recycling via additive manufacturing
+
+<!-- DRAM -->
+Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management [@CruzSanchez2020; @Santander2020]. 
+The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
+To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
+While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
+However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
+<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
+Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
+
+\textcolor{red}{ To complete ...}
 
@@
   <!-- Engineering withing ecological constraints -->
+ The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
+ <!-- Importance of ES in the decision making process -->
+The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
+It is difficult to provide information about pressure from industrial systems in corporate information systems. 
 Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@ref].
+
   <!-- MEA and Planeatry results -->
@@
 <!-- Purpose of strong sustainability -->
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
+Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
   <!-- Expand boundaries of Engineering -->
@@
 @Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-This theoretical framework aims to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
+THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
 for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
 
-relies on the idea of TES and develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
+-->
+<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
+-->
 
-The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
-More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not
+\textcolor{red}{
+Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
 
@@
 
-Four major steps are proposed as illustrated in figure XX .
-
-  <!-- Step 1 Assessments-->
-The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
-  <!-- Step 2 Plannig-->
-In the *Assessment* step, the main aim is to jeopordize the key ecosystems services and the respective scales that are going to be included in the analysis. 
-These elements will be a intersection of the technological and geographihcal issues based on a analysis of each systems.
-  <!-- Step 3 Evaluate-->
-In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
-  <!-- Step 3 Management-->
-Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
-This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
-
-An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
-In the following sub-sections, each stage of the methodology is explained.
-
-```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht'}
+```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht', fig.align='center'}
 
@@
 
+Four major steps are proposed as illustrated in figure \@ref(Fig-Methodology) .
+
+  <!-- Step 1 Assessments-->
+The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
+  <!-- Step 2 Plannig-->
+In the *Assessment* step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis. 
+These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
+  <!-- Step 3 Evaluate-->
+In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
+  <!-- Step 3 Management-->
+Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
+This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
+
+An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
+In the following sub-sections, each stage of the methodology is explained.
+
 ## Planning
 
-It is needed to define two types of scopes: technological and ecological.
+Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.
 
@@
 
+set_flextable_defaults(
+  padding = 0,
+  line_spacing = 1,
+  border.color = '#000000'
+)
 Terminology %>% flextable() %>%
@@
   width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
-  theme_booktabs() %>% 
+  # theme_booktabs() %>% 
   hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
+  #border(border.top = officer::fp_border(color = "black") ) %>% 
   padding(padding = 0)
@@
 
+```{r Fig-spheres, fig.cap='Notation for assessing techno-ecological synergies', out.width='100%', fig.pos='!ht'}
+
+# img_url <- paste0(URL, 'Everest-bio/Systemes.svg')
+# rsvg_pdf(img_url, "Figures/Systemes.pdf")
+
+knitr::include_graphics('Figures/Systemes.pdf')
+```
+
+### Territorial issues
+
+\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}
+
+### Industrial Issues
+
+\textcolor{red}{ To complete based on article that reading on...}
+
 ### Definition of the Tech-Sphere
 
+It is needed to define two types of scopes: technological and ecological.
 <!-- Technological -->
@@
   <!-- Economy -->
-Technological systems at the economy scale are represented as $\doverline{T_{j}}$.
+Technological systems at the economy scale are represented as $\overline{T_{j}}$.
 These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.
@@
 @Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
-It represents the total amount of ES needed to  mitigate the emission or atisfy the resource use?
+It represents the total amount of ES needed to  mitigate the emission or satisfy the resource use.
 For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.
@@
 <!-- Intro to problem of LCA -->
-Usually, Life cycle analysis  do not integrate explicitaly models and data about ecosystem goods and services [@ref]
+Usually, Life cycle analysis  do not integrate explicitly models and data about ecosystem goods and services [@ref]
 Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.
@@
   <!-- Ecological models -->
-i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas (USEPA
+i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..
 
-- to complete the different odels for each ES?
-- More references on this
+\textcolor{red}{to complete ... }
+
+1. to complete the different models for each ES?.
+2. More references on this
 
@@
 
-###Impact Assessment
+### Techno-ecological synergy
 
-In this step, the echno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
+In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
 Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
@@
 
-###
 ## Management
+
+### Interpretation
+
+A hierarchy of metrics 
+The Techno-Ecological Synergy (TES) metric obtained are multi-scale and multidimensional.
+Therefore, these metrics  may be interprested by plotting the local and servicehed scale metrics.
+
+```{r Fig:Quandrantes, out.width='100%'}
+# img_url <- paste0(URL, 'Everest-bio/Quadrantes-sustainability.svg')
+# rsvg_pdf(img_url, "Figures/Quadrantes-sustainability.pdf")
+
+knitr::include_graphics('Figures/Quadrantes-sustainability.pdf')
+```
+
+Figure \@ref(Figure-TES) present four quadrants that represent the sustainability.
+  <!-- Quadrant I -->
+Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
+In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed’s ecological capacity. 
+From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
+  <!-- Quadrant III -->
+On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
+Ecological overshoot exists at both local and serviceshed scales. 
+Efforts toward improvement should reduce emissions and restore ecosystems at both
+
+Regarding the quandrant II, it represents the situation where the ES is used sustainably in the serviceshed but not at the local scale. 
+This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand. 
+Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support [@ref].
+On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed. 
+Here, the activity is an “island of sustainability” [@Wallner1996].
+If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.
+
+### Improvements and Design in the system
+
+  <!-- Goal of the step -->
+In this step, the main goal is to put effort for making changes such that $V_{i,j,k} \geq 0, \forall\{i,j,k\}$.
+This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services. 
+This final vision is to encourage engineering and human activities to be within ecological constraints.
+
+Three main elements in terms of design is expected in this step
+The first is the explicit recognition of the inherent interdependencies between technological and ecological systems. 
+Such recognition enables a better understanding of the resiliency of coupled techno-ecological systems during any enhancement of technological efficiency or restoration of ecological service provision.
+The collaboration with multi-stakeholders is expected in this step.
+
+Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process. 
+If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for $V\{i,j,k\} \geq 0$ for some values of $i, j,$ and $k$. 
+Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc. 
+For such molecules, the only way to satisfy the TES objective of $V\{i,j,k\} \geq 0$ is by technological changes. 
+One approach is to treat such molecules as "technological nutrients" and like biological nutrients, to recycle in technological systems.
+Nonrenewable resources will invariably result in values of $V\{i,j,k\} \geq 0$. 
+Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.
+
+### Establishment on Scenarios
+
+\textcolor{red}{to complete ... }
 

### 2021-09-14 00-ES/Article/Draft.tex
version beta sent to Nadege

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  14pt,
]{extarticle}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Distributed recycling for additive manufacturing: an ecosystem services perspective},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=2cm, right=2cm,top=3cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{float}
\usepackage{subfig}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{pdflscape}
\usepackage{svg}
\usepackage{lineno}
\usepackage{setspace}
\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
\usepackage{tabu}

\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Distributed recycling for additive manufacturing: an ecosystem services perspective}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}
\linenumbers

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
No country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.

However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements.
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al. 2021}).
Therefore, new approaches need to be explored in order to reduce ar at least recycling this material.
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

The expected results seek to address the following questions:

\begin{itemize}
\tightlist
\item
  What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling?
\item
  How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
\item
  What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
  From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach,
\end{itemize}

In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.

\textcolor{red}{The article is structure as follows.... ( to complete) } section \ref{background} \ldots{}

\hypertarget{background}{%
\section{Background}\label{background}}

\label{background}

\hypertarget{ecosystem-services}{%
\subsection{Ecosystem services}\label{ecosystem-services}}

Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being (\protect\hyperlink{ref-Gomez-Baggethun2010}{Gómez-Baggethun et al. 2010}; \protect\hyperlink{ref-DeGroot2002}{De Groot, Wilson, and Boumans 2002}).
Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital (\protect\hyperlink{ref-Laurans2013}{Laurans et al. 2013}).
Nevertheless, commodification of nature's services by reductionist thinking about individual services runs the risk of unintended harm and unbalanced outputs.
Systems thinking is essential for avoiding such harm (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).

Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being (\protect\hyperlink{ref-Costanza1997}{Costanza et al. 1997}, \protect\hyperlink{ref-Costanza2017}{2017}). Ecosystem goods (e.g; Food) and services (e.g.~waste assimilation) illustrate the benefits that human derive from the ecosystem functions (\protect\hyperlink{ref-Costanza1997}{Costanza et al. 1997}).
It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself. The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits.
By contrast, the latter are those processes and functions where people can (or could have the potential (\protect\hyperlink{ref-ref}{\textbf{ref?}})) obtain benefits. The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach. Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in `negative' way, making damage and costs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al. 2003}). This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders (\protect\hyperlink{ref-Honeck2021}{Honeck et al. 2021}).

Using a systematic literature review approach, \protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson} (\protect\hyperlink{ref-Torres2021}{2021}) distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
Key approaches include methods (\protect\hyperlink{ref-Harrison2018}{Harrison et al. 2018}), tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.

Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies. Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.

Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment (\protect\hyperlink{ref-MEA2005}{MEA 2005}),
The Economics of Ecosystems and Biodiversity TEEB (\protect\hyperlink{ref-TEEB2010}{TEEB 2010}),
The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) (\protect\hyperlink{ref-ref}{\textbf{ref?}}) and the Common International Classification of Ecosystem Services (CICES).
In the heart of the four main, they share four main categories of ES:
\textbf{Provisioning} (e.g.~food and medicines);
\textbf{Regulating} (e.g.~pollination and climate regulation),
\textbf{Supporting} (e.g soil formation and fixation of solar energy) and
\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-PedersenZari2019}{Pedersen Zari 2019}).

\begin{figure}[!ht]

{\centering \includegraphics[width=1\linewidth]{Figures/Comparison}

}

\caption{ES conceptual framework}(\#fig:Fig:ES)
\end{figure}

Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital (\protect\hyperlink{ref-Costanza1997}{Costanza et al. 1997}) and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework (\protect\hyperlink{ref-Bruel2016}{Bruel et al. 2016}).
From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it (\protect\hyperlink{ref-Ekins2003}{Ekins et al. 2003}).
More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of \emph{critical} components that make a major contribution to welfare.
The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience (\protect\hyperlink{ref-Ekins2003}{Ekins et al. 2003}).

The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
In CICES framework, \protect\hyperlink{ref-Potschin-Young2018}{Potschin-Young et al.} (\protect\hyperlink{ref-Potschin-Young2018}{2018}) argued the conceptual framework of cascading aspect from ecosystesm service are commonly divided Groups, division.

\begin{figure}[!ht]

{\centering \includegraphics[width=1\linewidth]{Figures/cices}

}

\caption{ES conceptual framework}\label{fig:Fig-ES-cices}
\end{figure}

\textcolor{red}{to complete ... }

\hypertarget{distributed-recycling-via-additive-manufacturing}{%
\subsection{Distributed recycling via additive manufacturing}\label{distributed-recycling-via-additive-manufacturing}}

Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al. 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al. 2020}).
The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.

\textcolor{red}{ To complete ...}

\hypertarget{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}{%
\subsection{Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.}\label{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}}

The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal. This scenario is not true today.
The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al. 2019}).
It is difficult to provide information about pressure from industrial systems in corporate information systems.
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-ref}{\textbf{ref?}}).

According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al. 2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).

\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

\textcolor{red}{
Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filière considering the technological and ecological spheres.

\begin{figure}[!ht]

{\centering \includegraphics[width=1\linewidth]{Figures/Methodology}

}

\caption{Operational framework for evaluatig the ecosystem services of industrial systems}\label{fig:Fig-Methodology}
\end{figure}

Four major steps are proposed as illustrated in figure \ref{Fig-Methodology} .

The goal of \emph{Planning} step is to identify the boundaries for the technological and ecological systems to be evaluated.
In the \emph{Assessment} step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis.
These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
In the \emph{Evaluation} stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
Finally, in the last step \emph{Management}, the main goal is to establish scenarios of evaluation based on the `Bussiness-as-usual' and Synergy frameworks.
This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.

An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
In the following sub-sections, each stage of the methodology is explained.

\hypertarget{planning}{%
\subsection{Planning}\label{planning}}

Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{|p{1.00in}|p{1.50in}|p{1.50in}|p{2.00in}}

\caption{Terminology used in the deifnition of the spheres}\label{tab:Terminology}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}\endhead

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Techno-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Equipement\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Detailed\ models}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Corn\ production\ at\ a\ location}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Value\ chain\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ activities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ corn\ production\ in\ a\ region}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Economy\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Industrial\ sectors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Grain\ farming\ sector}}} \\

\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Eco-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecosystem\ Services\ (ES)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Benefits\ humans\ received\ from\ Nature}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Serviceshead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Area\ providing\ the\ ES\ to\ specific\ users\ of\ that\ servicee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Emissions\ and\ resource\ use\ by\ technological\ systems}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ supply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecological\ capacity\ to\ mediate/sequester/absord\ impacts}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\end{longtable}

\begin{figure}[!ht]
\includegraphics[width=1\linewidth]{Figures/Systemes} \caption{Notation for assessing techno-ecological synergies}\label{fig:Fig-spheres}
\end{figure}

\hypertarget{territorial-issues}{%
\subsubsection{Territorial issues}\label{territorial-issues}}

\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}

\hypertarget{industrial-issues}{%
\subsubsection{Industrial Issues}\label{industrial-issues}}

\textcolor{red}{ To complete based on article that reading on...}

\hypertarget{definition-of-the-tech-sphere}{%
\subsubsection{Definition of the Tech-Sphere}\label{definition-of-the-tech-sphere}}

It is needed to define two types of scopes: technological and ecological.
Regarding the technological sphere, three scales are analysed: \emph{Equipment}, \emph{Value chain} and \emph{Economy} scales.
The technological system at the equipment scale is represented as \(T_{i,j}\) which consists of the \emph{i-th} facility for the \emph{j-th} technological activity.
For example, in the case of a specific technological activity (\(j = 1\)) such as corn farming, \(T_{1,1}\) and \(T_{1,1}\) represent two different facilities or farms for this activity.
Technological systems at the value chain scale are indicated as \(\underline{T_{j}}\).
These represent average value chain activities within a region, whose information is generally available from inventory databases.
Technological systems at the economy scale are represented as \(\overline{T_{j}}\).
These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.

In a given problem, the scales at which technologies systems should be modeled are determined based on whether the data are available and whether the activities are site-specific.

\hypertarget{definition-of-the-eco-sphere}{%
\subsubsection{Definition of the Eco-sphere}\label{definition-of-the-eco-sphere}}

Concerning the ecological sphere, it relies on specifying the geographical regions where the activity is implemented.
The main aim is to include explicitly the ecosystem goods and services, and the ecosystem itself in the system boundary.
Thus, interactions within and between technological and ecological systems can be integred explicitly, enabling the assessment of regional variation and absolute environmental sustainability regarding each ES considered.

In this step requires information about ecosystems in which the selected technological systems are nested.
Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.
The ecosystem local to \(T_{i,j}\) is represented by \(E_{i,j}\).
For example, this could be the campus around a manufacturing facility or an agricultural farm.

At the \emph{value chain} scale, the ``local ecosystem'' for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
The averaged local ecosystem can be justified as the general landscape characteristics around the specific activity.
For instance, electricity generation from coal-fired power plants needs a large amount of water for cooling: thus, it is likely that these facilities are located close to water sources.

Likewise, the local ecosystem for an \emph{economic scale} may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as \(\overline{E}_{j}\).
The aggregation relationships between activities and their surrounding ecosystems at various scales have been depicted by the dotted lines in figure XX.

\hypertarget{scope-of-ecosystems-serviceshed}{%
\paragraph{Scope of Ecosystems Serviceshed}\label{scope-of-ecosystems-serviceshed}}

The largest ecological scale that needs to be considered varies according to the type of ES.
The ``largest ecological scale'' is analogous to the concept of a ``serviceshed'' in the ES literature (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).

It is indicated by outer circles in figure X.
The notation used is \(E^{*}_{i,j,k}\) to represent the serviceshed for the \(k-th\) ES, in which the \(i-th\) facility of the \(j-th\) technological activity is nested.

For example, due to the global flow of \(CO_{2}\), the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else.
Thus, the largest ecological scale to evaluate the carbon sequestration ES is the global scale.
In contrast, criteria air pollutants, such as \(SO_{2}\) and \(NO{x}\) can only be transported and regulated by ecosystems within a narrower geographic boundary.
Thus, the largest ecological scale to evaluate air quality regulation service is the regional scale.
Larger ecological scales, such as a global scale, may not be relevant to this service.

If facilities \(T_{1,n}\dots,T_{m,n}\) are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity \(\underline{T}_{n}\).
Although such averaging implicitly assumes substitutability by implying that ES produced in one serviceshed can be used by beneficiaries in another serviceshed, this average may have to be used in the absence of spatial information at the serviceshed or smaller scales.
The average serviceshed is denoted as \(\underline{E}^{*}_{j,k}\) for value chain activities and \(\overline{E}^{*}_{j,k}\) for economic activities.

\hypertarget{assesstment-of-demand-and-supply-for-key-es}{%
\subsection{Assesstment of Demand and Supply for key ES}\label{assesstment-of-demand-and-supply-for-key-es}}

\hypertarget{inventory-of-the-technological-systems}{%
\subsubsection{Inventory of the Technological Systems}\label{inventory-of-the-technological-systems}}

Consider a situation where a production flowsheet for an existing or new process is already available.
A preliminary assessment of these environmental interventions must be carried out to obtain information about the different types of demands created by manufacturing facilities, and the kind of ecosystems that can supply these services to satisfy the demand.

\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi} (\protect\hyperlink{ref-Liu2019g}{2019}) argued that the conventional Life Cycle Inveentory (LCI) of technological systems can be used as the \textbf{demand} (\(D_{k}\)) for the \(k-th\) ES.
It represents the total amount of ES needed to mitigate the emission or satisfy the resource use.
For example, the quantity of \(CO_{2}\) emitted by a technology indicate the demand for the carbon sequestration service.

Environmentally-extended input-output (EEIO) data for activities at equipment, value chain and economy scale, LCI databases, and detailed engineering models can supply information to quantify the respective demand for each service.
Also, inventory of technological systems comprises all relevant flows associated with the functional unit, regardless of the scale at which technological activities are modeled.

\hypertarget{inventory-of-the-ecological-systems}{%
\subsubsection{Inventory of the Ecological Systems}\label{inventory-of-the-ecological-systems}}

Usually, Life cycle analysis do not integrate explicitly models and data about ecosystem goods and services (\protect\hyperlink{ref-ref}{\textbf{ref?}})
Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the \textbf{supply} (\(S_{k}\)) of the \(k-th\) ES.

The main object is to establish the ability of of ecosystems to provide the demanded services.
For example, green plants supply the carbon sequestration service by taking up atmospheric \(CO_{2}\) and sequestering it as organic matter through photosynthesis.
This can be understood as the dependence of production systems on ES.
Alternatively, it can be interpreted as the ES that nature can supply in order to produce the functional unit.

There is a research efforts to establish the knowledge about the supply of ES using ecological models such as
i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al.~2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..

\textcolor{red}{to complete ... }

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  to complete the different models for each ES?.
\item
  More references on this
\end{enumerate}

\hypertarget{allocation}{%
\subsubsection{Allocation}\label{allocation}}

One key point is determining the allocation of each ES for multiple users in a selected servicehed.
Two possible allocation strategies are proportional or avoid allocation (\protect\hyperlink{ref-ref}{\textbf{ref?}}).

Proportional allocation splits the ES supply according to selected quantities such as population, demand, or money.
Avoided allocation only considers total demand and supply of an ES within the serviceshed.

Proportional allocation can face similar challenges as allocation between multiple co-products in conventional LCA.
Allocating an ES between multiple users is analogous to determining their right of use. Two ethics of interpreting this are as follows:

\begin{itemize}
\item
  \emph{Private ownership} implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed.
  For calculating ES supply under a private ownership scenario, land ownership information within the serviceshed is needed
\item
  \emph{Public ownership} implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership.
  This approach allocates all ES supply from the serviceshed based on the selected properties of the users.
  If allocation is done in proportion to the demand of ES, the resulting metric is identical to that of the avoided allocation approach.
\end{itemize}

However, there could be practical issues with this land ownership based allocation of ES are the public availability of land ownership data and the possible applicability of other ES ownership schemes.

Proportional allocation can provide local sustainability metrics; while for avoided allocation, all activities in a selected serviceshed are assumed to have identical sustainability metrics.

\hypertarget{evaluation}{%
\subsection{Evaluation}\label{evaluation}}

\hypertarget{techno-ecological-synergy}{%
\subsubsection{Techno-ecological synergy}\label{techno-ecological-synergy}}

In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied (\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech 2015}).
Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated.
For the k-th ES, the sustainability metric \(V_{k}\) is:

\[
V_{k} = \frac{S_{k} - D_{k}}{D_{k}}
\]

where, \(S_{k}\) and \(D_{k}\) are the supply and demand of the \(k-th\) ES, respectively.

The basic results from TES consist of of pairs of numbers \({D}\)

This metric indicates the extent to which the technological activity is within the relevant ecosystem's carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
Absolute environmental sustainability for the \(k-th\) ES is defined at the serviceshed scale (indicated by \$\^{}\{*\}) :

\[
V_{k}^{*} \geq 0, \forall k
\]

Strong sustainability requires satisfaction of this criterion in the corresponding servicesheds for each ES.
If metrics are calculated for the average serviceshed, then satisfaction of equation (2) suggests only weak sustainability, since it implicitly assumes that the absolute environmental sustainability in one serviceshed can be used to compensate for unsustainability in another.
Thus, the unsustainability in some servicesheds would be overlooked due to the averaging.
This problem would be potentially solved by disaggregating the average serviceshed and calculating the metrics for each component serviceshed separately.
However, this will require more data.

\hypertarget{management}{%
\subsection{Management}\label{management}}

\hypertarget{interpretation}{%
\subsubsection{Interpretation}\label{interpretation}}

A hierarchy of metrics
The Techno-Ecological Synergy (TES) metric obtained are multi-scale and multidimensional.
Therefore, these metrics may be interprested by plotting the local and servicehed scale metrics.

\includegraphics[width=1\linewidth]{Figures/Quadrantes-sustainability}

Figure \ref{Figure-TES} present four quadrants that represent the sustainability.
Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed's ecological capacity.
From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
Ecological overshoot exists at both local and serviceshed scales.
Efforts toward improvement should reduce emissions and restore ecosystems at both

Regarding the quandrant II, it represents the situation where the ES is used sustainably in the serviceshed but not at the local scale.
This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand.
Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed.
Here, the activity is an ``island of sustainability'' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}).
If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.

\hypertarget{improvements-and-design-in-the-system}{%
\subsubsection{Improvements and Design in the system}\label{improvements-and-design-in-the-system}}

In this step, the main goal is to put effort for making changes such that \(V_{i,j,k} \geq 0, \forall\{i,j,k\}\).
This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services.
This final vision is to encourage engineering and human activities to be within ecological constraints.

Three main elements in terms of design is expected in this step
The first is the explicit recognition of the inherent interdependencies between technological and ecological systems.
Such recognition enables a better understanding of the resiliency of coupled techno-ecological systems during any enhancement of technological efficiency or restoration of ecological service provision.
The collaboration with multi-stakeholders is expected in this step.

Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process.
If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for \(V\{i,j,k\} \geq 0\) for some values of \(i, j,\) and \(k\).
Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc.
For such molecules, the only way to satisfy the TES objective of \(V\{i,j,k\} \geq 0\) is by technological changes.
One approach is to treat such molecules as ``technological nutrients'' and like biological nutrients, to recycle in technological systems.
Nonrenewable resources will invariably result in values of \(V\{i,j,k\} \geq 0\).
Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.

\hypertarget{establishment-on-scenarios}{%
\subsubsection{Establishment on Scenarios}\label{establishment-on-scenarios}}

\textcolor{red}{to complete ... }

\hypertarget{case-study-distributing-recycling-via-additive-manufacturing}{%
\section{Case study: Distributing recycling via Additive Manufacturing}\label{case-study-distributing-recycling-via-additive-manufacturing}}

\hypertarget{indicators-in-ecosystem-services-distributed-recycling-the}{%
\subsection{Indicators in Ecosystem Services Distributed recycling The}\label{indicators-in-ecosystem-services-distributed-recycling-the}}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bakshi2015}{}%
Bakshi, Bhavik R, Guy Ziv, and Michael D Lepech. 2015. {``{Techno-ecological synergy: A framework for sustainable engineering}.''} \emph{Environ. Sci. Technol.} 49 (3): 1752--60. \url{https://doi.org/10.1021/es5041442}.

\leavevmode\hypertarget{ref-Bruel2018}{}%
Bruel, Aurélien, Jakub Kronenberg, Nadège Troussier, and Bertrand Guillaume. 2019. {``{Linking Industrial Ecology and Ecological Economics: A Theoretical and Empirical Foundation for the Circular Economy}.''} \emph{J. Ind. Ecol.} 23 (1): 12--21. \url{https://doi.org/10.1111/jiec.12745}.

\leavevmode\hypertarget{ref-Bruel2016}{}%
Bruel, Aurélien, Nadège Troussier, Bertrand Guillaume, and Natalia Sirina. 2016. {``{Considering Ecosystem Services in Life Cycle Assessment to Evaluate Environmental Externalities}.''} \emph{Procedia CIRP} 48: 382--87. \url{https://doi.org/10.1016/j.procir.2016.03.143}.

\leavevmode\hypertarget{ref-Ceschin2016}{}%
Ceschin, Fabrizio, and Idil Gaziulusoy. 2016. {``{Evolution of design for sustainability: From product design to design for system innovations and transitions}.''} \emph{Des. Stud.} 47 (November): 118--63. \url{https://doi.org/10.1016/j.destud.2016.09.002}.

\leavevmode\hypertarget{ref-Costanza1997}{}%
Costanza, Robert, Ralph D'Arge, Rudolf de Groot, Stephen Farber, Monica Grasso, Bruce Hannon, Karin Limburg, et al. 1997. {``{The value of the world's ecosystem services and natural capital}.''} \emph{Nature} 387 (6630): 253--60. \url{https://doi.org/10.1038/387253a0}.

\leavevmode\hypertarget{ref-Costanza2017}{}%
Costanza, Robert, Rudolf de Groot, Leon Braat, Ida Kubiszewski, Lorenzo Fioramonti, Paul Sutton, Steve Farber, and Monica Grasso. 2017. {``{Twenty years of ecosystem services: How far have we come and how far do we still need to go?}''} Elsevier B.V. \url{https://doi.org/10.1016/j.ecoser.2017.09.008}.

\leavevmode\hypertarget{ref-CruzSanchez2020}{}%
Cruz Sanchez, Fabio A., Hakim Boudaoud, Mauricio Camargo, and Joshua M. Pearce. 2020. {``{Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy}.''} \emph{J. Clean. Prod.} 264 (August): 121602. \url{https://doi.org/10.1016/j.jclepro.2020.121602}.

\leavevmode\hypertarget{ref-DeGroot2002}{}%
De Groot, Rudolf S., Matthew A. Wilson, and Roelof M. J. Boumans. 2002. {``{A typology for the classification, description and valuation of ecosystem functions, goods and services}.''} \emph{Ecol. Econ.} 41 (3): 393--408. \url{https://doi.org/10.1016/S0921-8009(02)00089-7}.

\leavevmode\hypertarget{ref-Diwekar2021}{}%
Diwekar, U., A. Amekudzi-Kennedy, B. Bakshi, R. Baumgartner, R. Boumans, P. Burger, H. Cabezas, et al. 2021. {``{A perspective on the role of uncertainty in sustainability science and engineering}.''} \emph{Resour. Conserv. Recycl.} 164 (January): 105140. \url{https://doi.org/10.1016/j.resconrec.2020.105140}.

\leavevmode\hypertarget{ref-Ekins2003}{}%
Ekins, Paul, Sandrine Simon, Lisa Deutsch, Carl Folke, and Rudolf De Groot. 2003. {``{A framework for the practical application of the concepts of critical natural capital and strong sustainability}.''} \emph{Ecol. Econ.} 44 (2-3): 165--85. \url{https://doi.org/10.1016/S0921-8009(02)00272-0}.

\leavevmode\hypertarget{ref-Gopalakrishnan2016}{}%
Gopalakrishnan, Varsha, Bhavik R. Bakshi, and Guy Ziv. 2016. {``{Assessing the capacity of local ecosystems to meet industrial demand for ecosystem services}.''} \emph{AIChE J.} 62 (9): 3319--33. \url{https://aiche.onlinelibrary.wiley.com/doi/full/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/abs/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/10.1002/aic.15340}.

\leavevmode\hypertarget{ref-Gomez-Baggethun2010}{}%
Gómez-Baggethun, Erik, Rudolf de Groot, Pedro L. Lomas, and Carlos Montes. 2010. {``{The history of ecosystem services in economic theory and practice: From early notions to markets and payment schemes}.''} \emph{Ecol. Econ.} 69 (6): 1209--18. \url{https://doi.org/10.1016/j.ecolecon.2009.11.007}.

\leavevmode\hypertarget{ref-Harrison2018}{}%
Harrison, Paula A., Rob Dunford, David N. Barton, Eszter Kelemen, Berta Martín-López, Lisa Norton, Mette Termansen, et al. 2018. {``{Selecting methods for ecosystem service assessment: A decision tree approach}.''} \emph{Ecosyst. Serv.} 29 (February): 481--98. \url{https://doi.org/10.1016/j.ecoser.2017.09.016}.

\leavevmode\hypertarget{ref-Honeck2021}{}%
Honeck, Erica, Louise Gallagher, Bertrand von Arx, Anthony Lehmann, Nicolas Wyler, Olga Villarrubia, Benjamin Guinaudeau, and Martin A. Schlaepfer. 2021. {``{Integrating ecosystem services into policymaking -- A case study on the use of boundary organizations}.''} \emph{Ecosyst. Serv.} 49 (June): 101286. \url{https://doi.org/10.1016/j.ecoser.2021.101286}.

\leavevmode\hypertarget{ref-Kumar2021}{}%
Kumar, Rakesh, Anurag Verma, Arkajyoti Shome, Rama Sinha, Srishti Sinha, Prakash Kumar Jha, Ritesh Kumar, et al. 2021. {``{Impacts of Plastic Pollution on Ecosystem Services, Sustainable Development Goals, and Need to Focus on Circular Economy and Policy Interventions}.''} \emph{Sustainability} 13 (17): 9963. \url{https://doi.org/10.3390/su13179963}.

\leavevmode\hypertarget{ref-Laurans2013}{}%
Laurans, Yann, Aleksandar Rankovic, Raphaël Billé, Romain Pirard, and Laurent Mermet. 2013. {``{Use of ecosystem services economic valuation for decision making: Questioning a literature blindspot}.''} Academic Press. \url{https://doi.org/10.1016/j.jenvman.2013.01.008}.

\leavevmode\hypertarget{ref-Liu2019g}{}%
Liu, Xinyu, and Bhavik R. Bakshi. 2019. {``{Ecosystem Services in Life Cycle Assessment while Encouraging Techno-Ecological Synergies}.''} \emph{J. Ind. Ecol.} 23 (2): 347--60. \url{https://doi.org/10.1111/jiec.12755}.

\leavevmode\hypertarget{ref-Lomborg2020}{}%
Lomborg, Bjorn. 2020. {``{Welfare in the 21st century: Increasing development, reducing inequality, the impact of climate change, and the cost of climate policies}.''} \emph{Technol. Forecast. Soc. Change} 156 (July): 119981. \url{https://doi.org/10.1016/j.techfore.2020.119981}.

\leavevmode\hypertarget{ref-Martinez-Hernandez2017}{}%
Martinez-Hernandez, Elias. 2017. {``{Trends in sustainable process design---from molecular to global scales}.''} \emph{Curr. Opin. Chem. Eng.} 17 (August): 35--41. \url{https://doi.org/10.1016/j.coche.2017.05.005}.

\leavevmode\hypertarget{ref-MEA2005}{}%
MEA. 2005. {``{Ecosystems and Human well-being: Synthesis}.''} \href{https://www.islandpress.org}{www.islandpress.org}.

\leavevmode\hypertarget{ref-ONeill2018}{}%
O'Neill, Daniel W., Andrew L. Fanning, William F. Lamb, and Julia K. Steinberger. 2018. {``{A good life for all within planetary boundaries}.''} \emph{Nat. Sustain.} 1 (2): 88--95. \url{https://doi.org/10.1038/s41893-018-0021-4}.

\leavevmode\hypertarget{ref-PedersenZari2019}{}%
Pedersen Zari, Maibritt. 2019. {``{Ecosystem services impacts as part of building materials selection criteria}.''} \emph{Mater. Today Sustain.} 3-4. \url{https://doi.org/10.1016/j.mtsust.2019.100010}.

\leavevmode\hypertarget{ref-Potschin-Young2018}{}%
Potschin-Young, M., R. Haines-Young, C. Görg, U. Heink, K. Jax, and C. Schleyer. 2018. {``{Understanding the role of conceptual frameworks: Reading the ecosystem service cascade}.''} \emph{Ecosyst. Serv.} 29 (February): 428--40. \url{https://doi.org/10.1016/j.ecoser.2017.05.015}.

\leavevmode\hypertarget{ref-Rockstrom2009}{}%
Rockström, Johan, Will Steffen, Kevin Noone, Åsa Persson, F. Stuart Chapin, Eric F. Lambin, Timothy M. Lenton, et al. 2009. {``{A safe operating space for humanity}.''} \url{https://doi.org/10.1038/461472a}.

\leavevmode\hypertarget{ref-Santander2020}{}%
Santander, Pavlo, Fabio A Cruz Sanchez, Hakim Boudaoud, and Mauricio Camargo. 2020. {``{Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach}.''} \emph{Resour. Conserv. Recycl.} 154 (March): 104531. \url{https://doi.org/10.1016/j.resconrec.2019.104531}.

\leavevmode\hypertarget{ref-TEEB2010}{}%
TEEB. 2010. \emph{{The Economics of Ecosystems and Biodiversity Ecological and Economic Foundations.}} \url{https://doi.org/10.4324/9781849775489}.

\leavevmode\hypertarget{ref-Torres2021}{}%
Torres, Angélica Valencia, Chetan Tiwari, and Samuel F. Atkinson. 2021. {``{Progress in ecosystem services research: A guide for scholars and practitioners}.''} \emph{Ecosyst. Serv.} 49 (June): 101267. \url{https://doi.org/10.1016/j.ecoser.2021.101267}.

\leavevmode\hypertarget{ref-Wallner1996}{}%
Wallner, H. P., M. Narodoslawsky, and F. Moser. 1996. {``{Islands of sustainability: A bottom-up approach towards sustainable development}.''} \emph{Environ. Plan. A} 28 (10): 1763--78. \url{https://doi.org/10.1068/a281763}.

\end{CSLReferences}

\end{document}

### 2021-10-01 00-ES/Article/Draft.Rmd
Version Beta 1.0

@@
 No country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
-Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
+Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
 We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.
@@
 It is difficult to provide information about pressure from industrial systems in corporate information systems. 
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@ref].
+Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].
 
@@
   <!-- Causas of exceeding Planeatry boundaries -->
-Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions [@Liu2019g].
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
 Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
@@
 @Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
 The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
@@
 
-The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filière considering the technological and ecological spheres.
+The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
 
@@
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.
+Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
 
@@
 
-\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}
+<!-- Urban Ecosystem Services -->
+More than two thirds of the world's population are expected to live in cities by 2050 [@ref].
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
+  <!-- Importance of Urban ES -->
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
+cooling, and runoff mitigation [@Bolund1999]. 
+  <!-- Classification of Urban ES -->
+@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
+They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
+
+  <!-- Goal -->
+The main purpose in this step is the identification of the main urban priorities in the territorial context from a perspective of ecosystem services.
+THe ES in a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
 

### 2021-10-01 00-ES/Article/Draft.tex
Version Beta 1.0

@@
 \subsubsection{Territorial issues}\label{territorial-issues}}
+
+More than two thirds of the world's population are expected to live in cities by 2050 (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities (\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton 2013}).
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
+cooling, and runoff mitigation (\protect\hyperlink{ref-Bolund1999}{Bolund and Hunhammar 1999}).
+\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton} (\protect\hyperlink{ref-Gomez-Baggethun2013}{2013}) draws on the developments of the ecosystem services for urban planning.
+They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
+
+The main purpose in this step is the identification of the main urban priorities in the territorial context, from a perspective of ecosystem services.
+
+example, if agroecosystems are critical for food production, wetlands for nutrient cycling, and forests for carbon sequestration,
+Which ecosystem services in a given city are most relevant varies greatly depending on the environmental and socio-economic characteristics of each site.
 
@@
 
+\leavevmode\hypertarget{ref-Bolund1999}{}%
+Bolund, Per, and Sven Hunhammar. 1999. {``{Ecosystem services in urban areas}.''} \emph{Ecol. Econ.} 29 (2): 293--301. \url{https://doi.org/10.1016/S0921-8009(99)00013-0}.
+
 \leavevmode\hypertarget{ref-Bruel2018}{}%
@@
 \url{https://aiche.onlinelibrary.wiley.com/doi/full/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/abs/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/10.1002/aic.15340}.
+
+\leavevmode\hypertarget{ref-Gomez-Baggethun2013}{}%
+Gómez-Baggethun, Erik, and David N.
+Barton.
+2013.
+{``{Classifying and valuing ecosystem services for urban planning}.''} \emph{Ecol.
+Econ.} 86 (February): 235--45.
+\url{https://doi.org/10.1016/j.ecolecon.2012.08.019}.
 

### 2021-10-20 00-ES/Article/Draft.Rmd
working on the strcuturation

@@
 ---
-title: "Distributed recycling for additive manufacturing: an ecosystem services perspective "
-documentclass: extarticle
-fontsize: 14pt
-geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
+title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
+#documentclass: extarticle
+#fontsize: 14pt
+#geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
 output: 
@@
 
+<!-- ## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity. -->
 <!-- Intro -->
 The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
-No country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
+<!-- Technological development claiming sustainabiilty -->
+Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs [@ref].
+For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
+This meta-principle is a imperative but not sufficient condition for sustainability.
+Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
 Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
-We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.
-
+We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
 <!-- Gap in the literature -->
 However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
+
+<!-- Sustainability frameworks -->
+@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
+They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
+<!-- They hightligthed that differens Systemic design approaches are   -->
+
+<!-- Importance of ES in the Engineering -->
+The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
+However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
+  <!-- Engineering blindness -->
+The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
+This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal.
+This scenario is not true today.
+  <!-- Engineering withing ecological constraints -->
+The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
+ <!-- Importance of ES in the decision making process -->
+The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
+It is difficult to provide information about pressure from industrial systems in corporate information systems. 
+Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].
+
+  <!-- MEA and Planeatry results -->
+According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
+Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
+  <!-- Causas of exceeding Planeatry boundaries -->
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
+Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
+<!-- Purpose of strong sustainability -->
+Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
+  <!-- Expand boundaries of Engineering -->
+Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].
+
+  <!-- TES -->
+@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
+for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
+
+<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
+-->
+<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
+-->
+
+\textcolor{red}{
+Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
+
 The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
@@
 
-\textcolor{red}{to complete ... }
+The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings [70]. 
+With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings. 
+The product-based CICES framework can enable clearer mapping between ecological and economic products. 
+The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level. 
+The following levels organize ES according to their divisions, groups and classes. 
+At lower levels, more specific services can be defined and characterized. 
+For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed. 
+Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
+
+Figure 2.2 demonstrates the hierarchical structure of CICES scheme.
 
@@
 
-## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.
-
-<!-- Importance of ES in the Engineering -->
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
-However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
-  <!-- Engineering blindness -->
-The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
-This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal.
-This scenario is not true today.
-  <!-- Engineering withing ecological constraints -->
- The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
- <!-- Importance of ES in the decision making process -->
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
-It is difficult to provide information about pressure from industrial systems in corporate information systems. 
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].
-
-  <!-- MEA and Planeatry results -->
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
-Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
-  <!-- Causas of exceeding Planeatry boundaries -->
-Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
-<!-- Purpose of strong sustainability -->
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
-  <!-- Expand boundaries of Engineering -->
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].
-
-<!-- Sustainability frameworks -->
-@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
-They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-<!-- They hightligthed that differens Systemic design approaches are   -->
-  <!-- TES -->
-@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
-for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
--->
-<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
--->
-
-\textcolor{red}{
-Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
-
 # Methodology
 
-The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
+The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
+A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
 
@@
 
-```{r Terminology}
-Terminology <- read_csv2("tables/Terminology.csv")
-# Terminology <-  table_1 %>%  set_names(" ", "PLA", "Recycled PLA")
-
-#std_border = officer::fp_border(color="orange", width = 1)
-
-set_flextable_defaults(
-  padding = 0,
-  line_spacing = 1,
-  border.color = '#000000'
-)
-Terminology %>% flextable() %>%
-  set_caption("Terminology used in the deifnition of the spheres") %>%
-  width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
-  # theme_booktabs() %>% 
-  hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
-  #border(border.top = officer::fp_border(color = "black") ) %>% 
-  padding(padding = 0)
-
-```
-
-```{r Fig-spheres, fig.cap='Notation for assessing techno-ecological synergies', out.width='100%', fig.pos='!ht'}
-
-# img_url <- paste0(URL, 'Everest-bio/Systemes.svg')
-# rsvg_pdf(img_url, "Figures/Systemes.pdf")
-
-knitr::include_graphics('Figures/Systemes.pdf')
-```
-
-### Territorial issues
-
-<!-- Urban Ecosystem Services -->
-More than two thirds of the world's population are expected to live in cities by 2050 [@ref].
-Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
-  <!-- Importance of Urban ES -->
-Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
-cooling, and runoff mitigation [@Bolund1999]. 
-  <!-- Classification of Urban ES -->
-@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
-They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
-
-  <!-- Goal -->
-The main purpose in this step is the identification of the main urban priorities in the territorial context from a perspective of ecosystem services.
-THe ES in a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
-
-### Industrial Issues
-
-\textcolor{red}{ To complete based on article that reading on...}
-
-### Definition of the Tech-Sphere
-
-It is needed to define two types of scopes: technological and ecological.
-<!-- Technological -->
-Regarding the technological sphere, three scales are analysed: *Equipment*, *Value chain* and *Economy* scales.
-  <!-- Equipment -->
-The technological system at the equipment scale is represented as $T_{i,j}$ which consists of the *i-th* facility for the *j-th* technological activity. 
-For example, in the case of a specific technological activity ($j = 1$) such as corn farming, $T_{1,1}$ and $T_{1,1}$ represent two different facilities or farms for this activity. 
-  <!-- Value chain -->
-Technological systems at the value chain scale are indicated as $\underline{T_{j}}$.
-These represent average value chain activities within a region, whose information is generally available from inventory databases.
-  <!-- Economy -->
-Technological systems at the economy scale are represented as $\overline{T_{j}}$.
-These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.
-
-In a given problem, the scales at which technologies systems should be modeled are determined based on whether the data are available and whether the activities are site-specific.
-
-### Definition of the Eco-sphere
-
-<!-- Intro -->
-Concerning the ecological sphere, it relies on specifying the geographical regions where the activity is implemented. 
-  <!-- GOal -->
-The main aim is to include explicitly the ecosystem goods and services, and the ecosystem itself in the system boundary. 
-Thus, interactions within and between technological and ecological systems can be integred explicitly, enabling the assessment of regional variation and absolute environmental sustainability regarding each ES considered.
-
-<!-- Procedure for the three levels -->
-In this step requires information about ecosystems in which the selected technological systems are nested. 
-Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.   <!-- Specification at Equipment scale -->
-The ecosystem local to $T_{i,j}$ is represented by $E_{i,j}$.
-For example, this could be the campus around a manufacturing facility or an agricultural farm.
-
-<!-- Value chain scale -->
-At the *value chain* scale, the "local ecosystem" for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
-The averaged local ecosystem can be justified as the general landscape characteristics around the specific activity.
-For instance, electricity generation from coal-fired power plants needs a large amount of water for cooling: thus, it is likely that these facilities are located close to water sources.
-
-Likewise, the local ecosystem for an *economic scale* may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as $\overline{E}_{j}$.
-The aggregation relationships between activities and their surrounding ecosystems at various scales have been depicted by the dotted lines in figure XX.
-
-#### Scope of Ecosystems Serviceshed
-
-The largest ecological scale that needs to be considered varies according to the type of ES. 
-The "largest ecological scale" is analogous to the concept of a “serviceshed” in the ES literature [@Liu2019g].
-
-It is indicated by outer circles in figure X. 
-The notation used is $E^{*}_{i,j,k}$ to represent the serviceshed for the $k-th$ ES, in which the $i-th$ facility of the $j-th$ technological activity is nested.
-
-For example, due to the global flow of $CO_{2}$, the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else. 
-Thus, the largest ecological scale to evaluate the carbon sequestration ES is the global scale. 
-In contrast, criteria air pollutants, such as $SO_{2}$ and $NO{x}$ can only be transported and regulated by ecosystems within a narrower geographic boundary. 
-Thus, the largest ecological scale to evaluate air quality regulation service is the regional scale. 
-Larger ecological scales, such as a global scale, may not be relevant to this service.
-
-If facilities $T_{1,n}\dots,T_{m,n}$ are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity $\underline{T}_{n}$.
-Although such averaging implicitly assumes substitutability by implying that ES produced in one serviceshed can be used by beneficiaries in another serviceshed, this average may have to be used in the absence of spatial information at the serviceshed or smaller scales.
-The average serviceshed is denoted as $\underline{E}^{*}_{j,k}$ for value chain activities and $\overline{E}^{*}_{j,k}$ for economic activities.
-
-## Assesstment of Demand and Supply for key ES
-
-### Inventory of the Technological Systems
-
-<!-- Intro -->
-Consider a situation where a production flowsheet for an existing or new process is already available.
-A preliminary assessment of these environmental interventions must be carried out to obtain information about the different types of demands created by manufacturing facilities, and the kind of ecosystems that can supply these services to satisfy the demand.
-
-@Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
-It represents the total amount of ES needed to  mitigate the emission or satisfy the resource use.
-For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.
-
-Environmentally-extended input-output (EEIO) data for activities at equipment, value chain and economy scale, LCI databases, and  detailed engineering models can supply information to quantify the respective demand for each service.
-Also, inventory of technological systems comprises all relevant flows associated with the functional unit, regardless of the scale at which technological activities are modeled.
-
-### Inventory of the Ecological Systems
-
-<!-- Intro to problem of LCA -->
-Usually, Life cycle analysis  do not integrate explicitly models and data about ecosystem goods and services [@ref]
-Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.
-
-The main object is to establish the ability of of ecosystems to provide the demanded services. 
-For example, green plants supply the carbon sequestration service by taking up atmospheric $CO_{2}$ and sequestering it as organic matter through photosynthesis. 
-This can be understood as the dependence of production systems on ES. 
-Alternatively, it can be interpreted as the ES that nature can supply in order to produce the functional unit.
-
-<!-- Establish ecological models -->
-There is a research efforts to establish the knowledge about the supply of ES using ecological models such as 
-  <!-- Ecological models -->
-i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..
-
-\textcolor{red}{to complete ... }
-
-1. to complete the different models for each ES?.
-2. More references on this
-
-### Allocation
-
-One key point is determining the allocation of each ES for multiple users in a selected servicehed.
-<!-- Strategies of allocation -->
-Two possible allocation strategies are proportional or avoid allocation [@ref].
-
-  <!-- Proportional -->
-Proportional allocation splits the ES supply according to selected quantities such as population, demand, or money.
-  <!-- Avoided -->
-Avoided allocation only considers total demand and supply of an ES within the serviceshed.
-
-  <!-- Explaining proportional -->
-Proportional allocation can face similar challenges as allocation between multiple co-products in conventional LCA. 
-Allocating an ES between multiple users is analogous to determining their right of use. Two ethics of interpreting this are as follows:
-
-- *Private ownership* implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed. 
-For calculating ES supply under a private ownership scenario, land ownership information within the serviceshed is needed
-
-- *Public ownership* implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership. 
-This approach allocates all ES supply from the serviceshed based on the selected properties of the users. 
-If allocation is done in proportion to the demand of ES, the resulting metric is identical to that of the avoided  allocation approach.
-
-However, there could be practical issues with this land ownership based allocation of ES are the public availability of land ownership data and the possible applicability of other ES ownership schemes.
-
-  <!-- Conclusion -->
-Proportional allocation can provide local sustainability metrics; while for avoided allocation, all activities in a selected serviceshed are assumed to have identical sustainability metrics.
-
-## Evaluation
-
-### Techno-ecological synergy
-
-In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
-Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
-For the k-th ES, the sustainability metric $V_{k}$ is:
-
-$$
-V_{k} = \frac{S_{k} - D_{k}}{D_{k}}
-$$
-
-where, $S_{k}$ and $D_{k}$ are the supply and demand of the $k-th$ ES, respectively.
-
-The basic results from TES consist of  of pairs of numbers ${D}$
-
-This metric indicates the extent to which the technological activity is within the relevant ecosystem’s carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
-Absolute environmental sustainability for the $k-th$ ES is defined at the serviceshed scale (indicated by $^{*}) :
-
-$$
-V_{k}^{*} \geq 0, \forall k
-$$
-
-Strong sustainability requires satisfaction of this criterion in the corresponding servicesheds for each ES. 
-If metrics are calculated for the average serviceshed, then satisfaction of equation (2) suggests only weak sustainability, since it implicitly assumes that the absolute environmental sustainability in one serviceshed can be used to compensate for unsustainability in another.
-Thus, the unsustainability in some servicesheds would be overlooked due to the averaging. 
-This problem would be potentially solved by disaggregating the average serviceshed and calculating the metrics for each component serviceshed separately. 
-However, this will require more data.
-
-## Management
-
-### Interpretation
-
-A hierarchy of metrics 
-The Techno-Ecological Synergy (TES) metric obtained are multi-scale and multidimensional.
-Therefore, these metrics  may be interprested by plotting the local and servicehed scale metrics.
-
-```{r Fig:Quandrantes, out.width='100%'}
-# img_url <- paste0(URL, 'Everest-bio/Quadrantes-sustainability.svg')
-# rsvg_pdf(img_url, "Figures/Quadrantes-sustainability.pdf")
-
-knitr::include_graphics('Figures/Quadrantes-sustainability.pdf')
-```
-
-Figure \@ref(Figure-TES) present four quadrants that represent the sustainability.
-  <!-- Quadrant I -->
-Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
-In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed’s ecological capacity. 
-From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
-  <!-- Quadrant III -->
-On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
-Ecological overshoot exists at both local and serviceshed scales. 
-Efforts toward improvement should reduce emissions and restore ecosystems at both
-
-Regarding the quandrant II, it represents the situation where the ES is used sustainably in the serviceshed but not at the local scale. 
-This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand. 
-Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support [@ref].
-On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed. 
-Here, the activity is an “island of sustainability” [@Wallner1996].
-If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.
-
-### Improvements and Design in the system
-
-  <!-- Goal of the step -->
-In this step, the main goal is to put effort for making changes such that $V_{i,j,k} \geq 0, \forall\{i,j,k\}$.
-This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services. 
-This final vision is to encourage engineering and human activities to be within ecological constraints.
-
-Three main elements in terms of design is expected in this step
-The first is the explicit recognition of the inherent interdependencies between technological and ecological systems. 
-Such recognition enables a better understanding of the resiliency of coupled techno-ecological systems during any enhancement of technological efficiency or restoration of ecological service provision.
-The collaboration with multi-stakeholders is expected in this step.
-
-Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process. 
-If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for $V\{i,j,k\} \geq 0$ for some values of $i, j,$ and $k$. 
-Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc. 
-For such molecules, the only way to satisfy the TES objective of $V\{i,j,k\} \geq 0$ is by technological changes. 
-One approach is to treat such molecules as "technological nutrients" and like biological nutrients, to recycle in technological systems.
-Nonrenewable resources will invariably result in values of $V\{i,j,k\} \geq 0$. 
-Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.
-
-### Establishment on Scenarios
-
-\textcolor{red}{to complete ... }
-
 # Case study: Distributing recycling via Additive Manufacturing
@@
 
+# Results of the
+
+## Planning
+
+### Goal and scope definition
+
+The system depicted is presented in the figure.
+The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
+Because Es are expected to be more relevant in the
+
+<!-- Funcitonal Unit -->
+The goal of this study is to evaluate and compare the change in ES provisioning 
+The functional unit (FU) is represented by *1kg of recycled filament delivered at school*.
+
+\newpage
 # References

### 2021-10-20 00-ES/Article/Ideas on draf.Rmd
working on the strcuturation

--- 2021-09-14 00-ES/Article/Draft.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[
-  14pt,
-]{extarticle}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Distributed recycling for additive manufacturing: an ecosystem services perspective},
-  colorlinks=true,
-  linkcolor=blue,
-  filecolor=Maroon,
-  citecolor=Blue,
-  urlcolor=Blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[left=2cm, right=2cm,top=3cm,bottom=2cm]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\usepackage{float}
-\usepackage{subfig}
-\usepackage[utf8]{inputenc}
-\def\tightlist{}
-\usepackage[bitstream-charter]{mathdesign}
-\usepackage{pdflscape}
-\usepackage{svg}
-\usepackage{lineno}
-\usepackage{setspace}
-\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
-\usepackage{tabu}
+```{r Terminology}
+Terminology <- read_csv2("tables/Terminology.csv")
+# Terminology <-  table_1 %>%  set_names(" ", "PLA", "Recycled PLA")
 
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+#std_border = officer::fp_border(color="orange", width = 1)
 
-\title{Distributed recycling for additive manufacturing: an ecosystem services perspective}
-\author{}
-\date{\vspace{-2.5em}}
+set_flextable_defaults(
+  padding = 0,
+  line_spacing = 1,
+  border.color = '#000000'
+)
+Terminology %>% flextable() %>%
+  set_caption("Terminology used in the deifnition of the spheres") %>%
+  width(j=1:4, width = c(1, 1.5, 1.5, 2)) %>% 
+  # theme_booktabs() %>% 
+  hline( i = 3, border = officer::fp_border( color = "black", width = 1)) %>% 
+  #border(border.top = officer::fp_border(color = "black") ) %>% 
+  padding(padding = 0)
 
-\begin{document}
-\maketitle
+```
 
-{
-\hypersetup{linkcolor=}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\linenumbers
+```{r Fig-spheres, fig.cap='Notation for assessing techno-ecological synergies', out.width='100%', fig.pos='!ht'}
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+# img_url <- paste0(URL, 'Everest-bio/Systemes.svg')
+# rsvg_pdf(img_url, "Figures/Systemes.pdf")
 
-The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
-No country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
-Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.
+knitr::include_graphics('Figures/Systemes.pdf')
+```
 
-However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
-The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
-This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements.
-As a case application, the study of distributed recycling manufacturing will be describe.
-Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al.
-2021}).
-Therefore, new approaches need to be explored in order to reduce ar at least recycling this material.
-Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
+### Territorial issues
 
-The expected results seek to address the following questions:
+<!-- Urban Ecosystem Services -->
+More than two thirds of the world's population are expected to live in cities by 2050 [@ref].
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
+  <!-- Importance of Urban ES -->
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
+cooling, and runoff mitigation [@Bolund1999]. 
+  <!-- Classification of Urban ES -->
+@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
+They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
 
-\begin{itemize}
-\tightlist
-\item
-  What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling?
-\item
-  How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
-\item
-  What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
-  From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach,
-\end{itemize}
+  <!-- Goal -->
+The main purpose in this step is the identification of the main urban priorities in the territorial context from a perspective of ecosystem services.
+THe ES in a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
 
-In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
-This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.
-
-\textcolor{red}{The article is structure as follows.... ( to complete) } section \ref{background} \ldots{}
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-\label{background}
-
-\hypertarget{ecosystem-services}{%
-\subsection{Ecosystem services}\label{ecosystem-services}}
-
-Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being (\protect\hyperlink{ref-Gomez-Baggethun2010}{Gómez-Baggethun et al.
-2010}; \protect\hyperlink{ref-DeGroot2002}{De Groot, Wilson, and Boumans 2002}).
-Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital (\protect\hyperlink{ref-Laurans2013}{Laurans et al.
-2013}).
-Nevertheless, commodification of nature's services by reductionist thinking about individual services runs the risk of unintended harm and unbalanced outputs.
-Systems thinking is essential for avoiding such harm (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
-
-Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}, \protect\hyperlink{ref-Costanza2017}{2017}).
-Ecosystem goods (e.g; Food) and services (e.g.~waste assimilation) illustrate the benefits that human derive from the ecosystem functions (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}).
-It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself.
-The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits.
-By contrast, the latter are those processes and functions where people can (or could have the potential (\protect\hyperlink{ref-ref}{\textbf{ref?}})) obtain benefits.
-The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach.
-Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in `negative' way, making damage and costs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
-This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders (\protect\hyperlink{ref-Honeck2021}{Honeck et al.
-2021}).
-
-Using a systematic literature review approach, \protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson} (\protect\hyperlink{ref-Torres2021}{2021}) distinguished and categorized 8 major key themes and 22 approaches in the ES field.
-Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
-Key approaches include methods (\protect\hyperlink{ref-Harrison2018}{Harrison et al.
-2018}), tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
-It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
-
-Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
-Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
-
-Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment (\protect\hyperlink{ref-MEA2005}{MEA 2005}),
-The Economics of Ecosystems and Biodiversity TEEB (\protect\hyperlink{ref-TEEB2010}{TEEB 2010}),
-The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) (\protect\hyperlink{ref-ref}{\textbf{ref?}}) and the Common International Classification of Ecosystem Services (CICES).
-In the heart of the four main, they share four main categories of ES:
-\textbf{Provisioning} (e.g.~food and medicines);
-\textbf{Regulating} (e.g.~pollination and climate regulation),
-\textbf{Supporting} (e.g soil formation and fixation of solar energy) and
-\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-PedersenZari2019}{Pedersen Zari 2019}).
-
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=1\linewidth]{Figures/Comparison}
-
-}
-
-\caption{ES conceptual framework}(\#fig:Fig:ES)
-\end{figure}
-
-Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}) and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework (\protect\hyperlink{ref-Bruel2016}{Bruel et al.
-2016}).
-From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
-More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of \emph{critical} components that make a major contribution to welfare.
-The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
-
-The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-In CICES framework, \protect\hyperlink{ref-Potschin-Young2018}{Potschin-Young et al.} (\protect\hyperlink{ref-Potschin-Young2018}{2018}) argued the conceptual framework of cascading aspect from ecosystesm service are commonly divided Groups, division.
-
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=1\linewidth]{Figures/cices}
-
-}
-
-\caption{ES conceptual framework}\label{fig:Fig-ES-cices}
-\end{figure}
-
-\textcolor{red}{to complete ... }
-
-\hypertarget{distributed-recycling-via-additive-manufacturing}{%
-\subsection{Distributed recycling via additive manufacturing}\label{distributed-recycling-via-additive-manufacturing}}
-
-Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al.
-2020}; \protect\hyperlink{ref-Santander2020}{Santander et al.
-2020}).
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
-
-\textcolor{red}{ To complete ...}
-
-\hypertarget{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}{%
-\subsection{Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.}\label{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}}
-
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
-However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
-The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
-This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal.
-This scenario is not true today.
-The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al.
-2019}).
-It is difficult to provide information about pressure from industrial systems in corporate information systems.
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
-Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al.
-2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al.
-2018}).
-Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).
-
-\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
-They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-\textcolor{red}{
-Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
-
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
-
-The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filière considering the technological and ecological spheres.
-
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=1\linewidth]{Figures/Methodology}
-
-}
-
-\caption{Operational framework for evaluatig the ecosystem services of industrial systems}\label{fig:Fig-Methodology}
-\end{figure}
-
-Four major steps are proposed as illustrated in figure \ref{Fig-Methodology} .
-
-The goal of \emph{Planning} step is to identify the boundaries for the technological and ecological systems to be evaluated.
-In the \emph{Assessment} step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis.
-These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
-In the \emph{Evaluation} stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
-Finally, in the last step \emph{Management}, the main goal is to establish scenarios of evaluation based on the `Bussiness-as-usual' and Synergy frameworks.
-This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
-
-An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
-In the following sub-sections, each stage of the methodology is explained.
-
-\hypertarget{planning}{%
-\subsection{Planning}\label{planning}}
-
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{1.5}
-
-\begin{longtable}[c]{|p{1.00in}|p{1.50in}|p{1.50in}|p{2.00in}}
-
-\caption{Terminology used in the deifnition of the spheres}\label{tab:Terminology}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Techno-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Equipement\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Detailed\ models}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Corn\ production\ at\ a\ location}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Value\ chain\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ activities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ corn\ production\ in\ a\ region}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Economy\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Industrial\ sectors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Grain\ farming\ sector}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Eco-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecosystem\ Services\ (ES)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Benefits\ humans\ received\ from\ Nature}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Serviceshead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Area\ providing\ the\ ES\ to\ specific\ users\ of\ that\ servicee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Emissions\ and\ resource\ use\ by\ technological\ systems}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ supply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecological\ capacity\ to\ mediate/sequester/absord\ impacts}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\end{longtable}
-
-\begin{figure}[!ht]
-\includegraphics[width=1\linewidth]{Figures/Systemes} \caption{Notation for assessing techno-ecological synergies}\label{fig:Fig-spheres}
-\end{figure}
-
-\hypertarget{territorial-issues}{%
-\subsubsection{Territorial issues}\label{territorial-issues}}
-
-\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}
-
-\hypertarget{industrial-issues}{%
-\subsubsection{Industrial Issues}\label{industrial-issues}}
+### Industrial Issues
 
@@
 
-\hypertarget{definition-of-the-tech-sphere}{%
-\subsubsection{Definition of the Tech-Sphere}\label{definition-of-the-tech-sphere}}
+### Definition of the Tech-Sphere
 
 It is needed to define two types of scopes: technological and ecological.
-Regarding the technological sphere, three scales are analysed: \emph{Equipment}, \emph{Value chain} and \emph{Economy} scales.
-The technological system at the equipment scale is represented as \(T_{i,j}\) which consists of the \emph{i-th} facility for the \emph{j-th} technological activity.
-For example, in the case of a specific technological activity (\(j = 1\)) such as corn farming, \(T_{1,1}\) and \(T_{1,1}\) represent two different facilities or farms for this activity.
-Technological systems at the value chain scale are indicated as \(\underline{T_{j}}\).
+<!-- Technological -->
+Regarding the technological sphere, three scales are analysed: *Equipment*, *Value chain* and *Economy* scales.
+  <!-- Equipment -->
+The technological system at the equipment scale is represented as $T_{i,j}$ which consists of the *i-th* facility for the *j-th* technological activity. 
+For example, in the case of a specific technological activity ($j = 1$) such as corn farming, $T_{1,1}$ and $T_{1,1}$ represent two different facilities or farms for this activity. 
+  <!-- Value chain -->
+Technological systems at the value chain scale are indicated as $\underline{T_{j}}$.
 These represent average value chain activities within a region, whose information is generally available from inventory databases.
-Technological systems at the economy scale are represented as \(\overline{T_{j}}\).
+  <!-- Economy -->
+Technological systems at the economy scale are represented as $\overline{T_{j}}$.
 These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.
@@
 
-\hypertarget{definition-of-the-eco-sphere}{%
-\subsubsection{Definition of the Eco-sphere}\label{definition-of-the-eco-sphere}}
+### Definition of the Eco-sphere
 
+<!-- Intro -->
 Concerning the ecological sphere, it relies on specifying the geographical regions where the activity is implemented. 
+  <!-- GOal -->
 The main aim is to include explicitly the ecosystem goods and services, and the ecosystem itself in the system boundary. 
@@
 
+<!-- Procedure for the three levels -->
 In this step requires information about ecosystems in which the selected technological systems are nested. 
-Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.
-The ecosystem local to \(T_{i,j}\) is represented by \(E_{i,j}\).
+Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.   <!-- Specification at Equipment scale -->
+The ecosystem local to $T_{i,j}$ is represented by $E_{i,j}$.
 For example, this could be the campus around a manufacturing facility or an agricultural farm.
 
-At the \emph{value chain} scale, the ``local ecosystem'' for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
+<!-- Value chain scale -->
+At the *value chain* scale, the "local ecosystem" for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
 The averaged local ecosystem can be justified as the general landscape characteristics around the specific activity.
@@
 
-Likewise, the local ecosystem for an \emph{economic scale} may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as \(\overline{E}_{j}\).
+Likewise, the local ecosystem for an *economic scale* may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as $\overline{E}_{j}$.
 The aggregation relationships between activities and their surrounding ecosystems at various scales have been depicted by the dotted lines in figure XX.
 
-\hypertarget{scope-of-ecosystems-serviceshed}{%
-\paragraph{Scope of Ecosystems Serviceshed}\label{scope-of-ecosystems-serviceshed}}
+#### Scope of Ecosystems Serviceshed
 
 The largest ecological scale that needs to be considered varies according to the type of ES. 
-The ``largest ecological scale'' is analogous to the concept of a ``serviceshed'' in the ES literature (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
+The "largest ecological scale" is analogous to the concept of a “serviceshed” in the ES literature [@Liu2019g].
 
 It is indicated by outer circles in figure X. 
-The notation used is \(E^{*}_{i,j,k}\) to represent the serviceshed for the \(k-th\) ES, in which the \(i-th\) facility of the \(j-th\) technological activity is nested.
+The notation used is $E^{*}_{i,j,k}$ to represent the serviceshed for the $k-th$ ES, in which the $i-th$ facility of the $j-th$ technological activity is nested.
 
-For example, due to the global flow of \(CO_{2}\), the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else.
+For example, due to the global flow of $CO_{2}$, the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else. 
 Thus, the largest ecological scale to evaluate the carbon sequestration ES is the global scale. 
-In contrast, criteria air pollutants, such as \(SO_{2}\) and \(NO{x}\) can only be transported and regulated by ecosystems within a narrower geographic boundary.
+In contrast, criteria air pollutants, such as $SO_{2}$ and $NO{x}$ can only be transported and regulated by ecosystems within a narrower geographic boundary. 
 Thus, the largest ecological scale to evaluate air quality regulation service is the regional scale. 
@@
 
-If facilities \(T_{1,n}\dots,T_{m,n}\) are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity \(\underline{T}_{n}\).
+If facilities $T_{1,n}\dots,T_{m,n}$ are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity $\underline{T}_{n}$.
 Although such averaging implicitly assumes substitutability by implying that ES produced in one serviceshed can be used by beneficiaries in another serviceshed, this average may have to be used in the absence of spatial information at the serviceshed or smaller scales.
-The average serviceshed is denoted as \(\underline{E}^{*}_{j,k}\) for value chain activities and \(\overline{E}^{*}_{j,k}\) for economic activities.
+The average serviceshed is denoted as $\underline{E}^{*}_{j,k}$ for value chain activities and $\overline{E}^{*}_{j,k}$ for economic activities.
 
-\hypertarget{assesstment-of-demand-and-supply-for-key-es}{%
-\subsection{Assesstment of Demand and Supply for key ES}\label{assesstment-of-demand-and-supply-for-key-es}}
+## Assesstment of Demand and Supply for key ES
 
-\hypertarget{inventory-of-the-technological-systems}{%
-\subsubsection{Inventory of the Technological Systems}\label{inventory-of-the-technological-systems}}
+### Inventory of the Technological Systems
 
+<!-- Intro -->
 Consider a situation where a production flowsheet for an existing or new process is already available.
@@
 
-\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi} (\protect\hyperlink{ref-Liu2019g}{2019}) argued that the conventional Life Cycle Inveentory (LCI) of technological systems can be used as the \textbf{demand} (\(D_{k}\)) for the \(k-th\) ES.
+@Liu2019g argued that the conventional Life Cycle Inveentory (LCI)  of technological systems can be used as the **demand** ($D_{k}$) for the $k-th$ ES.
 It represents the total amount of ES needed to  mitigate the emission or satisfy the resource use.
-For example, the quantity of \(CO_{2}\) emitted by a technology indicate the demand for the carbon sequestration service.
+For example, the quantity of $CO_{2}$ emitted by a technology indicate the demand for the carbon sequestration service.
 
@@
 
-\hypertarget{inventory-of-the-ecological-systems}{%
-\subsubsection{Inventory of the Ecological Systems}\label{inventory-of-the-ecological-systems}}
+### Inventory of the Ecological Systems
 
-Usually, Life cycle analysis do not integrate explicitly models and data about ecosystem goods and services (\protect\hyperlink{ref-ref}{\textbf{ref?}})
-Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the \textbf{supply} (\(S_{k}\)) of the \(k-th\) ES.
+<!-- Intro to problem of LCA -->
+Usually, Life cycle analysis  do not integrate explicitly models and data about ecosystem goods and services [@ref]
+Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the **supply** ($S_{k}$) of the $k-th$ ES.
 
 The main object is to establish the ability of of ecosystems to provide the demanded services. 
-For example, green plants supply the carbon sequestration service by taking up atmospheric \(CO_{2}\) and sequestering it as organic matter through photosynthesis.
+For example, green plants supply the carbon sequestration service by taking up atmospheric $CO_{2}$ and sequestering it as organic matter through photosynthesis. 
 This can be understood as the dependence of production systems on ES. 
@@
 
+<!-- Establish ecological models -->
 There is a research efforts to establish the knowledge about the supply of ES using ecological models such as 
-i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al.~2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..
+  <!-- Ecological models -->
+i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al. 2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  to complete the different models for each ES?.
-\item
-  More references on this
-\end{enumerate}
+1. to complete the different models for each ES?.
+2. More references on this
 
-\hypertarget{allocation}{%
-\subsubsection{Allocation}\label{allocation}}
+### Allocation
 
 One key point is determining the allocation of each ES for multiple users in a selected servicehed.
-Two possible allocation strategies are proportional or avoid allocation (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+<!-- Strategies of allocation -->
+Two possible allocation strategies are proportional or avoid allocation [@ref].
 
+  <!-- Proportional -->
 Proportional allocation splits the ES supply according to selected quantities such as population, demand, or money.
+  <!-- Avoided -->
 Avoided allocation only considers total demand and supply of an ES within the serviceshed.
 
+  <!-- Explaining proportional -->
 Proportional allocation can face similar challenges as allocation between multiple co-products in conventional LCA. 
@@
 
-\begin{itemize}
-\item
-  \emph{Private ownership} implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed.
+- *Private ownership* implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed. 
 For calculating ES supply under a private ownership scenario, land ownership information within the serviceshed is needed
-\item
-  \emph{Public ownership} implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership.
+
+- *Public ownership* implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership. 
 This approach allocates all ES supply from the serviceshed based on the selected properties of the users. 
 If allocation is done in proportion to the demand of ES, the resulting metric is identical to that of the avoided  allocation approach.
-\end{itemize}
 
@@
 
+  <!-- Conclusion -->
 Proportional allocation can provide local sustainability metrics; while for avoided allocation, all activities in a selected serviceshed are assumed to have identical sustainability metrics.
 
-\hypertarget{evaluation}{%
-\subsection{Evaluation}\label{evaluation}}
+## Evaluation
 
-\hypertarget{techno-ecological-synergy}{%
-\subsubsection{Techno-ecological synergy}\label{techno-ecological-synergy}}
+### Techno-ecological synergy
 
-In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied (\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech 2015}).
+In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied [@Bakshi2015]. 
 Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated. 
-For the k-th ES, the sustainability metric \(V_{k}\) is:
+For the k-th ES, the sustainability metric $V_{k}$ is:
 
-\[
+$$
 V_{k} = \frac{S_{k} - D_{k}}{D_{k}}
-\]
+$$
 
-where, \(S_{k}\) and \(D_{k}\) are the supply and demand of the \(k-th\) ES, respectively.
+where, $S_{k}$ and $D_{k}$ are the supply and demand of the $k-th$ ES, respectively.
 
-The basic results from TES consist of of pairs of numbers \({D}\)
+The basic results from TES consist of  of pairs of numbers ${D}$
 
-This metric indicates the extent to which the technological activity is within the relevant ecosystem's carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
-Absolute environmental sustainability for the \(k-th\) ES is defined at the serviceshed scale (indicated by \$\^{}\{*\}) :
+This metric indicates the extent to which the technological activity is within the relevant ecosystem’s carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
+Absolute environmental sustainability for the $k-th$ ES is defined at the serviceshed scale (indicated by $^{*}) :
 
-\[
+$$
 V_{k}^{*} \geq 0, \forall k
-\]
+$$
 
@@
 
-\hypertarget{management}{%
-\subsection{Management}\label{management}}
+## Management
 
-\hypertarget{interpretation}{%
-\subsubsection{Interpretation}\label{interpretation}}
+### Interpretation
 
@@
 
-\includegraphics[width=1\linewidth]{Figures/Quadrantes-sustainability}
+```{r Fig:Quandrantes, out.width='100%'}
+# img_url <- paste0(URL, 'Everest-bio/Quadrantes-sustainability.svg')
+# rsvg_pdf(img_url, "Figures/Quadrantes-sustainability.pdf")
 
-Figure \ref{Figure-TES} present four quadrants that represent the sustainability.
+knitr::include_graphics('Figures/Quadrantes-sustainability.pdf')
+```
+
+Figure \@ref(Figure-TES) present four quadrants that represent the sustainability.
+  <!-- Quadrant I -->
 Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
-In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed's ecological capacity.
+In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed’s ecological capacity. 
 From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
+  <!-- Quadrant III -->
 On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
@@
 This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand. 
-Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support [@ref].
 On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed. 
-Here, the activity is an ``island of sustainability'' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}).
+Here, the activity is an “island of sustainability” [@Wallner1996].
 If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.
 
-\hypertarget{improvements-and-design-in-the-system}{%
-\subsubsection{Improvements and Design in the system}\label{improvements-and-design-in-the-system}}
+### Improvements and Design in the system
 
-In this step, the main goal is to put effort for making changes such that \(V_{i,j,k} \geq 0, \forall\{i,j,k\}\).
+  <!-- Goal of the step -->
+In this step, the main goal is to put effort for making changes such that $V_{i,j,k} \geq 0, \forall\{i,j,k\}$.
 This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services. 
@@
 Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process. 
-If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for \(V\{i,j,k\} \geq 0\) for some values of \(i, j,\) and \(k\).
+If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for $V\{i,j,k\} \geq 0$ for some values of $i, j,$ and $k$. 
 Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc. 
-For such molecules, the only way to satisfy the TES objective of \(V\{i,j,k\} \geq 0\) is by technological changes.
-One approach is to treat such molecules as ``technological nutrients'' and like biological nutrients, to recycle in technological systems.
-Nonrenewable resources will invariably result in values of \(V\{i,j,k\} \geq 0\).
+For such molecules, the only way to satisfy the TES objective of $V\{i,j,k\} \geq 0$ is by technological changes. 
+One approach is to treat such molecules as "technological nutrients" and like biological nutrients, to recycle in technological systems.
+Nonrenewable resources will invariably result in values of $V\{i,j,k\} \geq 0$. 
 Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.
 
-\hypertarget{establishment-on-scenarios}{%
-\subsubsection{Establishment on Scenarios}\label{establishment-on-scenarios}}
+### Establishment on Scenarios
 
 \textcolor{red}{to complete ... }
-
-\hypertarget{case-study-distributing-recycling-via-additive-manufacturing}{%
-\section{Case study: Distributing recycling via Additive Manufacturing}\label{case-study-distributing-recycling-via-additive-manufacturing}}
-
-\hypertarget{indicators-in-ecosystem-services-distributed-recycling-the}{%
-\subsection{Indicators in Ecosystem Services Distributed recycling The}\label{indicators-in-ecosystem-services-distributed-recycling-the}}
-
-\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Bakshi2015}{}%
-Bakshi, Bhavik R, Guy Ziv, and Michael D Lepech.
-2015.
-{``{Techno-ecological synergy: A framework for sustainable engineering}.''} \emph{Environ.
-Sci.
-Technol.} 49 (3): 1752--60.
-\url{https://doi.org/10.1021/es5041442}.
-
-\leavevmode\hypertarget{ref-Bruel2018}{}%
-Bruel, Aurélien, Jakub Kronenberg, Nadège Troussier, and Bertrand Guillaume.
-2019.
-{``{Linking Industrial Ecology and Ecological Economics: A Theoretical and Empirical Foundation for the Circular Economy}.''} \emph{J.
-Ind.
-Ecol.} 23 (1): 12--21.
-\url{https://doi.org/10.1111/jiec.12745}.
-
-\leavevmode\hypertarget{ref-Bruel2016}{}%
-Bruel, Aurélien, Nadège Troussier, Bertrand Guillaume, and Natalia Sirina.
-2016.
-{``{Considering Ecosystem Services in Life Cycle Assessment to Evaluate Environmental Externalities}.''} \emph{Procedia CIRP} 48: 382--87.
-\url{https://doi.org/10.1016/j.procir.2016.03.143}.
-
-\leavevmode\hypertarget{ref-Ceschin2016}{}%
-Ceschin, Fabrizio, and Idil Gaziulusoy.
-2016.
-{``{Evolution of design for sustainability: From product design to design for system innovations and transitions}.''} \emph{Des.
-Stud.} 47 (November): 118--63.
-\url{https://doi.org/10.1016/j.destud.2016.09.002}.
-
-\leavevmode\hypertarget{ref-Costanza1997}{}%
-Costanza, Robert, Ralph D'Arge, Rudolf de Groot, Stephen Farber, Monica Grasso, Bruce Hannon, Karin Limburg, et al.
-1997.
-{``{The value of the world's ecosystem services and natural capital}.''} \emph{Nature} 387 (6630): 253--60.
-\url{https://doi.org/10.1038/387253a0}.
-
-\leavevmode\hypertarget{ref-Costanza2017}{}%
-Costanza, Robert, Rudolf de Groot, Leon Braat, Ida Kubiszewski, Lorenzo Fioramonti, Paul Sutton, Steve Farber, and Monica Grasso.
-2017.
-{``{Twenty years of ecosystem services: How far have we come and how far do we still need to go?}''} Elsevier B.V.
-\url{https://doi.org/10.1016/j.ecoser.2017.09.008}.
-
-\leavevmode\hypertarget{ref-CruzSanchez2020}{}%
-Cruz Sanchez, Fabio A., Hakim Boudaoud, Mauricio Camargo, and Joshua M.
-Pearce.
-2020.
-{``{Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy}.''} \emph{J.
-Clean.
-Prod.} 264 (August): 121602.
-\url{https://doi.org/10.1016/j.jclepro.2020.121602}.
-
-\leavevmode\hypertarget{ref-DeGroot2002}{}%
-De Groot, Rudolf S., Matthew A.
-Wilson, and Roelof M.
-J.
-Boumans.
-2002.
-{``{A typology for the classification, description and valuation of ecosystem functions, goods and services}.''} \emph{Ecol.
-Econ.} 41 (3): 393--408.
-\url{https://doi.org/10.1016/S0921-8009(02)00089-7}.
-
-\leavevmode\hypertarget{ref-Diwekar2021}{}%
-Diwekar, U., A.
-Amekudzi-Kennedy, B.
-Bakshi, R.
-Baumgartner, R.
-Boumans, P.
-Burger, H.
-Cabezas, et al.
-2021.
-{``{A perspective on the role of uncertainty in sustainability science and engineering}.''} \emph{Resour.
-Conserv.
-Recycl.} 164 (January): 105140.
-\url{https://doi.org/10.1016/j.resconrec.2020.105140}.
-
-\leavevmode\hypertarget{ref-Ekins2003}{}%
-Ekins, Paul, Sandrine Simon, Lisa Deutsch, Carl Folke, and Rudolf De Groot.
-2003.
-{``{A framework for the practical application of the concepts of critical natural capital and strong sustainability}.''} \emph{Ecol.
-Econ.} 44 (2-3): 165--85.
-\url{https://doi.org/10.1016/S0921-8009(02)00272-0}.
-
-\leavevmode\hypertarget{ref-Gopalakrishnan2016}{}%
-Gopalakrishnan, Varsha, Bhavik R.
-Bakshi, and Guy Ziv.
-2016.
-{``{Assessing the capacity of local ecosystems to meet industrial demand for ecosystem services}.''} \emph{AIChE J.} 62 (9): 3319--33.
-\url{https://aiche.onlinelibrary.wiley.com/doi/full/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/abs/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/10.1002/aic.15340}.
-
-\leavevmode\hypertarget{ref-Gomez-Baggethun2010}{}%
-Gómez-Baggethun, Erik, Rudolf de Groot, Pedro L.
-Lomas, and Carlos Montes.
-2010.
-{``{The history of ecosystem services in economic theory and practice: From early notions to markets and payment schemes}.''} \emph{Ecol.
-Econ.} 69 (6): 1209--18.
-\url{https://doi.org/10.1016/j.ecolecon.2009.11.007}.
-
-\leavevmode\hypertarget{ref-Harrison2018}{}%
-Harrison, Paula A., Rob Dunford, David N.
-Barton, Eszter Kelemen, Berta Martín-López, Lisa Norton, Mette Termansen, et al.
-2018.
-{``{Selecting methods for ecosystem service assessment: A decision tree approach}.''} \emph{Ecosyst.
-Serv.} 29 (February): 481--98.
-\url{https://doi.org/10.1016/j.ecoser.2017.09.016}.
-
-\leavevmode\hypertarget{ref-Honeck2021}{}%
-Honeck, Erica, Louise Gallagher, Bertrand von Arx, Anthony Lehmann, Nicolas Wyler, Olga Villarrubia, Benjamin Guinaudeau, and Martin A.
-Schlaepfer.
-2021.
-{``{Integrating ecosystem services into policymaking -- A case study on the use of boundary organizations}.''} \emph{Ecosyst.
-Serv.} 49 (June): 101286.
-\url{https://doi.org/10.1016/j.ecoser.2021.101286}.
-
-\leavevmode\hypertarget{ref-Kumar2021}{}%
-Kumar, Rakesh, Anurag Verma, Arkajyoti Shome, Rama Sinha, Srishti Sinha, Prakash Kumar Jha, Ritesh Kumar, et al.
-2021.
-{``{Impacts of Plastic Pollution on Ecosystem Services, Sustainable Development Goals, and Need to Focus on Circular Economy and Policy Interventions}.''} \emph{Sustainability} 13 (17): 9963.
-\url{https://doi.org/10.3390/su13179963}.
-
-\leavevmode\hypertarget{ref-Laurans2013}{}%
-Laurans, Yann, Aleksandar Rankovic, Raphaël Billé, Romain Pirard, and Laurent Mermet.
-2013.
-{``{Use of ecosystem services economic valuation for decision making: Questioning a literature blindspot}.''} Academic Press.
-\url{https://doi.org/10.1016/j.jenvman.2013.01.008}.
-
-\leavevmode\hypertarget{ref-Liu2019g}{}%
-Liu, Xinyu, and Bhavik R.
-Bakshi.
-2019.
-{``{Ecosystem Services in Life Cycle Assessment while Encouraging Techno-Ecological Synergies}.''} \emph{J.
-Ind.
-Ecol.} 23 (2): 347--60.
-\url{https://doi.org/10.1111/jiec.12755}.
-
-\leavevmode\hypertarget{ref-Lomborg2020}{}%
-Lomborg, Bjorn.
-2020.
-{``{Welfare in the 21st century: Increasing development, reducing inequality, the impact of climate change, and the cost of climate policies}.''} \emph{Technol.
-Forecast.
-Soc.
-Change} 156 (July): 119981.
-\url{https://doi.org/10.1016/j.techfore.2020.119981}.
-
-\leavevmode\hypertarget{ref-Martinez-Hernandez2017}{}%
-Martinez-Hernandez, Elias.
-2017.
-{``{Trends in sustainable process design---from molecular to global scales}.''} \emph{Curr.
-Opin.
-Chem.
-Eng.} 17 (August): 35--41.
-\url{https://doi.org/10.1016/j.coche.2017.05.005}.
-
-\leavevmode\hypertarget{ref-MEA2005}{}%
-MEA. 2005. {``{Ecosystems and Human well-being: Synthesis}.''} \href{https://www.islandpress.org}{www.islandpress.org}.
-
-\leavevmode\hypertarget{ref-ONeill2018}{}%
-O'Neill, Daniel W., Andrew L.
-Fanning, William F.
-Lamb, and Julia K.
-Steinberger.
-2018.
-{``{A good life for all within planetary boundaries}.''} \emph{Nat.
-Sustain.} 1 (2): 88--95.
-\url{https://doi.org/10.1038/s41893-018-0021-4}.
-
-\leavevmode\hypertarget{ref-PedersenZari2019}{}%
-Pedersen Zari, Maibritt.
-2019.
-{``{Ecosystem services impacts as part of building materials selection criteria}.''} \emph{Mater.
-Today Sustain.} 3-4.
-\url{https://doi.org/10.1016/j.mtsust.2019.100010}.
-
-\leavevmode\hypertarget{ref-Potschin-Young2018}{}%
-Potschin-Young, M., R.
-Haines-Young, C.
-Görg, U.
-Heink, K.
-Jax, and C.
-Schleyer.
-2018.
-{``{Understanding the role of conceptual frameworks: Reading the ecosystem service cascade}.''} \emph{Ecosyst.
-Serv.} 29 (February): 428--40.
-\url{https://doi.org/10.1016/j.ecoser.2017.05.015}.
-
-\leavevmode\hypertarget{ref-Rockstrom2009}{}%
-Rockström, Johan, Will Steffen, Kevin Noone, Åsa Persson, F.
-Stuart Chapin, Eric F.
-Lambin, Timothy M.
-Lenton, et al.
-2009.
-{``{A safe operating space for humanity}.''} \url{https://doi.org/10.1038/461472a}.
-
-\leavevmode\hypertarget{ref-Santander2020}{}%
-Santander, Pavlo, Fabio A Cruz Sanchez, Hakim Boudaoud, and Mauricio Camargo.
-2020.
-{``{Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach}.''} \emph{Resour.
-Conserv.
-Recycl.} 154 (March): 104531.
-\url{https://doi.org/10.1016/j.resconrec.2019.104531}.
-
-\leavevmode\hypertarget{ref-TEEB2010}{}%
-TEEB. 2010. \emph{{The Economics of Ecosystems and Biodiversity Ecological and Economic Foundations.}} \url{https://doi.org/10.4324/9781849775489}.
-
-\leavevmode\hypertarget{ref-Torres2021}{}%
-Torres, Angélica Valencia, Chetan Tiwari, and Samuel F.
-Atkinson.
-2021.
-{``{Progress in ecosystem services research: A guide for scholars and practitioners}.''} \emph{Ecosyst.
-Serv.} 49 (June): 101267.
-\url{https://doi.org/10.1016/j.ecoser.2021.101267}.
-
-\leavevmode\hypertarget{ref-Wallner1996}{}%
-Wallner, H.
-P., M.
-Narodoslawsky, and F.
-Moser.
-1996.
-{``{Islands of sustainability: A bottom-up approach towards sustainable development}.''} \emph{Environ.
-Plan.
-A} 28 (10): 1763--78.
-\url{https://doi.org/10.1068/a281763}.
-
-\end{CSLReferences}
-
-\end{document}

### 2021-10-20 00-ES/Article/PPQS.Rmd
working on the strcuturation

---
title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PPSQ

<!-- Problem -->
Ecosystem services is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
The problem is that it is complex to link between the local ecosystem services of a territory and the industrial systems placed in it to identify the interactions (as synergy and impacts) with the purpose to create strong sustainability.
From a decision-maker  perspective, there is no a aide decision tool to guide towards a  techno-ecological evaluation of the development of industrial systems in a territory.
<!-- Knowledge Gap -->
There have been major efforts in the valuation of ES given by ecosystems (terrestial,aquatic, atmospheric) to the human well-being. 
Likewise, LCA thinking have putting major attention in the impact of industrial filières to the environmental aspect. 
Nevertheless, few researches have been addressed in aligning the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems, particularity for design industrial landscapes that include the ES in the early-design phases of conception. 
<!-- Context -->
The technical advancements of recycling approaches using additive manufacturing are promising technical intervations to foster plastic recycling at a local level.

<!-- Logic & Evidence for Problem, KG and Context -->

<!-- Conceptual Framework -->
The use of

<!-- Purpose -->
The purpose of this article is to propose a methodological to prioritize ecosystem services in regarding the territorial and industrial priotities. 
This prioritazation is the firs istep to create techno-ecological sinergies between ecological and industrial systems
<!-- Reseacch Questions -->
-

### 2021-10-21 00-ES/PubliER/Draft.tex
First real PPQS 21-10-2021-PPQS.pdf

--- 2021-09-14 00-ES/Article/Draft.tex
@@
 \documentclass[
-  14pt,
-]{extarticle}
+]{article}
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={Distributed recycling for additive manufacturing: an ecosystem services perspective},
+  pdftitle={Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing},
   colorlinks=true,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage[left=2cm, right=2cm,top=3cm,bottom=2cm]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage{longtable,booktabs,array}
@@
 
-\title{Distributed recycling for additive manufacturing: an ecosystem services perspective}
+\title{Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing}
 \author{}
@@
 The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
-No country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
-Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.
+Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).
+This meta-principle is a imperative but not sufficient condition for sustainability.
+Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
+Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems.
+However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
 
-However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
+\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
+They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
+
+The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
+However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
+The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
+This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal.
+This scenario is not true today.
+The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
+The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al.
+2019}).
+It is difficult to provide information about pressure from industrial systems in corporate information systems.
+Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).
+
+According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
+Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al.
+2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al.
+2018}).
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al.
+2021}).
+Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
+Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
+Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).
+
+\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
+
+\textcolor{red}{
+Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
+
 The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
@@
 
-\textcolor{red}{to complete ... }
+The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings {[}70{]}.
+With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings.
+The product-based CICES framework can enable clearer mapping between ecological and economic products.
+The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
+The following levels organize ES according to their divisions, groups and classes.
+At lower levels, more specific services can be defined and characterized.
+For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
+Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
+
+Figure 2.2 demonstrates the hierarchical structure of CICES scheme.
 
@@
 
-\hypertarget{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}{%
-\subsection{Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.}\label{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}}
-
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
-However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
-The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
-This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal.
-This scenario is not true today.
-The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al.
-2019}).
-It is difficult to provide information about pressure from industrial systems in corporate information systems.
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
-Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al.
-2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al.
-2018}).
-Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).
-
-\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
-They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-\textcolor{red}{
-Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
-
 \hypertarget{methodology}{%
@@
 
-The purpose of this article is to propose a conceptual framework to evaluate the synergy of prospective industrial filière considering the technological and ecological spheres.
+The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
+A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
 
@@
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.
-
-\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{1.5}
-
-\begin{longtable}[c]{|p{1.00in}|p{1.50in}|p{1.50in}|p{2.00in}}
-
-\caption{Terminology used in the deifnition of the spheres}\label{tab:Terminology}\\
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\endfirsthead
-
-\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Techno-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Equipement\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Detailed\ models}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Corn\ production\ at\ a\ location}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Value\ chain\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ activities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ corn\ production\ in\ a\ region}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Economy\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Industrial\ sectors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Grain\ farming\ sector}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Eco-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecosystem\ Services\ (ES)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Benefits\ humans\ received\ from\ Nature}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Serviceshead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Area\ providing\ the\ ES\ to\ specific\ users\ of\ that\ servicee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Emissions\ and\ resource\ use\ by\ technological\ systems}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ supply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecological\ capacity\ to\ mediate/sequester/absord\ impacts}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\
-
-\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}
-
-\end{longtable}
-
-\begin{figure}[!ht]
-\includegraphics[width=1\linewidth]{Figures/Systemes} \caption{Notation for assessing techno-ecological synergies}\label{fig:Fig-spheres}
-\end{figure}
-
-\hypertarget{territorial-issues}{%
-\subsubsection{Territorial issues}\label{territorial-issues}}
-
-\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}
-
-\hypertarget{industrial-issues}{%
-\subsubsection{Industrial Issues}\label{industrial-issues}}
-
-\textcolor{red}{ To complete based on article that reading on...}
-
-\hypertarget{definition-of-the-tech-sphere}{%
-\subsubsection{Definition of the Tech-Sphere}\label{definition-of-the-tech-sphere}}
-
-It is needed to define two types of scopes: technological and ecological.
-Regarding the technological sphere, three scales are analysed: \emph{Equipment}, \emph{Value chain} and \emph{Economy} scales.
-The technological system at the equipment scale is represented as \(T_{i,j}\) which consists of the \emph{i-th} facility for the \emph{j-th} technological activity.
-For example, in the case of a specific technological activity (\(j = 1\)) such as corn farming, \(T_{1,1}\) and \(T_{1,1}\) represent two different facilities or farms for this activity.
-Technological systems at the value chain scale are indicated as \(\underline{T_{j}}\).
-These represent average value chain activities within a region, whose information is generally available from inventory databases.
-Technological systems at the economy scale are represented as \(\overline{T_{j}}\).
-These economic sectors, which aggregate similar activities at the value chain scale in the region or country, as in economic input-output models.
-
-In a given problem, the scales at which technologies systems should be modeled are determined based on whether the data are available and whether the activities are site-specific.
-
-\hypertarget{definition-of-the-eco-sphere}{%
-\subsubsection{Definition of the Eco-sphere}\label{definition-of-the-eco-sphere}}
-
-Concerning the ecological sphere, it relies on specifying the geographical regions where the activity is implemented.
-The main aim is to include explicitly the ecosystem goods and services, and the ecosystem itself in the system boundary.
-Thus, interactions within and between technological and ecological systems can be integred explicitly, enabling the assessment of regional variation and absolute environmental sustainability regarding each ES considered.
-
-In this step requires information about ecosystems in which the selected technological systems are nested.
-Each technological activity is nested within a local ecosystem, indicated by the first circle around the rectangle.
-The ecosystem local to \(T_{i,j}\) is represented by \(E_{i,j}\).
-For example, this could be the campus around a manufacturing facility or an agricultural farm.
-
-At the \emph{value chain} scale, the ``local ecosystem'' for an activity may be approximated by aggregating similar activities in a specific geographical region, which is similar to the approach used for building a conventional LCI database.
-The averaged local ecosystem can be justified as the general landscape characteristics around the specific activity.
-For instance, electricity generation from coal-fired power plants needs a large amount of water for cooling: thus, it is likely that these facilities are located close to water sources.
-
-Likewise, the local ecosystem for an \emph{economic scale} may also be defined in the same manner, since an economic sector aggregates similar value chain scale activities, and may be denoted as \(\overline{E}_{j}\).
-The aggregation relationships between activities and their surrounding ecosystems at various scales have been depicted by the dotted lines in figure XX.
-
-\hypertarget{scope-of-ecosystems-serviceshed}{%
-\paragraph{Scope of Ecosystems Serviceshed}\label{scope-of-ecosystems-serviceshed}}
-
-The largest ecological scale that needs to be considered varies according to the type of ES.
-The ``largest ecological scale'' is analogous to the concept of a ``serviceshed'' in the ES literature (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
-
-It is indicated by outer circles in figure X.
-The notation used is \(E^{*}_{i,j,k}\) to represent the serviceshed for the \(k-th\) ES, in which the \(i-th\) facility of the \(j-th\) technological activity is nested.
-
-For example, due to the global flow of \(CO_{2}\), the carbon sequestration ES provided by any part of the world can potentially satisfy the demand of this service anywhere else.
-Thus, the largest ecological scale to evaluate the carbon sequestration ES is the global scale.
-In contrast, criteria air pollutants, such as \(SO_{2}\) and \(NO{x}\) can only be transported and regulated by ecosystems within a narrower geographic boundary.
-Thus, the largest ecological scale to evaluate air quality regulation service is the regional scale.
-Larger ecological scales, such as a global scale, may not be relevant to this service.
-
-If facilities \(T_{1,n}\dots,T_{m,n}\) are located in different serviceheds for a particular ES, these servicesheds need to be averages for value chain activity \(\underline{T}_{n}\).
-Although such averaging implicitly assumes substitutability by implying that ES produced in one serviceshed can be used by beneficiaries in another serviceshed, this average may have to be used in the absence of spatial information at the serviceshed or smaller scales.
-The average serviceshed is denoted as \(\underline{E}^{*}_{j,k}\) for value chain activities and \(\overline{E}^{*}_{j,k}\) for economic activities.
-
-\hypertarget{assesstment-of-demand-and-supply-for-key-es}{%
-\subsection{Assesstment of Demand and Supply for key ES}\label{assesstment-of-demand-and-supply-for-key-es}}
-
-\hypertarget{inventory-of-the-technological-systems}{%
-\subsubsection{Inventory of the Technological Systems}\label{inventory-of-the-technological-systems}}
-
-Consider a situation where a production flowsheet for an existing or new process is already available.
-A preliminary assessment of these environmental interventions must be carried out to obtain information about the different types of demands created by manufacturing facilities, and the kind of ecosystems that can supply these services to satisfy the demand.
-
-\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi} (\protect\hyperlink{ref-Liu2019g}{2019}) argued that the conventional Life Cycle Inveentory (LCI) of technological systems can be used as the \textbf{demand} (\(D_{k}\)) for the \(k-th\) ES.
-It represents the total amount of ES needed to mitigate the emission or satisfy the resource use.
-For example, the quantity of \(CO_{2}\) emitted by a technology indicate the demand for the carbon sequestration service.
-
-Environmentally-extended input-output (EEIO) data for activities at equipment, value chain and economy scale, LCI databases, and detailed engineering models can supply information to quantify the respective demand for each service.
-Also, inventory of technological systems comprises all relevant flows associated with the functional unit, regardless of the scale at which technological activities are modeled.
-
-\hypertarget{inventory-of-the-ecological-systems}{%
-\subsubsection{Inventory of the Ecological Systems}\label{inventory-of-the-ecological-systems}}
-
-Usually, Life cycle analysis do not integrate explicitly models and data about ecosystem goods and services (\protect\hyperlink{ref-ref}{\textbf{ref?}})
-Therefore, this information needs to be added directly to a conventional inventory, which we refer to as the \textbf{supply} (\(S_{k}\)) of the \(k-th\) ES.
-
-The main object is to establish the ability of of ecosystems to provide the demanded services.
-For example, green plants supply the carbon sequestration service by taking up atmospheric \(CO_{2}\) and sequestering it as organic matter through photosynthesis.
-This can be understood as the dependence of production systems on ES.
-Alternatively, it can be interpreted as the ES that nature can supply in order to produce the functional unit.
-
-There is a research efforts to establish the knowledge about the supply of ES using ecological models such as
-i-Tree (USDA2016b), EPIC (EPIC 2016), InVEST(Nel- son et al.~2009), and remote sensing data from sources such as the National Land Cover Database (NLCD) (NLCD 2011) and EnviroAtlas..
-
-\textcolor{red}{to complete ... }
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  to complete the different models for each ES?.
-\item
-  More references on this
-\end{enumerate}
-
-\hypertarget{allocation}{%
-\subsubsection{Allocation}\label{allocation}}
-
-One key point is determining the allocation of each ES for multiple users in a selected servicehed.
-Two possible allocation strategies are proportional or avoid allocation (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-
-Proportional allocation splits the ES supply according to selected quantities such as population, demand, or money.
-Avoided allocation only considers total demand and supply of an ES within the serviceshed.
-
-Proportional allocation can face similar challenges as allocation between multiple co-products in conventional LCA.
-Allocating an ES between multiple users is analogous to determining their right of use. Two ethics of interpreting this are as follows:
-
-\begin{itemize}
-\item
-  \emph{Private ownership} implies that land owners own the ES produced from their land. In addition, they can also claim an allocated fraction of ES from publicly owned land in the serviceshed.
-  For calculating ES supply under a private ownership scenario, land ownership information within the serviceshed is needed
-\item
-  \emph{Public ownership} implies that ES produced from all land belongs equally to every activity in the serviceshed, regardless of their ownership.
-  This approach allocates all ES supply from the serviceshed based on the selected properties of the users.
-  If allocation is done in proportion to the demand of ES, the resulting metric is identical to that of the avoided allocation approach.
-\end{itemize}
-
-However, there could be practical issues with this land ownership based allocation of ES are the public availability of land ownership data and the possible applicability of other ES ownership schemes.
-
-Proportional allocation can provide local sustainability metrics; while for avoided allocation, all activities in a selected serviceshed are assumed to have identical sustainability metrics.
-
-\hypertarget{evaluation}{%
-\subsection{Evaluation}\label{evaluation}}
-
-\hypertarget{techno-ecological-synergy}{%
-\subsubsection{Techno-ecological synergy}\label{techno-ecological-synergy}}
-
-In this step, the Techno-Ecological Synergy (TES) Sustainability Metrics is applied (\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech 2015}).
-Once the demand and supply are quantified and allocated, TES sustainability metrics may be calculated.
-For the k-th ES, the sustainability metric \(V_{k}\) is:
-
-\[
-V_{k} = \frac{S_{k} - D_{k}}{D_{k}}
-\]
-
-where, \(S_{k}\) and \(D_{k}\) are the supply and demand of the \(k-th\) ES, respectively.
-
-The basic results from TES consist of of pairs of numbers \({D}\)
-
-This metric indicates the extent to which the technological activity is within the relevant ecosystem's carrying capacity, and may be calculated at each of the scales discussed in Step 1 to obtain indicators at local, serviceshed and average scales.
-Absolute environmental sustainability for the \(k-th\) ES is defined at the serviceshed scale (indicated by \$\^{}\{*\}) :
-
-\[
-V_{k}^{*} \geq 0, \forall k
-\]
-
-Strong sustainability requires satisfaction of this criterion in the corresponding servicesheds for each ES.
-If metrics are calculated for the average serviceshed, then satisfaction of equation (2) suggests only weak sustainability, since it implicitly assumes that the absolute environmental sustainability in one serviceshed can be used to compensate for unsustainability in another.
-Thus, the unsustainability in some servicesheds would be overlooked due to the averaging.
-This problem would be potentially solved by disaggregating the average serviceshed and calculating the metrics for each component serviceshed separately.
-However, this will require more data.
-
-\hypertarget{management}{%
-\subsection{Management}\label{management}}
-
-\hypertarget{interpretation}{%
-\subsubsection{Interpretation}\label{interpretation}}
-
-A hierarchy of metrics
-The Techno-Ecological Synergy (TES) metric obtained are multi-scale and multidimensional.
-Therefore, these metrics may be interprested by plotting the local and servicehed scale metrics.
-
-\includegraphics[width=1\linewidth]{Figures/Quadrantes-sustainability}
-
-Figure \ref{Figure-TES} present four quadrants that represent the sustainability.
-Quadrant I illustrated the most desirable situation where local and serviceshed scale metrics are sustainable.
-In other words, the industrial activity is within the ecological capacity of local ecosystems, and global activities in the serviceshed are also within the serviceshed's ecological capacity.
-From a perspective of absolute environmental sustainability, all systems should strive toward or maintain this situation.
-On the other hand, Quadrant III represents the most undesirable situation where local neither servicehed scale are sustainable.
-Ecological overshoot exists at both local and serviceshed scales.
-Efforts toward improvement should reduce emissions and restore ecosystems at both
-
-Regarding the quandrant II, it represents the situation where the ES is used sustainably in the serviceshed but not at the local scale.
-This implies that the activity is relying on ES outside its locality but within the serviceshed to satisfy its demand.
-Improvement of a system in this quadrant could involve enhancing local sustainability by either reducing demand, increasing the local ES supply, or payment to other activities in the serviceshed that provide support (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-On the contrary in Quadrant IV, the ES is used sustainably in the local region, but not in the serviceshed.
-Here, the activity is an ``island of sustainability'' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}).
-If all activities within a serviceshed strive toward becoming such islands, it will help in achieving serviceshed scale environmental sustainability.
-
-\hypertarget{improvements-and-design-in-the-system}{%
-\subsubsection{Improvements and Design in the system}\label{improvements-and-design-in-the-system}}
-
-In this step, the main goal is to put effort for making changes such that \(V_{i,j,k} \geq 0, \forall\{i,j,k\}\).
-This may be achieved by enhancing technological efficiency to reduce the demand for ecosystem services, or by restoring and protecting ecological systems to increase the supply of ecosystem services.
-This final vision is to encourage engineering and human activities to be within ecological constraints.
-
-Three main elements in terms of design is expected in this step
-The first is the explicit recognition of the inherent interdependencies between technological and ecological systems.
-Such recognition enables a better understanding of the resiliency of coupled techno-ecological systems during any enhancement of technological efficiency or restoration of ecological service provision.
-The collaboration with multi-stakeholders is expected in this step.
-
-Typically, changes are likely to be easiest at the smallest scale, such as a manufacturing process.
-If there are emissions that cannot be absorbed or mitigated by ecosystems, then it will be impossible for \(V\{i,j,k\} \geq 0\) for some values of \(i, j,\) and \(k\).
-Examples include processes that emit molecules that do not occur in nature such as chlorofluorocarbons, various synthetic polymers, many pharmaceutical molecules, etc.
-For such molecules, the only way to satisfy the TES objective of \(V\{i,j,k\} \geq 0\) is by technological changes.
-One approach is to treat such molecules as ``technological nutrients'' and like biological nutrients, to recycle in technological systems.
-Nonrenewable resources will invariably result in values of \(V\{i,j,k\} \geq 0\).
-Therefore, this framework will discourage their extraction and encourage their reuse and recycling by efforts such as industrial symbiosis.
-
-\hypertarget{establishment-on-scenarios}{%
-\subsubsection{Establishment on Scenarios}\label{establishment-on-scenarios}}
-
-\textcolor{red}{to complete ... }
+Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
 
@@
 
+\hypertarget{results-of-the}{%
+\section{Results of the}\label{results-of-the}}
+
+\hypertarget{planning-1}{%
+\subsection{Planning}\label{planning-1}}
+
+\hypertarget{goal-and-scope-definition}{%
+\subsubsection{Goal and scope definition}\label{goal-and-scope-definition}}
+
+The system depicted is presented in the figure.
+The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped by .
+Because Es are expected to be more relevant in the
+
+The goal of this study is to evaluate and compare the change in ES provisioning
+The functional unit (FU) is represented by \emph{1kg of recycled filament delivered at school}.
+
+\newpage
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Bakshi2018}{}%
+Bakshi, Bhavik R, Timothy G Gutowski, and Dusan P Sekulic.
+2018.
+{``{Claiming Sustainability: Requirements and Challenges}.''} \emph{ACS Sustain.
+Chem.
+Eng.} 6 (3): 3632--39.
+\url{https://doi.org/10.1021/acssuschemeng.7b03953}.
+
 \leavevmode\hypertarget{ref-Bakshi2015}{}%
@@
 2015.
-{``{Techno-ecological synergy: A framework for sustainable engineering}.''} \emph{Environ.
+{``{Techno-Ecological Synergy: A Framework for Sustainable Engineering}.''} \emph{Environ.
 Sci.
@@
 2019.
-{``{Ecosystem Services in Life Cycle Assessment while Encouraging Techno-Ecological Synergies}.''} \emph{J.
+{``{Ecosystem Services in Life Cycle Assessment while Encouraging Techno‐Ecological Synergies}.''} \emph{J.
 Ind.
@@
 
+\leavevmode\hypertarget{ref-Rodrigues2021}{}%
+Rodrigues, Jérémy, Natacha Gondran, Adrien Beziat, and Valérie Laforest.
+2021.
+{``{Application of the absolute environmental sustainability assessment framework to multifunctional systems -- The case of municipal solid waste management}.''} \emph{J.
+Clean.
+Prod.} 322: 129034.
+\url{https://doi.org/10.1016/j.jclepro.2021.129034}.
+
 \leavevmode\hypertarget{ref-Santander2020}{}%

### 2021-10-21 00-ES/PubliER/PPQS.Rmd
First real PPQS 21-10-2021-PPQS.pdf

---
title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
bibliography: library.bib
link-citations: yes
linkcolor: blue
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PPSQ

<!-- Intro -->
Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
<!-- Problem -->
The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
<!-- Conceptual Framework (broad theoretical) -->
   <!-- ES valuation and Urban  ES-->
There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being [@Costanza2017; @DeGroot2012; @MEA2005; @Costanza1997], and  great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)[@RoyHaines-Young2018]. 
<!-- Knowledge Gap -->
However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
<!-- Logic & Evidence for Problem, KG and Context -->
   <!-- LCA -->
In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021]. 
   <!-- LCA AND ES -->
Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales [@Liu2019g].
This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
<!-- Purpose Statement -->
The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
   <!-- Expand a methodology -->
This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
<!-- Context -->
This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France. 
The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
<!-- Reseacch Questions (NOt add more problems) -->
This study seeks to address the following questions:

- What are the main ecosystem services from a urban territorial perspective that DRAM can improve?.
- How to make the connections of ES with the industrial systems?. 
- How to connect the territorial issues and the industrial issues using the CICES framework to prioritize?

# References

### 2021-10-21 00-ES/PubliER/PubliER.Rmd
First real PPQS 21-10-2021-PPQS.pdf

--- 2021-10-20 00-ES/Article/Draft.Rmd
@@
 
-## Distributed recycling via additive manufacturing
-
-<!-- DRAM -->
-Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management [@CruzSanchez2020; @Santander2020]. 
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
-<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
-
-\textcolor{red}{ To complete ...}
-
 # Methodology
@@
 
-## Planning
+# Results
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+## Step I - Definition the Industrial system : Distributed recycling via additive manufacturing
 
-# Case study: Distributing recycling via Additive Manufacturing
-## Indicators in Ecosystem Services Distributed recycling The
+<!-- Distributed Fabrication -->
+Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication
 
-\newpage
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].
+The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
+To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
+While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
+However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
+<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
+Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
 
-# Results of the
-
-## Planning
-
-### Goal and scope definition
-
-The system depicted is presented in the figure.
+The system depicted is presented in the figure XX.
 The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
@@
 
+## Step II - Ecosystem services Priorities at the territorial level: Nancy, France
+
+Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+
+## Step III - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems
+
+## Step II - Identifying the Hot spot of the
+
+# Discussion and perspective of the analysis
+
+# Conclusions
+
 \newpage

### 2021-10-21 00-ES/PubliER/PubliER.tex
First real PPQS 21-10-2021-PPQS.pdf

--- 2021-10-21 00-ES/PubliER/Draft.tex
@@
 
-\hypertarget{distributed-recycling-via-additive-manufacturing}{%
-\subsection{Distributed recycling via additive manufacturing}\label{distributed-recycling-via-additive-manufacturing}}
-
-Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al.
-2020}; \protect\hyperlink{ref-Santander2020}{Santander et al.
-2020}).
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
-
-\textcolor{red}{ To complete ...}
-
 \hypertarget{methodology}{%
@@
 
-\hypertarget{planning}{%
-\subsection{Planning}\label{planning}}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+\hypertarget{step-i---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}{%
+\subsection{Step I - Definition the Industrial system : Distributed recycling via additive manufacturing}\label{step-i---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}}
 
-\hypertarget{case-study-distributing-recycling-via-additive-manufacturing}{%
-\section{Case study: Distributing recycling via Additive Manufacturing}\label{case-study-distributing-recycling-via-additive-manufacturing}}
+Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication
 
-\hypertarget{indicators-in-ecosystem-services-distributed-recycling-the}{%
-\subsection{Indicators in Ecosystem Services Distributed recycling The}\label{indicators-in-ecosystem-services-distributed-recycling-the}}
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al.
+2020}; \protect\hyperlink{ref-Santander2020}{Santander et al.
+2020}).
+The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
+To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
+While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
+However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
+Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
 
-\newpage
-
-\hypertarget{results-of-the}{%
-\section{Results of the}\label{results-of-the}}
-
-\hypertarget{planning-1}{%
-\subsection{Planning}\label{planning-1}}
-
-\hypertarget{goal-and-scope-definition}{%
-\subsubsection{Goal and scope definition}\label{goal-and-scope-definition}}
-
-The system depicted is presented in the figure.
+The system depicted is presented in the figure XX.
 The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped by .
@@
 The functional unit (FU) is represented by \emph{1kg of recycled filament delivered at school}.
+
+\hypertarget{step-ii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}{%
+\subsection{Step II - Ecosystem services Priorities at the territorial level: Nancy, France}\label{step-ii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}}
+
+Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+
+\hypertarget{step-iii---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}{%
+\subsection{Step III - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems}\label{step-iii---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}}
+
+\hypertarget{step-ii---identifying-the-hot-spot-of-the}{%
+\subsection{Step II - Identifying the Hot spot of the}\label{step-ii---identifying-the-hot-spot-of-the}}
+
+\hypertarget{discussion-and-perspective-of-the-analysis}{%
+\section{Discussion and perspective of the analysis}\label{discussion-and-perspective-of-the-analysis}}
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 

### 2021-10-22 00-ES/PubliER/PubliER.Rmd
dibujo conceptual

@@
 #output: rticles::tf_article
-# abstract
+abstract: |
+    <!-- Intro -->
+    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
+    <!-- Problem -->
+    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
+    From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
+    <!-- Conceptual Framework (broad theoretical) -->
+       <!-- ES valuation and Urban  ES-->
+    There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being [@Costanza2017; @DeGroot2012; @MEA2005; @Costanza1997], and  great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)[@RoyHaines-Young2018].
+    <!-- Knowledge Gap -->
+    However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+    <!-- Logic & Evidence for Problem, KG and Context -->
+       <!-- LCA -->
+    In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021].
+       <!-- LCA AND ES -->
+    Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales [@Liu2019g].
+    This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
+    <!-- Purpose Statement -->
+    The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
+       <!-- Expand a methodology -->
+    This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
+    The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
+    <!-- Context -->
+    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
+    The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
 always_allow_html: true
@@
 
-# img_url <- paste0(URL, 'Everest-bio/Methodology.svg')
+# img_url <- paste0(URL, 'Everest-bio/Publier/Methodology.svg')
 # rsvg_pdf(img_url, "Figures/Methodology.pdf")
@@
 <!-- Distributed Fabrication -->
-Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication
+Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].
 
-In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].
 The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 

### 2021-10-22 00-ES/PubliER/PubliER.tex
dibujo conceptual

@@
 \maketitle
+\begin{abstract}
+Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
+The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
+From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
+There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being (\protect\hyperlink{ref-Costanza2017}{Costanza et al.
+2017}, \protect\hyperlink{ref-Costanza1997}{1997}; \protect\hyperlink{ref-DeGroot2012}{Groot et al.
+2012}; \protect\hyperlink{ref-MEA2005}{MEA 2005}), and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)(\protect\hyperlink{ref-RoyHaines-Young2018}{Roy Haines-Young and Potschin 2018}).
+However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life (\protect\hyperlink{ref-Mahmud2021}{Mahmud et al.
+2021}; \protect\hyperlink{ref-Pryshlakivsky2021}{Pryshlakivsky and Searcy 2021}).
+Recently, several research efforts reported accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
+This techno-ecological synergy (TES) (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}; \protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech 2015}) to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
+The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
+This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
+The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
+This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
+The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
+\end{abstract}
 
@@
 
-Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication
-
+Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
 In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al.
@@
 2020}).
+
 The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
@@
 
+\leavevmode\hypertarget{ref-DeGroot2012}{}%
+Groot, Rudolf de, Luke Brander, Sander van der Ploeg, Robert Costanza, Florence Bernard, Leon Braat, Mike Christie, et al.
+2012.
+{``{Global estimates of the value of ecosystems and their services in monetary units}.''} \emph{Ecosyst.
+Serv.} 1 (1): 50--61.
+\url{https://doi.org/10.1016/j.ecoser.2012.07.005}.
+
 \leavevmode\hypertarget{ref-Harrison2018}{}%
@@
 
+\leavevmode\hypertarget{ref-Mahmud2021}{}%
+Mahmud, Roksana, Sheikh Moniruzzaman Moni, Karen High, and Michael Carbajales-Dale.
+2021.
+{``{Integration of techno-economic analysis and life cycle assessment for sustainable process design -- A review}.''} Elsevier.
+\url{https://doi.org/10.1016/j.jclepro.2021.128247}.
+
 \leavevmode\hypertarget{ref-Martinez-Hernandez2017}{}%
@@
 
+\leavevmode\hypertarget{ref-Pryshlakivsky2021}{}%
+Pryshlakivsky, Jonathan, and Cory Searcy.
+2021.
+{``{Life Cycle Assessment as a decision-making tool: Practitioner and managerial considerations}.''} Elsevier.
+\url{https://doi.org/10.1016/j.jclepro.2021.127344}.
+
 \leavevmode\hypertarget{ref-Rockstrom2009}{}%
@@
 \url{https://doi.org/10.1016/j.jclepro.2021.129034}.
+
+\leavevmode\hypertarget{ref-RoyHaines-Young2018}{}%
+Roy Haines-Young, by, and Marion Potschin.
+2018.
+{``{Common International Classification of Ecosystem Services (CICES) V5.1 Guidance on the Application of the Revised Structure}.''} \href{https://www.cices.eu}{www.cices.eu}.
 

### 2021-10-25 slides/index.Rmd
Presentation for tool preparation complete from CICES

@@
 
+library(readxl)
+library(here)
+library(flextable)
 library(tidyverse)
+
 # Link for the Figures
 URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
+
+# CICES File
+#file_cices <- list.files("../data/CICES")
+CICES <- read_excel(here("../data/CICES/Finalised-V5.1_18032018.xlsx"), sheet = "CICES V5.1",  skip = 4 )
 ```
@@
 ---
+# Tool for Everest Bio
+
+.pull-left[
+## Goal:
+The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
+]
+
+---
+## Structure of the tool
+
+1. Identification of the Territory
+1. Two types of actors:
+   1. Industrial Agent: **Identification of LCI of the Process**
+   1. Territorial Agent: **Identification of the Urban ES priorities**
 
@@
 
-class: middle, left
-background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
-background-position: center
-background-size: contain
-
----
 class: middle
 
-# EU projects
+# CICES
 
-.pull-left[
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
-```
-https://www.smagrinet.eu/
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
-```
-
-https://digiterri.eu/
-
-] 
-.pull-right[
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
-```
-
-https://www.inedit-project.eu/
-]
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.bg-yellow[Cultural]
 
@@
 
+# Provisioning Services (biotic & Abiotic)
+## Plants
+
+.pull-left[
+**Territorial Question**
+
+*Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are cultivated plants (Terrestrial or Aquatic) impacted in certain level by the use of your technology or proposition ?*
+
+]
+
+```{r}
+library(kableExtra)
+# Version Flextable
+# CICES_filter <- function(ID, size = 15, ...)
+# {
+#   Table <- CICES %>% select(Group, Class, Code) %>% 
+#   filter(Code %in% ID) %>% 
+#   flextable() %>% 
+#   merge_v( j = "Group") %>% 
+#   fontsize(size = size,  part = "all") %>% 
+#   width(width = c(2,8,1))
+#   return(Table)
+# }
+
+# Version Kableextrs
+CICES_filter <- function(ID, size = 15, ...)
+{
+  Table <- 
+    CICES %>% select(Group, Class, Code, 'Example Service') %>% 
+    filter(Code %in% ID) %>% 
+    kbl() %>%
+    #kable_paper("striped", full_width = TRUE) %>% 
+    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = size)  %>% 
+  collapse_rows(columns = 1:1)
+
+  return(Table)
+}
+
+CICES_filter(ID=c("1.1.1.1", "1.1.1.2", "1.1.1.3", 
+                     "1.1.2.1", "1.1.2.2", "1.1.2.3"), size = 15)
+
+```
+
+---
+# Provisioning Services (biotic & Abiotic)
+## Animals
+
+.pull-left[
+**Territorial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.1.3.1", "1.1.3.2", "1.1.3.3", "1.1.4.1", "1.1.4.2", "1.1.4.3"), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Wild Animals & Plants
+
+.pull-left[
+**Territorial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.1.5.1","1.1.5.2","1.1.5.3","1.1.6.1","1.1.6.2","1.1.6.3"), size = 13)
+```
+
+---
+# Provisioning Services (biotic & Abiotic)
+## Genetic Material
+
+.pull-left[
+**Territorial Question**
+
+*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) an important element for the territory ?*	]
+
+.pull-right[
+**Industrial Question**
+
+*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) affected by the use of your technology int the territory ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.2.1.1","1.2.1.2","1.2.1.3","1.2.2.1","1.2.2.2","1.2.2.3"), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Water
+
+.pull-left[
+**Territorial Question**
+
+*Is Water (for nutrition, materials or energy) an issue for the territory?*	]
+
+.pull-right[
+**Industrial Question**
+
+*The is the impact of LCI?*
+]
+
+```{r ES_Provision_water}
+CICES_filter(ID=c("4.2.1.1", "4.2.1.2", "4.2.1.3", "4.2.1.4", "4.2.2.1", "4.2.2.2", "4.2.2.3"
+), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Others Abiotic
+
+```{r ES_Provision_Abiotic}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 15)
+
+```
+
+---
+
+class: middle
+
+# CICES
+
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.bg-yellow[Cultural]
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+
+## Biochemical or physical inputs to ecosystems
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.1.1.1", "2.1.1.2", "2.1.2.1", "2.1.2.2", "2.1.2.3"), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.1.1", "2.2.1.2", "2.2.1.3", "2.2.1.4", "2.2.1.5" ), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.2.1", "2.2.2.2", "2.2.2.3", "2.2.3.1", "2.2.3.2", "2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
+```
+
+---
+
+# CICES
+
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.blue[Cultural]
+
+---
+
+# Cultural (Biotic) 
+## Direct contact with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("3.1.1.1", "3.1.1.2", "3.1.2.1", "3.1.2.2", "3.1.2.3", "3.1.2.4"), size = 15)
+```
+
+---
+
+# Cultural (Biotic) 
+## Indirect contact with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2"), size = 15)
+
+```
+
+---
+
+# Cultural (Abiotic) 
+## Direct and Indirect link with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("6.1.1.1","6.1.2.1","6.2.1.1","6.2.2.1"), size = 15)
+```
+
+---
 class: middle, center
 
-Thanks !
+# Thanks !
 

### 2021-10-25 slides/partials/EU-projects.Rmd
Presentation for tool preparation complete from CICES

---
class: middle, left
exclude: true

background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
background-position: center
background-size: contain

---
class: middle
exclude: true

# EU projects

.pull-left[
```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
```
https://www.smagrinet.eu/

```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
```

https://digiterri.eu/

] 
.pull-right[

```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
```

https://www.inedit-project.eu/
]

### 2021-10-26 00-ES/xar-EB-ES/xar-EB-ES.Rmd
reorganizando las vainas de los folderes

--- 2021-09-03 00-ES/ES-Literature/slides/Eco-Services.Rmd
@@
     css: xaringan-themer.css
+    seal: false
     nature:
@@
         scroll: false # disable slide transitions by scrolling
+always_allow_html: true
 ---
 
-```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
+```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
 library(tidyverse)
@@
 library(xaringanthemer)
+library(fontawesome)
+library(readxl)
+library(here)
 
-```
+source("xaringan-themer.R")
 
-```{r setup, include=FALSE}
 options(htmltools.dir.version = FALSE)
@@
 #library(xaringanBuilder)
-#build_pdf("ES-presentation.Rmd")
+#build_pdf("index.Rmd")
 
@@
 xaringanExtra::use_panelset()
+
+#xaringanExtra::use_share_again()
+
+## Loading data
+CICES <- read_excel(here("../../data/CICES/Finalised-V5.1_18032018.xlsx"), sheet = "CICES V5.1",  skip = 4 )
+
 ```
 
-```{r xaringan-themer, include=FALSE, warning=FALSE}
+class: title-slide, left, bottom
 
-style_duo_accent(
-  primary_color = "#1381B0",
-  secondary_color = "#FF961C",
-  inverse_header_color = "#FFFFFF", 
-  base_font_size = "24px",
-  colors = c(
-    red = "#f34213",
-    purple = "#3e2f5b",
-    orange = "#ff8811",
-    green = "#d9edc2",
-    white = "#FFFFFF",
-    grey = "#F5F5F5"
-  ),
-   extra_css = list(
-    ".remark-slide-content h1" = list(
-      "margin-bottom" = 0, 
-      "margin-top" = 0),
-     ".remark-slide-content > h1:first-of-type" = list(
-       "margin-top" = "5px",
-       "margin-bottom" = "10px"
-     ),
-    ".remark-slide-content > h2:first-of-type" = list(
-       "margin-top" = "5px",
-       "margin-bottom" = "10px"
-     ),
-    ".remark-slide-content > h3:first-of-type" = list(
-       "margin-top" = "5px",
-       "margin-bottom" = "10px"
-     ),
-    ".remark-slide-content" = list (
-        "padding-top" =  "25px",
-        "padding-left" =  "50px",
-        "padding-right" =  "50px",
-        "padding-bottom" =  "25px"
-    ),
+```{r, out.width = '250px', fig.align='right'}
+knitr::include_graphics(paste0(URL, 'Logos/ERPI/UL-ERPI.png'))
+```
 
-    ".small" = list("font-size" = "90%"),
+`r fa("map-marker-alt", fill = "steelblue")` `r rmarkdown::metadata$date`
 
-    ".Large , .Large .remark-code, .Large .remark-inline-code" = list("font-size"= "144%"), 
-    ".large , .large .remark-code, .large .remark-inline-code" = list("font-size"= "120%"), 
-    ".small , .small .remark-code, .small .remark-inline-code" = list("font-size"= "90%"), 
-    ".footnotesize, 
-    .footnotesize .remark-code, .footnotesize .remark-inline-code" = list( "font-size"= "80%"),
+# `r fa("comment", fill = "steelblue")` `r rmarkdown::metadata$title`
 
-    ".scriptsize , .scriptsize .remark-code, .scriptsize .remark-inline-code" = list("font-size"= "70%"),
-    ".tiny , .tiny .remark-code, .tiny .remark-inline-code" = list("font-size"= "60%"),
+`r fa("user-friends", fill = "steelblue")` `r rmarkdown::metadata$subtitle`
 
-    ".footnote" = list (
-        "position" =  "absolute",
-        "bottom" =  "0",
-        "padding-right" = "8em", # to avoid the page numbering 
-        "font-size" =  "60%"
-    ),
-    ".fn" = list(
-      "vertical-align" = "super",
-      "font-size" = "60%",
-      "color" = "purple"
-    )
-
-  )
-)
-
-```
+---
 
@@
 
-# Valorization of SE
-
----
-
 # Strong and Weak Sustainability
@@
 Weak: Coming from Economical rationality
+
+---
+# Tool for Everest Bio
+
+.pull-left[
+## Goal:
+The main foal of the tool will be the identification of ES that are priorities for an industrial system inside a Territory.
+]
+
+---
+## Structure of the tool
+
+1. Identification of the Territory
+1. Two types of actors:
+   1. Industrial Agent: **Identification of LCI of the Process**
+   1. Territorial Agent: **Identification of the Urban ES priorities**
+
+---
+
+class: middle
+
+# CICES
+
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.bg-yellow[Cultural]
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Plants
+
+.pull-left[
+**Territorial Question**
+
+*Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are cultivated plants (Terrestrial or Aquatic) impacted in certain level by the use of your technology or proposition ?*
+
+]
+
+```{r}
+
+library(kableExtra)
+# Version Flextable
+# CICES_filter <- function(ID, size = 15, ...)
+# {
+#   Table <- CICES %>% select(Group, Class, Code) %>% 
+#   filter(Code %in% ID) %>% 
+#   flextable() %>% 
+#   merge_v( j = "Group") %>% 
+#   fontsize(size = size,  part = "all") %>% 
+#   width(width = c(2,8,1))
+#   return(Table)
+# }
+
+# Version Kableextrs
+CICES_filter <- function(ID, size = 15, ...)
+{
+  Table <- 
+    CICES %>% select(Group, Class, Code, 'Example Service') %>% 
+    filter(Code %in% ID) %>% 
+    kbl() %>%
+    #kable_paper("striped", full_width = TRUE) %>% 
+    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = size)  %>% 
+  collapse_rows(columns = 1:1)
+
+  return(Table)
+}
+
+CICES_filter(ID=c("1.1.1.1", "1.1.1.2", "1.1.1.3", 
+                     "1.1.2.1", "1.1.2.2", "1.1.2.3"), size = 15)
+
+```
+
+---
+# Provisioning Services (biotic & Abiotic)
+## Animals
+
+.pull-left[
+**Territorial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.1.3.1", "1.1.3.2", "1.1.3.3", "1.1.4.1", "1.1.4.2", "1.1.4.3"), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Wild Animals & Plants
+
+.pull-left[
+**Territorial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*	
+]
+
+.pull-right[
+**Industrial Question**
+
+*Are Reared animals (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.1.5.1","1.1.5.2","1.1.5.3","1.1.6.1","1.1.6.2","1.1.6.3"), size = 13)
+```
+
+---
+# Provisioning Services (biotic & Abiotic)
+## Genetic Material
+
+.pull-left[
+**Territorial Question**
+
+*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) an important element for the territory ?*	]
+
+.pull-right[
+**Industrial Question**
+
+*Is the Genetic material from plants, algae or fungi (including seed, spore or gamete production) affected by the use of your technology int the territory ?*
+]
+
+```{r}
+CICES_filter(ID=c("1.2.1.1","1.2.1.2","1.2.1.3","1.2.2.1","1.2.2.2","1.2.2.3"), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Water
+
+.pull-left[
+**Territorial Question**
+
+*Is Water (for nutrition, materials or energy) an issue for the territory?*	]
+
+.pull-right[
+**Industrial Question**
+
+*The is the impact of LCI?*
+]
+
+```{r ES_Provision_water}
+CICES_filter(ID=c("4.2.1.1", "4.2.1.2", "4.2.1.3", "4.2.1.4", "4.2.2.1", "4.2.2.2", "4.2.2.3"
+), size = 15)
+```
+
+---
+
+# Provisioning Services (biotic & Abiotic)
+## Others Abiotic
+
+```{r ES_Provision_Abiotic}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 15)
+
+```
+
+---
+
+class: middle
+
+# CICES
+
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.bg-yellow[Cultural]
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+
+## Biochemical or physical inputs to ecosystems
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.1.1.1", "2.1.1.2", "2.1.2.1", "2.1.2.2", "2.1.2.3"), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.1.1", "2.2.1.2", "2.2.1.3", "2.2.1.4", "2.2.1.5" ), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.2.1", "2.2.2.2", "2.2.2.3", "2.2.3.1", "2.2.3.2", "2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
+
+```
+
+---
+
+# Regulation & Maintenance (biotic & Abiotic)
+## Regulation of physical, chemical, biological conditions
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+#CICES_filter(ID=c("4.3.1.1","4.3.1.2","4.3.1.3","4.3.2.1","4.3.2.2","4.3.2.3","4.3.2.4","4.3.2.5","4.3.2.6"), size = 12)
+
+CICES_filter(ID=c("2.2.4.1", "2.2.4.2", "2.2.5.1", "2.2.5.2", "2.2.6.1", "2.2.6.2" ), size = 15)
+```
+
+---
+
+# CICES
+
+1. .large.bg-yellow[Provisioning Services (biotic & Abiotic)]
+1. .large.bg-yellow[Regulation & Maintenance (biotic & Abiotic)]
+1. .large.blue[Cultural]
+
+---
+
+# Cultural (Biotic) 
+## Direct contact with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("3.1.1.1", "3.1.1.2", "3.1.2.1", "3.1.2.2", "3.1.2.3", "3.1.2.4"), size = 15)
+```
+
+---
+
+# Cultural (Biotic) 
+## Indirect contact with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("3.2.1.1","3.2.1.2","3.2.1.3","3.2.2.1","3.2.2.2"), size = 15)
+
+```
+
+---
+
+# Cultural (Abiotic) 
+## Direct and Indirect link with Nature
+
+.pull-left[
+**Territorial Question**
+
+*Is*	]
+
+.pull-right[
+**Industrial Question**
+
+*The *
+]
+
+```{r}
+CICES_filter(ID=c("6.1.1.1","6.1.2.1","6.2.1.1","6.2.2.1"), size = 15)
+```
+
+---
+
+Thanks

### 2021-10-26 00-ES/xar-EB-ES/xaringan-themer.R

@@ -1,0 +1,75 @@
+# Load data ----------------------------------------------------------------
+
+
+# set options ------------------------------------------------------------------
+style_duo_accent(
+   primary_color = "#1381B0",
+   secondary_color = "#FF961C",
+   inverse_header_color = "#FFFFFF", 
+   base_font_size = "18px",
+   text_font_family = 'Trebuchet-MS',
+   header_font_family = 'Trebuchet-MS',
+   title_slide_background_color = "#FFFFFF",
+   
+   colors = c(
+      red = "#f34213",
+      purple = "#3e2f5b",
+      orange = "#ff8811",
+      green = "#d9edc2",
+      white = "#FFFFFF",
+      grey = "#F5F5F5",
+      yellow = "#FAFE83",
+      blue = "#1381B0",
+      grey_Inedit = "#969696"
+   ),
+   extra_css = list(
+      ".remark-slide-content h1" = list(
+         "margin-bottom" = 0, 
+         "margin-top" = 0),
+      ".remark-slide-content > h1:first-of-type" = list(
+         "margin-top" = "5px",
+         "margin-bottom" = "10px"
+      ),
+      ".title-slide h2" = list("font-family" = "Trebuchet-MS"),
+      
+      ".remark-slide-content > h2:first-of-type" = list(
+         "margin-top" = "5px",
+         "margin-bottom" = "10px"
+      ),
+      ".remark-slide-content > h3:first-of-type" = list(
+         "margin-top" = "5px",
+         "margin-bottom" = "10px"
+      ),
+      ".remark-slide-content" = list (
+         "padding-top" =  "25px",
+         "padding-left" =  "50px",
+         "padding-right" =  "50px",
+         "padding-bottom" =  "25px"
+      ),
+      
+      ".small" = list("font-size" = "90%"),
+      
+      
+      ".Large , .Large .remark-code, .Large .remark-inline-code" = list("font-size"= "144%"), 
+      ".large , .large .remark-code, .large .remark-inline-code" = list("font-size"= "120%"), 
+      ".small , .small .remark-code, .small .remark-inline-code" = list("font-size"= "90%"), 
+      ".footnotesize, 
+    .footnotesize .remark-code, .footnotesize .remark-inline-code" = list( "font-size"= "80%"),
+      
+      ".scriptsize , .scriptsize .remark-code, .scriptsize .remark-inline-code" = list("font-size"= "70%"),
[…]

### 2021-11-09 00-ES/PubliER/PubliER.Rmd
mise à jour site

@@
 ---
-title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
+title: "Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory:  the case of distributed recycling at Nancy, France"
 #documentclass: extarticle
 #fontsize: 14pt
-#geometry: "left=2cm, right=2cm,top=3cm,bottom=2cm"
-output: 
-  bookdown::pdf_document2:
-    toc: true
-    keep_tex: TRUE
+geometry: "left=3cm, right=3cm,top=3cm,bottom=2cm"
+author:
+  - name: Fabio A. Cruz
+    email: cruzsanc1@univ-lorraine.fr
+    affiliation: UTT
+    footnote: 1
+  - name: Nadège Troussier
+    #email: bob@example.com
+    affiliation: UTT
+  - name: Hakim Boudaoud
+    #email: cat@example.com
+    affiliation: UL
+    #footnote: 2
+  - name: Mauricio Camargo
+    #email: derek@example.com
+    affiliation: UL
+    #footnote: 2
+address:
+  - code: UTT
+    address: "Universite de Technologie de Troyes, Troyes, France"
+  - code: UL
+    address: "ERPI, Université de Lorraine, F-54000 Nancy, France."
+footnote:
+  - code: 1
+    text: "Corresponding Author"
+journal: "PubliER2022 - The industry of the future : beyond the Anthropocene. 2-4 Feb 2022 Troyes (France)"
+date: "`r Sys.Date()`" 
+csl: journal-of-cleaner-production.csl
+output: rticles::elsevier_article
+# author:
+# - Fabio A. Cruz Sanchez^[Université de Lorraine]
+# - Nadège Troussier^[Université Technologique de Troyes]
+# - Hakim Boudaoud^[Université Technologique de Troyes]
+# - Mauricio Camargo^[Université Technologique de Troyes]
+# date: "`r format(Sys.time(), '%d %B %Y')`"
+
+# output:
+#   bookdown::pdf_document2:
+#     toc: true
+#     keep_tex: TRUE
     #pandoc_args: "--latex-engine-opt=--shell-escape"
@@
     <!-- Intro -->
-    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans received from nature, most of time for free.
+    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
     <!-- Problem -->
-    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it identifying the priority interactions (as synergy and impacts).
+    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
     From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
@@
        <!-- ES valuation and Urban  ES-->
-    There have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being [@Costanza2017; @DeGroot2012; @MEA2005; @Costanza1997], and  great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES)[@RoyHaines-Young2018].
+    On the ecological side, there have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES).
+       <!-- LCA -->
+    While on the industrial side, life cycle assessment (LCA) tool is focused on the quantification of the environmental impact of industrial interventions.
+Despite its ability to cover mutually exclusive and exhaustive impact categories, the LCA approach still has deficiencies: 1) it focuses on quantifying and reducing the net environmental impacts, but not on reducing ecological overshoot and establishing synergies with nature; 2) it considers the interactions between technological processes, but not the interactions between relevant ecosystems.
     <!-- Knowledge Gap -->
-    However, few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+    Few researches have addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+    There is a need to include the ES in the desicion making process to establish the capacity of the territory in order to evaluate an absolute environmental sustainability of industrial systems. 
     <!-- Logic & Evidence for Problem, KG and Context -->
-       <!-- LCA -->
-    In the industrial side, Life cycle thinking have been a major assessment tool putting a great attention in the quantification of the environmental impact of industrial interventions, and helping in the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021].
           <!-- LCA AND ES -->
-    Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales [@Liu2019g].
+    <!-- Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales.
     This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
+-->
     <!-- Purpose Statement -->
@@
        <!-- Expand a methodology -->
-    This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
+    A prioritization is made based on the connection of urban ES services and the techno-ecological synergy.
     The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
     <!-- Context -->
-    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
+    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework for the territory of Nancy, France.
     The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
@@
   \usepackage{tabu}
-
 ---
@@
 <!-- \onehalfspacing -->
+
+```{r, include=FALSE}
+knitr::knit_exit()
+```
 
@@
 -->
-
-\textcolor{red}{
-Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
 
@@
 
-## Step I - Definition the Industrial system : Distributed recycling via additive manufacturing
+## Step I - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems
+
+The goal of this first step is to highlight the main interactions (positive and negative) that the
+
+The global value chain of the plastic material
+
+## Step II - Definition the Industrial system : Distributed recycling via additive manufacturing
 
@@
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+Three main elements needs to be carry out in this phase:
 
-## Step III - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems
+1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
 

### 2021-11-09 docs/00-ES/PubliER/PubliER.tex
mise à jour site

--- 2021-11-09 00-ES/PubliER/PubliER.Rmd
@@
----
-title: "Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory:  the case of distributed recycling at Nancy, France"
-#documentclass: extarticle
-#fontsize: 14pt
-geometry: "left=3cm, right=3cm,top=3cm,bottom=2cm"
-author:
-  - name: Fabio A. Cruz
-    email: cruzsanc1@univ-lorraine.fr
-    affiliation: UTT
-    footnote: 1
-  - name: Nadège Troussier
-    #email: bob@example.com
-    affiliation: UTT
-  - name: Hakim Boudaoud
-    #email: cat@example.com
-    affiliation: UL
-    #footnote: 2
-  - name: Mauricio Camargo
-    #email: derek@example.com
-    affiliation: UL
-    #footnote: 2
-address:
-  - code: UTT
-    address: "Universite de Technologie de Troyes, Troyes, France"
-  - code: UL
-    address: "ERPI, Université de Lorraine, F-54000 Nancy, France."
-footnote:
-  - code: 1
-    text: "Corresponding Author"
-journal: "PubliER2022 - The industry of the future : beyond the Anthropocene. 2-4 Feb 2022 Troyes (France)"
-date: "`r Sys.Date()`" 
-csl: journal-of-cleaner-production.csl
-output: rticles::elsevier_article
-# author:
-# - Fabio A. Cruz Sanchez^[Université de Lorraine]
-# - Nadège Troussier^[Université Technologique de Troyes]
-# - Hakim Boudaoud^[Université Technologique de Troyes]
-# - Mauricio Camargo^[Université Technologique de Troyes]
-# date: "`r format(Sys.time(), '%d %B %Y')`"
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
 
-# output:
-#   bookdown::pdf_document2:
-#     toc: true
-#     keep_tex: TRUE
-    #pandoc_args: "--latex-engine-opt=--shell-escape"
-  # bookdown::html_document2: default
-  # bookdown::word_document2: default
-#output: rticles::tf_article
-abstract: |
-    <!-- Intro -->
-    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
-    <!-- Problem -->
-    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
-    From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
-    <!-- Conceptual Framework (broad theoretical) -->
-       <!-- ES valuation and Urban  ES-->
-    On the ecological side, there have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES).
-       <!-- LCA -->
-    While on the industrial side, life cycle assessment (LCA) tool is focused on the quantification of the environmental impact of industrial interventions.
-Despite its ability to cover mutually exclusive and exhaustive impact categories, the LCA approach still has deficiencies: 1) it focuses on quantifying and reducing the net environmental impacts, but not on reducing ecological overshoot and establishing synergies with nature; 2) it considers the interactions between technological processes, but not the interactions between relevant ecosystems.
-    <!-- Knowledge Gap -->
-    Few researches have addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
-    There is a need to include the ES in the desicion making process to establish the capacity of the territory in order to evaluate an absolute environmental sustainability of industrial systems. 
-    <!-- Logic & Evidence for Problem, KG and Context -->
-          <!-- LCA AND ES -->
-    <!-- Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales.
-    This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
--->
-    <!-- Purpose Statement -->
-    The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
-       <!-- Expand a methodology -->
-    A prioritization is made based on the connection of urban ES services and the techno-ecological synergy.
-    The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
-    <!-- Context -->
-    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework for the territory of Nancy, France.
-    The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
-always_allow_html: true
-# editor_options: 
-#   markdown: 
-#     wrap: 100
-bibliography: library.bib
-#bibliography: References.bib
-link-citations: yes
-linkcolor: blue
-header-includes: |
+  \journal{PubliER2022 - The industry of the future : beyond the
+Anthropocene. 2-4 Feb 2022 Troyes (France)} % Sets Journal name
+
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{graphicx}
+%%%%%%%%%%%%%%%% end my additions to header
+
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage[left=3cm, right=3cm,top=3cm,bottom=2cm]{geometry}
+\bibliographystyle{elsarticle-harv}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory: the case of distributed recycling at Nancy, France},
+            colorlinks=true,
+            urlcolor=blue,
+            linkcolor=blue,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+
+% Pandoc citation processing
+
+% Pandoc header
 \usepackage{float}
@@
 \usepackage{tabu}
----
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%')
-options(knitr.kable.NA = '')
-#options(tinytex.engine_args = '--shell-escape')
+\begin{document}
+\begin{frontmatter}
 
-library(readxl)
-library(here)
-library(tidyverse)
-library(flextable)
-library(rsvg)
-set_flextable_defaults(fonts_ignore=TRUE)
+  \title{Integrating and prioritizing ecosystems services at early
+development stages of industrial systems in a territory: the case of
+distributed recycling at Nancy, France}
+    \author[UTT]{Fabio A. Cruz\corref{1}}
+   \ead{cruzsanc1@univ-lorraine.fr} 
+    \author[UTT]{Nadège Troussier}
 
-#URL for Figurs
-URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
+    \author[UL]{Hakim Boudaoud}
 
-```
+    \author[UL]{Mauricio Camargo}
+
+      \address[UTT]{Universite de Technologie de Troyes, Troyes, France}
+    \address[UL]{ERPI, Université de Lorraine, F-54000 Nancy, France.}
+      \cortext[1]{Corresponding Author}
+
+  \begin{abstract}
+  Ecosystem services (ES) is a powerful conceptual framework to put in
+  evidence the benefits that humans receive from nature, most of time
+  for free. The problem is that it is complex to link between the local
+  ecosystem services of an urban territory and the industrial systems
+  placed within it, identifying the priority interactions (as synergy
+  and impacts). From a decision-maker perspective, there is no a aid
+  decision tool to guide a multicriteria evaluation at early development
+  stages of industrial systems. On the ecological side, there have been
+  major efforts in the valuation of ES given by ecosystems (terrestrial,
+  aquatic, atmospheric) to the human well-being and great advances in
+  the developing of a standard ES baselines such as Common International
+  Classification of Ecosystem Services (CICES). While on the industrial
+  side, life cycle assessment (LCA) tool is focused on the
+  quantification of the environmental impact of industrial
+  interventions. Despite its ability to cover mutually exclusive and
+  exhaustive impact categories, the LCA approach still has deficiencies:
+  1) it focuses on quantifying and reducing the net environmental
+  impacts, but not on reducing ecological overshoot and establishing
+  synergies with nature; 2) it considers the interactions between
+  technological processes, but not the interactions between relevant
+  ecosystems. Few researches have addressed the alignment the
+  territorial priorities in terms of ES for planning and urban
+  development with the supply/demand of ES by industrial systems. There
+  is a need to include the ES in the desicion making process to
+  establish the capacity of the territory in order to evaluate an
+  absolute environmental sustainability of industrial systems. The
+  purpose of this article is to propose a methodological approach in
+  order to include ecosystem services in regarding the territorial and
+  industrial endeavors. A prioritization is made based on the connection
+  of urban ES services and the techno-ecological synergy. The results of
+  are step forwards to create techno-ecological synergies between
+  ecological and industrial systems. This methodological steps will
+  applied to the case of distributed recycling via additive
+  manufacturing (DRAM) to highlight the relevant ES from the CICES
+  framework for the territory of Nancy, France. The technical
+  advancements of recycling approaches using additive manufacturing are
+  promising technical interventions to foster plastic recycling at a
+  local level.
+  \end{abstract}
+
+ \end{frontmatter}
 
 \linenumbers
-<!-- \onehalfspacing -->
 
-```{r, include=FALSE}
-knitr::knit_exit()
-```
-
-# Introduction
-
-<!-- ## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity. -->
-<!-- Intro -->
-The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
-<!-- Technological development claiming sustainabiilty -->
-Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs [@ref].
-For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
-This meta-principle is a imperative but not sufficient condition for sustainability.
-Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
-Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
-We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
-<!-- Gap in the literature -->
-However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
-
-<!-- Sustainability frameworks -->
-@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
-They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-<!-- They hightligthed that differens Systemic design approaches are   -->
-
-<!-- Importance of ES in the Engineering -->
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
-However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
-  <!-- Engineering blindness -->
-The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
-This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal.
-This scenario is not true today.
-  <!-- Engineering withing ecological constraints -->
-The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
- <!-- Importance of ES in the decision making process -->
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
-It is difficult to provide information about pressure from industrial systems in corporate information systems. 
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].
-
-  <!-- MEA and Planeatry results -->
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
-Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
-  <!-- Causas of exceeding Planeatry boundaries -->
-Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
-<!-- Purpose of strong sustainability -->
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
-  <!-- Expand boundaries of Engineering -->
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].
-
-  <!-- TES -->
-@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
-for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
--->
-<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
--->
-
-The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
-This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements. 
-  <!-- Case study -->
-As a case application, the study of distributed recycling manufacturing will be describe.
-Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
-Therefore, new approaches need to be explored in order to reduce ar at least recycling this material. 
-Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
-
-The expected results seek to address the following questions:
-
-- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
-- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
-- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory? 
-From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators   for deployments distributed recycling approach,
-
-In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
-This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.
-
-\textcolor{red}{The article is structure as follows.... ( to complete) } section \@ref(background) ...
-
-<!-- The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.
--->
-
-# Background
-\label{background}
-
-## Ecosystem services
-
-<!--# Intro -->
-Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002].
-Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
-Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
-Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].
-
-<!--# Definition of Ecosystem Services -->
-Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017].
-Ecosystem goods (e.g; Food) and services (e.g.
-waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997].
-  <!--# Functions vs Services -->
-It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself.
-The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits.
-By contrast, the latter are those processes and functions where people can (or could have the potential [@ref]) obtain benefits.
-The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach.
-Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@ref].
-One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003].
-This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders [@Honeck2021].
-
-<!--  Research themes in ES -->
-Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field.
-Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
-Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
-It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
-
-Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
-Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
-
-<!--# Classification of ES -->
-Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
-The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
-The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
-In the heart of the four main, they share four main categories of ES:
-**Provisioning** (e.g. food and medicines); 
-**Regulating** (e.g. pollination and climate regulation), 
-**Supporting** (e.g soil formation and fixation of solar energy) and 
-**Cultural / Information** services (e.g.
-artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].
-
-```{r Fig:ES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
-# img_url <- paste0(URL, 'Everest-bio/ES')
-#download.file(paste0(URL, 'Everest-bio/ES/', 'Comparison.png'), "Figures/Comparison.png")
-# rsvg_pdf(img_url, "Figures/Methodology.pdf")
-
-knitr::include_graphics('Figures/Comparison.png')
-
-```
-
-<!--# Strong sustainability and ES -->
-Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital [@Costanza1997] and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework [@Bruel2016].
-  <!-- Strong sustainability -->
-From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it [@Ekins2003].
-More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of *critical* components that make a major contribution to welfare.
-  <!--# Main environmental issue -->
-The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience [@Ekins2003].
-
-  <!-- CICES -->
-The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref].
-In CICES framework, @Potschin-Young2018 argued the conceptual framework of cascading aspect from ecosystesm service are  commonly divided Groups, division.
-<!-- @Mustajoki2019 -->
-
-<!-- \begin{landscape} -->
-```{r table-CICES, include=FALSE}
-# From the CICES intial
-CICES <- read_excel(here("tables/CICES.xlsx"), sheet = "CICES V5.1",  skip = 4 )
-CICES <- CICES %>% filter(Filter == "CICES" ) %>% select(Section,Division, Group, Class,`Class type`)
-
-CICES %>% pull(Section) 
-names(CICES)
-CICES %>% flextable() %>%
-  set_caption("CICES ") %>%
-  #autofit() %>% 
-  width(j=1:5, width = c(1, 1, 2, 2, 2)) %>% 
-  fontsize(size=10, part = "all") %>% 
-  #fit_to_width(max_width = 8) %>% 
-  merge_v(j = c("Section", "Division",  "Class type")) %>% #"Group", "Class",
-  theme_booktabs()
-
-#names(CICES)
-```
-<!-- \end{landscape} -->
-
-```{r Fig-ES-cices, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
-# img_url <- paste0(URL, 'Everest-bio/ES')
-# rsvg_pdf(img_url, "Figures/Methodology.pdf")
-
-knitr::include_graphics('Figures/cices.png')
-
-```
-
-The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings [70]. 
-With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings. 
-The product-based CICES framework can enable clearer mapping between ecological and economic products. 
-The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level. 
-The following levels organize ES according to their divisions, groups and classes. 
-At lower levels, more specific services can be defined and characterized. 
-For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed. 
-Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
-
-Figure 2.2 demonstrates the hierarchical structure of CICES scheme.
-
-# Methodology
-
-The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
-A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
-
-```{r Fig-Methodology, fig.cap='Operational framework for evaluatig the ecosystem services of industrial systems', out.width='100%', fig.pos='!ht', fig.align='center'}
-
-#library(magick)
-#image_write(image_read_svg(img_url,  width = 350), path = "Figures/Methodology.jpeg", format = "jpeg")
-
-# img_url <- paste0(URL, 'Everest-bio/Publier/Methodology.svg')
-# rsvg_pdf(img_url, "Figures/Methodology.pdf")
-
-knitr::include_graphics('Figures/Methodology.pdf')
-```
-
-Four major steps are proposed as illustrated in figure \@ref(Fig-Methodology) .
-
-  <!-- Step 1 Assessments-->
-The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
-  <!-- Step 2 Plannig-->
-In the *Assessment* step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis. 
-These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
-  <!-- Step 3 Evaluate-->
-In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
-  <!-- Step 3 Management-->
-Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
-This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
-
-An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
-In the following sub-sections, each stage of the methodology is explained.
-
-# Results
-
-## Step I - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems
-
-The goal of this first step is to highlight the main interactions (positive and negative) that the
-
-The global value chain of the plastic material
-
-## Step II - Definition the Industrial system : Distributed recycling via additive manufacturing
-
-<!-- Distributed Fabrication -->
-Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
-In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].
-
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
-<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
-
-The system depicted is presented in the figure XX.
-The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
-Because Es are expected to be more relevant in the
-
-<!-- Funcitonal Unit -->
-The goal of this study is to evaluate and compare the change in ES provisioning 
-The functional unit (FU) is represented by *1kg of recycled filament delivered at school*.
-
-## Step II - Ecosystem services Priorities at the territorial level: Nancy, France
-
-Three main elements needs to be carry out in this phase:
-
-1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
-
-## Step II - Identifying the Hot spot of the
-
-# Discussion and perspective of the analysis
-
-# Conclusions
-
-\newpage
-# References
+\end{document}

### 2021-11-09 docs/00-ES/xar-EB-ES/xar-EB-ES.Rmd
mise à jour site

--- 2021-10-26 00-ES/xar-EB-ES/xar-EB-ES.Rmd
@@
 ---
+include: false
 
@@
 
-# Methodology
+background-image: url('figures/ES-Rec.png')
+background-position: 100% 50%
+background-size: 60%
+
+# Literature review
 
@@
 class: top left
-background-image: url('figures/ES-Rec.png')
-background-position: 100% 50%
-background-size: 60%
 
 ## Definitions
+## Ecosystem function <br> & Services
 
 - *Ecosystem process:*
-
 - *Ecosystem Functions*
-
 - *Ecosystem Services*
-
-*- Goods and Services*:
-
----
-
-## Ecosystem function <br> & Services
+- *Goods and Services*:
 
@@
 ]
+
+---
+
+# Strong and Weak Sustainability
+
+Strong: Coming from Ecological rationality
+
+>The (Natural) capital is not sustiable, nor reemplazable, interchangable by the financial capital of the physical capital.
+
+Weak: Coming from Economical rationality
 
@@
 layout: false
+class: middle inverse
+
+# Common International Classification of Ecosystem Services (CICES) for Integrated Environmental and Economic Accounting
+
+---
 
@@
 
-## Barriers and complexities
+## CICES V5.1 Definitions
+
+According to CICES V5.1:  is built on the principle that a classification of services needs to describe the contribution that ecosystems make to human well-being, defined in terms of ‘what ecosystems do’.
+Thus, in the classification the definition of a service needs to highlight the ecological outcomes that particular ecosystem characteristics or processes generate, that can ultimately benefit people.
+The aim has therefore been to build a classification that identifies the purposes or uses that people have for the different kinds of ecosystem service and associate them with the particular ecosystem attributes or behaviours that support them
+
+---
+
+## Barriers and complexities of ES
 
@@
 
-# Prototyping the tool
-
----
-
-## Definitions
-
-According to CICES V5.1:  is built on the principle that a classification of services needs to describe the contribution that ecosystems make to human well-being, defined in terms of ‘what ecosystems do’.
-Thus, in the classification the definition of a service needs to highlight the ecological outcomes that particular ecosystem characteristics or processes generate, that can ultimately benefit people.
-The aim has therefore been to build a classification that identifies the purposes or uses that people have for the different kinds of ecosystem service and associate them with the particular ecosystem attributes or behaviours that support them
-
----
-
-# Strong and Weak Sustainability
-
-Strong: Coming from Ecological rationality
-
->The capital is not sustiable, nor reemplazable, interchangable by the financial capital of the physical capital.
-
-Weak: Coming from Economical rationality
+# Prototyping the tool for Everest Bio
 
@@
 .pull-left[
+
 ## Goal:
@@
 ---
+
 ## Structure of the tool

### 2021-11-09 xar-EB-general/index.Rmd
mise à jour site

--- 2021-04-12 slides/index.Rmd
@@
 
-class: middle, left
-
-# Agenda
-
-1. .content-box-yellow[Who am I?]
-2. ERPI Laboratory
-3. Green Fablab
-4. Everest Bio
-5. Proposition and Research axis
-
----
-
-class: top, left
-background-image: url(`r paste0(URL, 'Fabio/vosviewer/Fabio.jpg')`)
-background-position: right
-background-size: 70%
-
-# Who am I?
-
-.pull-left-1[
-```{r, echo=FALSE, out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Fabio/Fabio.png'))
-```
-]
-
----
-
-class: left middle
-
-## My research questions so far...
-
----
-
-class: left
-background-position: 0px 75px
-background-size: contain
-
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-01.jpg')`)
-
-## Are open source 3D printer good enough?
-
----
-
-## Are open source 3D printer good enough?
-
-Geometrical accuracy perspective
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Metodologies/Master-recherche/Master-00.png'))
+```{r, include=FALSE}
+Fabio <- TRUE
 ```
 
-.footnote[
-Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
-Towards a standard experimental protocol for open source additive manufacturing.
-Virtual Phys.
-Prototyp.
-9, 151–167.
-https://doi.org/10.1080/17452759.2014.919553
-]
+```{r, child= if (!Fabio) 'partials/Fabio-presentation.Rmd'}
 
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-02.jpg')`)
-background-position: 0px 75px
-background-size: contain
-
-## Can we print recycled objects?
-
-Recycling feasibility (Lab conditions)
-
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-03.jpg')`)
-background-position: 0px 75px
-background-size: contain
-
-## What about the supply chain printed recycled objects?
-
-.pull-down[Research of Pavlo Santander. Thesis Defended Dec. 2020]
-
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-05.jpeg')`)
-background-position: 100px 125px
-background-size: 80%
-
-## How an innovation lab could could help as agent of change?
-
-.footnote[
-Roux-Marchand, T., Cruz, F., Dupont, L., Camargo, M., Osorio, F., 2020.
-Connecting the strategic intent of innovation labs and projects: the case of the Green Fablab, in: 2020 IEEE International Conference on Engineering, Technology and Innovation (ICE/ITMC).
-IEEE, pp.
-1–10.
-https://doi.org/10.1109/ICE/ITMC49519.2020.9198320
-
-Alexandre, A., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
-Mechanical Properties of Direct Waste Printing of Polylactic Acid with Universal Pellets Extruder: Comparison to Fused Filament Fabrication on Open-Source Desktop Three-Dimensional Printers.
-3D Print.
-Addit.
-Manuf.
-3dp.2019.0195.
-https://doi.org/10.1089/3dp.2019.0195
-]
-
----
-
-## What if distributed recycling could be aligned with Circular Economy priorities?
-
-```{r, out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'DRAM/DRAM-10.png'))
 ```
-
-Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
-Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy.
-J.
-Clean.
-Prod.
-264, 121602.
-https://doi.org/10.1016/j.jclepro.2020.121602
-
----
-
-class: middle
-
-# However...
-
-.left-column[
-```{r, out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Various/Signos/attention-00.png'))
-```
-]
-
-.right-column[
-
-- Technical and economic criteria alone do not (yet) allow for informed decisions.
-
-- Where is the environment in the techno-centrical approaches?
-
--  The root of the plastic waste problem needs to be addressed: the extraction and production.
--  Responsibility to act in the plastics economy
-
-- **Adaptive injustice**: *those who find ways to adapt to changing social realities, whether forced or voluntary, are not those who are responsible for the negative changes to which they are adapting.
-Specifically, it is an adaptive injustice to expect communities to figure out what to do with continual flow of plastics into the economy.*
-
-.content-box-red[**It’s time to retire this ‘privatizing profits, socializing costs’ model.**]
-
-]
-
-.footnote[
-Conlon, K., 2020. Adaptive injustice: Responsibility to act in the plastics economy. Resour. Conserv. Recycl. 153, 104563. https://doi.org/10.1016/j.resconrec.2019.104563
-]
 
@@
 .pull-left[
-1. Who am I?
-2. .content-box-yellow[ERPI Laboratory]
-3. Green Fablab
-4. Everest Bio
-5. Proposition and Research axis
+1. .content-box-yellow[ERPI Laboratory]
+1. Green Fablab
+1. Everest Bio
+1. Proposition and Research axis
 ]
@@
 ---
-
----
-
-class: middle, left
-background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
-background-position: center
-background-size: contain
-
----
-class: middle
-
-# EU projects
-
-.pull-left[
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
-```
-https://www.smagrinet.eu/
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
-```
-
-https://digiterri.eu/
-
-] 
-.pull-right[
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
-```
-
-https://www.inedit-project.eu/
-]
-
----
-
 class: middle, center
 
-Thanks !
+# Thanks !
 

### 2021-11-29 00-ES/PubliER/Ideas on draf.Rmd
avancando hoy

--- 2021-10-20 00-ES/Article/Ideas on draf.Rmd
@@
 ```
-
-### Territorial issues
-
-<!-- Urban Ecosystem Services -->
-More than two thirds of the world's population are expected to live in cities by 2050 [@ref].
-Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
-  <!-- Importance of Urban ES -->
-Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
-cooling, and runoff mitigation [@Bolund1999]. 
-  <!-- Classification of Urban ES -->
-@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
-They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
-
-  <!-- Goal -->
-The main purpose in this step is the identification of the main urban priorities in the territorial context from a perspective of ecosystem services.
-THe ES in a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
-
-### Industrial Issues
-
-\textcolor{red}{ To complete based on article that reading on...}
 

### 2021-11-29 00-ES/PubliER/PPQS.Rmd
avancando hoy

@@
 Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales [@Liu2019g].
-This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
+This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] aims to reflect its emphasis on establishing mutually beneficial relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature.
 <!-- Purpose Statement -->
@@
 This prioritization is based on the connection of urban ES services and the techno-ecological synergy.
-The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
+The results seek a step forwards to create techno-ecological synergies between ecological and industrial systems.
 <!-- Context -->
-This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
+This methodological approach will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework of this industrial system for the territory of Nancy, France.
 The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.

### 2021-11-29 00-ES/PubliER/PubliER.Rmd
avancando hoy

@@
 csl: journal-of-cleaner-production.csl
-output: rticles::elsevier_article
-# author:
-# - Fabio A. Cruz Sanchez^[Université de Lorraine]
-# - Nadège Troussier^[Université Technologique de Troyes]
-# - Hakim Boudaoud^[Université Technologique de Troyes]
-# - Mauricio Camargo^[Université Technologique de Troyes]
-# date: "`r format(Sys.time(), '%d %B %Y')`"
-
-# output:
-#   bookdown::pdf_document2:
-#     toc: true
-#     keep_tex: TRUE
+output:
+  bookdown::pdf_book:
+    base_format: rticles::elsevier_article
   #pandoc_args: "--latex-engine-opt=--shell-escape"  
@@
   # bookdown::word_document2: default
-#output: rticles::tf_article
+
 abstract: |
@@
 always_allow_html: true
-# editor_options: 
-#   markdown: 
-#     wrap: 100
 bibliography: library.bib
-#bibliography: References.bib
 link-citations: yes
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%')
+knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%', cache = FALSE)
 options(knitr.kable.NA = '')
@@
 library(rsvg)
+library(kableExtra)
 set_flextable_defaults(fonts_ignore=TRUE)
@@
 ```{r, include=FALSE}
-knitr::knit_exit()
+
 ```
@@
 <!-- Technological development claiming sustainabiilty -->
-Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs [@ref].
+Even though engineering products and processes might meet the needs of the present society, many of the technological developments are compromising the ability of future generations to meet their own needs [@Bakshi2019a].
 For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
@@
 Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
-Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
+Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@Diwekar2021].
 We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
@@
 <!-- They hightligthed that differens Systemic design approaches are   -->
-
+@SousaRocha2019 revealed ten different models at operational, tactical, and strategical levels
 <!-- Importance of ES in the Engineering -->
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
+One strategical point in sustainability relies on the economic valuation of ecosystem goods and services framework.
+This approach gives an elegant framework highlighting their importance for society and human welfare.
 However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
@@
 
-  <!-- TES -->
-@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
-for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
--->
-<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
--->
-
-The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
-This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements. 
+The main purpose of this article is to propose a methodology in order to  prioritize the ecosystem services at early development stages of industrial systems in a territory.
+This methodology is based in the use of the ecosystem services as boundary object [@Abson2014] with the purpose to identify ES according to the perspective of global value chain, industrial chain and territorial perspective.
   <!-- Case study -->
@@
 Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
-Therefore, new approaches need to be explored in order to reduce ar at least recycling this material. 
+Therefore, new approaches need to be explored in order to reduce or at least recycling this material. 
 Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory. 
-
+<!-- Expected results -->
 The expected results seek to address the following questions:
@@
 - What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
-From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators   for deployments distributed recycling approach,
 
+From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach.
 In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
@@
 
-\textcolor{red}{The article is structure as follows.... ( to complete) } section \@ref(background) ...
+The article is structure as follows. 
+Section \@ref(background) presents a background on theoretical element of ecosystem service in link with life cycle assessment and the territorial planning.
+Section \@ref(methodology) presents the methodology proposed to identify and prioritize the ecosystems services. 
+In Section \label{results}, the results of the methodology are presented for the industrial system of distributed recycling for additive manufacturing at Nancy, France. 
+This industrial case enable to highlight the pertinence and limits of the methodology.
 
-<!-- The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.
--->
-
-# Background
+# Literature Review
 \label{background}
 
-## Ecosystem services
+## Ecosystem services and the global value chain
 
 <!--# Intro -->
-Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002].
-Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
-Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
-Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].
-
+Foundational ideas on ecosystem services (ES) seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002].
 <!--# Definition of Ecosystem Services -->
-Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017].
-Ecosystem goods (e.g; Food) and services (e.g.
-waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997].
+ES describes the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017]. 
+Ecosystem goods (e.g; Food) and services (e.g. waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997]. 
 <!--# Functions vs Services -->
@@
 The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits. 
-By contrast, the latter are those processes and functions where people can (or could have the potential [@ref]) obtain benefits.
+By contrast, the latter are those processes and functions where people can (or could have the potential) obtain benefits. 
 The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach.
-Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@ref].
+Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@TEEB2010]. 
 One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003].
@@
 It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
+   <!-- Conclusion of ES research -->
+Today, ecosystems services field are being included in the decision-making through promotion of market-based instruments for payment for ES schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
+Nevertheless, the commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs [@Gomez-Baggethun2010].
+Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].
 
-Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
+<!--# Strong sustainability and ES -->
+Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital [@Costanza1997] and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework [@Bruel2016].
+  <!-- Strong sustainability -->
+From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it [@Ekins2003].
+More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of *critical* components that make a major contribution to welfare.
+  <!--# Main environmental issue -->
+The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience [@Ekins2003].
+
+## Common standard of ecosystem services
+
+<!-- Efforts have been made in the literature to classify the methods used to assess ecosystem services.
 Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
+-->
 
@@
 **Cultural / Information** services (e.g.
-artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].
+artistic inspiration and recreation) services are four broad categories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].
 
@@
 ```
-
-<!--# Strong sustainability and ES -->
-Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital [@Costanza1997] and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework [@Bruel2016].
-  <!-- Strong sustainability -->
-From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it [@Ekins2003].
-More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of *critical* components that make a major contribution to welfare.
-  <!--# Main environmental issue -->
-The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience [@Ekins2003].
 
@@
 The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
+
 The following levels organize ES according to their divisions, groups and classes. 
 At lower levels, more specific services can be defined and characterized.
+
 For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
+
 Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
 
-Figure 2.2 demonstrates the hierarchical structure of CICES scheme.
+## Ecosystems services and industrial systems: Towards a synergy between
+
+One major point A holistic evaluation of the externalities that industrial system 
+Ecosystems services and industrial systems need to be confronten to holistic evaluation
+The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
+
+  <!-- TES -->
+@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.
+for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
+
+<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
+-->
+
+## Ecosystems services at the urban territorial planification
+
+<!-- Urban Ecosystem Services -->
+More than two thirds of the world's population are expected to live in cities by 2050 [@ref]. 
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
+  <!-- Importance of Urban ES -->
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
+cooling, and runoff mitigation [@Bolund1999]. 
+  <!-- Classification of Urban ES -->
+@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
+They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
 
 # Methodology
+\label{methodology}
 
-The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
-A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
+The purpose of this article is to identify main relevant ES services from a industrial and territorial perspective at the early design of industrial systems. 
+This identification is a first step with the purpose to evaluate the supply and demand of ecosystem services for these industrial systems.
 
@@
 
-  <!-- Step 1 Assessments-->
-The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
-  <!-- Step 2 Plannig-->
-In the *Assessment* step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis. 
-These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
-  <!-- Step 3 Evaluate-->
-In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
-  <!-- Step 3 Management-->
-Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
-This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
+- **I) Global value Planning**: the main goal is to identify the the links between the global value chain to be evaluated and the capital nature through the literature on ecological systems.
+The main purpose in this step is to map the the interactions positive and negative.
 
-An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
+- **II) Industrial system**: the main aim is to define the technosphere and identify the key ecosystems services that are impacted. 
+The identification is made using the lens of connection between the LCA and ES elements.
+
+- **II) Industrial system**: in this step, the main purpose is the identification of the key urban priorities in the territorial context from a perspective of ecosystem services.
+To establish these priorities, the territorial planification perspective is analysed given the fact that a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
+
+- Finally, in **IV) Synthesis**, the main goal is to converge on main ES that are identified for the three last perspectives,
+
 In the following sub-sections, each stage of the methodology is explained.
+An application of the framework will be presented in Section \label{results} using as case study of the distributed recycling chain via additive manufacturing.
 
 # Results
+\label{results}
+
+ Context of the industrial system
+
+ A prospective distributed recycling chain for additive manufacturing .
 
@@
 
-The goal of this first step is to highlight the main interactions (positive and negative) that the
+The goal of this first step is to highlight the main interactions that the value chain have with the natural ecosystems.
+This enables us to have a holistic picture of the impacts of plastic pollution in the natural ecosystems taking into account the highlighting the uncertainties and knowledge gaps that could exist in the field.
+
+```{r fig-Kumar2021, fig.cap= 'Illustration of MPs and NPs affecting various ecosystem services and climate change on terrestrial, aquatic, and atmospheric ecosystems. Source. Kumar2021.jpg' }
+
+#download.file(paste0(URL,'Plastics/ES/Kumar2021.jpg'), "Figures/Kumar2021.jpg")
+
+knitr::include_graphics('Figures/Kumar2021.jpg')
+
+```
+
+@Kumar2021 reported a complete description of the major impacts on the plastic pollution an the ecosystems services,identifying in what extend there are present the interlinkages between plastic pollution, waste management, and Sustainable Development Goals (SDG).
+  <!-- Presenting the Figure -->
+Figure \@ref(fig:fig-Kumar2021) presents an overview of the major interactions that plastic impact the ecosystem services in the terrestrial and aquatic ecosystems, representing a major societal issue.
+Macrosplastics -MP- (particules $\geq 5mm$ ), mesoplastics -MsP- ($1-5 mm$) and microplastics ($<1~mm$) are the major problems in the ecosystems.
+
+For aquatic ecosystems, main risks are linked to standing water that acts as a breeding niche (to mosquitoes, pests, vector-borne diseases transmission), becomes a vector for toxic chemicals and, ultimately, disturbs the natural cycles (biogeochemical cycle in terrestrial ecosystems).
+Additionally, the transfer of  plastic into the food chain is a clear danger to animal and, certainly, to humans as well.
+Thus, reducing the consumption of plastics is of great importance in the long term.
+
+The plastic value chain is one of the mo
+
+- Plastic materials have impats on the terrestrial, qauqtic, and atmospheric ecosystems.
+
+-
+
+Concerning the terrestrial impacts, the plastic degradation make and important impact on the pollitation of the
 
 The global value chain of the plastic material
+
+\renewcommand{\arraystretch}{1.5}
+```{r Value-chain-ES, include=TRUE}
+
+Value_chain <- 
+  tribble(
+  ~Description, ~ES, ~Ref,
+
+# Provisioning (Biotic)
+  'Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops',
+  '1.1.1.1 ; 1.2.1.1', 
+   '[@Kumar2021]',
+
+'MPs and their suspended solids hasten eutrophication.
+Eutrophication worsens as a result of both resuspension and algae growth, adding more contaminants to the food chain supply and primarily creating organic contamination.',
+  '1.1.5.1 ; 1.1.6.1 ', 
+    '[136]',
+
+# Regulation & Maintenance (Biotic)
+
+  'MPs and NPs in the atmosphere also lead to the obstruction and lowering of pollination.',
+  '2.2.2.1',
+    '[@Kumar2021]',
+
+"MPs and NPs are established to act as a vector and breach through any system (organisms) and even via trophic transfer (one trophic level to another via food chain), therefore, it can be hypothesized that MPs in the future can play a pivotal role in the spill over of infectious diseases, leading to an epidemic or pandemic of unknown scale",
+  '2.2.3.1; 2.2.3.1',
+  'Ref',
+
+  'MP and NP in terrestrial ecosystems reduce tha ability to sequester carbon.',
+    '2.1.1.2 ; 2.2.4.1', 
+      '[@Kumar2021]',
+
+  'Elements as nitrogen and phosphorous, are also vividly influenced due to MPs and NPs in the soil ecosystem',
+    '2.2.4.1 ; 2.2.4.2',
+      '[@Kumar2021]',
+
+    "MPs accumulation can promote mineralization, nitrification, and denitrification in aquatic ecosystems, therefore releasing CO2, CH4, and N2O.",
+    '2.2.6.1',
+      '[@Kumar2021]',
+
+  'marine carbon sinks are critical in analyzing the global climate change and are potentially affected by MPs and NPs pollution on phytoplankton-sequestered CO2 and their transmission to the deep ocean via zooplankton [77].',
+    '2.2.5.2 ',
+    '[@Kumar2021]',
+
+  'Plastics-induced variations in solar radiation in the water column can alter physical processes at the ocean’s surface and near-surface layers as well as trigger climate feedback mechanisms',
+    '2.2.6.1',
+    '[@Kumar2021]',
+
+  'MPs and NPs are known to cause a dynamic shift in the soil temperature as is commonly practiced in agriculture sectors with extreme climatic conditions.', 
+    '2.2.4.1',
+    '',
+
+  'MPs and NPs in the soil ecosystem are known to have a strong impact on the population structure and survival of these faunas [135,137,154,158].' ,
+  '2.2.4.1',
+  ' ',
+
+  'Small-sized plastics act as stressors, altering the ocean level and temperature and influencing the acidification.' ,
+  '2.2.6.1',
+  '',
+
+  'High amounts of MPs and NPs are more substantially found in pelagic species than in deep-water species.',
+  '1.1.5.1',
+  '',
+
+  'MPs and NPs act as vectors for toxic chemicals and microbes and can breach any ecosystem.',
+  '2.1.1.1',
+   'REf'
+
+# Cultural (Biotic)
+
+)
+
+ Value_chain %>% 
+  kbl(caption = "Plastic pollution impact on ES",  booktabs = T) %>%
+    kable_styling(latex_options = c("striped", "hold_position") ) %>% 
+    column_spec(1, width = "30em")
+
+```
 
@@
 <!-- Distributed Fabrication -->
-Major technological advance in the Additive manufacturing field have enable the validation of distributed fabrication.
-In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the socio-environmental challenges related to recycling option for AM technologies using plastic material as feedstock [@CruzSanchez2020; @Santander2020].
+Major technological advances in the additive manufacturing (AM) field have enable the validation of distributed fabrication [@Woern2017; @Petersen2017a; @Matt2015].
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assetes as feedstock [@CruzSanchez2020; @Santander2020].
+The use of recycled material, either in the form of raw material or blended with virgin material, is a method of special interest to contribute to sustainable manufacturing [@Zhao2018].
 
+<!-- Explaining DRAM -->
 The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community. 
 To do so, the use of additive manufacturing enables the technical paths to achieve this objective. 
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation. 
-<!-- Based on the sustainability concept, this research intends to investigate, how the ecosystem services are impacted due to the implementation of the plastic recycling chain.  -->
+   <!-- Reasons: Economic -->
+In the DRAM methodology, consumers have an economic incentive to recycle. 
+This is because they can use their waste as feedstock for a wide range of consumer products that can be produced for a fraction of the conventional cost of the equivalent products. 
+   <!-- Reasons: Design -->
+Moreover, 3D printing is especially well suited because it enables the production of parts with (almost) no waste, and could reduce the waste related to the material by more than 40 %, reusing 95 % of the unused material [@Petrovic2011].
+Currently, most of the cost of 3D printing is associated with filament in FFF techniques [@Wittbrodt2013].
+
+By recycling raw materials such as Polylactic acid (PLA), one of the most frequently used materials in 3D printing, it is possible to reduce the carbon dioxide emissions that are incurred by transport to landfills or shipping to customers, offering environmental benefits [@Santander2020].
+
+However, While not all types of materials can be recycled given the technical difficulties, the integral evaluation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
 Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
 
-The system depicted is presented in the figure XX.
-The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped  by . 
-Because Es are expected to be more relevant in the
+The technical system is depicted  in the figure XX.
 
-<!-- Funcitonal Unit -->
-The goal of this study is to evaluate and compare the change in ES provisioning 
-The functional unit (FU) is represented by *1kg of recycled filament delivered at school*.
+```{r DRAM}
 
-## Step II - Ecosystem services Priorities at the territorial level: Nancy, France
+```
 
-Three main elements needs to be carry out in this phase:
+From a perspective of AM process, several researches have used the life cycle impact assessment (LCIA) for the case of distributed recycling [@Kreiger2013; @Kreiger2014; @Kerdlap2021; @Garcia2021; @Zhao2018].
+The main element to highlight is that climate change (global warming potential -GWP-) and cumulative energy demand (CED) are the most studied impact factors in the literature of additive manufacturing.
+For instance, using a technical system *recyclebot* to create 3D printing recycled filament with High Density Polyethylen (HPDE),
+@Kreiger2014 argued that the distributed recycling can decrease the embodied energy by 69%-82% with respect to conventional recycling using CED estimations. 
+@Zhao2018 estimated the  environmental impacts associated with disposal of 1 kg PLA in three end-of-life options (landfill, recycling, incineration), making a point that recycling option is made using 3D printing technology.
+They used GWP (in kg CO2 eq), ozone depletion potential (ODP, in CFC-11 eq), fossil depletion potential (FDP, in kg oil eq), human toxicity potential (HTP, in kg 1,4-DB eq), particulate matter formation potential (PMFP, in kg PM10 eq), photochemical oxidant formation potential (POFP, in kg NMVOC), freshwater eutrophication potential (FEP, in kg P eq), freshwater ecotoxicity potential (FETP, in kg 1,4-DB eq), marine eutrophication potential (MEP, in kg N eq), marine ecotoxicity potential (METP, in kg 1,4-DB eq), terrestrial acidification potential (TAP, in kg SO2 eq), and terrestrial ecotoxicity potential (TETP, in kg 1,4-DB eq).
+In a more network level, @Kerdlap2021  quantify the LCIA  of distributed versus centralized  plastic recycling systems of small-scale distributed plastic sorting and recycling systems in comparison to traditional large-scale centralized systems in Singapore.
+They used climate change and cumulative energy, water depletion and terrestrial eco-toxicity as impact categories.
 
-1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+<!-- From perspective of the bioplastic material, @Bishop2021 reported a a comprehensive review of the appication of LCA studies on the comparative sustainability of bioplastics regarding petrol-based alternative.
+-->
 
-## Step II - Identifying the Hot spot of the
+```{r Tab:DRAM-ES}
+
+```
+
+Given these literature,  it is possible to conclude that GWP and
+
+@Vanderwilde2021 studied the connection of LCIA with the field of ecosystem services. 
+One major point from this studied is the proposition of the links that can connect the LCIA mid-point categories with the set of ES .
+Nevertheless, they used the version.
+
+Therefore, based on, table \@ref
+
+```{r, }
+
+ES_LCA <- 
+   tribble(~Description, ~ES, ~Ref,
+           'Climate change', '2.2.4.1; 2.1.1.2; 2.2.4.1; 2.2.4.2', ' ',
+           'Eutrophication', '2.2.5.1; 2.2.5.2; 2.1.1.1; 2.1.1.2 ', ' ',
+           'Ressources Depletion', 'All CICES-defined Provisioning (1.1.1.1 - 1.2.2.3; ) ES as potentially relevant; adding water availability (2.2.1.3; 2.2.5.1; 2.2.5.2', ' ',
+
+           'RD', '1.1.1.1; 1.1.1.2;
+1.1.1.3;
+1.1.2.1;
+1.1.2.2;
+1.1.2.3;
+1.1.3.1;
+1.1.3.2;
+1.1.3.3;
+1.1.4.1;
+1.1.4.2;
+1.1.4.3;
+1.1.5.1;
+1.1.5.2;
+1.1.5.3;
+1.1.6.1;
+1.1.6.2;
+1.1.6.3;
+1.2.1.1;
+1.2.1.2;
+1.2.1.3;
+1.2.2.1;
+1.2.2.2;
+1.2.2.3;
+
+2.2.1.3; 
+2.2.5.1; 
+2.2.5.2', ' '
+           )
+
+ ES_LCA %>% filter(Description != 'RD') %>% 
+  kbl(caption = "LCA impact categories of DRAM connecting with ES",  booktabs = T) %>%
+    kable_styling(latex_options = c("striped", "hold_position") ) %>% 
+    column_spec(1, width = "10em") %>% 
+    column_spec(2, width = "30em")
+
+```
+
+## Step III - Ecosystem services Priorities at the territorial level: Nancy, France
+
+In this step, the main goal is to identify the stratic axis that the territory put in the view of preserving/improving/restauring ecosystem services. 
+For that, we delimitate the city of Nancy, in the east region of , .
+
+Based on the three main perspectives of ES,
+
+- https://fr.calameo.com/read/005820422f7f4ab30f35b?page=1
+- https://www.ecologie.gouv.fr/levaluation-francaise-des-ecosystemes-et-des-services-ecosystemiques#scroll-nav__2
+
+- https://www.ecologie.gouv.fr/levaluation-francaise-des-ecosystemes-et-des-services-ecosystemiques#scroll-nav__3
+
+```{r Tab:Nancy-ES}
+
+Nancy_ES <- 
+   tribble(~Description, ~ES, ~Ref,
+
+           'Clima - Air', '2.2.6.1; 2.1.2.2', 'Calameo',
+           'Sol', '2.2.4.1; 2.2.4.2', 'Calameo'
+
+           )
+
+Nancy_ES %>% 
+  kbl(caption = "LCA impact categories of DRAM connecting with ES",  booktabs = T) %>%
+    kable_styling(latex_options = c("striped", "hold_position") ) %>% 
+    column_spec(1, width = "10em") %>% 
+    column_spec(2, width = "30em")
+
+```
+
+## Step IV - Identifying the Hot spot of the ES for the case of DRAM at Nancy, France
+
+```{r, include=FALSE, eval=FALSE}
+Value_chain <- Value_chain %>% mutate(Perspective = "Value chain of plastic")
+ES_LCA <- ES_LCA %>% mutate(Ref = ' ', Perspective = "LCA of DRAM") %>% filter(Description != 'Ressources Depletion' )
+Nancy_ES <- Nancy_ES %>% mutate(Perspective = "Territorial at Nancy")
+
+# Gathering all data
+Total_ES <- rbind(Value_chain, ES_LCA, Nancy_ES)
+
+Sankey <- Total_ES %>% select(Perspective, ES)
+
+Sankey <- Sankey %>% separate(ES, into=LETTERS[1:27], sep = ";")
+
+library(stringr)
+
+Sankey <- Sankey %>% pivot_longer(A:Z)
+Sankey$ES <- gsub('\\s+', '', Sankey$value)
+
+Sankey <-  Sankey %>% select(Perspective, ES)
+Sankey <- na.omit(Sankey)
+#Sankey$value = c(1)
+colnames(Sankey) <- c("source", "target")
+
+library(networkD3)
+
+# I need a long format
+Sankey <- Sankey %>% group_by(source, target) %>% summarise(value=sum (n()))
+
+# From these flows we need to create a node data frame: it lists every entities involved in the flow
+nodes <- data.frame(name=c(as.character(Sankey$source), as.character(Sankey$target)) %>% unique())
+
+# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
+Sankey$IDsource=match(Sankey$source, nodes$name)-1 
+Sankey$IDtarget=match(Sankey$target, nodes$name)-1
+
+# prepare colour scale
+ColourScal ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF","#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'
+
+# Make the Network
+Sankey_graf <-
+sankeyNetwork(Links = Sankey, Nodes = nodes,
+                     Source = "IDsource", Target = "IDtarget",
+                     Value = "value", NodeID = "name", fontSize=13 )
+
+                     #sinksRight=FALSE, colourScale=ColourScal, nodeWidth=40,  nodePadding=20)
+
+library(htmlwidgets)
+saveWidget(Sankey_graf, file="Sankey.html")
+
+library(webshot)
+webshot("Sankey.html", "Figures/Sankey.png")
+
+```
+
+\begin{landscape}
+```{r fig-sankey, fig.cap= 'Priorization of ES for the distributed recycling indsutrail system.' }
+
+#download.file(paste0(URL,'Plastics/ES/Kumar2021.jpg'), "Figures/Kumar2021.jpg")
+
+knitr::include_graphics('Figures/Sankey.png')
+```
+\end{landscape}
 

### 2021-11-29 00-ES/PubliER/PubliER.tex
avancando hoy

--- 2021-10-21 00-ES/PubliER/Draft.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[
-]{article}
-\usepackage{amsmath,amssymb}
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+
+  \journal{PubliER2022 - The industry of the future : beyond the Anthropocene. 2-4 Feb 2022 Troyes (France)} % Sets Journal name
+
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{graphicx}
+%%%%%%%%%%%%%%%% end my additions to header
+
+\usepackage[T1]{fontenc}
 \usepackage{lmodern}
+\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
   \fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing},
-  colorlinks=true,
-  linkcolor=blue,
-  filecolor=Maroon,
-  citecolor=Blue,
-  urlcolor=Blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage[left=3cm, right=3cm,top=3cm,bottom=2cm]{geometry}
+\bibliographystyle{elsarticle-harv}
 \usepackage{longtable,booktabs,array}
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory: the case of distributed recycling at Nancy, France},
+            colorlinks=true,
+            urlcolor=blue,
+            linkcolor=blue,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
 \setcounter{secnumdepth}{5}
-\usepackage{float}
-\usepackage{subfig}
-\usepackage[utf8]{inputenc}
-\def\tightlist{}
-\usepackage[bitstream-charter]{mathdesign}
-\usepackage{pdflscape}
-\usepackage{svg}
-\usepackage{lineno}
-\usepackage{setspace}
-\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
-\usepackage{tabu}
+% Pandoc toggle for numbering sections (defaults to be off)
 
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
+% Pandoc citation processing
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
 \newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
@@
 
-\title{Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing}
-\author{}
-\date{\vspace{-2.5em}}
+% Pandoc header
+\usepackage{float}
+\usepackage{subfig}
+\usepackage[utf8]{inputenc}
+\def\tightlist{}
+\usepackage[bitstream-charter]{mathdesign}
+\usepackage{pdflscape}
+\usepackage{svg}
+\usepackage{lineno}
+\usepackage{setspace}
+\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
+\usepackage{tabu}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{multicol}
+\usepackage{hhline}
+\usepackage{hyperref}
 
 \begin{document}
-\maketitle
+\begin{frontmatter}
 
-{
-\hypersetup{linkcolor=}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
+  \title{Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory: the case of distributed recycling at Nancy, France}
+    \author[UTT]{Fabio A. Cruz\corref{1}}
+   \ead{cruzsanc1@univ-lorraine.fr} 
+    \author[UTT]{Nadège Troussier}
+
+    \author[UL]{Hakim Boudaoud}
+
+    \author[UL]{Mauricio Camargo}
+
+      \address[UTT]{Universite de Technologie de Troyes, Troyes, France}
+    \address[UL]{ERPI, Université de Lorraine, F-54000 Nancy, France.}
+      \cortext[1]{Corresponding Author}
+
+  \begin{abstract}
+  Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
+  The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
+  From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
+  On the ecological side, there have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES).
+  While on the industrial side, life cycle assessment (LCA) tool is focused on the quantification of the environmental impact of industrial interventions.
+Despite its ability to cover mutually exclusive and exhaustive impact categories, the LCA approach still has deficiencies: 1) it focuses on quantifying and reducing the net environmental impacts, but not on reducing ecological overshoot and establishing synergies with nature; 2) it considers the interactions between technological processes, but not the interactions between relevant ecosystems.
+  Few researches have addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+  There is a need to include the ES in the desicion making process to establish the capacity of the territory in order to evaluate an absolute environmental sustainability of industrial systems.
+  The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
+  A prioritization is made based on the connection of urban ES services and the techno-ecological synergy.
+  The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
+  This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework for the territory of Nancy, France.
+  The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
+  \end{abstract}
+
+ \end{frontmatter}
+
 \linenumbers
@@
 
-The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
-Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).
+The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg, 2020}).
+Even though engineering products and processes might meet the needs of the present society, many of the technological developments are compromising the ability of future generations to meet their own needs (\protect\hyperlink{ref-Bakshi2019a}{Bakshi, 2019}).
+For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi et al., 2018}).
 This meta-principle is a imperative but not sufficient condition for sustainability.
-Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
-Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al., 2018}).
+Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al., 2021}).
 We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems.
@@
 They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-
-The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
-However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
+\protect\hyperlink{ref-SousaRocha2019}{Rocha et al.} (\protect\hyperlink{ref-SousaRocha2019}{2019}) revealed ten different models at operational, tactical, and strategical levels
+One strategical point in sustainability relies on the economic valuation of ecosystem goods and services framework.
+This approach gives an elegant framework highlighting their importance for society and human welfare.
+However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al., 2021}).
 The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
@@
 This scenario is not true today.
-The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
-The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al.
-2019}).
+The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres et al., 2021}).
+The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al., 2019}).
 It is difficult to provide information about pressure from industrial systems in corporate information systems.
-Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).
+Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-Bakshi2018}{Bakshi et al., 2018}).
 
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
-Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al.
-2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al.
-2018}).
-Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al.
-2021}).
+According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA, 2005}).
+Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-ONeill2018}{O'Neill et al., 2018}; \protect\hyperlink{ref-Rockstrom2009}{Rockström et al., 2009}).
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi, 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al., 2021}).
 Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).
+Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner et al., 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan et al., 2016}).
+Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez, 2017}).
 
-\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
-The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
-The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
-
-\textcolor{red}{
-Based on this background, in the following section a methodlogy will be presented in the analysis of the  To complete ...}
-
-The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
-This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements.
+The main purpose of this article is to propose a methodology in order to prioritize the ecosystem services at early development stages of industrial systems in a territory.
+This methodology is based in the use of the ecosystem services as boundary object (\protect\hyperlink{ref-Abson2014}{Abson et al., 2014}) with the purpose to identify ES according to the perspective of global value chain, industrial chain and territorial perspective.
 As a case application, the study of distributed recycling manufacturing will be describe.
-Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al.
-2021}).
-Therefore, new approaches need to be explored in order to reduce ar at least recycling this material.
+Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}).
+Therefore, new approaches need to be explored in order to reduce or at least recycling this material.
 Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
-
 The expected results seek to address the following questions:
@@
   What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling?
-\item
-  How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
+- How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
 \item
   What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
-  From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach,
 \end{itemize}
 
+From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach.
 In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
@@
 
-\textcolor{red}{The article is structure as follows.... ( to complete) } section \ref{background} \ldots{}
+The article is structure as follows.
+Section \ref{background} presents a background on theoretical element of ecosystem service in link with life cycle assessment and the territorial planning.
+Section \ref{methodology} presents the methodology proposed to identify and prioritize the ecosystems services.
+In Section \label{results}, the results of the methodology are presented for the industrial system of distributed recycling for additive manufacturing at Nancy, France.
+This industrial case enable to highlight the pertinence and limits of the methodology.
 
-\hypertarget{background}{%
-\section{Background}\label{background}}
+\hypertarget{literature-review}{%
+\section{Literature Review}\label{literature-review}}
 
@@
 
-\hypertarget{ecosystem-services}{%
-\subsection{Ecosystem services}\label{ecosystem-services}}
+\hypertarget{ecosystem-services-and-the-global-value-chain}{%
+\subsection{Ecosystem services and the global value chain}\label{ecosystem-services-and-the-global-value-chain}}
 
-Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being (\protect\hyperlink{ref-Gomez-Baggethun2010}{Gómez-Baggethun et al.
-2010}; \protect\hyperlink{ref-DeGroot2002}{De Groot, Wilson, and Boumans 2002}).
-Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital (\protect\hyperlink{ref-Laurans2013}{Laurans et al.
-2013}).
-Nevertheless, commodification of nature's services by reductionist thinking about individual services runs the risk of unintended harm and unbalanced outputs.
-Systems thinking is essential for avoiding such harm (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
-
-Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}, \protect\hyperlink{ref-Costanza2017}{2017}).
-Ecosystem goods (e.g; Food) and services (e.g.~waste assimilation) illustrate the benefits that human derive from the ecosystem functions (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}).
+Foundational ideas on ecosystem services (ES) seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being (\protect\hyperlink{ref-DeGroot2002}{De Groot et al., 2002}; \protect\hyperlink{ref-Gomez-Baggethun2010}{Gómez-Baggethun et al., 2010}).
+ES describes the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being (\protect\hyperlink{ref-Costanza2017}{Costanza et al., 2017}, \protect\hyperlink{ref-Costanza1997}{1997}).
+Ecosystem goods (e.g; Food) and services (e.g.~waste assimilation) illustrate the benefits that human derive from the ecosystem functions (\protect\hyperlink{ref-Costanza1997}{Costanza et al., 1997}).
 It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself.
 The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits.
-By contrast, the latter are those processes and functions where people can (or could have the potential (\protect\hyperlink{ref-ref}{\textbf{ref?}})) obtain benefits.
+By contrast, the latter are those processes and functions where people can (or could have the potential) obtain benefits.
 The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach.
-Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in `negative' way, making damage and costs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
-This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders (\protect\hyperlink{ref-Honeck2021}{Honeck et al.
-2021}).
+Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in `negative' way, making damage and costs (\protect\hyperlink{ref-TEEB2010}{TEEB, 2010}).
+One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al., 2003}).
+This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders (\protect\hyperlink{ref-Honeck2021}{Honeck et al., 2021}).
 
-Using a systematic literature review approach, \protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson} (\protect\hyperlink{ref-Torres2021}{2021}) distinguished and categorized 8 major key themes and 22 approaches in the ES field.
+Using a systematic literature review approach, \protect\hyperlink{ref-Torres2021}{Torres et al.} (\protect\hyperlink{ref-Torres2021}{2021}) distinguished and categorized 8 major key themes and 22 approaches in the ES field.
 Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field.
-Key approaches include methods (\protect\hyperlink{ref-Harrison2018}{Harrison et al.
-2018}), tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
+Key approaches include methods (\protect\hyperlink{ref-Harrison2018}{Harrison et al., 2018}), tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
 It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
+Today, ecosystems services field are being included in the decision-making through promotion of market-based instruments for payment for ES schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital (\protect\hyperlink{ref-Laurans2013}{Laurans et al., 2013}).
+Nevertheless, the commodification of nature's services by reductionist thinking about individual services runs the risk of unintended harm and unbalanced outputs (\protect\hyperlink{ref-Gomez-Baggethun2010}{Gómez-Baggethun et al., 2010}).
+Systems thinking is essential for avoiding such harm (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan et al., 2016}).
 
-Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies.
-Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
+Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital (\protect\hyperlink{ref-Costanza1997}{Costanza et al., 1997}) and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework (\protect\hyperlink{ref-Bruel2016}{Bruel et al., 2016}).
+From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it (\protect\hyperlink{ref-Ekins2003}{Ekins et al., 2003}).
+More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of \emph{critical} components that make a major contribution to welfare.
+The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience (\protect\hyperlink{ref-Ekins2003}{Ekins et al., 2003}).
 
-Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment (\protect\hyperlink{ref-MEA2005}{MEA 2005}),
-The Economics of Ecosystems and Biodiversity TEEB (\protect\hyperlink{ref-TEEB2010}{TEEB 2010}),
+\hypertarget{common-standard-of-ecosystem-services}{%
+\subsection{Common standard of ecosystem services}\label{common-standard-of-ecosystem-services}}
+
+Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment (\protect\hyperlink{ref-MEA2005}{MEA, 2005}),
+The Economics of Ecosystems and Biodiversity TEEB (\protect\hyperlink{ref-TEEB2010}{TEEB, 2010}),
 The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) (\protect\hyperlink{ref-ref}{\textbf{ref?}}) and the Common International Classification of Ecosystem Services (CICES).
@@
 \textbf{Supporting} (e.g soil formation and fixation of solar energy) and
-\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-PedersenZari2019}{Pedersen Zari 2019}).
+\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services are four broad categories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-PedersenZari2019}{Pedersen Zari, 2019}).
 
@@
 \end{figure}
-
-Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital (\protect\hyperlink{ref-Costanza1997}{Costanza et al.
-1997}) and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework (\protect\hyperlink{ref-Bruel2016}{Bruel et al.
-2016}).
-From a strong sustainability perspective, a declining capital stock is an unambiguous indicator of unsustainability in the flow of goods and services that derive from it (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
-More important, the recognition of the non-substitutability of natural capital with regard to the other forms of capital; acknowledging the characteristics of irreversibility (such as species extinction or climate change), uncertainty and the existence of \emph{critical} components that make a major contribution to welfare.
-The main core of the environmental problem relies on the use of use ecosystem's functions, mainly those that generate economic welfare, that are making a negative impact and influence on the natural capital stock, and even worse, on those functions that are responsible for ecosystem stability and resilience (\protect\hyperlink{ref-Ekins2003}{Ekins et al.
-2003}).
 
@@
 The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
+
 The following levels organize ES according to their divisions, groups and classes.
 At lower levels, more specific services can be defined and characterized.
+
 For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
+
 Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
 
-Figure 2.2 demonstrates the hierarchical structure of CICES scheme.
+\hypertarget{ecosystems-services-and-industrial-systems-towards-a-synergy-between}{%
+\subsection{Ecosystems services and industrial systems: Towards a synergy between}\label{ecosystems-services-and-industrial-systems-towards-a-synergy-between}}
 
-\hypertarget{distributed-recycling-via-additive-manufacturing}{%
-\subsection{Distributed recycling via additive manufacturing}\label{distributed-recycling-via-additive-manufacturing}}
+One major point A holistic evaluation of the externalities that industrial system
+Ecosystems services and industrial systems need to be confronten to holistic evaluation
+The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households (\protect\hyperlink{ref-Costanza2017}{Costanza et al., 2017}).
 
-Distributed plastic recycling has emerged in the literature to face the socio-environmental challenges related to plastic waste management (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al.
-2020}; \protect\hyperlink{ref-Santander2020}{Santander et al.
-2020}).
-The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
-To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
-However, as with any recycling system, its feasibility and real impact must be evaluated before its implementation.
-Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
+\protect\hyperlink{ref-Bakshi2015}{Bakshi et al.} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
+The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
 
-\textcolor{red}{ To complete ...}
+\hypertarget{ecosystems-services-at-the-urban-territorial-planification}{%
+\subsection{Ecosystems services at the urban territorial planification}\label{ecosystems-services-at-the-urban-territorial-planification}}
+
+More than two thirds of the world's population are expected to live in cities by 2050 (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities (\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton, 2013}).
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
+cooling, and runoff mitigation (\protect\hyperlink{ref-Bolund1999}{Bolund and Hunhammar, 1999}).
+\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton} (\protect\hyperlink{ref-Gomez-Baggethun2013}{2013}) draws on the developments of the ecosystem services for urban planning.
+They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
 
@@
 
-The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
+\label{methodology}
+
+The purpose of this article is to identify main relevant ES services from a industrial and territorial perspective at the early design of industrial systems.
+This identification is a first step with the purpose to evaluate the supply and demand of ecosystem services for these industrial systems.
+A prospective distributed recycling chain for additive manufacturing.
 A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
@@
 
-The goal of \emph{Planning} step is to identify the boundaries for the technological and ecological systems to be evaluated.
-In the \emph{Assessment} step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis.
-These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
-In the \emph{Evaluation} stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
-Finally, in the last step \emph{Management}, the main goal is to establish scenarios of evaluation based on the `Bussiness-as-usual' and Synergy frameworks.
-This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.
+\begin{itemize}
+\item
+  \textbf{I) Global value Planning}: the main goal is to identify the the links between the global value chain to be evaluated and the capital nature through the literature on ecological systems.
+  The main purpose in this step is to map the the interactions positive and negative.
+\item
+  \textbf{II) Industrial system}: the main aim is to define the technosphere and identify the key ecosystems services that are impacted.
+  The identification is made using the lens of connection between the LCA and ES elements.
+\item
+  \textbf{II) Industrial system}: in this step, the main purpose is the identification of the key urban priorities in the territorial context from a perspective of ecosystem services.
+  To establish these priorities, the territorial planification perspective is analysed given the fact that a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.
+\item
+  Finally, in \textbf{IV) Synthesis}, the main goal is to converge on main ES that are identified for the three last perspectives,
+\end{itemize}
 
-An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
 In the following sub-sections, each stage of the methodology is explained.
+An application of the framework will be presented in Section \label{results} using as case study of the distributed recycling chain via additive manufacturing.
 
-\hypertarget{planning}{%
-\subsection{Planning}\label{planning}}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
+\label{results}
 
-\hypertarget{case-study-distributing-recycling-via-additive-manufacturing}{%
-\section{Case study: Distributing recycling via Additive Manufacturing}\label{case-study-distributing-recycling-via-additive-manufacturing}}
+Context of the industrial system
 
-\hypertarget{indicators-in-ecosystem-services-distributed-recycling-the}{%
-\subsection{Indicators in Ecosystem Services Distributed recycling The}\label{indicators-in-ecosystem-services-distributed-recycling-the}}
+\hypertarget{step-i---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}{%
+\subsection{Step I - Ecosystem Services issues at the Value chain: Plastic issues at the ecosystems}\label{step-i---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}}
 
-\newpage
+The goal of this first step is to highlight the main interactions that the value chain have with the natural ecosystems.
+This enables us to have a holistic picture of the impacts of plastic pollution in the natural ecosystems taking into account the highlighting the uncertainties and knowledge gaps that could exist in the field.
 
-\hypertarget{results-of-the}{%
-\section{Results of the}\label{results-of-the}}
+\begin{figure}
+\includegraphics[width=1\linewidth]{Figures/Kumar2021} \caption{Illustration of MPs and NPs affecting various ecosystem services and climate change on terrestrial, aquatic, and atmospheric ecosystems.
+Source.
+Kumar2021.jpg}\label{fig:fig-Kumar2021}
+\end{figure}
 
-\hypertarget{planning-1}{%
-\subsection{Planning}\label{planning-1}}
+\protect\hyperlink{ref-Kumar2021}{Kumar et al.} (\protect\hyperlink{ref-Kumar2021}{2021}) reported a complete description of the major impacts on the plastic pollution an the ecosystems services,identifying in what extend there are present the interlinkages between plastic pollution, waste management, and Sustainable Development Goals (SDG).
+Figure \ref{fig:fig-Kumar2021} presents an overview of the major interactions that plastic impact the ecosystem services in the terrestrial and aquatic ecosystems, representing a major societal issue.
+Macrosplastics -MP- (particules \(\geq 5mm\) ), mesoplastics -MsP- (\(1-5 mm\)) and microplastics (\(<1~mm\)) are the major problems in the ecosystems.
 
-\hypertarget{goal-and-scope-definition}{%
-\subsubsection{Goal and scope definition}\label{goal-and-scope-definition}}
+For aquatic ecosystems, main risks are linked to standing water that acts as a breeding niche (to mosquitoes, pests, vector-borne diseases transmission), becomes a vector for toxic chemicals and, ultimately, disturbs the natural cycles (biogeochemical cycle in terrestrial ecosystems).
+Additionally, the transfer of plastic into the food chain is a clear danger to animal and, certainly, to humans as well.
+Thus, reducing the consumption of plastics is of great importance in the long term.
 
-The system depicted is presented in the figure.
-The ES-LCIA framework proposed by was applied to the version of life cycle analysis of distributed recycling develped by .
-Because Es are expected to be more relevant in the
+The plastic value chain is one of the mo
 
-The goal of this study is to evaluate and compare the change in ES provisioning
-The functional unit (FU) is represented by \emph{1kg of recycled filament delivered at school}.
+\begin{itemize}
+\item
+  Plastic materials have impats on the terrestrial, qauqtic, and atmospheric ecosystems.
+\item
+\end{itemize}
+
+Concerning the terrestrial impacts, the plastic degradation make and important impact on the pollitation of the
+
+The global value chain of the plastic material
+
+\renewcommand{\arraystretch}{1.5}
+\begin{table}[!h]
+
+\caption{\label{tab:Value-chain-ES}Plastic pollution impact on ES}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{30em}ll}
+\toprule
+Description & ES & Ref\\
+\midrule
+\cellcolor{gray!6}{Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops} & \cellcolor{gray!6}{1.1.1.1 ; 1.2.1.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+MPs and their suspended solids hasten eutrophication.
+Eutrophication worsens as a result of both resuspension and algae growth, adding more contaminants to the food chain supply and primarily creating organic contamination.
+& 1.1.5.1 ; 1.1.6.1 & {}[136]\\
+\cellcolor{gray!6}{MPs and NPs in the atmosphere also lead to the obstruction and lowering of pollination.} & \cellcolor{gray!6}{2.2.2.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+MPs and NPs are established to act as a vector and breach through any system (organisms) and even via trophic transfer (one trophic level to another via food chain), therefore, it can be hypothesized that MPs in the future can play a pivotal role in the spill over of infectious diseases, leading to an epidemic or pandemic of unknown scale & 2.2.3.1; 2.2.3.1 & Ref\\
+\cellcolor{gray!6}{MP and NP in terrestrial ecosystems reduce tha ability to sequester carbon.} & \cellcolor{gray!6}{2.1.1.2 ; 2.2.4.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+\addlinespace
+Elements as nitrogen and phosphorous, are also vividly influenced due to MPs and NPs in the soil ecosystem & 2.2.4.1 ; 2.2.4.2 & {}[@Kumar2021]\\
+\cellcolor{gray!6}{MPs accumulation can promote mineralization, nitrification, and denitrification in aquatic ecosystems, therefore releasing CO2, CH4, and N2O.} & \cellcolor{gray!6}{2.2.6.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+marine carbon sinks are critical in analyzing the global climate change and are potentially affected by MPs and NPs pollution on phytoplankton-sequestered CO2 and their transmission to the deep ocean via zooplankton [77].
+& 2.2.5.2 & {}[@Kumar2021]\\
+\cellcolor{gray!6}{Plastics-induced variations in solar radiation in the water column can alter physical processes at the ocean’s surface and near-surface layers as well as trigger climate feedback mechanisms} & \cellcolor{gray!6}{2.2.6.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+MPs and NPs are known to cause a dynamic shift in the soil temperature as is commonly practiced in agriculture sectors with extreme climatic conditions. & 2.2.4.1 & \\
+\addlinespace
+\cellcolor{gray!6}{MPs and NPs in the soil ecosystem are known to have a strong impact on the population structure and survival of these faunas [135,137,154,158].} & \cellcolor{gray!6}{2.2.4.1} & \cellcolor{gray!6}{}\\
+Small-sized plastics act as stressors, altering the ocean level and temperature and influencing the acidification. & 2.2.6.1 & \\
+\cellcolor{gray!6}{High amounts of MPs and NPs are more substantially found in pelagic species than in deep-water species.} & \cellcolor{gray!6}{1.1.5.1} & \cellcolor{gray!6}{}\\
+MPs and NPs act as vectors for toxic chemicals and microbes and can breach any ecosystem. & 2.1.1.1 & REf\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\hypertarget{step-ii---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}{%
+\subsection{Step II - Definition the Industrial system : Distributed recycling via additive manufacturing}\label{step-ii---definition-the-industrial-system-distributed-recycling-via-additive-manufacturing}}
+
+Major technological advances in the additive manufacturing (AM) field have enable the validation of distributed fabrication (\protect\hyperlink{ref-Matt2015}{Matt et al., 2015}; \protect\hyperlink{ref-Petersen2017a}{Petersen and Pearce, 2017}; \protect\hyperlink{ref-Woern2017}{Woern and Pearce, 2017}).
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assetes as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al., 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al., 2020}).
+The use of recycled material, either in the form of raw material or blended with virgin material, is a method of special interest to contribute to sustainable manufacturing (\protect\hyperlink{ref-Zhao2018}{Zhao et al., 2018}).
+
+The main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
+To do so, the use of additive manufacturing enables the technical paths to achieve this objective.
+In the DRAM methodology, consumers have an economic incentive to recycle.
+This is because they can use their waste as feedstock for a wide range of consumer products that can be produced for a fraction of the conventional cost of the equivalent products.
+Moreover, 3D printing is especially well suited because it enables the production of parts with (almost) no waste, and could reduce the waste related to the material by more than 40 \%, reusing 95 \% of the unused material (\protect\hyperlink{ref-Petrovic2011}{Petrovic et al., 2011}).
+Currently, most of the cost of 3D printing is associated with filament in FFF techniques (\protect\hyperlink{ref-Wittbrodt2013}{Wittbrodt et al., 2013}).
+
+By recycling raw materials such as Polylactic acid (PLA), one of the most frequently used materials in 3D printing, it is possible to reduce the carbon dioxide emissions that are incurred by transport to landfills or shipping to customers, offering environmental benefits (\protect\hyperlink{ref-Santander2020}{Santander et al., 2020}).
+
+However, While not all types of materials can be recycled given the technical difficulties, the integral evaluation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
+Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
+
+The technical system is depicted in the figure XX.
+
+From a perspective of AM process, several researches have used the life cycle impact assessment (LCIA) for the case of distributed recycling (\protect\hyperlink{ref-Garcia2021}{Garcia et al., 2021}; \protect\hyperlink{ref-Kerdlap2021}{Kerdlap et al., 2021}; \protect\hyperlink{ref-Kreiger2014}{Kreiger et al., 2014}; \protect\hyperlink{ref-Kreiger2013}{Kreiger and Pearce, 2013}; \protect\hyperlink{ref-Zhao2018}{Zhao et al., 2018}).
+The main element to highlight is that climate change (global warming potential -GWP-) and cumulative energy demand (CED) are the most studied impact factors in the literature of additive manufacturing.
+For instance, using a technical system \emph{recyclebot} to create 3D printing recycled filament with High Density Polyethylen (HPDE),
+\protect\hyperlink{ref-Kreiger2014}{Kreiger et al.} (\protect\hyperlink{ref-Kreiger2014}{2014}) argued that the distributed recycling can decrease the embodied energy by 69\%-82\% with respect to conventional recycling using CED estimations.
+\protect\hyperlink{ref-Zhao2018}{Zhao et al.} (\protect\hyperlink{ref-Zhao2018}{2018}) estimated the environmental impacts associated with disposal of 1 kg PLA in three end-of-life options (landfill, recycling, incineration), making a point that recycling option is made using 3D printing technology.
+They used GWP (in kg CO2 eq), ozone depletion potential (ODP, in CFC-11 eq), fossil depletion potential (FDP, in kg oil eq), human toxicity potential (HTP, in kg 1,4-DB eq), particulate matter formation potential (PMFP, in kg PM10 eq), photochemical oxidant formation potential (POFP, in kg NMVOC), freshwater eutrophication potential (FEP, in kg P eq), freshwater ecotoxicity potential (FETP, in kg 1,4-DB eq), marine eutrophication potential (MEP, in kg N eq), marine ecotoxicity potential (METP, in kg 1,4-DB eq), terrestrial acidification potential (TAP, in kg SO2 eq), and terrestrial ecotoxicity potential (TETP, in kg 1,4-DB eq).
+In a more network level, \protect\hyperlink{ref-Kerdlap2021}{Kerdlap et al.} (\protect\hyperlink{ref-Kerdlap2021}{2021}) quantify the LCIA of distributed versus centralized plastic recycling systems of small-scale distributed plastic sorting and recycling systems in comparison to traditional large-scale centralized systems in Singapore.
+They used climate change and cumulative energy, water depletion and terrestrial eco-toxicity as impact categories.
+
+Given these literature, it is possible to conclude that GWP and
+
+\protect\hyperlink{ref-Vanderwilde2021}{Vanderwilde and Newell} (\protect\hyperlink{ref-Vanderwilde2021}{2021}) studied the connection of LCIA with the field of ecosystem services.
+One major point from this studied is the proposition of the links that can connect the LCIA mid-point categories with the set of ES .
+Nevertheless, they used the version.
+
+Therefore, based on, table @ref
+
+\begin{table}[!h]
+
+\caption{\label{tab:unnamed-chunk-2}LCA impact categories of DRAM connecting with ES}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{30em}l}
+\toprule
+Description & ES & Ref\\
+\midrule
+\cellcolor{gray!6}{Climate change} & \cellcolor{gray!6}{2.2.4.1; 2.1.1.2; 2.2.4.1; 2.2.4.2} & \cellcolor{gray!6}{}\\
+Eutrophication & 2.2.5.1; 2.2.5.2; 2.1.1.1; 2.1.1.2 & \\
+\cellcolor{gray!6}{Ressources Depletion} & \cellcolor{gray!6}{All CICES-defined Provisioning (1.1.1.1 - 1.2.2.3; ) ES as potentially relevant; adding water availability (2.2.1.3; 2.2.5.1; 2.2.5.2} & \cellcolor{gray!6}{}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\hypertarget{step-iii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}{%
+\subsection{Step III - Ecosystem services Priorities at the territorial level: Nancy, France}\label{step-iii---ecosystem-services-priorities-at-the-territorial-level-nancy-france}}
+
+In this step, the main goal is to identify the stratic axis that the territory put in the view of preserving/improving/restauring ecosystem services.
+For that, we delimitate the city of Nancy, in the east region of , .
+
+Based on the three main perspectives of ES,
+
+\begin{itemize}
+\item
+  https://fr.calameo.com/read/005820422f7f4ab30f35b?page=1
+\item
+  https://www.ecologie.gouv.fr/levaluation-francaise-des-ecosystemes-et-des-services-ecosystemiques\#scroll-nav\_\_2
+\item
+  https://www.ecologie.gouv.fr/levaluation-francaise-des-ecosystemes-et-des-services-ecosystemiques\#scroll-nav\_\_3
+\end{itemize}
+
+\begin{table}[!h]
+
+\caption{(\#tab:Tab:Nancy-ES)LCA impact categories of DRAM connecting with ES}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{30em}l}
+\toprule
+Description & ES & Ref\\
+\midrule
+\cellcolor{gray!6}{Clima - Air} & \cellcolor{gray!6}{2.2.6.1; 2.1.2.2} & \cellcolor{gray!6}{Calameo}\\
+Sol & 2.2.4.1; 2.2.4.2 & Calameo\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\hypertarget{step-iv---identifying-the-hot-spot-of-the-es-for-the-case-of-dram-at-nancy-france}{%
+\subsection{Step IV - Identifying the Hot spot of the ES for the case of DRAM at Nancy, France}\label{step-iv---identifying-the-hot-spot-of-the-es-for-the-case-of-dram-at-nancy-france}}
+
+\begin{landscape}
+\begin{figure}
+\includegraphics[width=1\linewidth]{Figures/Sankey} \caption{Priorization of ES for the distributed recycling indsutrail system.}\label{fig:fig-sankey}
+\end{figure}
+\end{landscape}
+
+\hypertarget{discussion-and-perspective-of-the-analysis}{%
+\section{Discussion and perspective of the analysis}\label{discussion-and-perspective-of-the-analysis}}
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Bakshi2018}{}%
-Bakshi, Bhavik R, Timothy G Gutowski, and Dusan P Sekulic.
-2018.
-{``{Claiming Sustainability: Requirements and Challenges}.''} \emph{ACS Sustain.
-Chem.
-Eng.} 6 (3): 3632--39.
-\url{https://doi.org/10.1021/acssuschemeng.7b03953}.
+\leavevmode\vadjust pre{\hypertarget{ref-Abson2014}{}}%
+Abson, D.J., Wehrden, H.
+von, Baumgärtner, S., Fischer, J., Hanspach, J., Härdtle, W., Heinrichs, H., Klein, A.M., Lang, D.J., Martens, P., Walmsley, D., 2014.
+{Ecosystem services as a boundary object for sustainability}.
+\url{https://doi.org/10.1016/j.ecolecon.2014.04.012}
 
-\leavevmode\hypertarget{ref-Bakshi2015}{}%
-Bakshi, Bhavik R, Guy Ziv, and Michael D Lepech.
-2015.
-{``{Techno-Ecological Synergy: A Framework for Sustainable Engineering}.''} \emph{Environ.
-Sci.
-Technol.} 49 (3): 1752--60.
-\url{https://doi.org/10.1021/es5041442}.
+\leavevmode\vadjust pre{\hypertarget{ref-Bakshi2019a}{}}%
+Bakshi, B.R., 2019. {Toward sustainable chemical engineering: The role of process systems engineering}. \url{https://doi.org/10.1146/annurev-chembioeng-060718-030332}
 
-\leavevmode\hypertarget{ref-Bruel2018}{}%
-Bruel, Aurélien, Jakub Kronenberg, Nadège Troussier, and Bertrand Guillaume.
-2019.
-{``{Linking Industrial Ecology and Ecological Economics: A Theoretical and Empirical Foundation for the Circular Economy}.''} \emph{J.
+\leavevmode\vadjust pre{\hypertarget{ref-Bakshi2018}{}}%
+Bakshi, B.R., Gutowski, T.G., Sekulic, D.P., 2018. {Claiming Sustainability: Requirements and Challenges}. ACS Sustain. Chem. Eng. 6, 3632--3639. \url{https://doi.org/10.1021/acssuschemeng.7b03953}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bakshi2015}{}}%
+Bakshi, B.R., Ziv, G., Lepech, M.D., 2015. {Techno-Ecological Synergy: A Framework for Sustainable Engineering}. Environ. Sci. Technol. 49, 1752--1760. \url{https://doi.org/10.1021/es5041442}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bolund1999}{}}%
+Bolund, P., Hunhammar, S., 1999. {Ecosystem services in urban areas}. Ecol. Econ. 29, 293--301. \url{https://doi.org/10.1016/S0921-8009(99)00013-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bruel2018}{}}%
+Bruel, A., Kronenberg, J., Troussier, N., Guillaume, B., 2019.
+{Linking Industrial Ecology and Ecological Economics: A Theoretical and Empirical Foundation for the Circular Economy}.
+J.
 Ind.
-Ecol.} 23 (1): 12--21.
-\url{https://doi.org/10.1111/jiec.12745}.
+Ecol.
+23, 12--21.
+\url{https://doi.org/10.1111/jiec.12745}
 
-\leavevmode\hypertarget{ref-Bruel2016}{}%
-Bruel, Aurélien, Nadège Troussier, Bertrand Guillaume, and Natalia Sirina.
-2016.
-{``{Considering Ecosystem Services in Life Cycle Assessment to Evaluate Environmental Externalities}.''} \emph{Procedia CIRP} 48: 382--87.
-\url{https://doi.org/10.1016/j.procir.2016.03.143}.
+\leavevmode\vadjust pre{\hypertarget{ref-Bruel2016}{}}%
+Bruel, A., Troussier, N., Guillaume, B., Sirina, N., 2016.
+{Considering Ecosystem Services in Life Cycle Assessment to Evaluate Environmental Externalities}.
+Procedia CIRP 48, 382--387.
+\url{https://doi.org/10.1016/j.procir.2016.03.143}
 
-\leavevmode\hypertarget{ref-Ceschin2016}{}%
-Ceschin, Fabrizio, and Idil Gaziulusoy.
-2016.
-{``{Evolution of design for sustainability: From product design to design for system innovations and transitions}.''} \emph{Des.
-Stud.} 47 (November): 118--63.
-\url{https://doi.org/10.1016/j.destud.2016.09.002}.
+\leavevmode\vadjust pre{\hypertarget{ref-Ceschin2016}{}}%
+Ceschin, F., Gaziulusoy, I., 2016.
+{Evolution of design for sustainability: From product design to design for system innovations and transitions}.
+Des.
+Stud.
+47, 118--163.
+\url{https://doi.org/10.1016/j.destud.2016.09.002}
 
-\leavevmode\hypertarget{ref-Costanza1997}{}%
-Costanza, Robert, Ralph D'Arge, Rudolf de Groot, Stephen Farber, Monica Grasso, Bruce Hannon, Karin Limburg, et al.
-1997.
-{``{The value of the world's ecosystem services and natural capital}.''} \emph{Nature} 387 (6630): 253--60.
-\url{https://doi.org/10.1038/387253a0}.
+\leavevmode\vadjust pre{\hypertarget{ref-Costanza1997}{}}%
+Costanza, R., D'Arge, R., Groot, R.
+de, Farber, S., Grasso, M., Hannon, B., Limburg, K., Naeem, S., O'Neill, R.V., Paruelo, J., Raskin, R.G., Sutton, P., Belt, M.
+van den, 1997.
+{The value of the world's ecosystem services and natural capital}.
+Nature 387, 253--260.
+\url{https://doi.org/10.1038/387253a0}
 
-\leavevmode\hypertarget{ref-Costanza2017}{}%
-Costanza, Robert, Rudolf de Groot, Leon Braat, Ida Kubiszewski, Lorenzo Fioramonti, Paul Sutton, Steve Farber, and Monica Grasso.
-2017.
-{``{Twenty years of ecosystem services: How far have we come and how far do we still need to go?}''} Elsevier B.V.
-\url{https://doi.org/10.1016/j.ecoser.2017.09.008}.
+\leavevmode\vadjust pre{\hypertarget{ref-Costanza2017}{}}%
+Costanza, R., Groot, R.
+de, Braat, L., Kubiszewski, I., Fioramonti, L., Sutton, P., Farber, S., Grasso, M., 2017.
+{Twenty years of ecosystem services: How far have we come and how far do we still need to go?} \url{https://doi.org/10.1016/j.ecoser.2017.09.008}
 
-\leavevmode\hypertarget{ref-CruzSanchez2020}{}%
-Cruz Sanchez, Fabio A., Hakim Boudaoud, Mauricio Camargo, and Joshua M.
-Pearce.
-2020.
-{``{Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy}.''} \emph{J.
+\leavevmode\vadjust pre{\hypertarget{ref-CruzSanchez2020}{}}%
+Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
+{Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy}.
+J.
 Clean.
-Prod.} 264 (August): 121602.
-\url{https://doi.org/10.1016/j.jclepro.2020.121602}.
+Prod.
+264, 121602.
+\url{https://doi.org/10.1016/j.jclepro.2020.121602}
 
-\leavevmode\hypertarget{ref-DeGroot2002}{}%
-De Groot, Rudolf S., Matthew A.
-Wilson, and Roelof M.
+\leavevmode\vadjust pre{\hypertarget{ref-DeGroot2002}{}}%
+De Groot, R.S., Wilson, M.A., Boumans, R.M.J., 2002.
+{A typology for the classification, description and valuation of ecosystem functions, goods and services}.
+Ecol.
+Econ.
+41, 393--408.
+\url{https://doi.org/10.1016/S0921-8009(02)00089-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Diwekar2021}{}}%
+Diwekar, U., Amekudzi-Kennedy, A., Bakshi, B., Baumgartner, R., Boumans, R., Burger, P., Cabezas, H., Egler, M., Farley, J., Fath, B., Gleason, T., Huang, Y., Karunanithi, A., Khanna, V., Mangan, A., Mayer, A.L., Mukherjee, R., Mullally, G., Rico-Ramirez, V., Shonnard, D., Svanström, M., Theis, T., 2021.
+{A perspective on the role of uncertainty in sustainability science and engineering}.
+Resour.
+Conserv.
+Recycl.
+164, 105140.
+\url{https://doi.org/10.1016/j.resconrec.2020.105140}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ekins2003}{}}%
+Ekins, P., Simon, S., Deutsch, L., Folke, C., De Groot, R., 2003.
+{A framework for the practical application of the concepts of critical natural capital and strong sustainability}.
+Ecol.
+Econ.
+44, 165--185.
+\url{https://doi.org/10.1016/S0921-8009(02)00272-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Garcia2021}{}}%
+Garcia, F.L., Nunes, A.O., Martins, M.G., Belli, M.C., Saavedra, Y.M.B., Silva, D.A.L., Moris, V.A.
+da S., 2021.
+{Comparative LCA of conventional manufacturing vs.
+additive manufacturing: the case of injection moulding for recycled polymers}.
+Int.
 J.
-Boumans.
-2002.
-{``{A typology for the classification, description and valuation of ecosystem functions, goods and services}.''} \emph{Ecol.
-Econ.} 41 (3): 393--408.
-\url{https://doi.org/10.1016/S0921-8009(02)00089-7}.
+Sustain.
+Eng.
+00, 1--19.
+\url{https://doi.org/10.1080/19397038.2021.1990435}
 
-\leavevmode\hypertarget{ref-Diwekar2021}{}%
-Diwekar, U., A.
-Amekudzi-Kennedy, B.
-Bakshi, R.
-Baumgartner, R.
-Boumans, P.
-Burger, H.
-Cabezas, et al.
-2021.
-{``{A perspective on the role of uncertainty in sustainability science and engineering}.''} \emph{Resour.
-Conserv.
-Recycl.} 164 (January): 105140.
-\url{https://doi.org/10.1016/j.resconrec.2020.105140}.
+\leavevmode\vadjust pre{\hypertarget{ref-Gomez-Baggethun2013}{}}%
+Gómez-Baggethun, E., Barton, D.N., 2013. {Classifying and valuing ecosystem services for urban planning}. Ecol. Econ. 86, 235--245. \url{https://doi.org/10.1016/j.ecolecon.2012.08.019}
 
-\leavevmode\hypertarget{ref-Ekins2003}{}%
-Ekins, Paul, Sandrine Simon, Lisa Deutsch, Carl Folke, and Rudolf De Groot.
-2003.
-{``{A framework for the practical application of the concepts of critical natural capital and strong sustainability}.''} \emph{Ecol.
-Econ.} 44 (2-3): 165--85.
-\url{https://doi.org/10.1016/S0921-8009(02)00272-0}.
+\leavevmode\vadjust pre{\hypertarget{ref-Gomez-Baggethun2010}{}}%
+Gómez-Baggethun, E., Groot, R.
+de, Lomas, P.L., Montes, C., 2010.
+{The history of ecosystem services in economic theory and practice: From early notions to markets and payment schemes}.
+Ecol.
+Econ.
+69, 1209--1218.
+\url{https://doi.org/10.1016/j.ecolecon.2009.11.007}
 
-\leavevmode\hypertarget{ref-Gopalakrishnan2016}{}%
-Gopalakrishnan, Varsha, Bhavik R.
-Bakshi, and Guy Ziv.
-2016.
-{``{Assessing the capacity of local ecosystems to meet industrial demand for ecosystem services}.''} \emph{AIChE J.} 62 (9): 3319--33.
-\url{https://aiche.onlinelibrary.wiley.com/doi/full/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/abs/10.1002/aic.15340\%20https://aiche.onlinelibrary.wiley.com/doi/10.1002/aic.15340}.
+\leavevmode\vadjust pre{\hypertarget{ref-Gopalakrishnan2016}{}}%
+Gopalakrishnan, V., Bakshi, B.R., Ziv, G., 2016. {Assessing the capacity of local ecosystems to meet industrial demand for ecosystem services}. AIChE J. 62, 3319--3333.
 
-\leavevmode\hypertarget{ref-Gomez-Baggethun2010}{}%
-Gómez-Baggethun, Erik, Rudolf de Groot, Pedro L.
-Lomas, and Carlos Montes.
-2010.
-{``{The history of ecosystem services in economic theory and practice: From early notions to markets and payment schemes}.''} \emph{Ecol.
-Econ.} 69 (6): 1209--18.
-\url{https://doi.org/10.1016/j.ecolecon.2009.11.007}.
+\leavevmode\vadjust pre{\hypertarget{ref-Harrison2018}{}}%
+Harrison, P.A., Dunford, R., Barton, D.N., Kelemen, E., Martín-López, B., Norton, L., Termansen, M., Saarikoski, H., Hendriks, K., Gómez-Baggethun, E., Czúcz, B., García-Llorente, M., Howard, D., Jacobs, S., Karlsen, M., Kopperoinen, L., Madsen, A., Rusch, G., Van Eupen, M., Verweij, P., Smith, R., Tuomasjukka, D., Zulian, G., 2018.
+{Selecting methods for ecosystem service assessment: A decision tree approach}.
+Ecosyst.
+Serv.
+29, 481--498.
+\url{https://doi.org/10.1016/j.ecoser.2017.09.016}
 
-\leavevmode\hypertarget{ref-Harrison2018}{}%
-Harrison, Paula A., Rob Dunford, David N.
-Barton, Eszter Kelemen, Berta Martín-López, Lisa Norton, Mette Termansen, et al.
-2018.
-{``{Selecting methods for ecosystem service assessment: A decision tree approach}.''} \emph{Ecosyst.
-Serv.} 29 (February): 481--98.
-\url{https://doi.org/10.1016/j.ecoser.2017.09.016}.
+\leavevmode\vadjust pre{\hypertarget{ref-Honeck2021}{}}%
+Honeck, E., Gallagher, L., Arx, B.
+von, Lehmann, A., Wyler, N., Villarrubia, O., Guinaudeau, B., Schlaepfer, M.A., 2021.
+{Integrating ecosystem services into policymaking -- A case study on the use of boundary organizations}.
+Ecosyst.
+Serv.
+49, 101286.
+\url{https://doi.org/10.1016/j.ecoser.2021.101286}
 
-\leavevmode\hypertarget{ref-Honeck2021}{}%
-Honeck, Erica, Louise Gallagher, Bertrand von Arx, Anthony Lehmann, Nicolas Wyler, Olga Villarrubia, Benjamin Guinaudeau, and Martin A.
-Schlaepfer.
-2021.
-{``{Integrating ecosystem services into policymaking -- A case study on the use of boundary organizations}.''} \emph{Ecosyst.
-Serv.} 49 (June): 101286.
-\url{https://doi.org/10.1016/j.ecoser.2021.101286}.
+\leavevmode\vadjust pre{\hypertarget{ref-Kerdlap2021}{}}%
+Kerdlap, P., Purnama, A.R., Low, J.S.C., Tan, D.Z.L., Barlow, C.Y., Ramakrishna, S., 2021.
+{Comparing the environmental performance of distributed versus centralized plastic recycling systems: Applying hybrid simulation modeling to life cycle assessment}.
+J.
+Ind.
+Ecol.
+\url{https://doi.org/10.1111/jiec.13151}
 
-\leavevmode\hypertarget{ref-Kumar2021}{}%
-Kumar, Rakesh, Anurag Verma, Arkajyoti Shome, Rama Sinha, Srishti Sinha, Prakash Kumar Jha, Ritesh Kumar, et al.
-2021.
-{``{Impacts of Plastic Pollution on Ecosystem Services, Sustainable Development Goals, and Need to Focus on Circular Economy and Policy Interventions}.''} \emph{Sustainability} 13 (17): 9963.
-\url{https://doi.org/10.3390/su13179963}.
+\leavevmode\vadjust pre{\hypertarget{ref-Kreiger2014}{}}%
+Kreiger, M.a., Mulder, M.L., Glover, A.G., Pearce, J.M., 2014.
+{Life cycle analysis of distributed recycling of post-consumer high density polyethylene for 3-D printing filament}.
+J.
+Clean.
+Prod.
+70, 90--96.
+\url{https://doi.org/10.1016/j.jclepro.2014.02.009}
 
-\leavevmode\hypertarget{ref-Laurans2013}{}%
-Laurans, Yann, Aleksandar Rankovic, Raphaël Billé, Romain Pirard, and Laurent Mermet.
-2013.
-{``{Use of ecosystem services economic valuation for decision making: Questioning a literature blindspot}.''} Academic Press.
-\url{https://doi.org/10.1016/j.jenvman.2013.01.008}.
+\leavevmode\vadjust pre{\hypertarget{ref-Kreiger2013}{}}%
+Kreiger, M., Pearce, J.M., 2013.
+{Environmental Impacts of Distributed Manufacturing from 3-D Printing of Polymer Components and Products}.
+MRS Proc.
+1492, 85--90.
+\url{https://doi.org/10.1557/opl.2013.319}
 
-\leavevmode\hypertarget{ref-Liu2019g}{}%
-Liu, Xinyu, and Bhavik R.
-Bakshi.
-2019.
-{``{Ecosystem Services in Life Cycle Assessment while Encouraging Techno‐Ecological Synergies}.''} \emph{J.
-Ind.
-Ecol.} 23 (2): 347--60.
-\url{https://doi.org/10.1111/jiec.12755}.
+\leavevmode\vadjust pre{\hypertarget{ref-Kumar2021}{}}%
+Kumar, R., Verma, A., Shome, A., Sinha, R., Sinha, S., Jha, P.K., Kumar, R., Kumar, P., Shubham, Das, S., Sharma, P., Vara Prasad, P.V., 2021.
+{Impacts of Plastic Pollution on Ecosystem Services, Sustainable Development Goals, and Need to Focus on Circular Economy and Policy Interventions}.
+Sustainability 13, 9963.
+\url{https://doi.org/10.3390/su13179963}
 
-\leavevmode\hypertarget{ref-Lomborg2020}{}%
-Lomborg, Bjorn.
-2020.
-{``{Welfare in the 21st century: Increasing development, reducing inequality, the impact of climate change, and the cost of climate policies}.''} \emph{Technol.
+\leavevmode\vadjust pre{\hypertarget{ref-Laurans2013}{}}%
+Laurans, Y., Rankovic, A., Billé, R., Pirard, R., Mermet, L., 2013.
+{Use of ecosystem services economic valuation for decision making: Questioning a literature blindspot}.
+\url{https://doi.org/10.1016/j.jenvman.2013.01.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Liu2019g}{}}%
+Liu, X., Bakshi, B.R., 2019. {Ecosystem Services in Life Cycle Assessment while Encouraging Techno‐Ecological Synergies}. J. Ind. Ecol. 23, 347--360. \url{https://doi.org/10.1111/jiec.12755}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lomborg2020}{}}%
+Lomborg, B., 2020.
+{Welfare in the 21st century: Increasing development, reducing inequality, the impact of climate change, and the cost of climate policies}.
+Technol.
 Forecast.
 Soc.
-Change} 156 (July): 119981.
-\url{https://doi.org/10.1016/j.techfore.2020.119981}.
+Change 156, 119981.
+\url{https://doi.org/10.1016/j.techfore.2020.119981}
 
-\leavevmode\hypertarget{ref-Martinez-Hernandez2017}{}%
-Martinez-Hernandez, Elias.
-2017.
-{``{Trends in sustainable process design---from molecular to global scales}.''} \emph{Curr.
-Opin.
-Chem.
-Eng.} 17 (August): 35--41.
-\url{https://doi.org/10.1016/j.coche.2017.05.005}.
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez-Hernandez2017}{}}%
+Martinez-Hernandez, E., 2017. {Trends in sustainable process design---from molecular to global scales}. Curr. Opin. Chem. Eng. 17, 35--41. \url{https://doi.org/10.1016/j.coche.2017.05.005}
 
-\leavevmode\hypertarget{ref-MEA2005}{}%
-MEA. 2005. {``{Ecosystems and Human well-being: Synthesis}.''} \href{https://www.islandpress.org}{www.islandpress.org}.
+\leavevmode\vadjust pre{\hypertarget{ref-Matt2015}{}}%
+Matt, D.T., Rauch, E., Dallasega, P., 2015.
+{Trends towards Distributed Manufacturing Systems and Modern Forms for their Design}.
+Procedia CIRP 33, 185--190.
+\url{https://doi.org/10.1016/j.procir.2015.06.034}
 
-\leavevmode\hypertarget{ref-ONeill2018}{}%
-O'Neill, Daniel W., Andrew L.
-Fanning, William F.
-Lamb, and Julia K.
-Steinberger.
-2018.
-{``{A good life for all within planetary boundaries}.''} \emph{Nat.
-Sustain.} 1 (2): 88--95.
-\url{https://doi.org/10.1038/s41893-018-0021-4}.
+\leavevmode\vadjust pre{\hypertarget{ref-MEA2005}{}}%
+MEA, 2005. {Ecosystems and Human well-being: Synthesis}.
 
-\leavevmode\hypertarget{ref-PedersenZari2019}{}%
-Pedersen Zari, Maibritt.
-2019.
-{``{Ecosystem services impacts as part of building materials selection criteria}.''} \emph{Mater.
-Today Sustain.} 3-4.
-\url{https://doi.org/10.1016/j.mtsust.2019.100010}.
+\leavevmode\vadjust pre{\hypertarget{ref-ONeill2018}{}}%
+O'Neill, D.W., Fanning, A.L., Lamb, W.F., Steinberger, J.K., 2018. {A good life for all within planetary boundaries}. Nat. Sustain. 1, 88--95. \url{https://doi.org/10.1038/s41893-018-0021-4}
 
-\leavevmode\hypertarget{ref-Potschin-Young2018}{}%
-Potschin-Young, M., R.
-Haines-Young, C.
-Görg, U.
-Heink, K.
-Jax, and C.
-Schleyer.
-2018.
-{``{Understanding the role of conceptual frameworks: Reading the ecosystem service cascade}.''} \emph{Ecosyst.
-Serv.} 29 (February): 428--40.
-\url{https://doi.org/10.1016/j.ecoser.2017.05.015}.
+\leavevmode\vadjust pre{\hypertarget{ref-PedersenZari2019}{}}%
+Pedersen Zari, M., 2019. {Ecosystem services impacts as part of building materials selection criteria}. Mater. Today Sustain. 3-4. \url{https://doi.org/10.1016/j.mtsust.2019.100010}
 
-\leavevmode\hypertarget{ref-Rockstrom2009}{}%
-Rockström, Johan, Will Steffen, Kevin Noone, Åsa Persson, F.
-Stuart Chapin, Eric F.
-Lambin, Timothy M.
-Lenton, et al.
-2009.
-{``{A safe operating space for humanity}.''} \url{https://doi.org/10.1038/461472a}.
+\leavevmode\vadjust pre{\hypertarget{ref-Petersen2017a}{}}%
+Petersen, E., Pearce, J., 2017.
+{Emergence of Home Manufacturing in the Developed World: Return on Investment for Open-Source 3-D Printers}.
+Technologies 5, 7.
+\url{https://doi.org/10.3390/technologies5010007}
 
-\leavevmode\hypertarget{ref-Rodrigues2021}{}%
-Rodrigues, Jérémy, Natacha Gondran, Adrien Beziat, and Valérie Laforest.
-2021.
-{``{Application of the absolute environmental sustainability assessment framework to multifunctional systems -- The case of municipal solid waste management}.''} \emph{J.
+\leavevmode\vadjust pre{\hypertarget{ref-Petrovic2011}{}}%
+Petrovic, V., Vicente Haro Gonzalez, J., Jordá Ferrando, O., Delgado Gordillo, J., Ramón Blasco Puchades, J., Portolés Griñan, L., 2011.
+{Additive layered manufacturing: sectors of industrial application shown through case studies}.
+Int.
+J.
+Prod.
+Res.
+49, 1061--1079.
+\url{https://doi.org/10.1080/00207540903479786}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Potschin-Young2018}{}}%
+Potschin-Young, M., Haines-Young, R., Görg, C., Heink, U., Jax, K., Schleyer, C., 2018.
+{Understanding the role of conceptual frameworks: Reading the ecosystem service cascade}.
+Ecosyst.
+Serv.
+29, 428--440.
+\url{https://doi.org/10.1016/j.ecoser.2017.05.015}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SousaRocha2019}{}}%
+Rocha, C.S., Antunes, P., Partidário, P., 2019. {Design for sustainability models: A multiperspective review}. J. Clean. Prod. 234, 1428--1445. \url{https://doi.org/10.1016/j.jclepro.2019.06.108}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rockstrom2009}{}}%
+Rockström, J., Steffen, W., Noone, K., Persson, Å., Chapin, F.S., Lambin, E.F., Lenton, T.M., Scheffer, M., Folke, C., Schellnhuber, H.J., Nykvist, B., De Wit, C.A., Hughes, T., Van Der Leeuw, S., Rodhe, H., Sörlin, S., Snyder, P.K., Costanza, R., Svedin, U., Falkenmark, M., Karlberg, L., Corell, R.W., Fabry, V.J., Hansen, J., Walker, B., Liverman, D., Richardson, K., Crutzen, P., Foley, J.A., 2009.
+{A safe operating space for humanity}.
+\url{https://doi.org/10.1038/461472a}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rodrigues2021}{}}%
+Rodrigues, J., Gondran, N., Beziat, A., Laforest, V., 2021.
+{Application of the absolute environmental sustainability assessment framework to multifunctional systems -- The case of municipal solid waste management}.
+J.
 Clean.
-Prod.} 322: 129034.
-\url{https://doi.org/10.1016/j.jclepro.2021.129034}.
+Prod.
+322, 129034.
+\url{https://doi.org/10.1016/j.jclepro.2021.129034}
 
-\leavevmode\hypertarget{ref-Santander2020}{}%
-Santander, Pavlo, Fabio A Cruz Sanchez, Hakim Boudaoud, and Mauricio Camargo.
-2020.
-{``{Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach}.''} \emph{Resour.
+\leavevmode\vadjust pre{\hypertarget{ref-Santander2020}{}}%
+Santander, P., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., 2020.
+{Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach}.
+Resour.
 Conserv.
-Recycl.} 154 (March): 104531.
-\url{https://doi.org/10.1016/j.resconrec.2019.104531}.
+Recycl.
+154, 104531.
+\url{https://doi.org/10.1016/j.resconrec.2019.104531}
 
-\leavevmode\hypertarget{ref-TEEB2010}{}%
-TEEB. 2010. \emph{{The Economics of Ecosystems and Biodiversity Ecological and Economic Foundations.}} \url{https://doi.org/10.4324/9781849775489}.
+\leavevmode\vadjust pre{\hypertarget{ref-TEEB2010}{}}%
+TEEB, 2010. {The Economics of Ecosystems and Biodiversity Ecological and Economic Foundations.} \url{https://doi.org/10.4324/9781849775489}
 
-\leavevmode\hypertarget{ref-Torres2021}{}%
-Torres, Angélica Valencia, Chetan Tiwari, and Samuel F.
-Atkinson.
-2021.
-{``{Progress in ecosystem services research: A guide for scholars and practitioners}.''} \emph{Ecosyst.
-Serv.} 49 (June): 101267.
-\url{https://doi.org/10.1016/j.ecoser.2021.101267}.
+\leavevmode\vadjust pre{\hypertarget{ref-Torres2021}{}}%
+Torres, A.V., Tiwari, C., Atkinson, S.F., 2021.
+{Progress in ecosystem services research: A guide for scholars and practitioners}.
+Ecosyst.
+Serv.
+49, 101267.
+\url{https://doi.org/10.1016/j.ecoser.2021.101267}
 
-\leavevmode\hypertarget{ref-Wallner1996}{}%
-Wallner, H.
-P., M.
-Narodoslawsky, and F.
-Moser.
-1996.
-{``{Islands of sustainability: A bottom-up approach towards sustainable development}.''} \emph{Environ.
+\leavevmode\vadjust pre{\hypertarget{ref-Vanderwilde2021}{}}%
+Vanderwilde, C.P., Newell, J.P., 2021. {Ecosystem services and life cycle assessment: A bibliometric review}. \url{https://doi.org/10.1016/j.resconrec.2021.105461}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wallner1996}{}}%
+Wallner, H.P., Narodoslawsky, M., Moser, F., 1996.
+{Islands of sustainability: A bottom-up approach towards sustainable development}.
+Environ.
 Plan.
-A} 28 (10): 1763--78.
-\url{https://doi.org/10.1068/a281763}.
+A 28, 1763--1778.
+\url{https://doi.org/10.1068/a281763}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wittbrodt2013}{}}%
+Wittbrodt, B.T., Glover, A.G., Laureto, J., Anzalone, G.C., Oppliger, D., Irwin, J.L., Pearce, J.M., 2013.
+{Life-cycle economic analysis of distributed manufacturing with open-source 3-D printers}.
+Mechatronics 23, 713--726.
+\url{https://doi.org/10.1016/j.mechatronics.2013.06.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Woern2017}{}}%
+Woern, A., Pearce, J., 2017. {Distributed Manufacturing of Flexible Products: Technical Feasibility and Economic Viability}. Technologies 5, 71. \url{https://doi.org/10.3390/technologies5040071}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Zhao2018}{}}%
+Zhao, P., Rao, C., Gu, F., Sharmin, N., Fu, J., 2018.
+{Close-looped recycling of polylactic acid used in 3D printing: An experimental investigation and life cycle assessment}.
+J.
+Clean.
+Prod.
+197, 1046--1055.
+\url{https://doi.org/10.1016/j.jclepro.2018.06.275}
 

### 2022-02-13 xar-EB-general/index.Rmd
presentation

@@
   **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
-  Projet de recherche CREIDD et ERPI
 author: "Fabio Cruz / Mauricio Camargo / Nadège Troussier"
 institute: "CREIDD, ERPI"
-date: '2020/11/18 (updated: `r Sys.Date()`)'
+#date: "2020/11/18 (updated: Sys.Date())"
 output:
@@
     lib_dir: libs
-    css: ["default"]
+    css: ["assets/xaringan-themer.css", "assets/EB.css"]
     seal: false 
@@
 options(htmltools.dir.version = FALSE)
+source("xaringan-themer.R")
 
-knitr::opts_chunk$set(include= TRUE, echo=FALSE, message=FALSE, fig.path="figures/")
+library(vembedr)
 
-library(readxl)
-library(here)
-library(flextable)
-library(tidyverse)
+knitr::opts_chunk$set(
+   include = TRUE,
+  fig.width=9, fig.height=3.5, fig.retina=3,
+  fig.path="figures/",
+  out.width = "100%",
+  fig.align = 'center',
+  cache = FALSE,
+  echo = FALSE,
+  message = FALSE, 
+  warning = FALSE,
+  fig.show = TRUE,
+  hiline = TRUE
+)
 
@@
 
-```{r, include=TRUE, echo=FALSE}
-# CSS for the CSS
-htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
-htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
-```
-
-```{r share-again, echo=FALSE}
-xaringanExtra::use_share_again()
-```
-
----
-
 class: title-slide, left, middle
@@
 
+<br>
 # `r rmarkdown::metadata$title`
@@
 
-### `r rmarkdown::metadata$date`
+###**L'ingénierie et le management de l'innovation au service de la transformation des territoires**
+
+### `r Sys.Date()`
 
@@
 
-```{r, include=FALSE}
-Fabio <- TRUE
-```
-
-```{r, child= if (!Fabio) 'partials/Fabio-presentation.Rmd'}
-
-```
-
----
-
-class: middle
-
-# Agenda
-
-.pull-left[
-1. .content-box-yellow[ERPI Laboratory]
-1. Green Fablab
-1. Everest Bio
-1. Proposition and Research axis
-]
-
-.pull-right[
-
-.brand-blue[Equipe de Recherche sur le Processus Innovatifs - ERPI]
-
-```{r, out.width = '80%', fig.align='center'}
-knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
-```
-]
-
----
-
-## .small[Equipe de Recherche sur le Processus Innovatifs - ERPI]
-
-A .red[Multidisciplinary] team in **Industrial Engineering** specialized in the study of Innovation processes
-
-.pull-left[
-
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics('https://erpi.univ-lorraine.fr/assets/images/logo-ERPI.svg')
-```
-
-45 Members average
-
-24 permanent researchers <br>
-(10 full Pr., 13 associated Pr, 1 Research engineer) <br>
-1 Studies engineer <br>
-5 Postdoc  <br>
-3 Temporary lecturers  <br>
-2 Admin. <br>
-
-]
-
-.pull-right[
-
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'LF2L/Methodology-complet-00.jpg'))
-```
-
-Research platform: **LF2L** - http://lf2l.fr
-]
-
----
-
-# Research domains at ERPI:
-
-.pull-left[
-.pull-left[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/01-Innovation-metrology.jpg'))
-```
-
-.orange[
-**Innovation capability**
-
-Product <br>
-Process  <br>
-Business Model <br>
-
-]
-]
-.pull-right[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/02-Prospective.jpg'))
-```
-.blue[
-**Technological  Emergence/maturity**
-
-Product-Process <br>
-Industrial supply chain <br>
-]]]
-
-.pull-right[
-.pull-left[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/03-Design.jpg'))
-```
-.green[
-**Materialized**
-
-Creative Exploration <br>
-Feasibility Product-Process <br>
-Physic & digital (virtual) Prototyping <br>
-]
-]
-.pull-right[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/04-Acceptability.jpg'))
-```
-.purple[
-**Front-end validation**
-Multi-actors Acceptability <br>
-User eXperience & test by use <br>
-Living Lab <br>
-]]]
-
-.center.Large[Creator of **methods & tools** supporting innovation process]
-
----
-
-## Scope: The Fuzzy Front End of innovation
-
-.pull-left[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Scope-00.jpg'))
-```
-]
-
-.pull-right[
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Purpose-00.jpg'))
-```
-.footnote[
-Martinez-Hernandez, E., 2017. Trends in sustainable process design—from molecular to global scales. Curr. Opin. Chem. Eng. 17, 35–41. <br/> https://doi.org/10.1016/j.coche.2017.05.005 
-]
-]
-
-Think earlier in the sustainable design and their impact
-
----
-
-## Innovation: a response to current social challenges
-
-```{r, out.width = '95%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'ERPI/Presentation/Fields-00.jpg'))
-```
-
-.tiny[Tran Thi Hoang, G., Dupont, L., & Camargo, M. (2019). Application of Decision-Making Methods in Smart City Projects: A Systematic Literature Review. Smart Cities, 2(3), 433-452.]
-
----
-
+exclude: true
 class: middle
@@
 
-class: top, left
+class: middle, left
 background-image: url(`r paste0(URL, 'Plastics/Plastic-problem-03.svg')`)
-background-position: right
+background-position: 100% 20%
 background-size: 70%
 
-## Plastics waste since  olden times
-
-.left-column[
-.tiny[
-- US recycled less than 9% of its plastic waste.
-- EU, recycled about 30%. However, this number is what is collected, not from what is in circulation*. 
-- China’s ban on plastic trash
-- Plastic trash could top 13 billion tons by 2050
-- Economics of plastic recycling historically have been challenging
-- Little financial incentive to encourage consumers to recycle their own plastic waste
-
-```{r, out.width = '60%', fig.align='center'}
-knitr::include_graphics('https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80')
-```
-
-]]
+.left[
+## Plastics waste
+]
 
 .footnote[
-Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782
+- Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782
 
-*Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018.
+<!-- - Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018.
 Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling.
@@
 Res.
-36, 445–453
+36, 445–453 -->
 
@@
 
-# Challengue
+class: bg-gf middle
 
-The development of sustainable industrial supply chains
-
-.left-column[
-.footnotesize[
-- Only technico-economic criteria alone do not (no longer) enables a informed decision making 
-- Need to assess value chains in a different way, including actual impacts on ecosystems
-- A more holistic vision is needed to assess the feasibility of these new sectors.
-]
- ]
-
-.right-column[ 
-.polaroid[ ![](figures/Recycling.png) ]
-]
+# Green Fablab: 
+## .bg-green[ a demostrotar of: <br>*'design global, manufacturing [recycling] local'*]
 
@@
 
-## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
+# Green Fablab:
 
@@
 ```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
+knitr::include_graphics(paste0(URL, 'Inedit/INEDIT-logo-00.jpg'))
+```
+
+http://lf2l.fr/projects/green-fablab
+]
+
+.pull-right[
+```{r}
+embed_youtube(
+  "sJfIU2uE7Zs",
+  width = 400,
+  height = 500,
+  ratio = "4by3",
+  frameborder = 0,
+  allowfullscreen = TRUE,
+)
+```
+]
+
+---
+
+# Green Fablab:
+
+.pull-left[
+
+```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
 knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-2.jpg'))
@@
 
-```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-1.jpg'))
-```
-
-http://lf2l.fr/projects/green-fablab
 ]
@@
 
-## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
+## Green Fablab
 
@@
 ---
+
+exclude: true
 
@@
 ---
+background-image: url(`r paste0(URL, 'Recycling/Polymer-recycling-02.png')`)
+background-position: 50% 100%
+background-size: 60%
 
-## People in Everest Bio
+# Challengue
 
-.pull-left[
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Mauricio.jpg'))
-```
+The development of sustainable industrial supply chains
 
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Hakim.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Pavlo.jpg'))
-```
-
-]
-
-.pull-right[
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Nadege.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Cristian.jpg'))
-```
-
-]
+- Only **.red[tech-economic criteria]** alone do not (no longer) enables a .orange[informed decision making]. 
+- Need to assess value chains in a different way, including **actual impacts on ecosystems**
+- A more holistic vision is needed to assess the feasibility of these new bottom-up sectors for **territorial and industrial agents**.
 
@@
 
-## Purpose of Everest Bio
+## Purpose of the project
 
@@
 
+exclude: true
+## People in Everest Bio
+
+.pull-left[
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Mauricio.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Hakim.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Pavlo.jpg'))
+```
+
+]
+
+.pull-right[
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Nadege.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
+```
+
+```{r, out.width = '500px', fig.align='center'}
+knitr::include_graphics(paste0(URL, 'Everest-bio/Cristian.jpg'))
+```
+
+]
+---
 # Delivrables & Valorisations

### 2022-02-14 data/Scopus/ES-Literature/ES-Literature.Rmd
presentation

--- 2021-09-03 00-ES/ES-Literature/ES-Literature.Rmd
@@
 
-Test <- CICES %>% select(Division, Group, Class, Code, `Class type`, `Simple descriptor`)
+#CICES <- CICES %>% select(Filter, Section, Division, Group, Class, Code, `Class type`, `Simple descriptor`)
+
+#Test <- tibble(CICES = Test %>% pull(Group) %>% unique())
 #write_yaml(V1, "GF/CICES-GF.yml")
@@
 # Ordering the Factors
-Test <- Test %>%
-  mutate(Division = factor(Division, Test %>% pull(Division) %>% unique())) %>% 
-  mutate(Group = factor(Group, Test %>% pull(Group) %>% unique()))
+CICES <- 
+  CICES %>%
+  mutate(Section = factor(Section, CICES %>% pull(Section) %>% unique())) %>% 
+  mutate(Division = factor(Division, CICES %>% pull(Division) %>% unique())) %>% 
+  mutate(Group = factor(Group, CICES %>% pull(Group) %>% unique())) %>% 
+  mutate(Section = 
+           factor(Section, 
+            c("Provisioning (Biotic)", "Provisioning (Abiotic)",
+            "Regulation & Maintenance (Biotic)", "Regulation & Maintenance (Abiotic)",
+            "Cultural (Biotic)", "Cultural (Abiotic)") ))
 
-Divisiones <- Test$Division %>% levels()
+Cuestionario <- list()
+
+Cuestionario$Industrial <- 
+  CICES %>% group_by(Section,Group) %>% 
+  tally()
+
+CICES %>%
+  filter(Code %in% c("1.1.1.1", "1.1.1.2", "1.1.1.3"))
+
+# Identifying the codes
+Test <- 
+CICES %>%
+  group_by(Group) %>%
+  #arrange(stopSequence) %>%
+  filter(row_number()==1 | row_number()==n())
+
+library(readxl)
+library(here)
+library(flextable)
+
+ft_1 <- flextable(data_ex)
+ft_1 <- theme_box(ft_1)
+ft_2 <- merge_v(ft_1, j = "srdr_id",
+  target = c("srdr_id", "substances"))
+  ft_2
+
+CICES %>% select(Group, Class, Code) %>% 
+  filter(Code %in% c("1.1.1.1", "1.1.1.2", "1.1.1.3")) %>% 
+  flextable() %>% 
+  merge_v( j = "Group")
+
+  kbl(caption = "ES for Food Nutrition") %>%
+  collapse_rows(columns = 1:1)
+
+library(dplyr)
+library(flextable)
+
+devtools::install_github("haozhu233/kableExtra")
+
+collapse_rows_dt <- data.frame(C1 = c(rep("a", 10), rep("b", 5)),
+                 C2 = c(rep("c", 7), rep("d", 3), rep("c", 2), rep("d", 3)),
+                 C3 = 1:15,
+                 C4 = sample(c(0,1), 15, replace = TRUE))
+kbl(collapse_rows_dt, align = "c") %>%
+  kable_paper(full_width = F) %>%
+  column_spec(1, bold = T) %>%
+  collapse_rows(columns = 1:2, valign = "top")
+
+Divisiones <- CICES$Division %>% levels()
 Grupos <- Test$Group %>% levels()
 
-Total_preguntas <- Test %>% group_by(Division,Group) %>% tally()
+Total_preguntas <- CICES %>% group_by(Section,Group) %>% tally()
 #Encuesta <- list(Test$Division %>% levels())

### 2022-02-14 docs/PubliER/PPQS/PPQS.Rmd
presentation

--- 2021-11-29 00-ES/PubliER/PPQS.Rmd
@@
 ---
-title: "Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing"
-bibliography: library.bib
+title: "Structuration of Everest Bio Project"
+bibliography: "`r here::here('library.bib')`"
+date: "`r paste('Last Version of the document: ', format(Sys.time(), '%b %d/%Y'))`"
+fontsize: 12pt
 link-citations: yes
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 ```
 
-## PPSQ
+## Version I: Towards a robust desicion tool for ecosystems services in the industrial systems:  A case study of Distributed recycling for additive manufacturing
 
@@
 
+\newpage
+
+# Version II  Fev 08/2022
+
+<!-- Problem -->
+The evaluation of the environmental externalities of (emergent) industrial systems in a territory is a central problem for decision-maker and industrial agents.
+From an industrial perspective, techno-economical remains as the major and only criteria used to evaluate the feasibility of emergent industrial systems [in short circuit].
+From a decision-maker perspective, a complete information about the relation on the impacts/dependencies of industrial systems on the natural capital and the ecosystems services of a particular territory is difficult to foreseen in the early/fuzzy-front design phases of development.
+<!-- Knowledge Gap: Academic rational -->
+In the scientific literature, life cycle thinking is a major body of knowledge to the quantification of the environmental impacts of industrial interventions, being Life cycle analysis a decision-aid tool for the comparison of different scenarios in each aspect stage of the product life [@Mahmud2021; @Pryshlakivsky2021].
+Likewise, Ecosystem services have been a major conceptual framework in the evaluation of the natural capital and the valuation of supply/demand ES in a territory.
+However, the research gap in the literature consist that few researches have been addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
+<!-- Purpose Statement: -->
+The purpose of this research is to propose a methodological steps to identify the hotspot of ES in terms that converge in the industrial value chain and the territorial perspective.  
+<!-- Research questions -->
+
+\newpage
+
 # References

### 2022-02-14 docs/PubliER/PubliER.Rmd
presentation

--- 2021-11-29 00-ES/PubliER/PubliER.Rmd
@@
 csl: journal-of-cleaner-production.csl
+
 output:
@@
   # bookdown::html_document2: default
-  # bookdown::word_document2: default
+  #bookdown::word_document2: default
 
@@
     Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
-    <!-- Problem -->
+    <!-- Problem 
     The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
+-->
     From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
@@
   \usepackage{tabu}
+  \makeatletter
+  \renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
+           {12\p@ \@plus 6\p@ \@minus 3\p@}%
+           {3\p@ \@plus 6\p@ \@minus 3\p@}%
+           {\normalfont\normalsize\itshape\bfseries}}
+   \makeatother        
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%', cache = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%', cache = FALSE, fig.align='center')
 options(knitr.kable.NA = '')
@@
 
-```{r, include=FALSE}
-
-```
-
 # Introduction
@@
 Even though engineering products and processes might meet the needs of the present society, many of the technological developments are compromising the ability of future generations to meet their own needs [@Bakshi2019a].
-For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
-This meta-principle is a imperative but not sufficient condition for sustainability.
+Claiming for sustainability in technological development and interventions, implies that the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
+This meta-principle is an imperative but not sufficient condition for sustainability.
 Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
+  <!-- MEA and Planeatry results -->
+According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
+Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
+  <!-- Causas of exceeding Planeatry boundaries -->
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
 Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@Diwekar2021].
+  <!-- Expand boundaries of Engineering -->
+It is urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].
 We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
@@
 <!-- They hightligthed that differens Systemic design approaches are   -->
-@SousaRocha2019 revealed ten different models at operational, tactical, and strategical levels
+@SousaRocha2019 revealed ten different models at operational, tactical, and strategical levels.
 <!-- Importance of ES in the Engineering -->
@@
 
-  <!-- MEA and Planeatry results -->
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner [@MEA2005]. 
-Likewise, using the  planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the "safe operating zone" in terms of carbon and nitrogen cycles, and biodiversity loss [@Rockstrom2009; @ONeill2018].
-  <!-- Causas of exceeding Planeatry boundaries -->
-Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions [@Liu2019g; @Rodrigues2021].
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not translate into keeping human activities within ecological constraints.
-<!-- Purpose of strong sustainability -->
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
-  <!-- Expand boundaries of Engineering -->
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet [@Martinez-Hernandez2017].
-
 The main purpose of this article is to propose a methodology in order to  prioritize the ecosystem services at early development stages of industrial systems in a territory.
@@
   <!-- Case study -->
-As a case application, the study of distributed recycling manufacturing will be describe.
+As a case application, the study of distributed recycling manufacturing will be described.
 Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
@@
 Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@TEEB2010]. 
-One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003].
+One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital.
+Humans are part of, and not apart from, nature [@Ekins2003].
 This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders [@Honeck2021].
@@
 <!--# Strong sustainability and ES -->
+Therefore, it is needed the correlation of ES with the global value chain and the natural capital.
 Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital [@Costanza1997] and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework [@Bruel2016].
@@
 
-<!-- Efforts have been made in the literature to classify the methods used to assess ecosystem services.
-Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.
--->
-
 <!--# Classification of ES -->
@@
 The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
-The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
-In the heart of the four main, they share four main categories of ES:
+The Intergovernmetal Plateform of Biodiversity and Ecosystem Services (IPBES) [@IPBS2019] and the Common International Classification of Ecosystem Services (CICES) [@RoyHaines-Young2018]. 
+   <!-- Explanation of structure -->
+Essentially, there are four main categories:
 **Provisioning** (e.g. food and medicines); 
@@
 **Supporting** (e.g soil formation and fixation of solar energy) and 
-**Cultural / Information** services (e.g.
-artistic inspiration and recreation) services are four broad categories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].
+**Cultural / Information** services (e.g. artistic inspiration and recreation) services.
+These four broad categories constitutes the core of most recent classifications and that are shared by the most frameworks [@Costanza2017].
 
-```{r Fig:ES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
+```{r Fig:ES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', }
 # img_url <- paste0(URL, 'Everest-bio/ES')
-#download.file(paste0(URL, 'Everest-bio/ES/', 'Comparison.png'), "Figures/Comparison.png")
+#download.file(paste0(URL, 'Ecoservices/CICES/', 'Potschin-Burkhard2017.png'), "Figures/Potschin-Burkhard2017.png")
 # rsvg_pdf(img_url, "Figures/Methodology.pdf")
 
-knitr::include_graphics('Figures/Comparison.png')
+knitr::include_graphics(here("PubliER", "Figures", "Potschin-Burkhard2017.png"))
 
@@
   <!-- CICES -->
-The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes [@ref].
-In CICES framework, @Potschin-Young2018 argued the conceptual framework of cascading aspect from ecosystesm service are  commonly divided Groups, division.
-<!-- @Mustajoki2019 -->
+In the context of this article, the CICES approach is chosen by the fact that it establish hierarchically consistent and science-based classification to be used for natural capital accounting purposes.
+@Potschin-Young2018 argued the conceptual framework of 'ecosystem service cascade' feature make it possible to re-frame the analysis of ES helping in the clarification of the complex relationships that can be placed.
+CICES scheme refers to ES specifically as the products from ecosystem, which can be directly used by human-beings. 
+This implies that *supporting services*, defined in MEA framework, are excluded from CICES scheme, by the fact that human beings do not 'receive'consumed' directly the benefits of these services.
+Additionally, it tries to avoid the double-counting problem.
+In that sense, CICES has *regulation and maintenance services* as one section only.
+The other two are *provisioning services* and *cultural services*.
+From there, there are *Divisions* describing the main types of output or process, and these are further split into *groups* according to biological, physical or cultural type or process. 
+The lowest level is the *class*, which specify the biological / material outputs and bio-physical and cultural processes.
+Finally, the *class type* measures the  *class level* which are the individual entities of the ESs. 
+   <!-- Critic of cascade -->
+Nevertheless, this cascade aspect is not far from critics. 
+@Constanza2017 raised the point that the complex connections among the different ES and the benefits might be poorly represented by a linear 'cascade' model, which assumes simple linkages and effects.
+But on the other hand, the hierarchical structure can add different levels of detail needed by decision makers.
+
+Figure \@ref(fig:ES-CICES) presents the whole structure of ES from the CICES V5.1 [@]
 
 <!-- \begin{landscape} -->
-```{r table-CICES, include=FALSE}
+```{r table-CICES, include=FALSE, eval=FALSE}
 # From the CICES intial
@@
 
-```{r Fig-ES-cices, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
+```{r ES-CICES, fig.cap='ES conceptual framework', out.width='100%', fig.pos='!ht', fig.align='center'}
 # img_url <- paste0(URL, 'Everest-bio/ES')
@@
 
-knitr::include_graphics('Figures/cices.png')
+knitr::include_graphics(here("PubliER", "Figures", "CICES-diagram.pdf"))
 
@@
 
-The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings [70]. 
-With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings. 
-The product-based CICES framework can enable clearer mapping between ecological and economic products. 
-The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
+## Ecosystems services and industrial systems: Towards a synergy between both
 
-The following levels organize ES according to their divisions, groups and classes. 
-At lower levels, more specific services can be defined and characterized.
+<!-- Intro LCA -->
+In environmental management, major efforts have been dedicated to the evaluation of the environmental impact of industrial systems using Life cycle assessment (LCA). 
+LCA aims to assess impacts on ecosystems, natural resources, and human health, as three primary areas of protection.
+LCA proffers an internationally standardized approach to modeling, assessing, and valuing the impacts of a product or process throughout its life cycle. 
+<!-- Critique LCA -->
+However, a design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing "less bad", which need not necessary translate into keeping human activities within ecological constraints.
+Moreover, LCA does not fully acknowledge impacts on the supply of ES.
+Assessing the impacts of production systems on ES supply is a new – and contested – paradigm of the latest years [@Vanderwilde2021]
+<!-- Purpose of strong sustainability -->
+Ideally, it is needed to (re)designed industrial activities to reduce the demand of ecosystems services creating for a local '*island of sustainability*' [@Wallner1996] which is that the demand should not exceed the supply at the local scale [@Gopalakrishnan2016].
 
-For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
-
-Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
-
-## Ecosystems services and industrial systems: Towards a synergy between
-
-One major point A holistic evaluation of the externalities that industrial system 
-Ecosystems services and industrial systems need to be confronten to holistic evaluation
-The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].
-
+<!-- Focus on integration of the ES and LCA -->
+Ecosystems services and industrial systems need to be confronted to holistic evaluation to determine the externalities positive and negative.
+In particular, full cost accounting in the business and governmental sectors, including new comprehensive accounts that include both the negative impacts on ES from business activities and the positive contributions of ES to businesses and households are key to develop [@Costanza2017]
+Decision makers  at the early stages should take into account the potential synergies and threats that the development of industrial systems could have to the local ecosystems.
   <!-- TES -->
-@Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+For instance, @Bakshi2015 reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
 The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
@@
 
+In that sense, @Vanderwilde2021 reported a systematic literature review revealing that a persistent division between the LCA and ES research communities. 
+They putted forward that there are LCA research has focus on one or a few ES, especially carbon balance, sequestration, and emissions. 
+Also, the work has prioritized regulation and maintenance and provisioning services, with work especially scarce on cultural services.
+Likewise, @Rugani2019 proposed an approach towards consensus building in the assessment of human activities' impacts on the provision of ES and their beneficial uses for human well-being.
+More specifically, to harmonize the cascade concept [@RoyHaines-Young2018] from the ES literature and the cause- effect chain modelling used in LCIA.
 <!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.
@@
 
+```{r, include=FALSE}
+Urban_ES <- read_csv(file= here('Scopus', '02-12-2021-Urban-ES-review.csv'))
+Urban_ES <- Urban_ES %>% select(Title, Year, DOI)
+#View(Urban_ES)
+```
+
 <!-- Urban Ecosystem Services -->
 More than two thirds of the world's population are expected to live in cities by 2050 [@ref]. 
-Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for prioritizing the quality of life in cities [@Gomez-Baggethun2013], helping to urban planners to guarantee that future city districts the local people have access to urban greenery and their services
+
   <!-- Importance of Urban ES -->
-Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
-cooling, and runoff mitigation [@Bolund1999]. 
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban cooling, and runoff mitigation [@Bolund1999].
+@Croci2021 presented a critical review
   <!-- Classification of Urban ES -->
@@
 They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
+
+Using this background on ES from the different perspectives, in the following section a methodology is proposed converge main ES that are relevant for the industrial, territorial and global value chain.
 
@@
 
-knitr::include_graphics('Figures/Methodology.pdf')
+knitr::include_graphics(here("PubliER", "Figures", "Methodology.pdf"))
 ```
@@
 
-knitr::include_graphics('Figures/Kumar2021.jpg')
+knitr::include_graphics(here("PubliER", "Figures","Kumar2021.jpg"))
 
@@
 
+For terrestrial ecosystems,
+
+For atmospheric ecosystem, the pollution
+
 The plastic value chain is one of the mo
 
-- Plastic materials have impats on the terrestrial, qauqtic, and atmospheric ecosystems.
+- Plastic materials have impats on the terrestrial, auquatic, and atmospheric ecosystems.
 
@@
 \renewcommand{\arraystretch}{1.5}
-```{r Value-chain-ES, include=TRUE}
-
+```{r Value-chain-ES-table, include=TRUE}
 Value_chain <- 
   tribble(
-  ~Description, ~ES, ~Ref,
-
+  ~Description, ~"ES impact", ~Reference,
 # Provisioning (Biotic)
   'Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops',
-  '1.1.1.1 ; 1.2.1.1', 
-   '[@Kumar2021]',
+  '1.1.1.1 ; 1.2.1.1 &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;', 
+   '[@Kumar2021; @Garcia-Vazquez2021] 
+&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;',
 
-'MPs and their suspended solids hasten eutrophication.
-Eutrophication worsens as a result of both resuspension and algae growth, adding more contaminants to the food chain supply and primarily creating organic contamination.',
+'MPs and their suspended solids hasten eutrophication adding more contaminants to the food chain supply and primarily creating organic contamination.', 
   '1.1.5.1 ; 1.1.6.1 ', 
@@
 )
+```
 
- Value_chain %>% 
-  kbl(caption = "Plastic pollution impact on ES",  booktabs = T) %>%
-    kable_styling(latex_options = c("striped", "hold_position") ) %>% 
-    column_spec(1, width = "30em")
+```{r Value-chain-ES, include=TRUE}
+# Value_chain %>%
+#    kbl(caption = "Plastic pollution impact on ES",  booktabs = T) %>%
+#    kable_styling(latex_options = c("striped", "hold_position") ) %>%
+#    column_spec(1, width = "30em")
+  # xtable::xtable(Value_chain, caption = "Hello xtable",
+  #                align = c("l", "p{1.5in}", "p{0.5in}", "p{1in}")) %>%
+  #  xtable2kable() #%>%
+  # column_spec(1, color = "red")
 
+knitr::kable(Value_chain, "pipe")
 ```
@@
 Major technological advances in the additive manufacturing (AM) field have enable the validation of distributed fabrication [@Woern2017; @Petersen2017a; @Matt2015].
-In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assetes as feedstock [@CruzSanchez2020; @Santander2020].
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assets as feedstock [@CruzSanchez2020; @Santander2020].
 The use of recycled material, either in the form of raw material or blended with virgin material, is a method of special interest to contribute to sustainable manufacturing [@Zhao2018].
@@
 
-However, While not all types of materials can be recycled given the technical difficulties, the integral evaluation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
+However, while not all types of materials can be recycled given the technical difficulties, the integral evaluation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches.
 Although research has been conducted regarding on the technical and logistical feasibility of distributed plastic recycling, little is known about its pertinence from the ecosystem services perspective in a territory.
@@
 ES_LCA <- 
-   tribble(~Description, ~ES, ~Ref,
+   tribble(~Description, ~"ES impact", ~Reference,
            'Climate change', '2.2.4.1; 2.1.1.2; 2.2.4.1; 2.2.4.2', ' ',
@@
 Nancy_ES <- 
-   tribble(~Description, ~ES, ~Ref,
+   tribble(~Description, ~"ES impact", ~Reference,
 
@@
 Value_chain <- Value_chain %>% mutate(Perspective = "Value chain of plastic")
-ES_LCA <- ES_LCA %>% mutate(Ref = ' ', Perspective = "LCA of DRAM") %>% filter(Description != 'Ressources Depletion' )
+ES_LCA <- ES_LCA %>% mutate(Reference = ' ', Perspective = "LCA of DRAM") %>% filter(Description != 'Ressources Depletion' )
 Nancy_ES <- Nancy_ES %>% mutate(Perspective = "Territorial at Nancy")
@@
 
-Sankey <- Total_ES %>% select(Perspective, ES)
+Sankey <- Total_ES %>% select(Perspective, `ES impact`)
 
-Sankey <- Sankey %>% separate(ES, into=LETTERS[1:27], sep = ";")
+Sankey <- Sankey %>% separate(`ES impact`, into=LETTERS[1:27], sep = ";")
 
@@
                  Source = "IDsource", Target = "IDtarget",
-                     Value = "value", NodeID = "name", fontSize=13 )
+                 Value = "value", NodeID = "name", fontSize=13 ,
+                 LinkGroup = "source")
 
@@
 #download.file(paste0(URL,'Plastics/ES/Kumar2021.jpg'), "Figures/Kumar2021.jpg")
-
-knitr::include_graphics('Figures/Sankey.png')
+knitr::include_graphics(here("PubliER", "Figures", "Sankey.png"))
 ```
@@
 
+\bibliography{library.bib}
+
 \newpage

### 2022-02-14 docs/PubliER/PubliER.tex
presentation

--- 2021-11-29 00-ES/PubliER/PubliER.tex
@@
 \usepackage{tabu}
+\makeatletter
+\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
+         {12\p@ \@plus 6\p@ \@minus 3\p@}%
+         {3\p@ \@plus 6\p@ \@minus 3\p@}%
+         {\normalfont\normalsize\itshape\bfseries}}
+ \makeatother        
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-\usepackage{multicol}
-\usepackage{hhline}
-\usepackage{hyperref}
 
@@
   Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
-  The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
   From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
@@
 Even though engineering products and processes might meet the needs of the present society, many of the technological developments are compromising the ability of future generations to meet their own needs (\protect\hyperlink{ref-Bakshi2019a}{Bakshi, 2019}).
-For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi et al., 2018}).
-This meta-principle is a imperative but not sufficient condition for sustainability.
+Claiming for sustainability in technological development and interventions, implies that the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi et al., 2018}).
+This meta-principle is an imperative but not sufficient condition for sustainability.
 Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al., 2018}).
+According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA, 2005}).
+Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-ONeill2018}{O'Neill et al., 2018}; \protect\hyperlink{ref-Rockstrom2009}{Rockström et al., 2009}).
+Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi, 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al., 2021}).
 Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al., 2021}).
+It is urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez, 2017}).
 We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems.
@@
 They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
-\protect\hyperlink{ref-SousaRocha2019}{Rocha et al.} (\protect\hyperlink{ref-SousaRocha2019}{2019}) revealed ten different models at operational, tactical, and strategical levels
+\protect\hyperlink{ref-SousaRocha2019}{Rocha et al.} (\protect\hyperlink{ref-SousaRocha2019}{2019}) revealed ten different models at operational, tactical, and strategical levels.
 One strategical point in sustainability relies on the economic valuation of ecosystem goods and services framework.
@@
 
-According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA, 2005}).
-Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-ONeill2018}{O'Neill et al., 2018}; \protect\hyperlink{ref-Rockstrom2009}{Rockström et al., 2009}).
-Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi, 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al., 2021}).
-Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
-Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner et al., 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan et al., 2016}).
-Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez, 2017}).
-
 The main purpose of this article is to propose a methodology in order to prioritize the ecosystem services at early development stages of industrial systems in a territory.
 This methodology is based in the use of the ecosystem services as boundary object (\protect\hyperlink{ref-Abson2014}{Abson et al., 2014}) with the purpose to identify ES according to the perspective of global value chain, industrial chain and territorial perspective.
-As a case application, the study of distributed recycling manufacturing will be describe.
+As a case application, the study of distributed recycling manufacturing will be described.
 Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}).
@@
   What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling?
-- How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
+\item
+  How does the implementation of a distributed plastic recycling chain impact on ecosystem services?
 \item
@@
 Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in `negative' way, making damage and costs (\protect\hyperlink{ref-TEEB2010}{TEEB, 2010}).
-One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al., 2003}).
+One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the `functions of' natural capital.
+Humans are part of, and not apart from, nature (\protect\hyperlink{ref-Ekins2003}{Ekins et al., 2003}).
 This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders (\protect\hyperlink{ref-Honeck2021}{Honeck et al., 2021}).
@@
 
+Therefore, it is needed the correlation of ES with the global value chain and the natural capital.
 Efforts on biodiversity conservation relies on the highlight of the economic aspects of biodiversity and the natural capital (\protect\hyperlink{ref-Costanza1997}{Costanza et al., 1997}) and the environmental inaction related to the cost of policy damage occurring in the absence of an effective regulatory framework (\protect\hyperlink{ref-Bruel2016}{Bruel et al., 2016}).
@@
 The Economics of Ecosystems and Biodiversity TEEB (\protect\hyperlink{ref-TEEB2010}{TEEB, 2010}),
-The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) (\protect\hyperlink{ref-ref}{\textbf{ref?}}) and the Common International Classification of Ecosystem Services (CICES).
-In the heart of the four main, they share four main categories of ES:
+The Intergovernmetal Plateform of Biodiversity and Ecosystem Services (IPBES) (\protect\hyperlink{ref-IPBS2019}{IPBS, 2019}) and the Common International Classification of Ecosystem Services (CICES) (\protect\hyperlink{ref-RoyHaines-Young2018}{Roy Haines-Young and Potschin, 2018}).
+Essentially, there are four main categories:
 \textbf{Provisioning} (e.g.~food and medicines);
@@
 \textbf{Supporting} (e.g soil formation and fixation of solar energy) and
-\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services are four broad categories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-PedersenZari2019}{Pedersen Zari, 2019}).
+\textbf{Cultural / Information} services (e.g.~artistic inspiration and recreation) services.
+These four broad categories constitutes the core of most recent classifications and that are shared by the most frameworks (\protect\hyperlink{ref-Costanza2017}{Costanza et al., 2017}).
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figures/Comparison}
+{\centering \includegraphics[width=1\linewidth]{/Users/fabio/Documents/4-Projects/everest-bio/PubliER/Figures/Potschin-Burkhard2017}
 
@@
 
-The Common International Classification of Ecosystem Services (CICES) was developed to provide hiecharchally consistent and science-based classification to be used for natural capital accounting purposes (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-In CICES framework, \protect\hyperlink{ref-Potschin-Young2018}{Potschin-Young et al.} (\protect\hyperlink{ref-Potschin-Young2018}{2018}) argued the conceptual framework of cascading aspect from ecosystesm service are commonly divided Groups, division.
+In the context of this article, the CICES approach is chosen by the fact that it establish hierarchically consistent and science-based classification to be used for natural capital accounting purposes.
+\protect\hyperlink{ref-Potschin-Young2018}{Potschin-Young et al.} (\protect\hyperlink{ref-Potschin-Young2018}{2018}) argued the conceptual framework of `ecosystem service cascade' feature make it possible to re-frame the analysis of ES helping in the clarification of the complex relationships that can be placed.
+CICES scheme refers to ES specifically as the products from ecosystem, which can be directly used by human-beings.
+This implies that \emph{supporting services}, defined in MEA framework, are excluded from CICES scheme, by the fact that human beings do not `receive'consumed' directly the benefits of these services.
+Additionally, it tries to avoid the double-counting problem.
+In that sense, CICES has \emph{regulation and maintenance services} as one section only.
+The other two are \emph{provisioning services} and \emph{cultural services}.
+From there, there are \emph{Divisions} describing the main types of output or process, and these are further split into \emph{groups} according to biological, physical or cultural type or process.
+The lowest level is the \emph{class}, which specify the biological / material outputs and bio-physical and cultural processes.
+Finally, the \emph{class type} measures the \emph{class level} which are the individual entities of the ESs.
+Nevertheless, this cascade aspect is not far from critics.
+(\protect\hyperlink{ref-Constanza2017}{\textbf{Constanza2017?}}) raised the point that the complex connections among the different ES and the benefits might be poorly represented by a linear `cascade' model, which assumes simple linkages and effects.
+But on the other hand, the hierarchical structure can add different levels of detail needed by decision makers.
+
+Figure \ref{fig:ES-CICES} presents the whole structure of ES from the CICES V5.1 {[}@{]}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figures/cices}
+{\centering \includegraphics[width=1\linewidth]{/Users/fabio/Documents/4-Projects/everest-bio/PubliER/Figures/CICES-diagram}
 
@@
 
-\caption{ES conceptual framework}\label{fig:Fig-ES-cices}
+\caption{ES conceptual framework}\label{fig:ES-CICES}
 \end{figure}
 
-The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings {[}70{]}.
-With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings.
-The product-based CICES framework can enable clearer mapping between ecological and economic products.
-The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
+\hypertarget{ecosystems-services-and-industrial-systems-towards-a-synergy-between-both}{%
+\subsection{Ecosystems services and industrial systems: Towards a synergy between both}\label{ecosystems-services-and-industrial-systems-towards-a-synergy-between-both}}
 
-The following levels organize ES according to their divisions, groups and classes.
-At lower levels, more specific services can be defined and characterized.
+In environmental management, major efforts have been dedicated to the evaluation of the environmental impact of industrial systems using Life cycle assessment (LCA).
+LCA aims to assess impacts on ecosystems, natural resources, and human health, as three primary areas of protection.
+LCA proffers an internationally standardized approach to modeling, assessing, and valuing the impacts of a product or process throughout its life cycle.
+However, a design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not necessary translate into keeping human activities within ecological constraints.
+Moreover, LCA does not fully acknowledge impacts on the supply of ES.
+Assessing the impacts of production systems on ES supply is a new -- and contested -- paradigm of the latest years (\protect\hyperlink{ref-Vanderwilde2021}{Vanderwilde and Newell, 2021})
+Ideally, it is needed to (re)designed industrial activities to reduce the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner et al., 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan et al., 2016}).
 
-For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
-
-Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.
-
-\hypertarget{ecosystems-services-and-industrial-systems-towards-a-synergy-between}{%
-\subsection{Ecosystems services and industrial systems: Towards a synergy between}\label{ecosystems-services-and-industrial-systems-towards-a-synergy-between}}
-
-One major point A holistic evaluation of the externalities that industrial system
-Ecosystems services and industrial systems need to be confronten to holistic evaluation
-The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households (\protect\hyperlink{ref-Costanza2017}{Costanza et al., 2017}).
-
-\protect\hyperlink{ref-Bakshi2015}{Bakshi et al.} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
+Ecosystems services and industrial systems need to be confronted to holistic evaluation to determine the externalities positive and negative.
+In particular, full cost accounting in the business and governmental sectors, including new comprehensive accounts that include both the negative impacts on ES from business activities and the positive contributions of ES to businesses and households are key to develop (\protect\hyperlink{ref-Costanza2017}{Costanza et al., 2017})
+Decision makers at the early stages should take into account the potential synergies and threats that the development of industrial systems could have to the local ecosystems.
+For instance, \protect\hyperlink{ref-Bakshi2015}{Bakshi et al.} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
 The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
 The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.
+
+In that sense, \protect\hyperlink{ref-Vanderwilde2021}{Vanderwilde and Newell} (\protect\hyperlink{ref-Vanderwilde2021}{2021}) reported a systematic literature review revealing that a persistent division between the LCA and ES research communities.
+They putted forward that there are LCA research has focus on one or a few ES, especially carbon balance, sequestration, and emissions.
+Also, the work has prioritized regulation and maintenance and provisioning services, with work especially scarce on cultural services.
+Likewise, \protect\hyperlink{ref-Rugani2019}{Rugani et al.} (\protect\hyperlink{ref-Rugani2019}{2019}) proposed an approach towards consensus building in the assessment of human activities' impacts on the provision of ES and their beneficial uses for human well-being.
+More specifically, to harmonize the cascade concept (\protect\hyperlink{ref-RoyHaines-Young2018}{Roy Haines-Young and Potschin, 2018}) from the ES literature and the cause- effect chain modelling used in LCIA.
 
@@
 More than two thirds of the world's population are expected to live in cities by 2050 (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
-Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities (\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton, 2013}).
-Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
-cooling, and runoff mitigation (\protect\hyperlink{ref-Bolund1999}{Bolund and Hunhammar, 1999}).
+Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for prioritizing the quality of life in cities (\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton, 2013}), helping to urban planners to guarantee that future city districts the local people have access to urban greenery and their services
+
+Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban cooling, and runoff mitigation (\protect\hyperlink{ref-Bolund1999}{Bolund and Hunhammar, 1999}).
+\protect\hyperlink{ref-Croci2021}{Croci et al.} (\protect\hyperlink{ref-Croci2021}{2021}) presented a critical review
 \protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton} (\protect\hyperlink{ref-Gomez-Baggethun2013}{2013}) draws on the developments of the ecosystem services for urban planning.
 They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.
+
+Using this background on ES from the different perspectives, in the following section a methodology is proposed converge main ES that are relevant for the industrial, territorial and global value chain.
 
@@
 This identification is a first step with the purpose to evaluate the supply and demand of ecosystem services for these industrial systems.
-A prospective distributed recycling chain for additive manufacturing.
-A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figures/Methodology}
+{\centering \includegraphics[width=1\linewidth]{/Users/fabio/Documents/4-Projects/everest-bio/PubliER/Figures/Methodology}
 
@@
 
+A prospective distributed recycling chain for additive manufacturing .
+
 \hypertarget{step-i---ecosystem-services-issues-at-the-value-chain-plastic-issues-at-the-ecosystems}{%
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{Figures/Kumar2021} \caption{Illustration of MPs and NPs affecting various ecosystem services and climate change on terrestrial, aquatic, and atmospheric ecosystems.
-Source.
-Kumar2021.jpg}\label{fig:fig-Kumar2021}
+
+{\centering \includegraphics[width=1\linewidth]{/Users/fabio/Documents/4-Projects/everest-bio/PubliER/Figures/Kumar2021}
+
+}
+
+\caption{Illustration of MPs and NPs affecting various ecosystem services and climate change on terrestrial, aquatic, and atmospheric ecosystems. Source. Kumar2021.jpg}\label{fig:fig-Kumar2021}
 \end{figure}
@@
 \renewcommand{\arraystretch}{1.5}
-\begin{table}[!h]
 
-\caption{\label{tab:Value-chain-ES}Plastic pollution impact on ES}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{30em}ll}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.68}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.10}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.22}}@{}}
 \toprule
-Description & ES & Ref\\
+\begin{minipage}[b]{\linewidth}\raggedright
+Description
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+ES impact
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Ref
+\end{minipage} \\
 \midrule
-\cellcolor{gray!6}{Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops} & \cellcolor{gray!6}{1.1.1.1 ; 1.2.1.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
-MPs and their suspended solids hasten eutrophication.
-Eutrophication worsens as a result of both resuspension and algae growth, adding more contaminants to the food chain supply and primarily creating organic contamination.
-& 1.1.5.1 ; 1.1.6.1 & {}[136]\\
-\cellcolor{gray!6}{MPs and NPs in the atmosphere also lead to the obstruction and lowering of pollination.} & \cellcolor{gray!6}{2.2.2.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
-MPs and NPs are established to act as a vector and breach through any system (organisms) and even via trophic transfer (one trophic level to another via food chain), therefore, it can be hypothesized that MPs in the future can play a pivotal role in the spill over of infectious diseases, leading to an epidemic or pandemic of unknown scale & 2.2.3.1; 2.2.3.1 & Ref\\
-\cellcolor{gray!6}{MP and NP in terrestrial ecosystems reduce tha ability to sequester carbon.} & \cellcolor{gray!6}{2.1.1.2 ; 2.2.4.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
-\addlinespace
-Elements as nitrogen and phosphorous, are also vividly influenced due to MPs and NPs in the soil ecosystem & 2.2.4.1 ; 2.2.4.2 & {}[@Kumar2021]\\
-\cellcolor{gray!6}{MPs accumulation can promote mineralization, nitrification, and denitrification in aquatic ecosystems, therefore releasing CO2, CH4, and N2O.} & \cellcolor{gray!6}{2.2.6.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
-marine carbon sinks are critical in analyzing the global climate change and are potentially affected by MPs and NPs pollution on phytoplankton-sequestered CO2 and their transmission to the deep ocean via zooplankton [77].
-& 2.2.5.2 & {}[@Kumar2021]\\
-\cellcolor{gray!6}{Plastics-induced variations in solar radiation in the water column can alter physical processes at the ocean’s surface and near-surface layers as well as trigger climate feedback mechanisms} & \cellcolor{gray!6}{2.2.6.1} & \cellcolor{gray!6}{{}[@Kumar2021]}\\
+\endhead
+Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops & 1.1.1.1 ; 1.2.1.1 ~~~~~ & (\protect\hyperlink{ref-Garcia-Vazquez2021}{Garcia-Vazquez and Garcia-Ael, 2021}; \protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+~~~~~~ ~~~~~~ & & \\
+MPs and their suspended solids hasten eutrophication adding more contaminants to the food chain supply and primarily creating organic contamination. & 1.1.5.1 ; 1.1.6.1 & {[}136{]} \\
+MPs and NPs in the atmosphere also lead to the obstruction and lowering of pollination. & 2.2.2.1 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+MPs and NPs are established to act as a vector and breach through any system (organisms) and even via trophic transfer (one trophic level to another via food chain), therefore, it can be hypothesized that MPs in the future can play a pivotal role in the spill over of infectious diseases, leading to an epidemic or pandemic of unknown scale & 2.2.3.1; 2.2.3.1 & Ref \\
+MP and NP in terrestrial ecosystems reduce tha ability to sequester carbon. & 2.1.1.2 ; 2.2.4.1 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+Elements as nitrogen and phosphorous, are also vividly influenced due to MPs and NPs in the soil ecosystem & 2.2.4.1 ; 2.2.4.2 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+MPs accumulation can promote mineralization, nitrification, and denitrification in aquatic ecosystems, therefore releasing CO2, CH4, and N2O.
+& 2.2.6.1 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+marine carbon sinks are critical in analyzing the global climate change and are potentially affected by MPs and NPs pollution on phytoplankton-sequestered CO2 and their transmission to the deep ocean via zooplankton {[}77{]}.
+& 2.2.5.2 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
+Plastics-induced variations in solar radiation in the water column can alter physical processes at the ocean's surface and near-surface layers as well as trigger climate feedback mechanisms & 2.2.6.1 & (\protect\hyperlink{ref-Kumar2021}{Kumar et al., 2021}) \\
 MPs and NPs are known to cause a dynamic shift in the soil temperature as is commonly practiced in agriculture sectors with extreme climatic conditions. & 2.2.4.1 & \\
-\addlinespace
-\cellcolor{gray!6}{MPs and NPs in the soil ecosystem are known to have a strong impact on the population structure and survival of these faunas [135,137,154,158].} & \cellcolor{gray!6}{2.2.4.1} & \cellcolor{gray!6}{}\\
+MPs and NPs in the soil ecosystem are known to have a strong impact on the population structure and survival of these faunas {[}135,137,154,158{]}. & 2.2.4.1 & \\
 Small-sized plastics act as stressors, altering the ocean level and temperature and influencing the acidification. & 2.2.6.1 & \\
-\cellcolor{gray!6}{High amounts of MPs and NPs are more substantially found in pelagic species than in deep-water species.} & \cellcolor{gray!6}{1.1.5.1} & \cellcolor{gray!6}{}\\
-MPs and NPs act as vectors for toxic chemicals and microbes and can breach any ecosystem. & 2.1.1.1 & REf\\
+High amounts of MPs and NPs are more substantially found in pelagic species than in deep-water species. & 1.1.5.1 & \\
+MPs and NPs act as vectors for toxic chemicals and microbes and can breach any ecosystem. & 2.1.1.1 & REf \\
 \bottomrule
-\end{tabular}
-\end{table}
+\end{longtable}
 
@@
 Major technological advances in the additive manufacturing (AM) field have enable the validation of distributed fabrication (\protect\hyperlink{ref-Matt2015}{Matt et al., 2015}; \protect\hyperlink{ref-Petersen2017a}{Petersen and Pearce, 2017}; \protect\hyperlink{ref-Woern2017}{Woern and Pearce, 2017}).
-In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assetes as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al., 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al., 2020}).
+In the same logic, recently, the concept of distributed recycling via additive manufacturing (DRAM) emerged in the literature to face the technico-environmental challenges related to recycling option, mostly for material-extrusion based technologies using thermoplastic assets as feedstock (\protect\hyperlink{ref-CruzSanchez2020}{Cruz Sanchez et al., 2020}; \protect\hyperlink{ref-Santander2020}{Santander et al., 2020}).
 The use of recycled material, either in the form of raw material or blended with virgin material, is a method of special interest to contribute to sustainable manufacturing (\protect\hyperlink{ref-Zhao2018}{Zhao et al., 2018}).
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{Figures/Sankey} \caption{Priorization of ES for the distributed recycling indsutrail system.}\label{fig:fig-sankey}
+
+{\centering \includegraphics[width=1\linewidth]{/Users/fabio/Documents/4-Projects/everest-bio/PubliER/Figures/Sankey}
+
+}
+
+\caption{Priorization of ES for the distributed recycling indsutrail system.}\label{fig:fig-sankey}
 \end{figure}
@@
 \section{Conclusions}\label{conclusions}}
+
+\bibliography{library.bib}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Croci2021}{}}%
+Croci, E., Lucchitta, B., Penati, T., 2021. {Valuing ecosystem services at the urban level: A critical review}. \url{https://doi.org/10.3390/su13031129}
+
 \leavevmode\vadjust pre{\hypertarget{ref-CruzSanchez2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Garcia-Vazquez2021}{}}%
+Garcia-Vazquez, E., Garcia-Ael, C., 2021.
+{The invisible enemy.
+Public knowledge of microplastics is needed to face the current microplastics crisis}.
+Sustain.
+Prod.
+Consum.
+28, 1076--1089.
+\url{https://doi.org/10.1016/j.spc.2021.07.032}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Gomez-Baggethun2013}{}}%
@@
 \url{https://doi.org/10.1016/j.ecoser.2021.101286}
+
+\leavevmode\vadjust pre{\hypertarget{ref-IPBS2019}{}}%
+IPBS, 2019. {Global assessment report on biodiversity and ecosystem services of the Intergovernmental Science-Policy Platform on Biodiversity and Ecosystem Services}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-PedersenZari2019}{}}%
-Pedersen Zari, M., 2019. {Ecosystem services impacts as part of building materials selection criteria}. Mater. Today Sustain. 3-4. \url{https://doi.org/10.1016/j.mtsust.2019.100010}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Petersen2017a}{}}%
@@
 \url{https://doi.org/10.1016/j.jclepro.2021.129034}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RoyHaines-Young2018}{}}%
+Roy Haines-Young, by, Potschin, M., 2018. {Common International Classification of Ecosystem Services (CICES) V5.1 Guidance on the Application of the Revised Structure}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rugani2019}{}}%
+Rugani, B., Maia de Souza, D., Weidema, B.P., Bare, J., Bakshi, B., Grann, B., Johnston, J.M., Pavan, A.L.R., Liu, X., Laurent, A., Verones, F., 2019.
+{Towards integrating the ecosystem services cascade framework within the Life Cycle Assessment (LCA) cause-effect methodology}.
+Sci.
+Total Environ.
+690, 1284--1298.
+\url{https://doi.org/10.1016/j.scitotenv.2019.07.023}
 

### 2022-02-14 docs/varios/02-supply-chain.Rmd
presentation

--- 2021-01-19 02-supply-chain.Rmd
@@
 
+```{r, include=FALSE}
+
+#library(rticles)
+#library(rmarkdown)
+#render("02-supply-chain.Rmd", output_format = "word_document", output_dir = "02-supply-chain")
+
+#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document", output_dir = "01-Sustainable-Indicators")
+#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article", output_dir = "01-Sustainable-Indicators")
+
+```
+
 # Abstract

### 2022-02-14 docs/varios/Ideas.Rmd
presentation

--- 2021-01-19 02-supply-chain.Rmd
@@
 ---
-title: "DRAM and ES"
-description: |
-  Some additional details about the website
-output:
-  distill::distill_article:
-    toc: true
-    toc_depth: 2
-repository_url: https://github.com/LF2L/everest-bio
-#bibliography: 02-supply-chain.bib
-bibliography: library.bib
-#nocite: '@*'
-
-author:
-  - first_name: "Sabrina?"
-    last_name: "Master 2"
-    url: 
-    affiliation: CREIDD?, ERPI?
-    affiliation_url:
-
-  - first_name: "Fedoua"
-    last_name: "Kasmi"
-    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    orcid_id: 0000-0001-5159-0264
-
-  - first_name: "Pavlo"
-    last_name: "Santander"
-    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    #orcid_id: 0000-0001-6328-1338
-
-  - first_name: "Fabio"
-    last_name: "Cruz"
-    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    orcid_id: 0000-0001-8529-5327
-
-  - first_name: "Nadège"
-    last_name: "Troussier"
-    url: https://recherche.utt.fr/icd-directory/nadege-troussier
-    affiliation: CREIDD
-    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
-    orcid_id: 0000-0001-6707-0300
-
-  - first_name: "Hakim"
-    last_name: "Boudaoud"
-    url: https://erpi.univ-lorraine.fr/people/Hakim-Boudaoud/
-    affiliation: ERPI
-    affiliation_url: https://erpi.univ-lorraine.fr/
-    orcid_id: 0000-0003-4452-5952
-
+title: "Ramdom ideas"
+output: html_document
 ---
 
-# Abstract
-
-Master 2: sur la chaine de valeur localisée sur le cas d’étude (périmètre de pavlo) sur la base d’une analyse par les acteurs effectifs et potentiels; quels ont les freins et leviers au développement du plastique recyclé dans le territoire envisagé; analyse des services écosystémiques actuels et impactés.
-Pas que PLA mais aussi polypro en particulier… (Sabrina, avec Fedoua Kasmi et Hakim)
-
-[**Link to modify the Graph**](https://lucid.app/lucidchart/invitations/accept/f6847ab0-3fd4-4749-a581-669058760d2d)
-
-:::l-page
-<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
-:::
-
-# Rationale
-
-A new paradigm of plastic recycling, called distributed plastic recycling, has emerged in the literature in order to face the socio-environmental challenges related to plastic waste management.
-Under this new model of small recycling centers, the main hypothesis relies on the fact that a distributed and local spaces can provide recycled feedstock to transform it into finish (or prototypes) for a local community.
-To do so, the use of additive manufacturing enables the technical paths.
-
-  However, as with any recycling system, its feasibility must be evaluated before its implementation.
-Although research has been conducted regarding the technical feasibility of distributed plastic recycling, little is known about its feasibility from the supply chain perspective [@CruzSanchez2020] and its impact in ecosystem services.
 From a supply chain perspective, the feasibility evaluation for the establishment of recycling networks should be oriented towards sustainable development. 
@@
 [@EspinozaPerez2017c, @Fonseca2018, @Moreno-Camacho2019].
-
-This study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.
-
-The purpose of this research is to explore and assess the local impact, considering sustainability dimensions and ecosystem services, derived from the implementation of a distributed plastic recycling chain.
-The study intends to research, based on the notion of sustainability, which and how the ecosystem services are impacted due to the implementation of the plastic recycling chain proposed. 
-While not all types of materials can be recycled given the technical difficulties, the estimation of the environmental advantage is needed to assess at early stages the pertinence of this distributed approaches
-
-This study seeks to address the following questions:
-
-- What are the appropriate ecosystem service indicators for assessing distributed plastic recycling? 
-- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
-- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?
-
-## Ideas
-
-- @Alkhuzaim2020 provide insights into more effective environmentally sustainable supply chain and circularity performance evaluation, accounting, and appraisal using emergy based performance measurements.

### 2022-02-14 docs/xar-EB-ES/Questionnaire.Rmd
presentation

---
title: "Questionnaire for Everest Bio Tool"
output: pdf_document
header-includes:
   - \usepackage{tabu}
   - \usepackage{booktabs}
   - \usepackage{xcolor}
   - \def\DefaultOptionsofCheckBox{print,bordercolor=blue}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Main Structure of the questionnaire

1. Characterization of the respondent 
   1. Identification of the Geographical area.
   2.
2. Selection of the

## Questionnaire for the Territorial side

\begin{Form}

\begin{tabu} to \linewidth {X[2,l] | X[1,c] | X[1p, c]}

\midrule
\textbf{Characterizing the respondant} & & \\
\midrule

\TextField[width=15em, bordercolor={0 0 0}]{Enter your name:} & & \\

\midrule
\textbf{Provisioning Services (biotic \& Abiotic)} & & \\
\midrule

\textit{Are cultivated plants (Terrestrial or Aquatic) strategic for the territory for nutrition, materials or energy ?} & 
         \CheckBox[name=optionA, width=10pt]{Yes  Not} & \\

 & & \\
 & & \\
 & & \\

\end{tabu}

\end{Form}

### 2022-02-14 docs/xar-EB-general/index.Rmd
presentation

--- 2022-02-13 xar-EB-general/index.Rmd
@@
 
-# Green Fablab:
-
-.pull-left[
-
-```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
-knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-2.jpg'))
-```
-
-]
-.pull-right[
-
-]
-
-.footnote[
-Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
-Towards a standard experimental protocol for open source additive manufacturing.
-Virtual Phys.
-Prototyp.
-9, 151–167.
-https://doi.org/10.1080/17452759.2014.919553
-]
-
----
-
 ## Green Fablab
@@
 ---
+background-image: url(`r paste0(URL, 'Everest-bio/ipad/Articulo-6.jpg')`)
+background-position: 50% 100%
+background-size: 55%
 
@@
 ---
+background-image: url(`r paste0(URL, 'Ecoservices/CICES/Potschin-Burkhard2017.png')`)
+background-position: 1-90%% 80%
+background-size: 60%
 
+### Ecosystem Services as a **boundary object** for sustainability
+
+.footnote[
+La Notte, A., D’Amato, D., Mäkinen, H., Paracchini, M.L., Liquete, C., Egoh, B., Geneletti, D., Crossman, N.D., 2017.
+Ecosystem services classification: A systems ecology perspective of the cascade framework.
+Ecol.
+Indic.
+74, 392–402.
+https://doi.org/10.1016/j.ecolind.2016.11.030
+]
+
+---
+background-image: url(`r paste0(URL, 'Ecoservices/Vanderwilde2021-00.jpg')`)
+background-position: 50% 80%
+background-size: 70%
+
+### Ecosystem Services as a **boundary object** for sustainability
+
+---
+exclude: true
 class: middle
@@
 class: top, left
+background-image: url(`r paste0(URL, 'Ecoservices/Kumar2021.jpg')`)
+background-position: 50% 50%
+background-size: 80%
+
+### Ecosystem services and the global value chain of plastic
+
+.footnote[
+Kumar, Rakesh, Verma, A., Shome, A., Sinha, R., Sinha, S., Jha, P.K., Kumar, Ritesh, Kumar, P., Shubham, Das, S., Sharma, P., Vara Prasad, P.
+V., 2021.
+Impacts of Plastic Pollution on Ecosystem Services, Sustainable Development Goals, and Need to Focus on Circular Economy and Policy Interventions.
+Sustainability 13, 9963.
+https://doi.org/10.3390/su13179963
+]
+
+---
+class: top, left
 background-image: url(`r paste0(URL, 'Ecoservices/Vanderwilde2021-01.jpg')`)
-background-position: 290px 0px
-background-size: 75%
+background-position: 100% 50%
+background-size: 60%
 
-### We look to connect <br> Ecosystem services and LCA
+### Ecosystem services and LCA
 
@@
 Vanderwilde, C.P., Newell, J.P., 2021. Ecosystem services and life cycle assessment: A bibliometric review. https://doi.org/10.1016/j.resconrec.2021.105461 <br>
-Diwekar, U., Amekudzi-Kennedy, A., Bakshi, B., Baumgartner,et al, 2021.
-A perspective on the role of uncertainty in sustainability science and engineering.
-Resour.
-Conserv.
-Recycl.
-164, 105140.
-https://doi.org/10.1016/j.resconrec.2020.105140
 ]
+
+---
+
+class: top, left
+background-image: url(`r paste0(URL, 'Ecoservices/FR/efese.png')`)
+background-position: 50% 50%
+background-size: 80%
+
+### Ecosystem services and Territorial issues
+
+---
+### Ecosystem services and Territorial issues
+
+```{r, out.width = '60%', fig.align='center', echo=FALSE}
+knitr::include_graphics("figures/Sankey.png")
+```
 
@@
 ---
+exclude: true
+
 # Delivrables & Valorisations
@@
 # Thanks !
-
-![:scale 70%](figures/DRAM-bd.png)

### 2022-02-14 docs/xar-EB-general/partials/ERPI.Rmd
presentation

--- 2021-04-12 slides/index.Rmd
@@
 ---
-title: "Everest Bio"
-subtitle: |
-  **ÉV**aluation du r**É**seau de **RE**cyclage pour **S**outenir la **T**ransition vers une **BIO**économie <br/>
-  Projet de recherche CREIDD et ERPI
-author: "Fabio Cruz / Mauricio Camargo / Nadège Troussier"
-institute: "CREIDD, ERPI"
-date: '2020/11/18 (updated: `r Sys.Date()`)'
-output:
-  xaringan::moon_reader:
-    lib_dir: libs
-    css: ["default"]
-    seal: false 
-    nature:
-      ratio: "16:9"
-      highlightStyle: github
-      highlightLines: true
-      countIncrementalSlides: false
-      beforeInit: "assets/macros.js"
-      navigation:
-        scroll: false # disable slide transitions by scrolling
----
-
-```{r setup, include = FALSE, echo=FALSE, message=FALSE}
-options(htmltools.dir.version = FALSE)
-
-knitr::opts_chunk$set(include= TRUE, echo=FALSE, message=FALSE, fig.path="figures/")
-
-library(tidyverse)
-# Link for the Figures
-URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
-```
-
-```{r, include=TRUE, echo=FALSE}
-# CSS for the CSS
-htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
-htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
-```
-
-```{r share-again, echo=FALSE}
-xaringanExtra::use_share_again()
-```
-
----
-
-class: title-slide, left, middle
-background-image: url(`r paste0(URL, 'Everest-bio/logos/Logos.png')`)
-background-position: 0px 0px
-background-size: contain
-
-# `r rmarkdown::metadata$title`
-
-## `r rmarkdown::metadata$subtitle`
-
-### `r rmarkdown::metadata$author`
-
-### `r rmarkdown::metadata$date`
-
----
-
-class: middle, left
-
-# Agenda
-
-1. .content-box-yellow[Who am I?]
-2. ERPI Laboratory
-3. Green Fablab
-4. Everest Bio
-5. Proposition and Research axis
-
----
-
-class: top, left
-background-image: url(`r paste0(URL, 'Fabio/vosviewer/Fabio.jpg')`)
-background-position: right
-background-size: 70%
-
-# Who am I?
-
-.pull-left-1[
-```{r, echo=FALSE, out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Fabio/Fabio.png'))
-```
-]
-
----
-
-class: left middle
-
-## My research questions so far...
-
----
-
-class: left
-background-position: 0px 75px
-background-size: contain
-
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-01.jpg')`)
-
-## Are open source 3D printer good enough?
-
----
-
-## Are open source 3D printer good enough?
-
-Geometrical accuracy perspective
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Metodologies/Master-recherche/Master-00.png'))
-```
-
-.footnote[
-Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
-Towards a standard experimental protocol for open source additive manufacturing.
-Virtual Phys.
-Prototyp.
-9, 151–167.
-https://doi.org/10.1080/17452759.2014.919553
-]
-
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-02.jpg')`)
-background-position: 0px 75px
-background-size: contain
-
-## Can we print recycled objects?
-
-Recycling feasibility (Lab conditions)
-
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-Clean-03.jpg')`)
-background-position: 0px 75px
-background-size: contain
-
-## What about the supply chain printed recycled objects?
-
-.pull-down[Research of Pavlo Santander. Thesis Defended Dec. 2020]
-
----
-
-class: left
-background-image: url(`r paste0(URL, 'DRAM/DRAM-05.jpeg')`)
-background-position: 100px 125px
-background-size: 80%
-
-## How an innovation lab could could help as agent of change?
-
-.footnote[
-Roux-Marchand, T., Cruz, F., Dupont, L., Camargo, M., Osorio, F., 2020.
-Connecting the strategic intent of innovation labs and projects: the case of the Green Fablab, in: 2020 IEEE International Conference on Engineering, Technology and Innovation (ICE/ITMC).
-IEEE, pp.
-1–10.
-https://doi.org/10.1109/ICE/ITMC49519.2020.9198320
-
-Alexandre, A., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
-Mechanical Properties of Direct Waste Printing of Polylactic Acid with Universal Pellets Extruder: Comparison to Fused Filament Fabrication on Open-Source Desktop Three-Dimensional Printers.
-3D Print.
-Addit.
-Manuf.
-3dp.2019.0195.
-https://doi.org/10.1089/3dp.2019.0195
-]
-
----
-
-## What if distributed recycling could be aligned with Circular Economy priorities?
-
-```{r, out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'DRAM/DRAM-10.png'))
-```
-
-Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., Pearce, J.M., 2020.
-Plastic recycling in additive manufacturing: A systematic literature review and opportunities for the circular economy.
-J.
-Clean.
-Prod.
-264, 121602.
-https://doi.org/10.1016/j.jclepro.2020.121602
-
----
-
-class: middle
-
-# However...
-
-.left-column[
-```{r, out.width = '80%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Various/Signos/attention-00.png'))
-```
-]
-
-.right-column[
-
-- Technical and economic criteria alone do not (yet) allow for informed decisions.
-
-- Where is the environment in the techno-centrical approaches?
-
--  The root of the plastic waste problem needs to be addressed: the extraction and production.
--  Responsibility to act in the plastics economy
-
-- **Adaptive injustice**: *those who find ways to adapt to changing social realities, whether forced or voluntary, are not those who are responsible for the negative changes to which they are adapting.
-Specifically, it is an adaptive injustice to expect communities to figure out what to do with continual flow of plastics into the economy.*
-
-.content-box-red[**It’s time to retire this ‘privatizing profits, socializing costs’ model.**]
-
-]
-
-.footnote[
-Conlon, K., 2020. Adaptive injustice: Responsibility to act in the plastics economy. Resour. Conserv. Recycl. 153, 104563. https://doi.org/10.1016/j.resconrec.2019.104563
-]
-
----
-
 class: middle
@@
 ---
-
-class: middle
-
-# Agenda
-
-.pull-left[
-1. Who am I?
-2. ERPI Laboratory
-3. .content-box-yellow[Green Fablab]
-4. Everest Bio
-5. Proposition and Research axis
-]
-
-.pull-right[
-
-```{r, out.width = '100%', fig.align='center'}
-knitr::include_graphics('http://lf2l.fr/assets/images/3-projects/gf/Logo-GF.png')
-```
-*Circular economy and 3D printing: Towards a distributed recycling paradigm*
-]
-
----
-
-class: top, left
-background-image: url(`r paste0(URL, 'Plastics/Plastic-problem-03.svg')`)
-background-position: right
-background-size: 70%
-
-## Plastics waste since  olden times
-
-.left-column[
-.tiny[
-- US recycled less than 9% of its plastic waste.
-- EU, recycled about 30%. However, this number is what is collected, not from what is in circulation*. 
-- China’s ban on plastic trash
-- Plastic trash could top 13 billion tons by 2050
-- Economics of plastic recycling historically have been challenging
-- Little financial incentive to encourage consumers to recycle their own plastic waste
-
-```{r, out.width = '60%', fig.align='center'}
-knitr::include_graphics('https://images.unsplash.com/photo-1537084642907-629340c7e59c?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1567&q=80')
-```
-
-]]
-
-.footnote[
-Geyer, R., Jambeck, J.R., Law, K.L., 2017. Production, use, and fate of all plastics ever made. Sci. Adv. 3, e1700782. https://doi.org/10.1126/sciadv.1700782
-
-*Kranzinger, L., Pomberger, R., Schwabl, D., Flachberger, H., Bauer, M., Lehner, M., Hofer, W., 2018.
-Output-oriented analysis of the wet mechanical processing of polyolefin-rich waste for feedstock recycling.
-Waste Manag.
-Res.
-36, 445–453
-
-]
-
----
-
-# Challengue
-
-The development of sustainable industrial supply chains
-
-.left-column[
-.footnotesize[
-- Only technico-economic criteria alone do not (no longer) enables a informed decision making 
-- Need to assess value chains in a different way, including actual impacts on ecosystems
-- A more holistic vision is needed to assess the feasibility of these new sectors.
-]
- ]
-
-.right-column[ 
-.polaroid[ ![](figures/Recycling.png) ]
-]
-
----
-
-## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
-
-.pull-left[
-
--Local closed loop  <br>
--AM adds value  <br>
--Small quantities   <br>
--Reduction of landfilling  <br>
--Minimize the use of virgin materials  <br>
-
-```{r, include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='left'}
-knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-2.jpg'))
-```
-
-]
-.pull-right[
-
-```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Green-Fablab/Green-fablab-1.jpg'))
-```
-
-http://lf2l.fr/projects/green-fablab
-]
-
-.footnote[
-Cruz Sanchez, F.A., Boudaoud, H., Muller, L., Camargo, M., 2014.
-Towards a standard experimental protocol for open source additive manufacturing.
-Virtual Phys.
-Prototyp.
-9, 151–167.
-https://doi.org/10.1080/17452759.2014.919553
-]
-
----
-
-## Green Fablab: Towards a distributed recycling via additive manufacturing (DRAM)
-
-.left-column[ 
-Small scale: 2 km radius (neighbourhood scale) <br>
-Low processing capacity, <br>
-Technologies: cheap, easy to use <br>
-Active role of users <br>
-
-```{r, include=TRUE, echo=FALSE, out.width = '100%', fig.align='center'}
-knitr::include_graphics('figures/GF-users.jpg')
-```
-]
-
-.right-column[ 
-.center[![:scale 70%](figures/Green-fablab-circuit.png)]
-
-]
-
----
-
-class: middle
-
-# Agenda
-
-.pull-left[
-1. Who am I?
-2. ERPI Laboratory
-3. Green Fablab
-4. .content-box-yellow[Everest Bio]
-5. Proposition and Research axis
-]
-
-.pull-right[
-
-```{r, out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/logos/logo-2.jpg'))
-```
-]
-
----
-
-## People in Everest Bio
-
-.pull-left[
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Mauricio.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Hakim.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
-```
-]
-
-.pull-right[
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Nadege.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Alexis.jpg'))
-```
-
-```{r, out.width = '500px', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Everest-bio/Cristian.jpg'))
-```
-
-]
-
----
-
-## Research Question & Goal
-
-- To develop a generic methodology to assess the **ecosystem services** rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors.
-
-- Validation on the case of a short-circuit plastic recycling chain.
-
----
-
-## Methodology
-
-- In line with the thesis work previously carried out by the two teams, development of a coupled **Systems Dynamics and LCA approach**.
-
-- Application on a case study, the Green Fablab, by evaluating its environmental impact when setting up a short plastic recycling circuit.
-
-.center[ ![:scale 80%](figures/Goals.png)]
-
----
-
-## Purpose of Everest Bio
-
-Taking into account the environment and their ecosystem services (ES).
-
-.pull-left[
-
-```{r, out.width = '90%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Ecoservices/Eco-Services-00.jpg'))
-```
-]
-
-.pull-right[
-![](figures/Eco-Services-01.png)
-
-- How the future recycling chain could be including the environment?
-]
-
-.footnote[
-Bruel, A., Kronenberg, J., Troussier, N., & Guillaume, B.
-(2019).
-Linking industrial ecology and ecological economics: A theoretical and empirical foundation for the circular economy.
-Journal of Industrial Ecology, 23(1), 12-21.
-]
-
----
-
-class: middle
-
-### Ecosystem Services as a **boundary object** for sustainability
-
-.pull-left[
-
-In that sense, Our focus is towards becoming an explicit management tool:
-
-- Creating Systems, Normative and Transformative knowledge using as case study distributed recycling
-
-- better interdisciplinary knowledge integration, greater focus on normative knowledge, and improved recognition of the ecosystem services concept as a potential transformative tool.
-
-]
-
-.pull-right[
-```{r, out.width = '90%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Ecoservices/Abson2014-00.jpg'))
-```
-]
-
-.footnote[
-Abson, D.J., von Wehrden, H., Baumgärtner, S., Fischer, J., Hanspach, J., Härdtle, W., Heinrichs, H., Klein, A.M., Lang, D.J., Martens, P., Walmsley, D., 2014.
-Ecosystem services as a boundary object for sustainability.
-Ecol.
-Econ.
-https://doi.org/10.1016/j.ecolecon.2014.04.012
-]
-
----
-
-class: top, left
-background-image: url(`r paste0(URL, 'Ecoservices/Vanderwilde2021-01.jpg')`)
-background-position: 290px 0px
-background-size: 75%
-
-### We look to connect <br> Ecosystem services and LCA
-
-Hoping to contributing in <br> sustainability uncertainties.
-
-.footnote[
-Vanderwilde, C.P., Newell, J.P., 2021. Ecosystem services and life cycle assessment: A bibliometric review. https://doi.org/10.1016/j.resconrec.2021.105461 <br>
-Diwekar, U., Amekudzi-Kennedy, A., Bakshi, B., Baumgartner,et al, 2021.
-A perspective on the role of uncertainty in sustainability science and engineering.
-Resour.
-Conserv.
-Recycl.
-164, 105140.
-https://doi.org/10.1016/j.resconrec.2020.105140
-]
-
----
-
-### Systems Dynamics of DRAM
-
-Technical system --> Global *system* embedded in a *territory*!
-
-```{r, out.width = '90%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'DRAM/DRAM-Territory-00.jpg'))
-```
-
----
-
-## Towards systemic solutions
-
-Global system
-
-.pull-left[
-```{r, out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'DRAM/DRAM-08.png'))
-```
-
-]
-
-.pull-right[
-- Establish and evaluate scenarios in a systemic and dynamic way
-- Evaluate the influences of the main operating variables on the system taking ecosystem services boundaries
-- Taking into account the priorities of the multiple stakeholders
-- Facilitate your decision making public-private actors
-]
-
-.footnote[
-Santander, P., Cruz Sanchez, F.A., Boudaoud, H., Camargo, M., 2020.
-Closed loop supply chain network for local and distributed plastic recycling for 3D printing: a MILP-based optimization approach.
-Resour.
-Conserv.
-Recycl.
-154, 104531.
-https://doi.org/10.1016/j.resconrec.2019.104531
-]
-
----
-
-# Delivrables & Valorisations
-
-1. An article in an indexed international journal
-2. Participation in an international conference 
-3. An operational model with a model of a software tool for assessing local impacts
-4. Final report on the evaluation of Green Fablab and possible generalisations for short industrial circuits.
-
-- Method and [**prototype of a tool**](https://fabbiocrux.github.io/everest-bio-tool/) for the evaluation of local impacts of circular production systems
-
----
-
----
-
-class: middle, left
-background-image: url(`r paste0(URL, 'Climatelabs/Climatelabs.png')`)
-background-position: center
-background-size: contain
-
----
-class: middle
-
-# EU projects
-
-.pull-left[
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Smagrinet/Smagrinet-00.jpg'))
-```
-https://www.smagrinet.eu/
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '60%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Digiterri/Digiterri'))
-```
-
-https://digiterri.eu/
-
-] 
-.pull-right[
-
-```{r , include=TRUE, echo=FALSE, fig.cap=" ", out.width = '100%', fig.align='center'}
-knitr::include_graphics(paste0(URL, 'Inedit/Inedit-00.png'))
-```
-
-https://www.inedit-project.eu/
-]
-
----
-
-class: middle, center
-
-Thanks !
-
-![:scale 70%](figures/DRAM-bd.png)

### 2022-02-14 index.Rmd
hakim
presentation

@@
 Il est donc temps de rendre nos filières industrielles plus résilientes et adaptées aux nouvelles conditions imposées par la planète.
-Pour soutenir une transition industrielle, dont celle vers une bioéconomie répondant au concept d’économie circulaire, ce projet cherche à développer une méthodologie permettant d’évaluer les services écosystémiques, et donc les externalités des organisations industrielles émergentes.
-Par la mise en commun de compétences du ICD/CREIDD^[Institut Charles Delaunay/Centre de recherches et d’études interdisciplinaires sur le développement durable de l'UTT (Université technologique de Troyes)]   et de l’ERPI^[  Equipe de Recherche sur les Processus Innovatifs de l’UL (Université de Lorraine)], cette méthodologie, basée sur un couplage analyse du cycle de vie et modélisation par dynamique de systèmes, cherche à faciliter l’évaluation d’un projet industriel dès sa phase amont en considérant ses potentiels impacts positifs et/ou négatifs sur son territoire.
+Pour soutenir une transition industrielle, dont celle vers une bioéconomie répondant au concept d’économie circulaire, *ce projet cherche à développer une méthodologie permettant d’évaluer les services écosystémiques, et donc les externalités des organisations industrielles émergentes.* Par la mise en commun de compétences du ICD/CREIDD^[Institut Charles Delaunay/Centre de recherches et d’études interdisciplinaires sur le développement durable de l'UTT (Université technologique de Troyes)]   et de l’ERPI^[  Equipe de Recherche sur les Processus Innovatifs de l’UL (Université de Lorraine)], cette méthodologie, basée sur un couplage analyse du cycle de vie et modélisation par dynamique de systèmes, cherche à faciliter l’évaluation d’un projet industriel dès sa phase amont en considérant ses potentiels impacts positifs et/ou négatifs sur son territoire.
 L’approche proposée sera testée sur le cas du recyclage, l’un des piliers de l’économie circulaire, et en particulier sur la mise en place d’un démonstrateur de type « smart-grid du recyclage » du plastique en circuit court.
@@
 
-```{r embed-xaringan, echo=FALSE}
+```{r embed-xaringan, echo=FALSE, include=FALSE, eval=FALSE}
 
@@
 De plus, les changements environnementaux sont liés à des effets de deux natures: leviers indirects et pressions directes. 
+   <!-- Indirect drivers -->
 Par leviers indirects, le Millenium Ecosystem Assessment (MEA) [@MEA2005] adresse les changements démographiques, économiques, sociopolitiques, scientifiques et technologiques. 
+   <!-- Direct drivers -->
 Quant aux pressions directes, elles incluent la conversion des sols, la surexploitation des ressources naturelles, l’apport excessif de nutriments, les maladies, les invasions d’espèces et le changement climatique.
+   <!-- Pressures on the ecosystem -->
 Ces pressions affectent les écosystèmes de différentes manières selon les contextes et agissent à travers différentes échelles organisationnelles, temporelles et spatiales. 
+   <!-- Major issues on the Ecosystems -->
 Les systèmes industriels sont fortement impliqués et responsables des pressions qu’ils exercent sur la biodiversité et les services écosystémiques. 
-Le MEA a identifié six défis majeurs concernant directement les impacts des activités industrielles :la rareté de l’eau douce, le changement climatique, les changements d’habitat, les espèces invasives, la surexploitation des océans et la surcharge de nutriments.
+Le MEA a identifié six défis majeurs concernant directement les impacts des activités industrielles :
+1) la rareté de l’eau douce, 
+2) le changement climatique, 
+3) les changements d’habitat, 
+4) les espèces invasives, 
+5) la surexploitation des océans et 
+6) la surcharge de nutriments. 
 Ces derniers peuvent conduire à des dépendances qui varient en fonction des secteurs d’activités et au sein même d’un même secteur, selon la technologie employée et du contexte de l’activité de production ou de consommation <span style="color:blue">*</span>.
@@
 
+<!-- Ecosystem Services -->
+   <!-- New opportunities to consider in the design of industrial systems -->
 Par ailleurs, la prise en compte des services écosystémiques peut présenter de nouvelles opportunités pour les entreprises, comme favoriser l’émergence de nouvelles technologies et de nouveaux produits permettant de réduire la dégradation, de restaurer les écosystèmes ou d’augmenter l’efficacité dans l’utilisation des services écosystémiques.
+   <!-- Eco-labelisation  -->
 Cela peut aussi permettre l’obtention de nouvelles parts de marché grâce au lancement d’un nouveau produit ou service à faible impact sur les écosystèmes, donc disposant d’une éco-labellisation. 
+   <!-- Strategy of the Goverment: Biodiversity Conservation -->
 Au niveau de la réglementation, on peut noter l’engagement du gouvernement, concrétisé notamment par la Stratégie Nationale pour la Biodiversité (SNB), pour développer des politiques favorables à la conservation des écosystèmes ou des incitations visant à protéger ou restaurer des écosystèmes qui fournissent des services.
+   <!-- Integration des Impacts/Dependance systems Industriels on the Ecosystems -->
 L’intégration de cette relation impacts/dépendances au niveau des systèmes d’information permettrait d’avoir une autre vision des entreprises au regard de leurs activités industrielles. 
 Cependant, elle est complexe à mettre en œuvre et spécifique à chaque secteur.
+   <!-- Problem: Integration des ES Impacts/Dependance systems Industriels on the Ecosystems  -->
 Aujourd’hui, la valeur des services écosystémiques est peu prise en compte voire pas reconnue par et dans notre système économique, que ce soit aux yeux des décideurs privés et publics ou des consommateurs.
+   <!-- Problem 2: Invisibilité de Naatural capital loss -->
 La perte de valeur causée par l’ensemble des pressions qui s’exercent sur les services écosystémiques est invisible, ce qui ne permet pas d’influencer les décideurs et de peser dans les arbitrages au niveau des processus de décisions.
@@
 
+<!-- Green Fablab Demostrator -->
 Un premier démonstrateur a été conçu pour traiter le problème du recyclage de matières plastiques issues des déchets domestiques, adoptant une approche de type recyclage distribué en circuit court et en petites quantités ou « smart-grid du recyclage » [@Santander2020].
@@
 
+<!-- Characterization of the process -->
 Les travaux iniciaux, ont démontré dans un premier temps, la faisabilité technique de cette approche qui intègre plusieurs technologies (imprimantes 3D, extrudeuses et dispositifs de mesure notamment) pour fabriquer les fils supports à l’impression 3D [@CruzSanchez2017], conduisant plus récemment à un recyclage par extrusion directe [@Arthur2020].
 Pour assurer la faisabilité économique, le système de fabrication se doit d’être peu cher, facile d’utilisation et adapté à la production de petites quantités. 
+   <!-- Open source -->
 Pour cette raison, dès le début de leur réflexion, les chercheurs ont fait le choix d’utiliser des technologies open source [@CruzSanchez2014].
@@
 ICD/CREIDD apportera sa compétence sur l’évaluation des impacts écologiques et sociaux via la monétarisation des services écosystémiques.
+
 Les deux partenaires collaboreront autour du même cas d’étude qui permettra de déployer de façon conjointe les méthodologies déjà mises au point dans le cadre de travaux de thèse dans chacun des laboratoires pour proposer un modèle d’analyse des impacts locaux (écologiques et sociaux) des transformations des systèmes de production.
@@
 3.	Un modèle opérationnel avec une maquette d’outil logiciel d’évaluation des impacts locaux
-4.	Rapport final sur l’évaluation du GreenFablab et les généralisations possibles pour les circuits industriels courts.
+4.	Rapport final sur l’évaluation du Green Fablab et les généralisations possibles pour les circuits industriels courts.
 

### 2022-02-14 varios/00-References.Rmd
presentation

--- 2020-11-20 00-References.Rmd
@@
     toc_depth: 2
-repository_url: https://github.com/LF2L/everest-bio
+# repository_url: https://github.com/LF2L/everest-bio
 #bibliography: Biblio.bib

### 2022-02-14 docs/00-ES/xar-EB-ES/xaringan-themer.R

@@ -1,75 +1,0 @@
-# Load data ----------------------------------------------------------------
-
-
-# set options ------------------------------------------------------------------
-style_duo_accent(
-   primary_color = "#1381B0",
-   secondary_color = "#FF961C",
-   inverse_header_color = "#FFFFFF", 
-   base_font_size = "18px",
-   text_font_family = 'Trebuchet-MS',
-   header_font_family = 'Trebuchet-MS',
-   title_slide_background_color = "#FFFFFF",
-   
-   colors = c(
-      red = "#f34213",
-      purple = "#3e2f5b",
-      orange = "#ff8811",
-      green = "#d9edc2",
-      white = "#FFFFFF",
-      grey = "#F5F5F5",
-      yellow = "#FAFE83",
-      blue = "#1381B0",
-      grey_Inedit = "#969696"
-   ),
-   extra_css = list(
-      ".remark-slide-content h1" = list(
-         "margin-bottom" = 0, 
-         "margin-top" = 0),
-      ".remark-slide-content > h1:first-of-type" = list(
-         "margin-top" = "5px",
-         "margin-bottom" = "10px"
-      ),
-      ".title-slide h2" = list("font-family" = "Trebuchet-MS"),
-      
-      ".remark-slide-content > h2:first-of-type" = list(
-         "margin-top" = "5px",
-         "margin-bottom" = "10px"
-      ),
-      ".remark-slide-content > h3:first-of-type" = list(
-         "margin-top" = "5px",
-         "margin-bottom" = "10px"
-      ),
-      ".remark-slide-content" = list (
-         "padding-top" =  "25px",
-         "padding-left" =  "50px",
-         "padding-right" =  "50px",
-         "padding-bottom" =  "25px"
-      ),
-      
-      ".small" = list("font-size" = "90%"),
-      
-      
-      ".Large , .Large .remark-code, .Large .remark-inline-code" = list("font-size"= "144%"), 
-      ".large , .large .remark-code, .large .remark-inline-code" = list("font-size"= "120%"), 
-      ".small , .small .remark-code, .small .remark-inline-code" = list("font-size"= "90%"), 
-      ".footnotesize, 
-    .footnotesize .remark-code, .footnotesize .remark-inline-code" = list( "font-size"= "80%"),
-      
-      ".scriptsize , .scriptsize .remark-code, .scriptsize .remark-inline-code" = list("font-size"= "70%"),
[…]

### 2022-02-14 docs/xar-EB-general/xaringan-themer.R

@@ -1,0 +1,151 @@
+# load packages ----------------------------------------------------------------
+library(tidyverse)
+library(xaringanExtra)
+library(xaringanthemer)
+library(fontawesome)
+library(readxl)
+library(here)
+library(flextable)
+
+
+
+
+# set options ------------------------------------------------------------------
+#style_duo_accent(
+style_mono_accent(   
+   # Colors
+   base_color = "#1381B0",
+   black_color = "#272822",
+   white_color = "#FFFFFF",
+   
+   # Fonts
+   base_font_size = "20px",
+   
+   # Text
+   text_font_size = "1rem",
+   text_font_google  = google_font("Sen"),
+   #text_font_family = 'Trebuchet-MS',
+   #text_font_url = 'https://raw.githubusercontent.com/LF2L/INEDIT-WP6/main/xar-WP6/assets/WP6.css',
+   text_font_weight = 400,
+   #text_font_family_fallback = "serif",
+   
+   # H1
+   #header_font_family = 'Titles',
+   header_font_google  = google_font("Noto Serif JP"),
+   #header_font_family_fallback = "Source Code Pro",
+   header_h1_font_size = "2.50rem",
+   header_font_weight = "700",
+   
+   #H2
+   header_h2_font_size = "2rem",
+   
+   #H3
+   header_h3_font_size = "1.75rem",
+   
+   
+   
+   # Title slide
+   title_slide_background_color = '#FFFFFF',
+   title_slide_background_image = "https://raw.githubusercontent.com/fabbiocrux/Figures/main/Inedit/INEDIT-logo-00.jpg",
+   title_slide_background_size = '80%',
+   title_slide_background_position = '50% 15%',
+   title_slide_text_color = "#4D4D4E",
+   
+   
+   # Slide content
+   #header_background_auto = 'FALSE',
+   #header_background_color = '#FFFFFF',
+   #header_background_text_color = "#1381B0",
+   #header_background_padding = '0px 0px',
+   #header_background_content_padding_top = "5px",
+   padding = '25px 25px 25px 25px',
+   
+   # Footnote
+   footnote_position_bottom = '0px',
+   footnote_font_size = "0.9rem",
+   
+   colors = c(
+      red = "#f34213",
+      purple = "#3e2f5b",
+      orange = "#ff8811",
+      green = "#d9edc2",
+      white = "#FFFFFF",
+      grey = "#F5F5F5",
+      yellow = "#FAFE83",
+      blue = "#1381B0",
+      grey_Inedit = "#969696"
+   ),
[…]
